### 2013-07-11 article.tex
Basically the iccp2013 in the optics express template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{article}

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}

%\usepackage{ae} %%for Computer Modern fonts

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}

\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% title page information %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Sky Tomography for 3D Aerosol Distribution Recovery}

\author{Amit~Aides and Yoav~Y.~Schechner and Vadim~Holodovsky}

\address{Electrical Engineering Dept., Technion - Israel Inst. Tech., \\ Haifa 32000, Israel}

\email{amitibo@tx.technion.ac.il} %% email address is required

% \homepage{http:...} %% author's URL, if desired

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%% abstract and OCIS codes %%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]

\begin{abstract}
  Aerosols effect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer. We propose a principle to recover the atmosphere
  as it really is: a three dimensional (3D), volumetric, transparent
  huge object. Tomography is the key to recovery. The process involves
  acquiring the sky lightfield by multi-view wide-angle photography on
  a very large scale. The tomography model is distinct, as the light
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.  We formulate an image formation model based
  on 3D radiative transfer. Model inversion is done using optimization
  methods, exploiting a closed-form gradient which we derive for the
  model-fit cost function. The problem is complex but tractable and
  parallelizable, eventually estimating the 3D aerosol distribution.
\end{abstract}

\ocis{(000.0000) General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{article}{}
\bibliographystyle{osajnl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:front}).
\begin{figure}[t!]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/front_img.pdf}}
  \caption{\small The sky is photographed from multiple viewpoints
    using wide angle (hemispherical) cameras, in a very wide area. The
    three dimensional distribution of aerosols in the atmosphere
    affects the images. This distribution is then recovered by a
    dedicated tomography formulation.}
  \label{fig:front}
\end{figure}

Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

We do not deal with clouds here. Clouds scatter sunlight very strongly
and are easily observed. Hence they are directly recovered using
common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
On the other hand, aerosols have much more subtle visual effects and
are thus more difficult to recover. We focus on them.  In remote
sensing~\cite{diner}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}. In this
discipline, the atmosphere is often assumed to be plane-parallel, for
simplicity, using only 1D vertical radiative transfer. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
recovery. Computational photography offers new ways to peer into
media. In addition to active descattering~\cite{fuchs,kim,Ng1948} and
recovery of refractive transparent objects~\cite{ihrke}, overcoming
the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects
was studied in horizontal, fixed
views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
this paper, however, the medium itself, at all relevant altitudes is
the object of interest.

3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths. To keep safe, today's coarse sensing limits flight
capacity. A prominent example is the 2010 eruption of Iceland's
Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
much of Europe's airspace, grounding $\approx 100,000$
flights. Knowing the 3D distribution of aerosol density may indicate
safe 3D corridors to safely pass through, enhancing airspace
use. Viewing beyond the medium, atmospheric correction is needed, for
example, in satellite tracking of chlorophyll
distributions~\cite{johnsen}. Additional bodies in the solar system
have atmospheres. These objects can be viewed from multiple directions
by probes.  The approach described here may be helpful there.

We model passive optical tomographic imaging of 3D atmospheric
scatterer distributions in cloudless conditions. Then, we solve this
tomography problem, to recover the distribution. Recovery is
formulated as an optimization that minimizes a cost function. We
derive the gradient of this cost function, to enable efficient
optimization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Theoretical Background}
\label{sec:back}
\vspace{-0.2cm}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
$1/({\rm m}\cdot{{\rm strad}})$) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein function,
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Image Acquisition Principle}
\label{sec:setup} \vspace{-0.2cm}

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
\begin{figure*}[t!]
  \begin{center}
    \vspace{-0.4cm}
    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
  \end{center}\vspace{-1.5cm}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}

Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,Martonchikc,vanMol}. However, current
multiview spaceborne systems are very coarse. For example, aerosol
retrieval in the most complex instrument, MISR, requires spatial
blocks that are about $17\times 17$km wide, each observed from just 9
views along-track. This practically leads to vertical radiative
transfer analysis, degenerating atmospheric analysis to
1D. Experimental airborne instruments under
development~\cite{baxter,dinerDavis10} may provide better, if still
coarse resolution once they are operational.

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upwards and capturing the sky lightfield.
Moreover, satellites image close to the orbit track (a 1D array of
viewpoints). In contrast, land-based cameras can form a 2D set of
viewpoints~\cite{DBLP:journals/pieee/SnavelySGSS10} as easy or hard as
a 1D grid~\cite{Joshi06naturalvideo}. However, before designing and
setting up such a very large scale system requires assessment of many
details that had not been explored. These include camera
specifications needed to recover typical distributions. Hence, a major
theoretic and numerical research phase is ahead.

This paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Forward Model}
\label{sec:skymodel} \vspace{-0.2cm}

This section describes models for image formation. In the consecutive
section, we describe how the image formation is inverted to recover
the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
Ground-based wide-angle sky-cameras capture the sky lightfield from
below. Per viewpoint, the view azimuth and elevation angles (relative
to the zenith and north) are encapsulated in the vector
${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
camera's location ${\bf x}$ is fixed, while any pixel in a frame
represents an angle ${\bf{\Theta}}$.  The measured radiance in all
locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
lightfield.
% Alternatively, several ground-based cameras can be mounted on moving
% vehicles, assuming that the aerosol distribution does not change
% much during the time-lapse of the camera trajectory.

Sunlight is scattered in the medium, creating {\em
  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
generally different, depending on the distribution of aerosols both
along a LOS, and along the SRs that hit the LOS.  As
Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
  x},{\bf{\Theta}}$) cut through different sets atmospheric
voxels. Thus, for each view, the radiance scattered from a voxel is
attenuated differently, depending on the distribution of aerosols
along the LOS~\cite{hansen}.

A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints. The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics. We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera. This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply. Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\

\vspace{-0.35cm}
\noindent
1. Attenuation of a SR propagating from the top of the atmosphere
(TOA) to voxel $k$. \\

\vspace{-0.35cm}
\noindent
2. Light scattering at voxel $k$, towards a camera.\\

\vspace{-0.35cm}
\noindent
3. Light attenuation on the LOS from voxel $k$ to the camera.

\noindent
Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
involves the scattering coefficient at voxel $k$, described in
Sec.~\ref{sec:scattering}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optical Depth}
\label{sec:optical-depth}

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
In addition, the infinitesimal volume contain also air
molecules. Hence, the overall extinction and scattering coefficients
in this small volume are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. As approximation, assume that within any
voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
constants, e.g., corresponding to the value at each voxel
center. These parameters may change between voxels.

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
$q$. The geometric length of this intersection line segment is $\Delta
z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
  [0,1]$} expresses how much of the vertical thickness of $q$ is
crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
optical depth between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta(q)\Delta z  f_{\rm SR}(q)
  \;\;.
  \label{eq:lSRn}
\end{equation}
Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
\begin{equation}
  \tau_{\rm SR}(k)=
  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lSRaa}
\end{equation}
where
\begin{equation}
  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta^{\rm air}(q)  f_{\rm SR}(q)
  \label{eq:lSRair}
\end{equation}
and
\begin{equation}
  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
  \label{eq:lSRaeros}
\end{equation}

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
      & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
depths due to aerosols (See Fig.~\ref{fig:optidepth}):
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$. The overall
    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
    optical depth affecting $k$. It is formalized in matrix-vector
    operations. }
  \label{fig:optidepth}
\end{figure}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $\Delta z f_{\rm
  LOS_c}(q)/\cos\Phi^{\rm LOS}_c$: the factor $f_{\rm LOS_c}(q)\in
[0,1]$ expresses how much of the vertical thickness of $q$ is crossed
by the LOS.  Analogously to
Eqs.~(\ref{eq:lSRaa},\ref{eq:lSRair},\ref{eq:lSRaeros}), The optical
depth %path length
along a LOS to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm LOS}_c}
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  f_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)=
  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~%\nonumber
  ~~~~~
  \\
  % ~~~~
  \frac{\Delta z}{\cos\Phi^{\rm LOS}_c} \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm LOS_c}(q).
  \nonumber
\end{align}
Eq.~(\ref{eq:lLOSaeros}) leads to a vector of LOS optical depths due
to aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta z f_{\rm LOS_c}(q)}{\cos\Phi^{\rm LOS}_c}
      & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of LOS optical
depths due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bf D}_c=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using Eq.~(\ref{eq:rayleighbeta}) for $\beta^{\rm air}$ in all voxels,
the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle.

Using
Eqs.~(\ref{eq:lSRaa},\ref{eq:tauSRvec1},\ref{eq:lLOSair},\ref{eq:tauLOSvec1},\ref{eq:Dtotal},\ref{eq:tauairtotal}),
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
(See Fig.~\ref{fig:optidepth}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scattering}
\label{sec:scattering}

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
which is pre-calculated.
% Eq.~(\ref{eq:mu}) yields its cosine, $\mu_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using
Eqs.~(\ref{eq:alphabasic},\ref{eq:rayleighP},\ref{eq:betaer},\ref{eq:betair}),
the angular scattering coefficients across the domain are expressed in
vector form by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)   \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bf g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in Eq.~(\ref{eq:aerosol_scatter}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Image Capture}
\label{sec:captured-image}

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(Eqs.~\ref{eq:beer-lambert},\ref{eq:betair},\ref{eq:tautotal}), the
radiant power contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  e^{-[\tau_c(k)]}
  \;\;.
  \label{eq:ick}
\end{equation}
A column-stack vector of all voxel contributions is
\begin{equation}
  {\bf p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot e^{-\vect{\tau}_c}
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest.  Thus light power captured at a
pixel is weighted sum of the power $p_c(k)$ from all voxels: most
voxels have null weight, since they fall outside the pixels's conic
field of view, while the rest of the voxels are aggregated.

This linear sum is formulated by a matrix operation over ${\bf
  p}_c$. The measured image is column-stacked to a vector $N_{\rm
  pix}$ long. It is given by
\begin{equation}
  {\bf i}_c= {\vect{\Pi}}_c{\bf p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}
The $N_{\rm pix}\times N_{\rm voxels}$ sparse matrix ${\vect{\Pi}}_c$
expresses {\em projection} of light into camera $c$. For pixel
$\Theta$ and voxel $k$, there is an {\em intersection} volume ${\bf
  V}_c(\Theta,k)$ between the cone volume of the pixel's field of
view, and the voxel, as illustrated in Fig.~\ref{fig:projection}.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/sensor.pdf_tex}}
  \caption{\small An image pixel captures light emanating in a cone in
    space. Voxels that fully or partially fall in this cone are sensed
    by the pixel. Factoring out scattering and attenuation (which are
    dealt elsewhere in our analysis), the relative contribution of
    each voxel depends on its distance and intersection with the
    cone. This is formalized a matrix-vector operation.}
  \label{fig:projection}
\end{figure}
The corresponding element in the matrix ${\vect{\Pi}}_c$ is
\begin{equation}
  \Pi_c(\Theta,k)=
  % \frac{a}{|{\bf V}(k)|}
  a
  \iiint_{{\bf V}_c(\Theta,k)}
  \frac{1}{[R({\bf v})]^2} d{\bf v}
  \;\;,
  \label{eq:Pc}
\end{equation}
where $a$ is the effective area of the camera lens.
% and $|{\bf V}(k)|$ is the volume of voxel $k$.
The distance $R({\bf v})$ is measured between the camera and an
infinitesimal volume element at ${\bf v}\in {\bf V}_c(\Theta,k)$.

Combining Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the
captured image is thus
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bf D}_c
      (\vect{\sigma} \odot {\bf n})]} \right\}
  \label{eq:bigIc}
\end{align}
Most often, there is only a single type of aerosol over a
scene. Hence, the three-element vector $[{\sigma}^{\rm
  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
the density distribution ${\bf n}$ is variable. Then,
Eq.~(\ref{eq:bigIc}) degenerates to
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inverse Problem}
\label{sec:inverse-problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unknowns and Prior Knowledge}
\label{sec:prior}

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bf n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bf g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

Prior knowledge reduces the unknowns. Sec.~\ref{sec:captured-image}
mentions a prior: in many cases a single aerosol type dominates a
scene. Then, the three-element vector $[\varpi^{\rm
  aerosol},{\sigma}^{\rm aerosol},g]$ is rather spatially uniform. In
such cases, the set of unknowns reduces to $ {\cal V}= \left\{ {\bf
    n}, \left\{ {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
      aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda} \right\} $ and
\mbox{$|{\cal V}|=N_{\rm voxels}+3N_{\rm spectral}$}.

Furthermore, the elements in the aerosol characteristics set $\left\{
  {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
    aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda}$ is not
arbitrary, since all these characteristics have physical origins. This
set is constrained to comply with what nature allows (aerosol
classes).  This significantly constrains the unknown
characteristics. State-of-the-art aerosol retrieval, as used by NASA's
MISR products indeed employ an aerosol-class prior. Types of aerosol
mixtures are discretized to $N_{\rm models}=74$
classes~\cite{Martonchikc}, called {\em models}. Each class $m$
represents aerosols having a distinct characteristics set.  State of
the art retrieval is 1D (only vertical radiative transfer per large
areas). Nevertheless, we use this prior in our 3D problem. Then, the
set of unknowns reduces to $ {\cal V}= \left\{ {\bf n},m \right\}$ and
\mbox{$|{\cal V}|=N_{\rm voxels}+N_{\rm models}$}.

The atmosphere is photographed from $N_{\rm views}$ viewpoints. Each
photograph provides $N_{\rm pix}$ measurements (pixels), {\em
  including} their possible division to color channels. Hence, the
data at our disposal comprises $N_{\rm views}N_{\rm pix}$
measurements.  For the recovery task to be well-posed, it is necessary
that $N_{\rm views}N_{\rm pix}>|{\cal V}|$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Objective Function}
\label{sec:objective-function}

The inverse problem (tomography) seeks recovery of the 3D aerosol
distribution in the atmosphere. From
Eqs.~(\ref{eq:alpha_matrix},\ref{eq:bigIc},\ref{eq:bigIA},\ref{eq:calV}),
the images $\{ {\bf i}_c\}_{c=1}^{N_{\rm views}}$ depend on the
variables set ${\cal V}$, particularly on the unknown field ${\bf
  n}$. The recovery task is phrased as optimization of an objective
function, that fits the image-formation
model~(\ref{eq:bigIc},\ref{eq:bigIA}) to measured photographs $\{ {\bf
  i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:mingenobjective}
  \hat{\cal V} = \argmin_{{\cal V}\in {\cal C}} F({\cal V})
\end{equation}
where
\begin{equation}
  \label{eq:genobjective}
  F({\cal V}) = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\cal V})\| + {\rm Regularization}({\cal V})
  \;.
\end{equation}
Here ${\cal C}$ is a constraints set, which encapsulates part of the
prior knowledge, as well as nonnegativity bounds, while $\|~\|$ is
some error-distance measure.  Here ${\rm Regularization}({\cal V})$
describes spatial regularization terms of the variables, such as
smoothness, or a blobby or layered structure.

Spatial regularization can help overcome lack of data, if $N_{\rm
  views}$ is too small, and it is definitely helpful. In this work,
however, we formulate and demonstrate the basic principle of our
tomography task, hence we proceed without regularization. Relying on
prior knowledge described in Sec.~\ref{sec:prior}, the problem
complexity is by far dominated by the $N_{\rm voxels}$-large array
${\bf n}$, which is continuously valued. Hence, we focus here on
retrieving ${\bf n}$ through continuous optimization. Relying on the
least-squares measure, we seek:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bf n} =
  \argmin_{{\bf n}} F({\bf n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bf n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
\end{equation}
This is solved using standard optimization tools. Fast optimization
that leads to to local minima ($F$ is not convex) exploits the
gradient of $F$.

Since our model uses close-form expressions, $F$ is
differentiable. The gradient of $F$ with respect to ${\bf n}$ is
\begin{align}
  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
    measured}_c - {\bf i}_c({\bf n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.

Denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$ into a
diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$.  A close-form expression of our Jacobian is
\begin{align}
  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bf n}
    ]} \nonumber \\
  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of
Eqs.~(\ref{eq:gradient2},\ref{eq:gradient3}), we refer the reader to
the supplementary material.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations}
\label{sec:simul}

To test the model, we made simulations based on atmospheric models in the literature. Here are the details.\\

\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$. Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of
$L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm B}=255:236:224$.\\

\noindent{\bf Dimensions}: The domain of sky we simulate and recover has area of $50\times 50$km, and it extends from the ground up to altitude of 10km. This volume is divided to a $50\times50\times100$ grid, where each voxel has area of $1\times1$km and vertical thickness of 100 meters. The dimension of the problem is thus $250,000$ variables.\\

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm B}]=[16.5,16.2,15.9][1/\mu m^2]$.  Its
single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all channels.

We simulated various spatial distributions. All were set as a product
of two functions. The first function is an exponential
decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {\sigma^{\rm aerosol}_{\rm G} \mathrm{MFP^{sea
        level}}} \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2\ km$. This expresses a general trend of
reduced atmospheric density with height. Here the mean free path (MFP)
of the aerosols layer at sea level was set to $\mathrm{MFP^{sea
    level}}=1/5~{\rm[1/km]}$.
% is a typical characteristic thickness of the aerosol
% layer~\cite{Levi1980}.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bf n}^{\rm true}={\bf w}_1\odot {\bf w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene
(Fig.~\ref{fig:simulation1}) using two ellipsoid blobs: \begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small Simulated 3D aerosol distribution composed of {\em
      Haze Blobs}. Its reconstruction is shown in
    Fig.~\ref{fig:front}. Color represents aerosol density. The
    density units are $10^{15}~{\rm particles}/{\rm cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude $3.3km$, and has horizontal width of $32km$ and vertical thickness of $2.8km$. The second ellipsoid is centered at altitude $6.6km$, and has lateral width of $24km$ and vertical thickness of $2.1km$. Note that the horizontal widths are much larger than the vertical ones. This is consistent with scales of atmospheric aerosol distributions.\\

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used 95
viewpoints on a grid, each view $\approx 4.4$km from its neighbors.
The resolution of each camera is low: $128\times 128$ pixels,
expressing the fact that cloudless (yet hazy) sky images are rather
smooth, hence there is no need for high image resolution. Each pixel
has full-well depth of 40000 electrons, which corresponds to the
brightest pixel value. Each measurement has photon noise, which is
Poissonian distributed, according to each image-pixel value $i_c$ and
the full-well depth. For example, Fig.~\ref{fig:simulation-results1}
shows two modeled photographs
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/ref_images.pdf}}
  \caption{\small Rendered photographs (contrast enhanced)
    corresponding to different viewpoints, of sky that includes {\em
      Haze Blobs}. A yellow dot marks the Sun location. Dashed white
    circles mark elevation angles.}
  \label{fig:simulation-results1}
\end{figure}
of the  {\em Haze Blobs} scene that corresponds to Fig.~\ref{fig:simulation1}.\\

\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
with 8GB
DDR3 memory per core. Out of it, we used 8 nodes, corresponding to 96 cores. Each core was dedicated to rendering a modeled image (in each interaction) as if captured by one of the 95 cameras. Each iteration (varying the model according to the gradient-based algorithm and varying all the rendered images) took $\approx 7$sec.\\

\noindent{\bf Optimization}: We used the L-BFGS-B
algorithm~\cite{BFGS}. The algorithm was initialized by ${\bf
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total. For
example, Fig.~\ref{fig:objective} shows
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/objective.pdf}}
  % \includegraphics[width=\columnwidth]{images/objective.pdf}
  \caption{\small The decay of $\log F({\bf n})$ with the iteration
    index.}
  \label{fig:objective}
\end{figure}
the progression of the objective as a function of the iteration
number, when recovering the the {\em Haze Blobs} scene.

% 26, 48, 1320, 590
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Results}
\label{sec:optimization-results}

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in Fig.~\ref{fig:simulation1}, while the
recovered 3D distribution is visualized in Fig.~\ref{fig:front}. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bf n}  - {\bf n}^{\rm true} \|_1}
  {\| {\bf n}^{\rm true} \|_1} ,
  \hspace{-0.05cm}
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

We created a {\em Haze Front} scene. Fig.~\ref{fig:simulation2}a shows
an iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation2}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of a
    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation2}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude $5km$, has
vertical thickness of $4km$ and length of $32km$ (only part of which
enters the volume). The haze front stretches across the width of the
volume.  Fig.~\ref{fig:simulation2}b visualizes the recovered 3D
distribution of this scene. For the {\em Haze Front},
$\epsilon=0.198$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}

We describe a new way to sense the 3D atmosphere. We show feasibility
of departing from common 1D aerosol distribution models, in favor of
detailed 3D analysis.  The paper describes both a novel data
acquisition system concept for this recovery task, and a dedicated
algorithm for reconstructing aerosol distributions.

Even without regularization, the reconstruction algorithm handles
arbitrary density distributions. Using more prior knowledge,
e.g. spatial smoothness will improve the recovery.  The algorithm uses
a single scattering model. This approximation is valid when the
optical depth is small, which is common. To handle dense atmospheric
conditions (smoke, clouds), multi-scattering must be incorporated.

The goal, of coarse, is to deploy such a system on a very large
scale. However, this must first ensure that camera units are both cost
effective and field-robust, and that their positioning density is
proper. This will require a long-term engineering effort. Camera
specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research and development phase.  The new sensing modality and object
of interest offer a new domain for computational photography
problems. For example, how can compressed sensing principles be
employed here? How can priors be used to make data acquisition more
efficient? How can such a system be calibrated over time? Many such
questions and solutions would rise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%
% David brady
% Sing Bing Kang
%
% keep article 20 and remove all other citations
%

### 2013-07-11 supplementary.tex
Basically the iccp2013 in the optics express template

--- 2013-07-11 article.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[a4paper]{article}
 
-\documentclass[10pt,letterpaper]{article}
-
-\usepackage{opex3}
-\usepackage{times}
-\usepackage{graphicx}
-\graphicspath{{./images/}}
-\usepackage{epstopdf}
-\usepackage{caption}
-\usepackage{subcaption}
+\usepackage{hyperref}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{url}
 \usepackage{bm}
-\usepackage{enumerate}
-
-%\usepackage{ae} %%for Computer Modern fonts
 
@@
 
-\newcommand{\yoavcomment}[1]{}
-\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%% title page information %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{\vspace{-2cm}Supplementary material: \\Sky Tomography for 3D Aerosol Distribution Recovery}
+\author{Paper ID: 19}
+\date{}
 
-\title{Sky Tomography for 3D Aerosol Distribution Recovery}
+\maketitle
 
-\author{Amit~Aides and Yoav~Y.~Schechner and Vadim~Holodovsky}
+\section{Gradient Derivation}
+\label{sec:gradient-derivation}
 
-\address{Electrical Engineering Dept., Technion - Israel Inst. Tech., \\ Haifa 32000, Israel}
-
-\email{amitibo@tx.technion.ac.il} %% email address is required
-
-% \homepage{http:...} %% author's URL, if desired
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%% abstract and OCIS codes %%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]
-
-\begin{abstract}
-  Aerosols effect climate, health and aviation.  Currently, their
-  retrieval assumes a plane-parallel atmosphere and solely vertical
-  radiative transfer. We propose a principle to recover the atmosphere
-  as it really is: a three dimensional (3D), volumetric, transparent
-  huge object. Tomography is the key to recovery. The process involves
-  acquiring the sky lightfield by multi-view wide-angle photography on
-  a very large scale. The tomography model is distinct, as the light
-  source is unidirectional and uncontrolled, while off-axis scattering
-  dominates the images.  We formulate an image formation model based
-  on 3D radiative transfer. Model inversion is done using optimization
-  methods, exploiting a closed-form gradient which we derive for the
-  model-fit cost function. The problem is complex but tractable and
-  parallelizable, eventually estimating the 3D aerosol distribution.
-\end{abstract}
-
-\ocis{(000.0000) General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{article}{}
-\bibliographystyle{osajnl}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-\label{sec:intro}
-
-Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
-samples the optical radiance distribution in location and
-direction. It is mainly used in small-scale setups. This paper deals
-with a huge scale, up to Earth's size.  The atmosphere allows light to
-pass through in multiple locations and directions. Light is affected
-by this medium. Therefore, in this paper we lay out a principle to
-recover this 3D medium using measured and modeled lightfields
-(Fig.~\ref{fig:front}).
-\begin{figure}[t!]
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/front_img.pdf}}
-  \caption{\small The sky is photographed from multiple viewpoints
-    using wide angle (hemispherical) cameras, in a very wide area. The
-    three dimensional distribution of aerosols in the atmosphere
-    affects the images. This distribution is then recovered by a
-    dedicated tomography formulation.}
-  \label{fig:front}
-\end{figure}
-
-Projecting this large object to various directions is similar to
-tomography in other scientific domains. However, the formulation here
-is distinct. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
-our source is the uncontrolled, unidirectional Sun. Moreover, typical
-tomography relies on a linear model~\cite{gregson}: the pixel value is
-a linear combination of components along a line of sight (LOS), or a
-multiplicative combination (linearized by a logarithm). Linear
-tomography can detect volcanic gas~\cite{wright}, which absorbs
-UV. Other gases in the atmosphere absorb IR. However, in visible
-light, atmospheric attenuation is typically dominated by {\em
-  scattering} by particles (aerosols), rather than absorption by
-gasses. Thus, in our problem, we cannot rely on direct illumination,
-but on sunlight scattered into the LOS.  The model turns out to be
-{\em nonlinear, yet tractable}.
-
-We do not deal with clouds here. Clouds scatter sunlight very strongly
-and are easily observed. Hence they are directly recovered using
-common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
-On the other hand, aerosols have much more subtle visual effects and
-are thus more difficult to recover. We focus on them.  In remote
-sensing~\cite{diner}, imaging through air is associated with {\em
-  atmospheric correction}, based on {\em aerosol retrieval}. In this
-discipline, the atmosphere is often assumed to be plane-parallel, for
-simplicity, using only 1D vertical radiative transfer. Consequently
-state-of-the-art aerosol retrieval is done in distinct large lateral
-blocks~\cite{Martonchikc} with limited height
-resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
-recovery. Computational photography offers new ways to peer into
-media. In addition to active descattering~\cite{fuchs,kim,Ng1948} and
-recovery of refractive transparent objects~\cite{ihrke}, overcoming
-the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects
-was studied in horizontal, fixed
-views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
-this paper, however, the medium itself, at all relevant altitudes is
-the object of interest.
-
-3D recovery of this medium has direct implications to various
-scientific communities that either rely on remotely-sensed imagery,
-study the atmosphere, or overcome the medium to see beyond. These
-include meteorology, atmospheric sciences, volcanology, and
-climatology.  Aerosol retrieval is important for understanding climate
-evolution~\cite{Dayan2008,kalashnikova} and monitoring air
-quality. Mapping aerosol density is significant to aviation safety,
-which needs real time assessment of conditions and visibility around
-flight paths. To keep safe, today's coarse sensing limits flight
-capacity. A prominent example is the 2010 eruption of Iceland's
-Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
-much of Europe's airspace, grounding $\approx 100,000$
-flights. Knowing the 3D distribution of aerosol density may indicate
-safe 3D corridors to safely pass through, enhancing airspace
-use. Viewing beyond the medium, atmospheric correction is needed, for
-example, in satellite tracking of chlorophyll
-distributions~\cite{johnsen}. Additional bodies in the solar system
-have atmospheres. These objects can be viewed from multiple directions
-by probes.  The approach described here may be helpful there.
-
-We model passive optical tomographic imaging of 3D atmospheric
-scatterer distributions in cloudless conditions. Then, we solve this
-tomography problem, to recover the distribution. Recovery is
-formulated as an optimization that minimizes a cost function. We
-derive the gradient of this cost function, to enable efficient
-optimization.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
-\section{Theoretical Background}
-\label{sec:back}
-\vspace{-0.2cm}
-
-\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
-that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
-interacting with the irradiance. The volume includes many particles of
-this type. The denser the volume, the stronger is the extinction.  The
-density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
-volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
-is
-\begin{align}
-  \beta= \sigma n \;.
-  \label{eq:extinctc}
-\end{align}
-The volume has infinitesimal length $dl$. Then, the relative portion
-of extinct SR irradiance is the unitless differential {\em optical
-  depth}
-\begin{align}
-  d\tau= \beta dl=\sigma n dl \;.
-  \label{eq:extinct}
-\end{align}
-The optical depth aggregates in extended propagation:
-\begin{align}
-  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
-  \label{eq:tau}
-\end{align}
-Through an attenuating volume, the {\em transmittance} exponentially
-decays with the optical depth:
-\begin{align}
-  t=\exp^{-\tau}
-  \label{eq:beer-lambert}
-\end{align}
-
-\noindent {\bf Scattering}: Interaction of a single particle with the
-irradiance is by absorption and scattering. The weight of scattering
-(to all directions), relative to the total extinction is given by the
-unitless {\em single scattering albedo} $\varpi$ of the particle. The
-{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
-\begin{align}
-  \alpha= \varpi\beta=\varpi \sigma n \;.
-  \label{eq:alph}
-\end{align}
-Scattering is generally anisotropic. Its angular distribution is
-determined by a {\em phase function} $P$. Part of the light scatters
-towards a camera's line of sight (LOS), as illustrated in
-Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
-scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
-  scatter})$ is normalized: its integral over all solid angles is
-unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
-$1/({\rm m}\cdot{{\rm strad}})$) is
-\begin{align}
-  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
-  = \varpi \sigma n P(\Phi^{\rm scatter}).
-  \label{eq:alphabasic}
-\end{align}
-
-The phase function is often approximated by a parametric expression,
-as the Henyey-Greenstein function,
-\begin{align}
-  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
-    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
-  \label{eq:aerosol_scatter}
-\end{align}
-where $g$ is an {\em anisotropy parameter} and
-\begin{align}
-  \mu\equiv \cos \Phi^{\rm scatter}.
-  \label{eq:mu}
-\end{align}
-
-\noindent {\bf Air molecules}: Scattering by air molecules follows the
-{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
-\begin{align}
-  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
-  \label{eq:rayleighP}
-\end{align}
-and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
-off approximately exponentially with altitude, with a
-characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
-km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
-scattering by air molecules are modeled by
-\begin{align}
-  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
-  \frac{1.09 \times 10^{-3}}{\lambda^4}
-  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
-  \label{eq:rayleighbeta}
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
-\section{Image Acquisition Principle}
-\label{sec:setup} \vspace{-0.2cm}
-
-The atmosphere has a non-uniform distribution of scattering
-aerosols. We seek to recover this 3D volumetric distribution. To solve
-this problem, we formulate a process analogous to tomographic
-reconstruction. The scene is projected to multiple directions. Thus, a
-system captures integrated radiance as a function of direction and 2D
-projected location. Any voxel in the atmosphere contributes to the
-integrated radiance in multiple directional measurements
-(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
-number of constraints, to recover the distribution: the density and
-type of aerosols, per voxel.
-\begin{figure*}[t!]
-  \begin{center}
-    \vspace{-0.4cm}
-    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
-  \end{center}\vspace{-1.5cm}
-  \caption{\small Lightfield imaging through a volumetric distribution
-    in the atmosphere, using ground-based cameras. Our tomographic
-    reconstruction follows the acquisition. The atmosphere is analyzed
-    in a voxel grid.}
-  \label{fig:groundgrid}
-\end{figure*}
-
-Earth's radiation is sampled both spatially and angularly from
-space~\cite{breon,diner,Martonchikc,vanMol}. However, current
-multiview spaceborne systems are very coarse. For example, aerosol
-retrieval in the most complex instrument, MISR, requires spatial
-blocks that are about $17\times 17$km wide, each observed from just 9
-views along-track. This practically leads to vertical radiative
-transfer analysis, degenerating atmospheric analysis to
-1D. Experimental airborne instruments under
-development~\cite{baxter,dinerDavis10} may provide better, if still
-coarse resolution once they are operational.
-
-We believe that high resolution atmospheric recovery can be achieved
-by a large set of ground-based wide-angle~\cite{Cossairt2011,
-  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-sky-cameras, looking upwards and capturing the sky lightfield.
-Moreover, satellites image close to the orbit track (a 1D array of
-viewpoints). In contrast, land-based cameras can form a 2D set of
-viewpoints~\cite{DBLP:journals/pieee/SnavelySGSS10} as easy or hard as
-a 1D grid~\cite{Joshi06naturalvideo}. However, before designing and
-setting up such a very large scale system requires assessment of many
-details that had not been explored. These include camera
-specifications needed to recover typical distributions. Hence, a major
-theoretic and numerical research phase is ahead.
-
-This paper takes the first step, of formulating this principle and
-demonstrating feasibility using realistic simulations. The formulation
-of this paper can also apply to multiview images that are captured
-from satellites, for future spaceborne instruments of this capacity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
-\section{Forward Model}
-\label{sec:skymodel} \vspace{-0.2cm}
-
-This section describes models for image formation. In the consecutive
-section, we describe how the image formation is inverted to recover
-the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
-Ground-based wide-angle sky-cameras capture the sky lightfield from
-below. Per viewpoint, the view azimuth and elevation angles (relative
-to the zenith and north) are encapsulated in the vector
-${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
-camera's location ${\bf x}$ is fixed, while any pixel in a frame
-represents an angle ${\bf{\Theta}}$.  The measured radiance in all
-locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
-$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
-lightfield.
-% Alternatively, several ground-based cameras can be mounted on moving
-% vehicles, assuming that the aerosol distribution does not change
-% much during the time-lapse of the camera trajectory.
-
-Sunlight is scattered in the medium, creating {\em
-  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
-${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
-generally different, depending on the distribution of aerosols both
-along a LOS, and along the SRs that hit the LOS.  As
-Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
-  x},{\bf{\Theta}}$) cut through different sets atmospheric
-voxels. Thus, for each view, the radiance scattered from a voxel is
-attenuated differently, depending on the distribution of aerosols
-along the LOS~\cite{hansen}.
-
-A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints.
-The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics.
-We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera.
-This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply.
-Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\
-
-\vspace{-0.35cm}
-\noindent
-1. Attenuation of a SR propagating from the top of the atmosphere
-(TOA) to voxel $k$. \\
-
-\vspace{-0.35cm}
-\noindent
-2. Light scattering at voxel $k$, towards a camera.\\
-
-\vspace{-0.35cm}
-\noindent
-3. Light attenuation on the LOS from voxel $k$ to the camera.
-
-\noindent
-Steps 1 and 3 involve the optical depth along the light path to and
-from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
-involves the scattering coefficient at voxel $k$, described in
-Sec.~\ref{sec:scattering}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Optical Depth}
-\label{sec:optical-depth}
-
-An infinitesimal volume contains aerosols. The extinction and
-scattering coefficients due to aerosols in this volume are,
-respectively
+Here we detail the derivation of the gradient of the objective
+function:
 \begin{equation}
-  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
-  \;\;,\;\;
-  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
-  \;.
-  \label{eq:betaer}
+  \label{eq:objectiveA}
+  F({\bf n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
 \end{equation}
-In addition, the infinitesimal volume contain also air
-molecules. Hence, the overall extinction and scattering coefficients
-in this small volume are, respectively
-\begin{equation}
-  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
-  \;\;,\;\;
-  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
-  \;.
-  \label{eq:betair}
-\end{equation}
-
-Any voxel generally contains both air molecules and aerosols. Voxels
-are indexed by $k$ or $q$. As approximation, assume that within any
-voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
-  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
-  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
-constants, e.g., corresponding to the value at each voxel
-center. These parameters may change between voxels.
-
-A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
-angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
-the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
-$q$. The geometric length of this intersection line segment is $\Delta
-z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
-  [0,1]$} expresses how much of the vertical thickness of $q$ is
-crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
-optical depth between the TOA and voxel $k$ is
-\begin{equation}
-  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
-  \sum_{q \in[{\rm SR},k]}
-  \beta(q)\Delta z  f_{\rm SR}(q)
-  \;\;.
-  \label{eq:lSRn}
-\end{equation}
-Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
-\begin{equation}
-  \tau_{\rm SR}(k)=
-  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
-  \;\;,
-  \label{eq:lSRaa}
-\end{equation}
-where
-\begin{equation}
-  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
-  \sum_{q \in[{\rm SR},k]}
-  \beta^{\rm air}(q)  f_{\rm SR}(q)
-  \label{eq:lSRair}
-\end{equation}
-and
-\begin{equation}
-  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
-  \sum_{q \in[{\rm SR},k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
-  \label{eq:lSRaeros}
-\end{equation}
-
-The number of voxels is $N_{\rm voxels}$. All their associated
-variables are concatenated into columns stack vectors, each $N_{\rm
-  voxels}$ long. Aerosol densities and cross sections in all voxels
-are stored in the respective vectors ${\bf n}$ and
-$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
-matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
-$(k,q)$ is
-\begin{equation}
-  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
-  \left\{
-    \begin{array}{ll}
-      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
-      & \mbox{ if $q \in[{\rm SR},k]$} \\
-      0  & \mbox{ otherwise}
-      \label{eq:Dsv}
-    \end{array}
-  \right.
-  .
-  \hspace{-0.05cm}
-\end{equation}
-Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
-depths due to aerosols (See Fig.~\ref{fig:optidepth}):
-\begin{equation}
-  \vect{\tau}_{\rm SR}^{\rm aerosol}=
-  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
-  (\vect{\sigma} \odot {\bf n})
-  \label{eq:tauSRvec1}
-\end{equation}
-where the operator $\odot$ denotes the Hadamard (element-wise)
-product.
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
-  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
-    above it on a SR. The scattered radiance from voxel $k$ is then
-    attenuated by voxels below it on a LOS to camera $c$. The overall
-    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
-    optical depth affecting $k$. It is formalized in matrix-vector
-    operations. }
-  \label{fig:optidepth}
-\end{figure}
-Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
-depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.
-
-Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
-between the camera and the center of voxel $k$. The LOS zenith angle
-is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
-length of this intersection line segment is $\Delta z f_{\rm
-  LOS_c}(q)/\cos\Phi^{\rm LOS}_c$: the factor $f_{\rm LOS_c}(q)\in
-[0,1]$ expresses how much of the vertical thickness of $q$ is crossed
-by the LOS.  Analogously to
-Eqs.~(\ref{eq:lSRaa},\ref{eq:lSRair},\ref{eq:lSRaeros}), The optical
-depth %path length
-along a LOS to $k$ is
-\begin{equation}
-  \tau_{{\rm LOS}_c}(k)=
-  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
-  \;\;,
-  \label{eq:lLOSaerot}
-\end{equation}
-where
-\begin{equation}
-  \tau_{{\rm LOS}_c}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm LOS}_c}
-  \sum_{q \in[{\rm LOS}_c,k]}
-  \beta^{\rm air}(q)  f_{\rm LOS_c}(q)
-  \label{eq:lLOSair}
-\end{equation}
-and
-\begin{align}
-  \label{eq:lLOSaeros}
-  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)=
-  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~%\nonumber
-  ~~~~~
-  \\
-  % ~~~~
-  \frac{\Delta z}{\cos\Phi^{\rm LOS}_c} \sum_{q \in[{\rm LOS}_c,k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm LOS_c}(q).
-  \nonumber
-\end{align}
-Eq.~(\ref{eq:lLOSaeros}) leads to a vector of LOS optical depths due
-to aerosols:
-\begin{equation}
-  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
-  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
-  (\vect{\sigma} \odot {\bf n})
-  \label{eq:tauLOSvec1}
-\end{equation}
-Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
-  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
-\begin{equation}
-  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
-  \left\{
-    \begin{array}{ll}
-      \frac{\Delta z f_{\rm LOS_c}(q)}{\cos\Phi^{\rm LOS}_c}
-      & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
-      0  & \mbox{ otherwise}
-      \label{eq:Dvc}
-    \end{array}
-  \right.
-  .
-  \hspace{-0.05cm}
-\end{equation}
-Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of LOS optical
-depths due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.
-
-The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
-and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
-single matrix
-\begin{equation}
-  {\bf D}_c=
-  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
-  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
-  \;\;.
-  \label{eq:Dtotal}
-\end{equation}
-Similarly, the molecular optical depths along all trajectories between
-the sun, each voxel and camera $c$ are compounded to a vector
-\begin{equation}
-  \vect{\tau}_c^{\rm air}=
-  \vect{\tau}_{\rm SR}^{\rm air}+
-  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
-  \;\;.
-  \label{eq:tauairtotal}
-\end{equation}
-Using Eq.~(\ref{eq:rayleighbeta}) for $\beta^{\rm air}$ in all voxels,
-the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
-$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
-angle.
-
-Using
-Eqs.~(\ref{eq:lSRaa},\ref{eq:tauSRvec1},\ref{eq:lLOSair},\ref{eq:tauLOSvec1},\ref{eq:Dtotal},\ref{eq:tauairtotal}),
-the total optical depths corresponding to LOSs (of camera $c$) and SRs
-that cross all voxels comprise the vector
-\begin{equation}
-  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
-  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
-  \;\;.
-  \label{eq:tautotal}
-\end{equation}
-This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
-(See Fig.~\ref{fig:optidepth}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scattering}
-\label{sec:scattering}
-
-Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
-  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
-which is pre-calculated.
-% Eq.~(\ref{eq:mu}) yields its cosine, $\mu_c(k)$.
-Column-stacking all voxels yields the vector representation of all
-scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
-camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
-  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
-Using
-Eqs.~(\ref{eq:alphabasic},\ref{eq:rayleighP},\ref{eq:betaer},\ref{eq:betair}),
-the angular scattering coefficients across the domain are expressed in
-vector form by
-\begin{align}
-  \tilde{\vect{\alpha}}^{\rm air}_c &=
-  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)   \nonumber \\
-  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
-  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
-    g}(\vect{\Phi}^{\rm scatter}_c)
-  \label{eq:alpha_matrix}
-\end{align}
-The vector ${\bf g}$ column-stacks the anisotropy parameter of the
-phase function, in all voxels. We use this notation, to indicate a
-parametric phase function as in Eq.~(\ref{eq:aerosol_scatter}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Image Capture}
-\label{sec:captured-image}
-
-Compounding the attenuation of irradiance along both $[{\rm SR},k]$
-and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(Eqs.~\ref{eq:beer-lambert},\ref{eq:betair},\ref{eq:tautotal}), the
-radiant power contributed by the voxel is
-\begin{equation}
-  p_c(k)= L^{\rm TOA}
-  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
-  e^{-[\tau_c(k)]}
-  \;\;.
-  \label{eq:ick}
-\end{equation}
-A column-stack vector of all voxel contributions is
-\begin{equation}
-  {\bf p}_c= L^{\rm TOA}
-  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
-  \odot e^{-\vect{\tau}_c}
-  \;\;.
-  \label{eq:pc}
-\end{equation}
-
-A camera pixel collects light from a narrow cone in the
-atmosphere. The cone includes some voxels, intersects with some other
-voxels, and oblivious to all the rest.  Thus light power captured at a
-pixel is weighted sum of the power $p_c(k)$ from all voxels: most
-voxels have null weight, since they fall outside the pixels's conic
-field of view, while the rest of the voxels are aggregated.
-
-This linear sum is formulated by a matrix operation over ${\bf
-  p}_c$. The measured image is column-stacked to a vector $N_{\rm
-  pix}$ long. It is given by
-\begin{equation}
-  {\bf i}_c= {\vect{\Pi}}_c{\bf p}_c
-  \;\;.
-  \label{eq:IcP}
-\end{equation}
-The $N_{\rm pix}\times N_{\rm voxels}$ sparse matrix ${\vect{\Pi}}_c$
-expresses {\em projection} of light into camera $c$. For pixel
-$\Theta$ and voxel $k$, there is an {\em intersection} volume ${\bf
-  V}_c(\Theta,k)$ between the cone volume of the pixel's field of
-view, and the voxel, as illustrated in Fig.~\ref{fig:projection}.
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/sensor.pdf_tex}}
-  \caption{\small An image pixel captures light emanating in a cone in
-    space. Voxels that fully or partially fall in this cone are sensed
-    by the pixel. Factoring out scattering and attenuation (which are
-    dealt elsewhere in our analysis), the relative contribution of
-    each voxel depends on its distance and intersection with the
-    cone. This is formalized a matrix-vector operation.}
-  \label{fig:projection}
-\end{figure}
-The corresponding element in the matrix ${\vect{\Pi}}_c$ is
-\begin{equation}
-  \Pi_c(\Theta,k)=
-  % \frac{a}{|{\bf V}(k)|}
-  a
-  \iiint_{{\bf V}_c(\Theta,k)}
-  \frac{1}{[R({\bf v})]^2} d{\bf v}
-  \;\;,
-  \label{eq:Pc}
-\end{equation}
-where $a$ is the effective area of the camera lens.
-% and $|{\bf V}(k)|$ is the volume of voxel $k$.
-The distance $R({\bf v})$ is measured between the camera and an
-infinitesimal volume element at ${\bf v}\in {\bf V}_c(\Theta,k)$.
-
-Combining Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the
-captured image is thus
-\begin{align}
-  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
-    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
-      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bf D}_c
-      (\vect{\sigma} \odot {\bf n})]} \right\}
-  \label{eq:bigIc}
-\end{align}
-Most often, there is only a single type of aerosol over a
-scene. Hence, the three-element vector $[{\sigma}^{\rm
-  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
-the density distribution ${\bf n}$ is variable. Then,
-Eq.~(\ref{eq:bigIc}) degenerates to
+Here ${\bf i}^{\rm measured}_c$ is the image captured by camera $c$
+and ${\bf i}_c({\bf n})$ is an image modeled from the viewpoint of
+camera $c$ according to the density distribution ${\bf n}$. In the
+article we show that ${\bf i}_c({\bf n})$ can be expressed by
 \begin{align}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Inverse Problem}
-\label{sec:inverse-problem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Unknowns and Prior Knowledge}
-\label{sec:prior}
-
-In general terms, the variables are the set
-\begin{equation}
-  {\cal V}\equiv
-  \left\{
-    {\bf n},
-    \left\{
-      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bf g}_{\lambda}
-    \right\}_{\lambda}
-  \right\}
-  \;\;,
-  \label{eq:calV}
-\end{equation}
-where $\lambda$ denotes the spectral (color) channel.  There are
-$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
-variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
-    spectral})$}.
-
-Prior knowledge reduces the unknowns. Sec.~\ref{sec:captured-image}
-mentions a prior: in many cases a single aerosol type dominates a
-scene. Then, the three-element vector $[\varpi^{\rm
-  aerosol},{\sigma}^{\rm aerosol},g]$ is rather spatially uniform. In
-such cases, the set of unknowns reduces to $ {\cal V}= \left\{ {\bf
-    n}, \left\{ {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
-      aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda} \right\} $ and
-\mbox{$|{\cal V}|=N_{\rm voxels}+3N_{\rm spectral}$}.
-
-Furthermore, the elements in the aerosol characteristics set $\left\{
-  {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
-    aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda}$ is not
-arbitrary, since all these characteristics have physical origins. This
-set is constrained to comply with what nature allows (aerosol
-classes).  This significantly constrains the unknown
-characteristics. State-of-the-art aerosol retrieval, as used by NASA's
-MISR products indeed employ an aerosol-class prior. Types of aerosol
-mixtures are discretized to $N_{\rm models}=74$
-classes~\cite{Martonchikc}, called {\em models}. Each class $m$
-represents aerosols having a distinct characteristics set.  State of
-the art retrieval is 1D (only vertical radiative transfer per large
-areas). Nevertheless, we use this prior in our 3D problem. Then, the
-set of unknowns reduces to $ {\cal V}= \left\{ {\bf n},m \right\}$ and
-\mbox{$|{\cal V}|=N_{\rm voxels}+N_{\rm models}$}.
-
-The atmosphere is photographed from $N_{\rm views}$ viewpoints. Each
-photograph provides $N_{\rm pix}$ measurements (pixels), {\em
-  including} their possible division to color channels. Hence, the
-data at our disposal comprises $N_{\rm views}N_{\rm pix}$
-measurements.  For the recovery task to be well-posed, it is necessary
-that $N_{\rm views}N_{\rm pix}>|{\cal V}|$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Objective Function}
-\label{sec:objective-function}
-
-The inverse problem (tomography) seeks recovery of the 3D aerosol
-distribution in the atmosphere. From
-Eqs.~(\ref{eq:alpha_matrix},\ref{eq:bigIc},\ref{eq:bigIA},\ref{eq:calV}),
-the images $\{ {\bf i}_c\}_{c=1}^{N_{\rm views}}$ depend on the
-variables set ${\cal V}$, particularly on the unknown field ${\bf
-  n}$. The recovery task is phrased as optimization of an objective
-function, that fits the image-formation
-model~(\ref{eq:bigIc},\ref{eq:bigIA}) to measured photographs $\{ {\bf
-  i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$:
-\begin{equation}
-  \label{eq:mingenobjective}
-  \hat{\cal V} = \argmin_{{\cal V}\in {\cal C}} F({\cal V})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:genobjective}
-  F({\cal V}) = \sum_{c=1}^{N_{\rm views}}
-  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\cal V})\| + {\rm Regularization}({\cal V})
-  \;.
-\end{equation}
-Here ${\cal C}$ is a constraints set, which encapsulates part of the
-prior knowledge, as well as nonnegativity bounds, while $\|~\|$ is
-some error-distance measure.  Here ${\rm Regularization}({\cal V})$
-describes spatial regularization terms of the variables, such as
-smoothness, or a blobby or layered structure.
-
-Spatial regularization can help overcome lack of data, if $N_{\rm
-  views}$ is too small, and it is definitely helpful. In this work,
-however, we formulate and demonstrate the basic principle of our
-tomography task, hence we proceed without regularization. Relying on
-prior knowledge described in Sec.~\ref{sec:prior}, the problem
-complexity is by far dominated by the $N_{\rm voxels}$-large array
-${\bf n}$, which is continuously valued. Hence, we focus here on
-retrieving ${\bf n}$ through continuous optimization. Relying on the
-least-squares measure, we seek:
-\begin{equation}
-  \label{eq:minobjectiveA}
-  \hat{\bf n} =
-  \argmin_{{\bf n}} F({\bf n})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bf n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
-\end{equation}
-This is solved using standard optimization tools. Fast optimization
-that leads to to local minima ($F$ is not convex) exploits the
-gradient of $F$.
-
-Since our model uses close-form expressions, $F$ is
-differentiable. The gradient of $F$ with respect to ${\bf n}$ is
+The gradient of $F$ with respect to ${\bf n}$ is
 \begin{align}
@@
 
-Denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$ into a
-diagonal matrix, whose main diagonal elements correspond to the
-elements of $\vect{v}$.  A close-form expression of our Jacobian is
+In order to describe the derivation of the Jacobian ${\bf J}_{{\bf i}_c}({\bf n})$, we first show some results relating to differentiation. Let $\vect{n}$
+be a vector of length $q$. Let $\vect{g}(\vect{n})$ be a vector
+function: it outputs a vector of length $r$. Let $\mat{B}$ be a $q
+\times r$ matrix and
+\begin{align}
+  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
+  \label{eq:example1}
+\end{align}
+In Eq.~(\ref{eq:example1}), the exponential is element-wise (not
+raising an operator to some power). Then
+\begin{align}
+  \label{eq:partial2}
+  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
+  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
+\end{align}
+Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
+into a diagonal matrix, whose main diagonal elements correspond to the
+elements of $\vect{v}$. Using~(\ref{eq:partial2}) we can calculate
+\begin{align}
+  \label{eq:partial4}
+  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+      {\bf D}_c {\bf n})}}
+  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+      {\bf D}_c {\bf n})}}
+\end{align}
+In~(\ref{eq:partial4}) we assume that $\vect{\tau}_c^{\rm air}$ is
+known and constant.
+
+To calculate the derivative of the Hadamard product
+in~(\ref{eq:bigIA}) we first note the following: Let
+$\vect{u}(\vect{n})$ be a vector function that outputs a vector of
+length $r$. Let $\mat{B}$ be a $r \times q$ matrix. Then,
+\begin{align}
+  \label{eq:partial1}
+  \PartDeriv{\transpose{\mat{B}} (\vect{g} \odot \vect{u})}{\vect{n}}
+  = \left[ \PartDeriv{\vect{g}}{\vect{n}} \OpDiag{\vect{u}} +
+    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{g}} \right] \mat{B}.
+\end{align}
+Then,
+\begin{align}
+  \label{eq:partial3}
+  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n}}{\vect{n}}
+  =
+  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
+  \nonumber \\
+  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
+  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
+\end{align}
+
+Based on~(\ref{eq:partial4},~\ref{eq:partial1})
+and~(\ref{eq:partial3}) we can derive a close-form expression for the
+Jacobian of~(\ref{eq:bigIA}):
 \begin{align}
@@
 \end{align}
-For a detailed derivation of
-Eqs.~(\ref{eq:gradient2},\ref{eq:gradient3}), we refer the reader to
-the supplementary material.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Simulations}
-\label{sec:simul}
-
-To test the model, we made simulations based on atmospheric models in the literature. Here are the details.\\
-
-\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
-  SR}=45^o$. Its $L^{\rm TOA}$ is obtained
-from~\cite{BBradiance,sun_composition}, with respective red-green-blue
-ratios of
-$L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm B}=255:236:224$.\\
-
-\noindent{\bf Dimensions}: The domain of sky we simulate and recover has area of $50\times 50$km, and it extends from the ground up to altitude of 10km.
-This volume is divided to a $50\times50\times100$ grid, where each voxel has area of $1\times1$km and vertical thickness of 100 meters.
-The dimension of the problem is thus $250,000$ variables.\\
-
-\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
-in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
-sea-salt/organic particle, whose anisotropy parameter per color
-channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
-corresponding extinction cross sections are $[\sigma^{\rm
-  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
-  aerosol}_{\rm B}]=[16.5,16.2,15.9][1/\mu m^2]$.  Its
-single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all channels.
-
-We simulated various spatial distributions. All were set as a product
-of two functions. The first function is an exponential
-decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
-\begin{align}
-  w_1[h(k)] = \frac{1} {\sigma^{\rm aerosol}_{\rm G} \mathrm{MFP^{sea
-        level}}} \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
-\end{align}
-where $H^\mathrm{aerosol}=2\ km$. This expresses a general trend of
-reduced atmospheric density with height. Here the mean free path (MFP)
-of the aerosols layer at sea level was set to $\mathrm{MFP^{sea
-    level}}=1/5~{\rm[1/km]}$.
-% is a typical characteristic thickness of the aerosol
-% layer~\cite{Levi1980}.
-
-The second function, $w_2$, expresses a clustered nature of aerosol
-``clouds''. We define blobs in the form of 3D ellipsoids. There may be
-multiple ellipsoids suspended.  Then
-\begin{equation}
-  w_2(k) =
-  \left\{
-    \begin{array}{ll}
-      1  & \mbox{ if $k\in$ any blob cluster} \\
-      0  & \mbox{ otherwise}
-      \label{eq:f2}
-    \end{array}
-  \right.
-  .
-  \hspace{-0.05cm}
-\end{equation}
-The true aerosol distribution is then
-\begin{equation}
-  \label{eq:ntrue}
-  {\bf n}^{\rm true}={\bf w}_1\odot {\bf w}_2  .
-  \hspace{-0.05cm}
-\end{equation}
-As an example, we created a {\em Haze Blobs} scene
-(Fig.~\ref{fig:simulation1}) using two ellipsoid blobs: \begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
-  \caption{\small Simulated 3D aerosol distribution composed of {\em
-      Haze Blobs}. Its reconstruction is shown in
-    Fig.~\ref{fig:front}. Color represents aerosol density. The
-    density units are $10^{15}~{\rm particles}/{\rm cm}^3.$}
-  \label{fig:simulation1}
-\end{figure}
-the first is centered at altitude $3.3km$, and has horizontal width of $32km$ and vertical thickness of $2.8km$.
-The second ellipsoid is centered at altitude $6.6km$, and has lateral width of $24km$ and vertical thickness of $2.1km$.
-Note that the horizontal widths are much larger than the vertical ones.
-This is consistent with scales of atmospheric aerosol distributions.\\
-
-\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
-field of view, capturing the entire sky from its viewpoint. We used 95
-viewpoints on a grid, each view $\approx 4.4$km from its neighbors.
-The resolution of each camera is low: $128\times 128$ pixels,
-expressing the fact that cloudless (yet hazy) sky images are rather
-smooth, hence there is no need for high image resolution. Each pixel
-has full-well depth of 40000 electrons, which corresponds to the
-brightest pixel value. Each measurement has photon noise, which is
-Poissonian distributed, according to each image-pixel value $i_c$ and
-the full-well depth. For example, Fig.~\ref{fig:simulation-results1}
-shows two modeled photographs
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/ref_images.pdf}}
-  \caption{\small Rendered photographs (contrast enhanced)
-    corresponding to different viewpoints, of sky that includes {\em
-      Haze Blobs}. A yellow dot marks the Sun location. Dashed white
-    circles mark elevation angles.}
-  \label{fig:simulation-results1}
-\end{figure}
-of the  {\em Haze Blobs} scene that corresponds to Fig.~\ref{fig:simulation1}.\\
-
-\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
-that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
-with 8GB
-DDR3 memory per core.
-Out of it, we used 8 nodes, corresponding to 96 cores.
-Each core was dedicated to rendering a modeled image (in each interaction) as if captured by one of the 95 cameras.
-Each iteration (varying the model according to the gradient-based algorithm and varying all the rendered images) took $\approx 7$sec.\\
-
-\noindent{\bf Optimization}: We used the L-BFGS-B
-algorithm~\cite{BFGS}. The algorithm was initialized by ${\bf
-  n}=0$. Satisfactory convergence occurred in several thousand
-iterations, taking a couple of hours to complete in total. For
-example, Fig.~\ref{fig:objective} shows
-\begin{figure}[t]
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/objective.pdf}}
-  % \includegraphics[width=\columnwidth]{images/objective.pdf}
-  \caption{\small The decay of $\log F({\bf n})$ with the iteration
-    index.}
-  \label{fig:objective}
-\end{figure}
-the progression of the objective as a function of the iteration
-number, when recovering the the {\em Haze Blobs} scene.
-
-% 26, 48, 1320, 590
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Results}
-\label{sec:optimization-results}
-
-An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in Fig.~\ref{fig:simulation1}, while the
-recovered 3D distribution is visualized in Fig.~\ref{fig:front}. The
-distributions appear consistent, though there are errors that stem
-from the random noise in the images. To quantify the results, we use a
-relative error measure based on the $\ell_1$ norm
-\begin{equation}
-  \label{eq:ndiff}
-  \epsilon=\frac{\| \hat{\bf n}  - {\bf n}^{\rm true} \|_1}
-  {\| {\bf n}^{\rm true} \|_1} ,
-  \hspace{-0.05cm}
-\end{equation}
-It is equivalent to the aerosol mass that is over and under-estimated
-in all voxels, relative to the total aerosol mass in the scene.  In
-the {\em Haze Blobs} case, $\epsilon=0.202$.
-
-We created a {\em Haze Front} scene. Fig.~\ref{fig:simulation2}a shows
-an iso-surface visualization of this distribution.
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation2}}
-  \caption{\small [a] Simulated 3D aerosol distribution composed of a
-    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
-    density. The density units are $10^{15}~{\rm particles}/{\rm
-      cm}^3.$}
-  \label{fig:simulation2}
-\end{figure}
-Here an ellipsoid degenerated to an elliptic cylinder that partly
-enters the analyzed volume. It is centered at altitude $5km$, has
-vertical thickness of $4km$ and length of $32km$ (only part of which
-enters the volume). The haze front stretches across the width of the
-volume.  Fig.~\ref{fig:simulation2}b visualizes the recovered 3D
-distribution of this scene. For the {\em Haze Front},
-$\epsilon=0.198$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-\label{sec:conclusions}
-
-We describe a new way to sense the 3D atmosphere. We show feasibility
-of departing from common 1D aerosol distribution models, in favor of
-detailed 3D analysis.  The paper describes both a novel data
-acquisition system concept for this recovery task, and a dedicated
-algorithm for reconstructing aerosol distributions.
-
-Even without regularization, the reconstruction algorithm handles
-arbitrary density distributions. Using more prior knowledge,
-e.g. spatial smoothness will improve the recovery.  The algorithm uses
-a single scattering model. This approximation is valid when the
-optical depth is small, which is common. To handle dense atmospheric
-conditions (smoke, clouds), multi-scattering must be incorporated.
-
-The goal, of coarse, is to deploy such a system on a very large
-scale. However, this must first ensure that camera units are both cost
-effective and field-robust, and that their positioning density is
-proper. This will require a long-term engineering effort. Camera
-specifications should be set to optimally recover a wide range of
-aerosol distributions. This requires a major theoretic and numerical
-research and development phase.  The new sensing modality and object
-of interest offer a new domain for computational photography
-problems. For example, how can compressed sensing principles be
-employed here? How can priors be used to make data acquisition more
-efficient? How can such a system be calibrated over time? Many such
-questions and solutions would rise.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \end{document}
-
-%
-% David brady
-% Sing Bing Kang
-%
-% keep article 20 and remove all other citations
-%

### 2013-07-11 article.tex
Copied whole sections from the phd.tex.

@@
 \usepackage{epstopdf}
-\usepackage{caption}
-\usepackage{subcaption}
 \usepackage{amsmath}
@@
 \usepackage{enumerate}
+\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
 
 %\usepackage{ae} %%for Computer Modern fonts
+
+\usepackage{hyperref}
+\hypersetup{pdfborder={0 0 0}}
+
+%
+% subfiles is useful for having the abstract (and possible other
+% sections/chapters) as separate files.
+%
+\usepackage{subfiles}
+
+\usepackage[]{siunitx}
+
+%
+% The cleveref package seems very cool but currently it doesn't support hebrew
+% (babel) very well, so I just use if for single references.
+% As a work around I redefine the number definition as suggested in:
+% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
+%
+\usepackage[capitalise]{cleveref}
+\makeatletter
+\def\@@number#1{#1}
+\makeatother
 
@@
 \newcommand{\derivsym}[1]{\,d{#1}}
-
 \newcommand{\yoavcomment}[1]{}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Theoretical Background}
 \label{sec:back}
-\vspace{-0.2cm}
 
@@
 that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
+  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
 interacting with the irradiance. The volume includes many particles of
 this type. The denser the volume, the stronger is the extinction.  The
-density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
-volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
-is
+density of the particles is $n$ (units
+\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
+  extinction coefficient} $\beta$ (units \si{\per\meter}) is
 \begin{align}
@@
 unitless {\em single scattering albedo} $\varpi$ of the particle. The
-{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
+{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
 \begin{align}
@@
 towards a camera's line of sight (LOS), as illustrated in
-Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
+\cref{fig:groundgrid}. The angle between the SR and LOS is the
 scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
@@
 unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
-$1/({\rm m}\cdot{{\rm strad}})$) is
+\si[sticky-per]{\per\meter\steradian}) is
 \begin{align}
@@
 The phase function is often approximated by a parametric expression,
-as the Henyey-Greenstein function,
+as the Henyey-Greenstein~\cite{Cornette1995} function\todo{Correct the Henyey-Greenstein function},
 \begin{align}
@@
 \noindent {\bf Air molecules}: Scattering by air molecules follows the
-{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
-\begin{align}
-  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
+{\em Rayleigh} model:
+\begin{align}
+  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
   \label{eq:rayleighP}
@@
 characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
-km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
-scattering by air molecules are modeled by
+\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
+extinction and scattering by air molecules are modeled by
 \begin{align}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Image Acquisition Principle}
-\label{sec:setup} \vspace{-0.2cm}
+\label{sec:setup}
 
@@
   \begin{center}
-    \vspace{-0.4cm}
-    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
-  \end{center}\vspace{-1.5cm}
+    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
+  \end{center}
   \caption{\small Lightfield imaging through a volumetric distribution
@@
 \end{figure*}
-
 Earth's radiation is sampled both spatially and angularly from
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \vspace{-0.25cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Forward Model}
-\label{sec:skymodel} \vspace{-0.2cm}
-
-This section describes models for image formation. In the consecutive
-section, we describe how the image formation is inverted to recover
-the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
-Ground-based wide-angle sky-cameras capture the sky lightfield from
-below. Per viewpoint, the view azimuth and elevation angles (relative
-to the zenith and north) are encapsulated in the vector
-${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
-camera's location ${\bf x}$ is fixed, while any pixel in a frame
-represents an angle ${\bf{\Theta}}$.  The measured radiance in all
-locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
-$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
-lightfield.
-% Alternatively, several ground-based cameras can be mounted on moving
-% vehicles, assuming that the aerosol distribution does not change
-% much during the time-lapse of the camera trajectory.
-
-Sunlight is scattered in the medium, creating {\em
-  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
-${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
-generally different, depending on the distribution of aerosols both
-along a LOS, and along the SRs that hit the LOS.  As
-Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
-  x},{\bf{\Theta}}$) cut through different sets atmospheric
-voxels. Thus, for each view, the radiance scattered from a voxel is
-attenuated differently, depending on the distribution of aerosols
-along the LOS~\cite{hansen}.
-
-A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints.
-The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics.
-We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera.
-This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply.
-Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\
-
-\vspace{-0.35cm}
-\noindent
-1. Attenuation of a SR propagating from the top of the atmosphere
-(TOA) to voxel $k$. \\
-
-\vspace{-0.35cm}
-\noindent
-2. Light scattering at voxel $k$, towards a camera.\\
-
-\vspace{-0.35cm}
-\noindent
-3. Light attenuation on the LOS from voxel $k$ to the camera.
-
-\noindent
+\label{sec:skymodel}
+
+A forward model takes as input the aerosol distribution, and outputs
+images as if captured at various viewpoints.  We use a
+\emph{single-scattering} model, in which any SR changes direction
+(scatters) only once on the way to the camera. This model is valid in
+atmospheres that are not very dense: inside fog and clouds this model
+does not apply.
+
+Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
+capture the sky lightfield from below. Per viewpoint, the view azimuth
+and elevation angles (relative to the zenith and north) are
+encapsulated in the vector ${\bf{\Theta}}$.  A raw image is $i_{\bf
+  x}({\bf{\Theta}})$: a camera's location ${\bf x}$ is fixed, while
+any pixel in a frame represents an angle ${\bf{\Theta}}$.  The
+measured radiance in all locations ${\bf x}$ and angles
+${\bf{\Theta}}$ is the {\em lightfield} $I({\bf
+  x},{\bf{\Theta}})$. Individual images are slices of the lightfield.
+
+Under single-scattering approximation, radiative transfer has three
+steps (\cref{fig:groundgrid}):
+\begin{enumerate}
+\item Attenuation of a SR propagating from the top of the atmosphere
+  (TOA) to voxel $k$.
+\item Light scattering at voxel $k$, towards a camera.
+\item Light attenuation on the LOS from voxel $k$ to the camera.
+\end{enumerate}
+
 Steps 1 and 3 involve the optical depth along the light path to and
-from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
-involves the scattering coefficient at voxel $k$, described in
-Sec.~\ref{sec:scattering}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+from voxel $k$, analyzed in \cref{sec:optical-depth}.  Step 2 involves
+the scattering coefficient at voxel $k$, described in
+\cref{sec:scattering}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Optical Depth}
@@
 \end{equation}
-In addition, the infinitesimal volume contain also air
-molecules. Hence, the overall extinction and scattering coefficients
-in this small volume are, respectively
+The infinitesimal volume contain also air molecules. Hence, the
+overall extinction and scattering coefficients in this small volume
+are, respectively
 \begin{equation}
@@
 the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
-$q$. The geometric length of this intersection line segment is $\Delta
-z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
-  [0,1]$} expresses how much of the vertical thickness of $q$ is
-crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
-optical depth between the TOA and voxel $k$ is
-\begin{equation}
-  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
-  \sum_{q \in[{\rm SR},k]}
-  \beta(q)\Delta z  f_{\rm SR}(q)
-  \;\;.
+$q$. The geometric length of this intersection line segment is $l_{\rm
+  SR}(q)$ which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.
+Following \cref{eq:tau,eq:betair}, the optical depth between the TOA
+and voxel $k$ is
+\begin{equation}
+  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
   \label{eq:lSRn}
 \end{equation}
-Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
+Based on \cref{eq:betaer,eq:betair,eq:lSRn},
 \begin{equation}
@@
 \begin{equation}
-  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
+  \tau_{\rm SR}^{\rm air}(k)=
   \sum_{q \in[{\rm SR},k]}
-  \beta^{\rm air}(q)  f_{\rm SR}(q)
+  \beta^{\rm air}(q)  l_{\rm SR}(q)
   \label{eq:lSRair}
@@
 \begin{equation}
-  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
+  \tau_{\rm SR}^{\rm aerosol}(k)
   \sum_{q \in[{\rm SR},k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
+  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm SR}(q)
   \label{eq:lSRaeros}
@@
     \begin{array}{ll}
-      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
-      & \mbox{ if $q \in[{\rm SR},k]$} \\
+      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
       0  & \mbox{ otherwise}
@@
 \end{equation}
-Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
-depths due to aerosols (See Fig.~\ref{fig:optidepth}):
+\cref{eq:lSRaeros,eq:Dsv} lead to a vector of SR optical depths due to
+aerosols (See \cref{fig:projection})a:
 \begin{equation}
@@
 where the operator $\odot$ denotes the Hadamard (element-wise)
-product.
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
-  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
-    above it on a SR. The scattered radiance from voxel $k$ is then
-    attenuated by voxels below it on a LOS to camera $c$. The overall
-    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
-    optical depth affecting $k$. It is formalized in matrix-vector
-    operations. }
-  \label{fig:optidepth}
-\end{figure}
-Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
+product. Similarly, \cref{eq:lSRair} leads to a vector of SR optical
 depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.
@@
 is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
-length of this intersection line segment is $\Delta z f_{\rm
-  LOS_c}(q)/\cos\Phi^{\rm LOS}_c$: the factor $f_{\rm LOS_c}(q)\in
-[0,1]$ expresses how much of the vertical thickness of $q$ is crossed
-by the LOS.  Analogously to
-Eqs.~(\ref{eq:lSRaa},\ref{eq:lSRair},\ref{eq:lSRaeros}), The optical
-depth %path length
-along a LOS to $k$ is
+length of this intersection line segment is $l_{\rm LOS_c}(q)$which
+depends on $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
+\cref{eq:lSRaa,eq:lSRair,eq:lSRaeros}, the optical depth along a LOS
+to $k$ is
 \begin{equation}
@@
 \begin{equation}
-  \tau_{{\rm LOS}_c}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm LOS}_c}
+  \tau_{{\rm LOS}_c}^{\rm air}(k)=
   \sum_{q \in[{\rm LOS}_c,k]}
-  \beta^{\rm air}(q)  f_{\rm LOS_c}(q)
+  \beta^{\rm air}(q)  l_{\rm LOS_c}(q)
   \label{eq:lLOSair}
@@
   \label{eq:lLOSaeros}
-  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)=
-  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~%\nonumber
-  ~~~~~
-  \\
-  % ~~~~
-  \frac{\Delta z}{\cos\Phi^{\rm LOS}_c} \sum_{q \in[{\rm LOS}_c,k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm LOS_c}(q).
-  \nonumber
-\end{align}
-Eq.~(\ref{eq:lLOSaeros}) leads to a vector of LOS optical depths due
-to aerosols:
+  \tau_{{\rm LOS}_c}^{\rm aerosol}(k) = \sum_{q \in[{\rm LOS}_c,k]}
+  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm LOS_c}(q).
+\end{align}
+\cref{eq:lLOSaeros} leads to a vector of LOS optical depths due to
+aerosols:
 \begin{equation}
@@
     \begin{array}{ll}
-      \frac{\Delta z f_{\rm LOS_c}(q)}{\cos\Phi^{\rm LOS}_c}
-      & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
+      l_{\rm LOS_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
       0  & \mbox{ otherwise}
@@
 \end{equation}
-Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of LOS optical
-depths due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.
+Similarly, \cref{eq:lSRair} leads to a vector of LOS optical depths
+due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.
 
@@
 \end{equation}
-Using Eq.~(\ref{eq:rayleighbeta}) for $\beta^{\rm air}$ in all voxels,
-the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
-$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
-angle.
+Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in all voxels, the
+vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus $\vect{\tau}_c^{\rm
+  air}$ can be calculated once, per sun zenith angle.
 
 Using
-Eqs.~(\ref{eq:lSRaa},\ref{eq:tauSRvec1},\ref{eq:lLOSair},\ref{eq:tauLOSvec1},\ref{eq:Dtotal},\ref{eq:tauairtotal}),
+\cref{eq:lSRaa,eq:tauSRvec1,eq:lLOSair,eq:tauLOSvec1,eq:Dtotal,eq:tauairtotal},
 the total optical depths corresponding to LOSs (of camera $c$) and SRs
@@
 This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
-(See Fig.~\ref{fig:optidepth}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+(See~\cref{fig:projection}a).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Scattering}
@@
   LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
-which is pre-calculated.
-% Eq.~(\ref{eq:mu}) yields its cosine, $\mu_c(k)$.
-Column-stacking all voxels yields the vector representation of all
-scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
-camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
-  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
-Using
-Eqs.~(\ref{eq:alphabasic},\ref{eq:rayleighP},\ref{eq:betaer},\ref{eq:betair}),
-the angular scattering coefficients across the domain are expressed in
-vector form by
+which is pre-calculated.  Column-stacking all voxels yields the vector
+representation of all scattering angles in the domain,
+$\vect{\Phi}^{\rm scatter}_c$ per camera $c$. Similarly, the
+single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are
+stacked to vector $\vect{\varpi}$.  Using
+\cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the angular
+scattering coefficients across the domain are expressed in vector form
+by
 \begin{align}
@@
 phase function, in all voxels. We use this notation, to indicate a
-parametric phase function as in Eq.~(\ref{eq:aerosol_scatter}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+parametric phase function as in \cref{eq:aerosol_scatter}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Image Capture}
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(Eqs.~\ref{eq:beer-lambert},\ref{eq:betair},\ref{eq:tautotal}), the
-radiant power contributed by the voxel is
+(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
+contributed by the voxel is
 \begin{equation}
@@
   [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
-  e^{-[\tau_c(k)]}
-  \;\;.
+  e^{-\tau_c(k)}
+  \;\;,
   \label{eq:ick}
 \end{equation}
-A column-stack vector of all voxel contributions is
+where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
+of all voxel contributions is
 \begin{equation}
@@
 atmosphere. The cone includes some voxels, intersects with some other
-voxels, and oblivious to all the rest.  Thus light power captured at a
-pixel is weighted sum of the power $p_c(k)$ from all voxels: most
-voxels have null weight, since they fall outside the pixels's conic
-field of view, while the rest of the voxels are aggregated.
-
-This linear sum is formulated by a matrix operation over ${\bf
-  p}_c$. The measured image is column-stacked to a vector $N_{\rm
-  pix}$ long. It is given by
+voxels, and oblivious to all the rest~(\cref{fig:projection}b).
+\begin{figure}
+  \centering
+  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
+  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
+    above it on a SR. The scattered radiance from voxel $k$ is then
+    attenuated by voxels below it on a LOS to camera $c$.  [b] An
+    image pixel captures light emanating in a cone in space. Voxels
+    that fully or partially fall in this cone are sensed by the
+    pixel.}
+  \label{fig:projection}
+\end{figure}
+Thus light power captured at a pixel is a weighted sum of the power
+$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
+operation over ${\bf p}_c$. The measured image is column-stacked to a
+vector $N_{\rm pix}$ long. It is given by
 \begin{equation}
@@
 \end{equation}
-The $N_{\rm pix}\times N_{\rm voxels}$ sparse matrix ${\vect{\Pi}}_c$
-expresses {\em projection} of light into camera $c$. For pixel
-$\Theta$ and voxel $k$, there is an {\em intersection} volume ${\bf
-  V}_c(\Theta,k)$ between the cone volume of the pixel's field of
-view, and the voxel, as illustrated in Fig.~\ref{fig:projection}.
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/sensor.pdf_tex}}
-  \caption{\small An image pixel captures light emanating in a cone in
-    space. Voxels that fully or partially fall in this cone are sensed
-    by the pixel. Factoring out scattering and attenuation (which are
-    dealt elsewhere in our analysis), the relative contribution of
-    each voxel depends on its distance and intersection with the
-    cone. This is formalized a matrix-vector operation.}
-  \label{fig:projection}
-\end{figure}
-The corresponding element in the matrix ${\vect{\Pi}}_c$ is
-\begin{equation}
-  \Pi_c(\Theta,k)=
-  % \frac{a}{|{\bf V}(k)|}
-  a
-  \iiint_{{\bf V}_c(\Theta,k)}
-  \frac{1}{[R({\bf v})]^2} d{\bf v}
-  \;\;,
-  \label{eq:Pc}
-\end{equation}
-where $a$ is the effective area of the camera lens.
-% and $|{\bf V}(k)|$ is the volume of voxel $k$.
-The distance $R({\bf v})$ is measured between the camera and an
-infinitesimal volume element at ${\bf v}\in {\bf V}_c(\Theta,k)$.
-
-Combining Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the
-captured image is thus
+
+Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
 \begin{align}
@@
 \end{align}
-Most often, there is only a single type of aerosol over a
-scene. Hence, the three-element vector $[{\sigma}^{\rm
-  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
-the density distribution ${\bf n}$ is variable. Then,
-Eq.~(\ref{eq:bigIc}) degenerates to
+
+To simplify the case in study, let us assume there is only a single
+type of aerosol over a scene. Hence, the three-element vector
+$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
+the scene, but the density distribution ${\bf n}$ is variable. Then,
+\cref{eq:bigIc} degenerates to
 \begin{align}
@@
       air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
-  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
-  \nonumber \\
-  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
+  [\tilde{\vect{\alpha}}^{\rm air}_c + 
   \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subfile{monte_carlo}
+
+\section{Monte Carlo Simulations}
+\label{sec:monte-carlo-simul}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Inverse Problem}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Unknowns and Prior Knowledge}
@@
 
-Prior knowledge reduces the unknowns. Sec.~\ref{sec:captured-image}
-mentions a prior: in many cases a single aerosol type dominates a
-scene. Then, the three-element vector $[\varpi^{\rm
-  aerosol},{\sigma}^{\rm aerosol},g]$ is rather spatially uniform. In
-such cases, the set of unknowns reduces to $ {\cal V}= \left\{ {\bf
-    n}, \left\{ {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
-      aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda} \right\} $ and
-\mbox{$|{\cal V}|=N_{\rm voxels}+3N_{\rm spectral}$}.
-
-Furthermore, the elements in the aerosol characteristics set $\left\{
-  {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
-    aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda}$ is not
-arbitrary, since all these characteristics have physical origins. This
-set is constrained to comply with what nature allows (aerosol
-classes).  This significantly constrains the unknown
-characteristics. State-of-the-art aerosol retrieval, as used by NASA's
-MISR products indeed employ an aerosol-class prior. Types of aerosol
-mixtures are discretized to $N_{\rm models}=74$
-classes~\cite{Martonchikc}, called {\em models}. Each class $m$
-represents aerosols having a distinct characteristics set.  State of
-the art retrieval is 1D (only vertical radiative transfer per large
-areas). Nevertheless, we use this prior in our 3D problem. Then, the
-set of unknowns reduces to $ {\cal V}= \left\{ {\bf n},m \right\}$ and
-\mbox{$|{\cal V}|=N_{\rm voxels}+N_{\rm models}$}.
-
-The atmosphere is photographed from $N_{\rm views}$ viewpoints. Each
-photograph provides $N_{\rm pix}$ measurements (pixels), {\em
-  including} their possible division to color channels. Hence, the
-data at our disposal comprises $N_{\rm views}N_{\rm pix}$
-measurements.  For the recovery task to be well-posed, it is necessary
-that $N_{\rm views}N_{\rm pix}>|{\cal V}|$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Prior knowledge reduces the unknowns. For simplicity we assume a
+single aerosol type dominates a scene. Furthermore, in the following
+section we assume that we know the type of the particle. Hence, we
+focus here on retrieving ${\bf n}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Objective Function}
@@
 
-The inverse problem (tomography) seeks recovery of the 3D aerosol
-distribution in the atmosphere. From
-Eqs.~(\ref{eq:alpha_matrix},\ref{eq:bigIc},\ref{eq:bigIA},\ref{eq:calV}),
-the images $\{ {\bf i}_c\}_{c=1}^{N_{\rm views}}$ depend on the
-variables set ${\cal V}$, particularly on the unknown field ${\bf
-  n}$. The recovery task is phrased as optimization of an objective
-function, that fits the image-formation
-model~(\ref{eq:bigIc},\ref{eq:bigIA}) to measured photographs $\{ {\bf
-  i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$:
-\begin{equation}
-  \label{eq:mingenobjective}
-  \hat{\cal V} = \argmin_{{\cal V}\in {\cal C}} F({\cal V})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:genobjective}
-  F({\cal V}) = \sum_{c=1}^{N_{\rm views}}
-  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\cal V})\| + {\rm Regularization}({\cal V})
-  \;.
-\end{equation}
-Here ${\cal C}$ is a constraints set, which encapsulates part of the
-prior knowledge, as well as nonnegativity bounds, while $\|~\|$ is
-some error-distance measure.  Here ${\rm Regularization}({\cal V})$
-describes spatial regularization terms of the variables, such as
-smoothness, or a blobby or layered structure.
-
-Spatial regularization can help overcome lack of data, if $N_{\rm
-  views}$ is too small, and it is definitely helpful. In this work,
-however, we formulate and demonstrate the basic principle of our
-tomography task, hence we proceed without regularization. Relying on
-prior knowledge described in Sec.~\ref{sec:prior}, the problem
-complexity is by far dominated by the $N_{\rm voxels}$-large array
-${\bf n}$, which is continuously valued. Hence, we focus here on
-retrieving ${\bf n}$ through continuous optimization. Relying on the
-least-squares measure, we seek:
+The recovery task is phrased as optimization of an objective function,
+that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
+measured photographs $\{ {\bf i}^{\rm measured}_c\}_{c=1}^{N_{\rm
+    views}}$:
 \begin{equation}
@@
 \end{equation}
-This is solved using standard optimization tools. Fast optimization
-that leads to to local minima ($F$ is not convex) exploits the
-gradient of $F$.
-
-Since our model uses close-form expressions, $F$ is
-differentiable. The gradient of $F$ with respect to ${\bf n}$ is
+This is solved using standard optimization tools.  The gradient of $F$
+with respect to ${\bf n}$ is
 \begin{align}
@@
 Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
-vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
-this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
-viewpoint $c$) with variation of the density at voxel $k$, i.e.,
-$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.
-
-Denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$ into a
-diagonal matrix, whose main diagonal elements correspond to the
-elements of $\vect{v}$.  A close-form expression of our Jacobian is
+vector ${\bf i}_c$ with respect to ${\bf n}$. A close-form expression
+of our Jacobian is
 \begin{align}
@@
 \end{align}
-For a detailed derivation of
-Eqs.~(\ref{eq:gradient2},\ref{eq:gradient3}), we refer the reader to
-the supplementary material.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
+refer the reader to \cref{sec:gradient-derivation}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Simulations}
@@
 
-To test the model, we made simulations based on atmospheric models in the literature. Here are the details.\\
+To test the model, we made simulations based on atmospheric models in
+the literature. Here are the details.
 
@@
 from~\cite{BBradiance,sun_composition}, with respective red-green-blue
-ratios of
-$L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm B}=255:236:224$.\\
-
-\noindent{\bf Dimensions}: The domain of sky we simulate and recover has area of $50\times 50$km, and it extends from the ground up to altitude of 10km.
-This volume is divided to a $50\times50\times100$ grid, where each voxel has area of $1\times1$km and vertical thickness of 100 meters.
-The dimension of the problem is thus $250,000$ variables.\\
+ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
+  B}=255:236:224$.
+
+\noindent{\bf Dimensions}: The domain of sky we simulate and recover
+has area of \SI{50 x 50}{\km}, and it extends from the ground up to
+altitude of \SI{10}{\km}. This volume is divided to a \num{50 x 50 x
+  100} grid, where each voxel has area of \SI{1 x 1}{\km} and vertical
+thickness of \SI{100}{\metre}. The dimension of the problem is thus
+$250,000$ variables.
 
@@
   aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
-  aerosol}_{\rm B}]=[16.5,16.2,15.9][1/\mu m^2]$.  Its
-single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all channels.
+  aerosol}_{\rm
+  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.
+Its single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all
+channels.
 
@@
 \end{align}
-where $H^\mathrm{aerosol}=2\ km$. This expresses a general trend of
-reduced atmospheric density with height. Here the mean free path (MFP)
-of the aerosols layer at sea level was set to $\mathrm{MFP^{sea
-    level}}=1/5~{\rm[1/km]}$.
-% is a typical characteristic thickness of the aerosol
-% layer~\cite{Levi1980}.
+where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
+of reduced atmospheric density with height. Here the mean free path
+(MFP) of the aerosols layer at sea level was set to \linebreak
+\mbox{$\mathrm{MFP^{sea level}}=1/5$~\si{\per\km}}.
+
+\todo[inline]{Update the quantities above especially the visibility or
+  fix the images}
 
@@
 \end{equation}
-As an example, we created a {\em Haze Blobs} scene
-(Fig.~\ref{fig:simulation1}) using two ellipsoid blobs: \begin{figure}
-  \centering
+As an example, we created a {\em Haze Blobs} scene using two ellipsoid
+blobs (\cref{fig:simulation1}a):
+\begin{figure} \centering
   \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
-  \caption{\small Simulated 3D aerosol distribution composed of {\em
-      Haze Blobs}. Its reconstruction is shown in
-    Fig.~\ref{fig:front}. Color represents aerosol density. The
-    density units are $10^{15}~{\rm particles}/{\rm cm}^3.$}
+  \caption{\small [a] Simulated 3D aerosol distribution composed of
+    {\em Haze Blobs}. [b] Its reconstruction. Color represents aerosol
+    density. The density units are $10^{15}~{\rm particles}/{\rm
+      cm}^3.$}
   \label{fig:simulation1}
 \end{figure}
-the first is centered at altitude $3.3km$, and has horizontal width of $32km$ and vertical thickness of $2.8km$.
-The second ellipsoid is centered at altitude $6.6km$, and has lateral width of $24km$ and vertical thickness of $2.1km$.
-Note that the horizontal widths are much larger than the vertical ones.
-This is consistent with scales of atmospheric aerosol distributions.\\
+the first is centered at altitude \SI{3.3}{\km}, and has horizontal
+width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
+second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
+lateral width of \SI{24}{\km} and vertical thickness of
+\SI{2.1}{\km}. Note that the horizontal widths are much larger than
+the vertical ones. This is consistent with scales of atmospheric
+aerosol distributions.
 
 \noindent{\bf Cameras}: Each ground-based camera has a hemispherical
-field of view, capturing the entire sky from its viewpoint. We used 95
-viewpoints on a grid, each view $\approx 4.4$km from its neighbors.
-The resolution of each camera is low: $128\times 128$ pixels,
-expressing the fact that cloudless (yet hazy) sky images are rather
-smooth, hence there is no need for high image resolution. Each pixel
-has full-well depth of 40000 electrons, which corresponds to the
+field of view, capturing the entire sky from its viewpoint. We used
+100 viewpoints on a grid, each view \SI{\approx 4.4}{\km} from its
+neighbors.  The resolution of each camera is low: \num{128 x 128}
+pixels, expressing the fact that cloudless (yet hazy) sky images are
+rather smooth, hence there is no need for high image resolution. Each
+pixel has full-well depth of 40000 electrons, which corresponds to the
 brightest pixel value. Each measurement has photon noise, which is
 Poissonian distributed, according to each image-pixel value $i_c$ and
-the full-well depth. For example, Fig.~\ref{fig:simulation-results1}
-shows two modeled photographs
+the full-well depth. For example, \cref{fig:simulation-results1}a
+shows an example of a modeled photograph
 \begin{figure}
   \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/ref_images.pdf}}
-  \caption{\small Rendered photographs (contrast enhanced)
-    corresponding to different viewpoints, of sky that includes {\em
-      Haze Blobs}. A yellow dot marks the Sun location. Dashed white
-    circles mark elevation angles.}
+  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
+  \caption{\small [a] Photograph of a sky that includes {\em Haze
+      Blobs} rendered using the single-scattering model.  A yellow dot
+    marks the Sun location. Dashed white circles mark elevation
+    angles.  [b] Photograph of the same sky and view point rendered
+    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
   \label{fig:simulation-results1}
 \end{figure}
-of the  {\em Haze Blobs} scene that corresponds to Fig.~\ref{fig:simulation1}.\\
+of the {\em Haze Blobs} scene that corresponds to
+\cref{fig:simulation1}a.
 
@@
 that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
-with 8GB
-DDR3 memory per core.
-Out of it, we used 8 nodes, corresponding to 96 cores.
-Each core was dedicated to rendering a modeled image (in each interaction) as if captured by one of the 95 cameras.
-Each iteration (varying the model according to the gradient-based algorithm and varying all the rendered images) took $\approx 7$sec.\\
+with 8GB DDR3 memory per core. Out of it, we used 8 nodes,
+corresponding to 96 cores. Each core was dedicated to rendering a
+modeled image (in each interaction) as if captured by one of the 95
+cameras. Each iteration (varying the model according to the
+gradient-based algorithm and varying all the rendered images) took
+\SI{\approx 7}{\second}.
 
@@
   n}=0$. Satisfactory convergence occurred in several thousand
-iterations, taking a couple of hours to complete in total. For
-example, Fig.~\ref{fig:objective} shows
-\begin{figure}[t]
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/objective.pdf}}
-  % \includegraphics[width=\columnwidth]{images/objective.pdf}
-  \caption{\small The decay of $\log F({\bf n})$ with the iteration
-    index.}
-  \label{fig:objective}
-\end{figure}
-the progression of the objective as a function of the iteration
-number, when recovering the the {\em Haze Blobs} scene.
-
-% 26, 48, 1320, 590
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Results}
+iterations, taking a couple of hours to complete in total.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
 \label{sec:optimization-results}
@@
 An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in Fig.~\ref{fig:simulation1}, while the
-recovered 3D distribution is visualized in Fig.~\ref{fig:front}. The
+distribution is shown in \cref{fig:simulation1}a, while the recovered
+3D distribution is visualized in \cref{fig:simulation1}b. The
 distributions appear consistent, though there are errors that stem
@@
 
-We created a {\em Haze Front} scene. Fig.~\ref{fig:simulation2}a shows
-an iso-surface visualization of this distribution.
+We created a {\em Haze Front} scene. \cref{fig:simulation2}a shows an
+iso-surface visualization of this distribution.
 \begin{figure}
@@
 Here an ellipsoid degenerated to an elliptic cylinder that partly
-enters the analyzed volume. It is centered at altitude $5km$, has
-vertical thickness of $4km$ and length of $32km$ (only part of which
-enters the volume). The haze front stretches across the width of the
-volume.  Fig.~\ref{fig:simulation2}b visualizes the recovered 3D
-distribution of this scene. For the {\em Haze Front},
+enters the analyzed volume. It is centered at altitude \SI{5}{\km},
+has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
+part of which enters the volume). The haze front stretches across the
+width of the volume.  \cref{fig:simulation2}b visualizes the recovered
+3D distribution of this scene. For the {\em Haze Front},
 $\epsilon=0.198$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gradient Derivation}
+\label{sec:gradient-derivation}
+
+Here we detail the derivation of the gradient of the objective
+function:
+\begin{equation}
+  \label{eq:objectiveA}
+  F({\bf n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
+\end{equation}
+Here ${\bf i}^{\rm measured}_c$ is the image captured by camera $c$
+and ${\bf i}_c({\bf n})$ is an image modeled from the viewpoint of
+camera $c$ according to the density distribution ${\bf n}$. In
+\cref{sec:captured-image} article we show that ${\bf i}_c({\bf n})$
+can be expressed by
+\begin{align}
+  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
+      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
+  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
+  \nonumber \\
+  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
+  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
+  \label{eq:bigIA}
+\end{align}
+
+The gradient of $F$ with respect to ${\bf n}$ is
+\begin{align}
+  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
+    measured}_c - {\bf i}_c({\bf n})] \;.
+  \label{eq:gradient1}
+\end{align}
+Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
+vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
+this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
+viewpoint $c$) with variation of the density at voxel $k$, i.e.,
+$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.
+
+In order to describe the derivation of the Jacobian ${\bf J}_{{\bf
+    i}_c}({\bf n})$, we first show some results relating to
+differentiation. Let $\vect{n}$ be a vector of length $q$. Let
+$\vect{g}(\vect{n})$ be a vector function: it outputs a vector of
+length $r$. Let $\mat{B}$ be a $q \times r$ matrix and
+\begin{align}
+  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
+  \label{eq:example1}
+\end{align}
+In \cref{eq:example1}, the exponential is element-wise (not raising an
+operator to some power). Then
+\begin{align}
+  \label{eq:partial2}
+  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
+  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
+\end{align}
+Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
+into a diagonal matrix, whose main diagonal elements correspond to the
+elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
+\begin{align}
+  \label{eq:partial4}
+  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+      {\bf D}_c {\bf n})}}
+  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+      {\bf D}_c {\bf n})}}
+\end{align}
+In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
+known and constant.
+
+To calculate the derivative of the Hadamard product in \cref{eq:bigIA}
+we first note the following: Let $\vect{u}(\vect{n})$ be a vector
+function that outputs a vector of length $r$. Let $\mat{B}$ be a $r
+\times q$ matrix. Then,
+\begin{align}
+  \label{eq:partial1}
+  \PartDeriv{\transpose{\mat{B}} (\vect{g} \odot \vect{u})}{\vect{n}}
+  = \left[ \PartDeriv{\vect{g}}{\vect{n}} \OpDiag{\vect{u}} +
+    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{g}} \right] \mat{B}.
+\end{align}
+Then,
+\begin{align}
+  \label{eq:partial3}
+  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n}}{\vect{n}}
+  =
+  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
+  \nonumber \\
+  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
+  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
+\end{align}
+
+Based on \cref{eq:partial4,eq:partial1,eq:partial3} we can derive a
+close-form expression for the Jacobian of \cref{eq:bigIA}:
+\begin{align}
+  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
+  ,
+  \label{eq:gradient2}
+\end{align}
+where
+\begin{align}
+  \label{eq:gradient3}
+  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
+  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bf n}
+    ]} \nonumber \\
+  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
+\end{align}
 
 \end{document}
-
-%
-% David brady
-% Sing Bing Kang
-%
-% keep article 20 and remove all other citations
-%

### 2013-07-11 monte_carlo.tex
Copied whole sections from the phd.tex.

\documentclass[article.tex]{subfiles} 
\begin{document}

\section{Monte Carlo Simulations}
\label{sec:monte-carlo-simul}

\todo[inline]{Write the Monte-Carlo section}

\end{document}
% -----------------------------------------------------------

### 2013-07-14 monte_carlo.tex
monte carlo first commit. Just for testing.

@@
 
-\todo[inline]{Write the Monte-Carlo section}
+We used Monte Carlo (MC) photon tracing, and implemented the algorithm with matlab code, using Parallel for loop (parfor loop, with 8 workers in our case), to accelerate the simulations. 
+We simulate backward MC, it means that we trace photons from the detector to source.
+In our case the detector is the equidistant camera, and the source is the sun.
+We consider sun parallel illuminate the top of the atmosphere, so the photons who exit the atmosphere in sun direction, it’s the only photons that contribute to the image.
+We don't consider periodic atmosphere so we stop tracing photons that exit the atmosphere from the sides (except photons who goes to the sun), and stop tracing photons who hits the ground.
+Photons absorption by atmospheric particles we treat with Russian roulette method~\cite{Buras2011}.
+The simulation requires camera definition; in this definition, at each pixel on image plane, we calculate the leaving photon direction (MC model is backward).
+In standard simulation we have 128x128 pixels and we shoot 10000 photons from each pixel, and in each pixel we apply Uniform Supersampling [] .
+After the photon leaves the camera in determined direction, it starts his traveling in the atmosphere.
+As mentioned before, the atmosphere is inhomogeneous media, and we divide this media to uniform grid.
+When photon travel in the media it passes a lot of grid cells, and the calculations of photon path becomes very
+To accelerate MC simulation we use local estimation (LE) method []. In this method a Weight of LE calculated at each scatter event 
+ We prepare a pre-computed table that contains the probabilities that photon will scatter to the sun without any additional scattering
 

### 2013-07-15 article.tex
monte carlo first commit. Just for testing.
Split the theoretic background

@@
 
-\section{Theoretical Background}
-\label{sec:back}
-
-\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
-that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
-interacting with the irradiance. The volume includes many particles of
-this type. The denser the volume, the stronger is the extinction.  The
-density of the particles is $n$ (units
-\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
-  extinction coefficient} $\beta$ (units \si{\per\meter}) is
-\begin{align}
-  \beta= \sigma n \;.
-  \label{eq:extinctc}
-\end{align}
-The volume has infinitesimal length $dl$. Then, the relative portion
-of extinct SR irradiance is the unitless differential {\em optical
-  depth}
-\begin{align}
-  d\tau= \beta dl=\sigma n dl \;.
-  \label{eq:extinct}
-\end{align}
-The optical depth aggregates in extended propagation:
-\begin{align}
-  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
-  \label{eq:tau}
-\end{align}
-Through an attenuating volume, the {\em transmittance} exponentially
-decays with the optical depth:
-\begin{align}
-  t=\exp^{-\tau}
-  \label{eq:beer-lambert}
-\end{align}
-
-\noindent {\bf Scattering}: Interaction of a single particle with the
-irradiance is by absorption and scattering. The weight of scattering
-(to all directions), relative to the total extinction is given by the
-unitless {\em single scattering albedo} $\varpi$ of the particle. The
-{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
-\begin{align}
-  \alpha= \varpi\beta=\varpi \sigma n \;.
-  \label{eq:alph}
-\end{align}
-Scattering is generally anisotropic. Its angular distribution is
-determined by a {\em phase function} $P$. Part of the light scatters
-towards a camera's line of sight (LOS), as illustrated in
-\cref{fig:groundgrid}. The angle between the SR and LOS is the
-scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
-  scatter})$ is normalized: its integral over all solid angles is
-unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
-\si[sticky-per]{\per\meter\steradian}) is
-\begin{align}
-  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
-  = \varpi \sigma n P(\Phi^{\rm scatter}).
-  \label{eq:alphabasic}
-\end{align}
-
-The phase function is often approximated by a parametric expression,
-as the Henyey-Greenstein~\cite{Cornette1995} function\todo{Correct the Henyey-Greenstein function},
-\begin{align}
-  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
-    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
-  \label{eq:aerosol_scatter}
-\end{align}
-where $g$ is an {\em anisotropy parameter} and
-\begin{align}
-  \mu\equiv \cos \Phi^{\rm scatter}.
-  \label{eq:mu}
-\end{align}
-
-\noindent {\bf Air molecules}: Scattering by air molecules follows the
-{\em Rayleigh} model:
-\begin{align}
-  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
-  \label{eq:rayleighP}
-\end{align}
-and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
-off approximately exponentially with altitude, with a
-characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
-\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
-extinction and scattering by air molecules are modeled by
-\begin{align}
-  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
-  \frac{1.09 \times 10^{-3}}{\lambda^4}
-  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
-  \label{eq:rayleighbeta}
-\end{align}
+\subfile{theoretic_back}
 
@@
 
-\section{Monte Carlo Simulations}
-\label{sec:monte-carlo-simul}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-15 theoretic_back.tex
Split the theoretic background

\documentclass[article.tex]{subfiles} 
\begin{document}

\section{Theoretical Background}
\label{sec:back}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units
\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
  extinction coefficient} $\beta$ (units \si{\per\meter}) is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
\cref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
\si[sticky-per]{\per\meter\steradian}) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein~\cite{Cornette1995} function\todo{Correct the Henyey-Greenstein function},
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model:
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

\end{document}
% -----------------------------------------------------------

### 2013-07-22 article.tex
bf -> bm due to font problems (note that it is good only for math symbols and not for text)

@@
 and elevation angles (relative to the zenith and north) are
-encapsulated in the vector ${\bf{\Theta}}$.  A raw image is $i_{\bf
-  x}({\bf{\Theta}})$: a camera's location ${\bf x}$ is fixed, while
-any pixel in a frame represents an angle ${\bf{\Theta}}$.  The
-measured radiance in all locations ${\bf x}$ and angles
-${\bf{\Theta}}$ is the {\em lightfield} $I({\bf
-  x},{\bf{\Theta}})$. Individual images are slices of the lightfield.
+encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
+  x}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
+any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
+measured radiance in all locations ${\bm x}$ and angles
+${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
+  x},{\bm{\Theta}})$. Individual images are slices of the lightfield.
 
@@
   voxels}$ long. Aerosol densities and cross sections in all voxels
-are stored in the respective vectors ${\bf n}$ and
+are stored in the respective vectors ${\bm n}$ and
 $\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
-matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
+matrix ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
 $(k,q)$ is
@@
   \vect{\tau}_{\rm SR}^{\rm aerosol}=
-  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
-  (\vect{\sigma} \odot {\bf n})
+  {\bm D}^{\mathrm{Sun \rightarrow voxel}}
+  (\vect{\sigma} \odot {\bm n})
   \label{eq:tauSRvec1}
@@
   \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
-  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
-  (\vect{\sigma} \odot {\bf n})
+  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
+  (\vect{\sigma} \odot {\bm n})
   \label{eq:tauLOSvec1}
 \end{equation}
-Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
+Here ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
   voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
@@
 
-The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
-and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
+The fixed sparse matrices ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$
+and ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
 single matrix
 \begin{equation}
-  {\bf D}_c=
-  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
-  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
+  {\bm D}_c=
+  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
+  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
   \;\;.
@@
   \vect{\tau}_c= \vect{\tau}_c^{\rm air}
-  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
+  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
   \;\;.
@@
 \end{equation}
-This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
+This vector depends on the variables $\vect{\sigma}$ and ${\bm n}$
 (See~\cref{fig:projection}a).
@@
   \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
-  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
+  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
     g}(\vect{\Phi}^{\rm scatter}_c)
@@
 \end{align}
-The vector ${\bf g}$ column-stacks the anisotropy parameter of the
+The vector ${\bm g}$ column-stacks the anisotropy parameter of the
 phase function, in all voxels. We use this notation, to indicate a
@@
 \begin{equation}
-  {\bf p}_c= L^{\rm TOA}
+  {\bm p}_c= L^{\rm TOA}
   [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
@@
 $p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
-operation over ${\bf p}_c$. The measured image is column-stacked to a
+operation over ${\bm p}_c$. The measured image is column-stacked to a
 vector $N_{\rm pix}$ long. It is given by
 \begin{equation}
-  {\bf i}_c= {\vect{\Pi}}_c{\bf p}_c
+  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
   \;\;.
@@
 \begin{align}
-  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
     (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
-      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bf D}_c
-      (\vect{\sigma} \odot {\bf n})]} \right\}
+      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
+      (\vect{\sigma} \odot {\bm n})]} \right\}
   \label{eq:bigIc}
@@
 $[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
-the scene, but the density distribution ${\bf n}$ is variable. Then,
+the scene, but the density distribution ${\bm n}$ is variable. Then,
 \cref{eq:bigIc} degenerates to
 \begin{align}
-  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
-      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
+      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
   [\tilde{\vect{\alpha}}^{\rm air}_c + 
   \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
+    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
   \label{eq:bigIA}
@@
   \left\{
-    {\bf n},
+    {\bm n},
     \left\{
-      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bf g}_{\lambda}
+      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
     \right\}_{\lambda}
@@
 section we assume that we know the type of the particle. Hence, we
-focus here on retrieving ${\bf n}$.
+focus here on retrieving ${\bm n}$.
 
@@
 that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-measured photographs $\{ {\bf i}^{\rm measured}_c\}_{c=1}^{N_{\rm
+measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
     views}}$:
@@
   \label{eq:minobjectiveA}
-  \hat{\bf n} =
-  \argmin_{{\bf n}} F({\bf n})
+  \hat{\bm n} =
+  \argmin_{{\bm n}} F({\bm n})
 \end{equation}
@@
   \label{eq:objectiveA}
-  F({\bf n})
+  F({\bm n})
   = \sum_{c=1}^{N_{\rm views}}
-  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
+  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
 \end{equation}
 This is solved using standard optimization tools.  The gradient of $F$
-with respect to ${\bf n}$ is
+with respect to ${\bm n}$ is
 \begin{align}
-  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
-    measured}_c - {\bf i}_c({\bf n})] \;.
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] \;.
   \label{eq:gradient1}
 \end{align}
-Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
-vector ${\bf i}_c$ with respect to ${\bf n}$. A close-form expression
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression
 of our Jacobian is
 \begin{align}
-  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
   ,
@@
   \label{eq:gradient3}
-  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
+  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
   & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
       aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bf n}
+      scatter}_c) \odot{\bm n}
     ]} \nonumber \\
-  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
+  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
 \end{align}
@@
   \label{eq:ntrue}
-  {\bf n}^{\rm true}={\bf w}_1\odot {\bf w}_2  .
+  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
   \hspace{-0.05cm}
@@
 \noindent{\bf Optimization}: We used the L-BFGS-B
-algorithm~\cite{BFGS}. The algorithm was initialized by ${\bf
+algorithm~\cite{BFGS}. The algorithm was initialized by ${\bm
   n}=0$. Satisfactory convergence occurred in several thousand
@@
   \label{eq:ndiff}
-  \epsilon=\frac{\| \hat{\bf n}  - {\bf n}^{\rm true} \|_1}
-  {\| {\bf n}^{\rm true} \|_1} ,
+  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
+  {\| {\bm n}^{\rm true} \|_1} ,
   \hspace{-0.05cm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%  Appendix  %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \label{eq:objectiveA}
-  F({\bf n})
+  F({\bm n})
   = \sum_{c=1}^{N_{\rm views}}
-  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
+  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
 \end{equation}
-Here ${\bf i}^{\rm measured}_c$ is the image captured by camera $c$
-and ${\bf i}_c({\bf n})$ is an image modeled from the viewpoint of
-camera $c$ according to the density distribution ${\bf n}$. In
-\cref{sec:captured-image} article we show that ${\bf i}_c({\bf n})$
+Here ${\bm i}^{\rm measured}_c$ is the image captured by camera $c$
+and ${\bm i}_c({\bm n})$ is an image modeled from the viewpoint of
+camera $c$ according to the density distribution ${\bm n}$. In
+\cref{sec:captured-image} article we show that ${\bm i}_c({\bm n})$
 can be expressed by
 \begin{align}
-  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
-      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
+      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
   \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
@@
   \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
+    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
   \label{eq:bigIA}
@@
 
-The gradient of $F$ with respect to ${\bf n}$ is
+The gradient of $F$ with respect to ${\bm n}$ is
 \begin{align}
-  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
-    measured}_c - {\bf i}_c({\bf n})] \;.
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] \;.
   \label{eq:gradient1}
 \end{align}
-Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
-vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
-this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$. Element $(\Theta,k)$ of
+this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
 viewpoint $c$) with variation of the density at voxel $k$, i.e.,
-$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.
+$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.
 
-In order to describe the derivation of the Jacobian ${\bf J}_{{\bf
-    i}_c}({\bf n})$, we first show some results relating to
+In order to describe the derivation of the Jacobian ${\bm J}_{{\bm
+    i}_c}({\bm n})$, we first show some results relating to
 differentiation. Let $\vect{n}$ be a vector of length $q$. Let
@@
   \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
-      {\bf D}_c {\bf n})}}
+      {\bm D}_c {\bm n})}}
   {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
   \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
-      {\bf D}_c {\bf n})}}
+      {\bm D}_c {\bm n})}}
 \end{align}
@@
   \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n}}{\vect{n}}
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}}{\vect{n}}
   =
@@
 \begin{align}
-  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
   ,

### 2013-07-23 article.tex
bookmark (returned the theoretical background section into the main article)

@@
 recover this 3D medium using measured and modeled lightfields
-(Fig.~\ref{fig:front}).
-\begin{figure}[t!]
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/front_img.pdf}}
-  \caption{\small The sky is photographed from multiple viewpoints
-    using wide angle (hemispherical) cameras, in a very wide area. The
-    three dimensional distribution of aerosols in the atmosphere
-    affects the images. This distribution is then recovered by a
-    dedicated tomography formulation.}
-  \label{fig:front}
-\end{figure}
-
+(Fig.~\ref{fig:groundgrid}).
+\begin{figure*}[t!]
+  \begin{center}
+    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
+  \end{center}
+  \caption{\small Lightfield imaging through a volumetric distribution
+    in the atmosphere, using ground-based cameras. Our tomographic
+    reconstruction follows the acquisition. The atmosphere is analyzed
+    in a voxel grid.}
+  \label{fig:groundgrid}
+\end{figure*}
 Projecting this large object to various directions is similar to
@@
 
-\subfile{theoretic_back}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Image Acquisition Principle}
-\label{sec:setup}
+\section{Related Work}
+\label{sec:literature}
+
+{\em Lightfield}, or {\em integral}
+imaging~\cite{Ng2006,bishop,Ng1948}, samples the radiance distribution
+in location and direction. It has so far been used in small-scale
+setups. Our proposed research deals with huge scale, up to Earth's
+size. Capturing the lightfield in very large scales requires uncommon
+sensors. Sampling Earth both spatially and angularly is done by the
+Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
+space (\cref{fig:misr}), the Airborne Multiangle SpectroPolarimetric
+Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
+airborne instruments.
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.90\textwidth]{misr.pdf}
+  \caption{\small{[Left] NASA's MISR instrument, developed by the Jet
+      Propulsion Laboratory (JPL), provides multiangular,
+      multispectral images of Earth.  It scans Earth from 9 view
+      angles, at resolution of $\approx 300$m.  [Right] A series of
+      MISR images from different viewing angles showing an assortment
+      of clouds over Florida.}  }
+  \label{fig:misr}
+\end{figure}
+
+Dehazing strives to improve quality of images taken through a
+semi-transparent medium, be it murky liquid~\cite{kim,fuchs},
+haze~\cite{fattal,Hschechner2}, or fog~\cite{narasimhan2}.  In remote
+sensing~\cite{kokhan}, imaging through air is associated with {\em
+  atmospheric correction}, based on {\em aerosol retrieval}.  In this
+methods the medium is usually assumed to be uniform or at least
+plane-parallel.  We, however, seek 3D recovery.  Another major
+difference is that these methods see the translucent medium as a
+disturbance that algorithms need to overcome, while in our research it
+is the medium that we want to recover.
+
+Computed Tomography (CT) refers to the reconstruction of a 3D object
+from a collection of projections of the object using any kind of
+penetrating radiation. CT finds wide use in medical imaging but is
+also valuable in other scientific fields, like
+geophysics~\cite{Kazahaya2008}, material science~\cite{Baruchel2000},
+astrophysics, and more.  Imaging of gaseous materials is also the
+target of extensive CT research~\cite{Price2001,Cosofret2009}. CT is
+based on an image formation model that describes the physical process
+underlying the projected measurements.  Most image formation models
+assume either absorption or emission processes. Other image formation
+models assume dominant diffusion by scattering~\cite{Boas2001}.
+
+CT uses several different methods for reconstructing the underlying
+medium. Transform algorithms are based on the Fourier and Radon
+transforms. Both relate the projection (or its Fourier transform) to
+the medium (or its Fourier transform). Solving for the medium involves
+calculating the inverse transform in an iterative process.  These
+algorithms assume a linear image formation model and require large
+amount of projections to give reasonable results. The simultaneous
+algebraic reconstruction technique
+(SART)~\cite{KakAvinashC.andSlaney2001} is another common method which
+is used when the image formation model is too big for explicit matrix
+representation. Stochastic Tomography~\cite{gregson} uses a different
+approach where the reconstruction is done in the space of projections
+using a probabilistic process based on random walk. This bypasses the
+need to discretize the signal, usually represented over a grid, and
+the use of large matrices to represent the formation model.
+
+Our research topic is closely related to optical
+tomography~\cite{Arridge}. Optical tomography uses light to visualize
+tissue, usually from close range.  Due to the highly scattering nature
+of biological tissue, optical tomography uses diffusive approximation
+in the image formation model.  Another method, based on scattering, is
+the X-Ray Scatter CT~\cite{Aviles2011} which measures the absorption
+and scattering coefficients of the medium separately.
+
+However, the formulation of our problem is {\em different} than prior
+situations. Most tomography setups have a controlled and/or
+multidirectional radiation source~\cite{messer}. In contrast, our
+source is the uncontrolled, unidirectional Sun. Moreover, typical
+tomography relies on a linear model: the pixel value is a linear
+combination of components along a line of sight (LOS), or a
+multiplicative combination which is linearized by a logarithm.
+However, photographs of the atmosphere are a mixture of {\em
+  scattering}, and absorption. The model turns out to be {\em
+  nonlinear, yet tractable}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Theoretical Background}
+\label{sec:theor-backgr}
+
+\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
+that includes particles of a certain type.  Each particle has an {\em
+  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
+interacting with the irradiance. The volume includes many particles of
+this type. The denser the volume, the stronger is the extinction.  The
+density of the particles is $n$ (units
+\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
+  extinction coefficient} $\beta$ (units \si{\per\meter}) is
+\begin{align}
+  \beta= \sigma n \;.
+  \label{eq:extinctc}
+\end{align}
+The volume has infinitesimal length $dl$. Then, the relative portion
+of extinct SR irradiance is the unitless differential {\em optical
+  depth}
+\begin{align}
+  d\tau= \beta dl=\sigma n dl \;.
+  \label{eq:extinct}
+\end{align}
+The optical depth aggregates in extended propagation:
+\begin{align}
+  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
+  \label{eq:tau}
+\end{align}
+Through an attenuating volume, the {\em transmittance} exponentially
+decays with the optical depth:
+\begin{align}
+  t=\exp^{-\tau}
+  \label{eq:beer-lambert}
+\end{align}
+
+\noindent {\bf Scattering}: Interaction of a single particle with the
+irradiance is by absorption and scattering. The weight of scattering
+(to all directions), relative to the total extinction is given by the
+unitless {\em single scattering albedo} $\varpi$ of the particle. The
+{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
+\begin{align}
+  \alpha= \varpi\beta=\varpi \sigma n \;.
+  \label{eq:alph}
+\end{align}
+Scattering is generally anisotropic. Its angular distribution is
+determined by a {\em phase function} $P$. Part of the light scatters
+towards a camera's line of sight (LOS), as illustrated in
+\cref{fig:groundgrid}. The angle between the SR and LOS is the
+scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
+  scatter})$ is normalized: its integral over all solid angles is
+unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
+\si[sticky-per]{\per\meter\steradian}) is
+\begin{align}
+  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
+  = \varpi \sigma n P(\Phi^{\rm scatter}).
+  \label{eq:alphabasic}
+\end{align}
+
+The phase function is often approximated by a parametric expression,
+as the Henyey-Greenstein~\cite{Cornette1995} function,
+\begin{align}
+  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
+    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
+  \label{eq:aerosol_scatter}
+\end{align}
+where $g$ is an {\em anisotropy parameter} and
+\begin{align}
+  \mu\equiv \cos \Phi^{\rm scatter}.
+  \label{eq:mu}
+\end{align}
+
+\noindent {\bf Air molecules}: Scattering by air molecules follows the
+{\em Rayleigh} model:
+\begin{align}
+  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
+  \label{eq:rayleighP}
+\end{align}
+and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
+off approximately exponentially with altitude, with a
+characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
+\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
+extinction and scattering by air molecules are modeled by
+\begin{align}
+  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
+  \frac{1.09 \times 10^{-3}}{\lambda^4}
+  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
+  \label{eq:rayleighbeta}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Methodology}
+\label{sec:methodology}
 
@@
 type of aerosols, per voxel.
-\begin{figure*}[t!]
-  \begin{center}
-    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
-  \end{center}
-  \caption{\small Lightfield imaging through a volumetric distribution
-    in the atmosphere, using ground-based cameras. Our tomographic
-    reconstruction follows the acquisition. The atmosphere is analyzed
-    in a voxel grid.}
-  \label{fig:groundgrid}
-\end{figure*}
 Earth's radiation is sampled both spatially and angularly from
@@
 
-\section{Forward Model}
-\label{sec:skymodel}
+\section{Single-Scattering Model}
+\label{sec:single-scatt-model}
 
@@
   = \sum_{c=1}^{N_{\rm views}}
-  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
-\end{equation}
-This is solved using standard optimization tools.  The gradient of $F$
-with respect to ${\bm n}$ is
+  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2 + \eta \cdot \Psi({\bm n})
+\end{equation}
+Here $\Psi({\bm n})$ is a regularization term that expresses some
+prior knowledge on the solution and $\eta$ is the regularization
+coefficient.  We enforce smoothness of the solution by using the
+\emph{Laplacian} operator.
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
+\end{equation}
+We solve~\cref{eq:minobjectiveA} using standard optimization tools.
+The gradient of $F$ with respect to ${\bm n}$ is
 \begin{align}
@@
   \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] \;.
+    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
+  \nabla^2\nabla^2{\bm n} \;.
   \label{eq:gradient1}
@@
 Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression
-of our Jacobian is
+vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
+symmetry of the \emph{Laplacian} operator. A close-form expression of
+our Jacobian is
 \begin{align}

### 2013-07-23 article.tex
bookmark

@@
   \caption{\small Lightfield imaging through a volumetric distribution
-    in the atmosphere, using ground-based cameras. Our tomographic
-    reconstruction follows the acquisition. The atmosphere is analyzed
-    in a voxel grid.}
+    in the atmosphere, using ground-based cameras.}
   \label{fig:groundgrid}
@@
 
-The atmosphere has a non-uniform distribution of scattering
-aerosols. We seek to recover this 3D volumetric distribution. To solve
-this problem, we formulate a process analogous to tomographic
-reconstruction. The scene is projected to multiple directions. Thus, a
-system captures integrated radiance as a function of direction and 2D
-projected location. Any voxel in the atmosphere contributes to the
-integrated radiance in multiple directional measurements
-(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
-number of constraints, to recover the distribution: the density and
-type of aerosols, per voxel.
-Earth's radiation is sampled both spatially and angularly from
-space~\cite{breon,diner,Martonchikc,vanMol}. However, current
-multiview spaceborne systems are very coarse. For example, aerosol
-retrieval in the most complex instrument, MISR, requires spatial
-blocks that are about $17\times 17$km wide, each observed from just 9
-views along-track. This practically leads to vertical radiative
-transfer analysis, degenerating atmospheric analysis to
-1D. Experimental airborne instruments under
-development~\cite{baxter,dinerDavis10} may provide better, if still
-coarse resolution once they are operational.
-
 We believe that high resolution atmospheric recovery can be achieved
@@
   Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-sky-cameras, looking upwards and capturing the sky lightfield.
-Moreover, satellites image close to the orbit track (a 1D array of
-viewpoints). In contrast, land-based cameras can form a 2D set of
-viewpoints~\cite{DBLP:journals/pieee/SnavelySGSS10} as easy or hard as
-a 1D grid~\cite{Joshi06naturalvideo}. However, before designing and
-setting up such a very large scale system requires assessment of many
-details that had not been explored. These include camera
-specifications needed to recover typical distributions. Hence, a major
-theoretic and numerical research phase is ahead.
-
-This paper takes the first step, of formulating this principle and
+sky-cameras, looking upwards and capturing the sky lightfield.  This
+paper takes the first step, of formulating this principle and
 demonstrating feasibility using realistic simulations. The formulation
@@
 from satellites, for future spaceborne instruments of this capacity.
+
+We simulate image acquisition using Monte Carlo simulations
+(\cref{sec:monte-carlo-simul}).  Monte carlo model multiple scattering
+and therefore enable simulating realistic scenarios. Our
+reconstruction algorithm is based on the Single-Scattering model
+(\cref{sec:single-scatt-model}). The Single-Scattering approximation
+enables state the solution to the Radiative Transform in a closed
+form. This closed is beneficial to us as it enables us to invert the
+model and thus recover the underlying atmosphere
+(\cref{sec:inverse-problem}).
 
@@
 
-\subfile{monte_carlo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Inverse Problem}
@@
 
+\section{Monte Carlo RT}
+\label{sec:monte-carlo-simul}
+
+Monte Carlo (MC) methods enable rigorous modeling of photon
+propagation in the atmosphere. The radiative transfer is expressed as
+probability distributions which describe the distance travelled by the
+photon between scatterings and the angle of deflection at each
+scatter.  This enables simulating multiple scattering and produce
+realistic results.  MC simulations can be made arbitrarily accurate by
+increasing the number of photons.  Another advantage of the MC methods
+is that they are highly parallelable.
+
+The MC simulations use the same atmosphere grid described in
+\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
+traced from the detector to the sun. Photons are emitted from each
+pixel of the camera in the direction determined by the camera
+model. The optical distance that the photon travels before scattering
+is determined according to the Beer-Lambert law~\cref{eq:beer-lambert}
+and the inversion sampling method. Once the optical distance is
+determined the ``real'' distance is determined by summing the optical
+depth of the discrete voxels (\cref{sec:optical-depth}) along the
+photon direction till the desired optical distance is reached.  At
+each scattering event, first the type of aerosol is determined by
+sampling the different aerosols distributions inside the voxel. The
+new direction is determined by inverse sampling the phase function of
+the relevant aerosols: Rayleigh, \cref{eq:rayleighP} or
+Henyey-Greenstein \cref{eq:aerosol_scatter}.  To accelerate the MC we
+use the local estimation (LE) method.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Simulations}
@@
 has area of \SI{50 x 50}{\km}, and it extends from the ground up to
-altitude of \SI{10}{\km}. This volume is divided to a \num{50 x 50 x
-  100} grid, where each voxel has area of \SI{1 x 1}{\km} and vertical
-thickness of \SI{100}{\metre}. The dimension of the problem is thus
-$250,000$ variables.
+altitude of \SI{10}{\km}. This volume is divided into a rectilinear
+grid. We used different grid sizes from \num{50 x 50 x 100} grid,
+where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
+\SI{100}{\metre} and down to num{10 x 10 x 20} grid, where each voxel
+has area of \SI{5 x 5}{\km} and vertical thickness of
+\SI{500}{\metre}. The different grid sizes determine the number of
+variables.
 
@@
 \begin{align}
-  w_1[h(k)] = \frac{1} {\sigma^{\rm aerosol}_{\rm G} \mathrm{MFP^{sea
-        level}}} \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
+  w_1[h(k)] = \frac{1} {n^{sea level}}
+  \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
 \end{align}
 where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
-of reduced atmospheric density with height. Here the mean free path
-(MFP) of the aerosols layer at sea level was set to \linebreak
-\mbox{$\mathrm{MFP^{sea level}}=1/5$~\si{\per\km}}.
-
-\todo[inline]{Update the quantities above especially the visibility or
-  fix the images}
+of reduced atmospheric density with height.
 
@@
   \caption{\small [a] Simulated 3D aerosol distribution composed of
-    {\em Haze Blobs}. [b] Its reconstruction. Color represents aerosol
-    density. The density units are $10^{15}~{\rm particles}/{\rm
-      cm}^3.$}
+    {\em Haze Blobs} and [b] its reconstruction. Color represents
+    aerosol density. The density units are $10^{15}~{\rm
+      particles}/{\rm cm}^3.$}
   \label{fig:simulation1}
@@
 
-\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
-field of view, capturing the entire sky from its viewpoint. We used
-100 viewpoints on a grid, each view \SI{\approx 4.4}{\km} from its
-neighbors.  The resolution of each camera is low: \num{128 x 128}
-pixels, expressing the fact that cloudless (yet hazy) sky images are
-rather smooth, hence there is no need for high image resolution. Each
-pixel has full-well depth of 40000 electrons, which corresponds to the
-brightest pixel value. Each measurement has photon noise, which is
-Poissonian distributed, according to each image-pixel value $i_c$ and
-the full-well depth. For example, \cref{fig:simulation-results1}a
-shows an example of a modeled photograph
+\noindent{\bf Cameras}: The cameras are created by the MC simulations.
+Each ground-based camera has a hemispherical field of view, capturing
+the entire sky from its viewpoint. Again, we used different numbers of
+cameras ranging from 100 viewpoints to 12. The cameras are arranged on
+a grid.  The resolution of each camera is low, expressing the fact
+that cloudless (yet hazy) sky images are rather smooth, hence there is
+no need for high image resolution.  For example,
+\cref{fig:simulation-results1}b shows an example of a modeled
+photograph
 \begin{figure}
@@
 that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
-with 8GB DDR3 memory per core. Out of it, we used 8 nodes,
-corresponding to 96 cores. Each core was dedicated to rendering a
-modeled image (in each interaction) as if captured by one of the 95
-cameras. Each iteration (varying the model according to the
-gradient-based algorithm and varying all the rendered images) took
-\SI{\approx 7}{\second}.
+with 8GB DDR3 memory per core. The number of cures used is depends
+on the size of the simulations. Each core was dedicated to rendering a
+modeled image.
 

### 2013-07-24 article.tex
Added current simulation images.

@@
 As an example, we created a {\em Haze Blobs} scene using two ellipsoid
-blobs (\cref{fig:simulation1}a):
-\begin{figure} \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
-  \caption{\small [a] Simulated 3D aerosol distribution composed of
-    {\em Haze Blobs} and [b] its reconstruction. Color represents
-    aerosol density. The density units are $10^{15}~{\rm
-      particles}/{\rm cm}^3.$}
-  \label{fig:simulation1}
-\end{figure}
+blobs (\cref{fig:two_clouds_sim}a):
 the first is centered at altitude \SI{3.3}{\km}, and has horizontal
@@
 of the {\em Haze Blobs} scene that corresponds to
-\cref{fig:simulation1}a.
+\cref{fig:two_clouds_sim}a.
 
@@
 An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in \cref{fig:simulation1}a, while the recovered
-3D distribution is visualized in \cref{fig:simulation1}b. The
+distribution is shown in \cref{fig:two_clouds_sim}a, while the recovered
+3D distribution is visualized in \cref{fig:two_clouds_sim}b. The
 distributions appear consistent, though there are errors that stem
@@
   {\| {\bm n}^{\rm true} \|_1} ,
-  \hspace{-0.05cm}
 \end{equation}
@@
 
-We created a {\em Haze Front} scene. \cref{fig:simulation2}a shows an
+We created a {\em Haze Front} scene. \cref{fig:front_sim}a shows an
 iso-surface visualization of this distribution.
@@
   \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation2}}
+  \yoavcomment{\includegraphics[width=\columnwidth]{images/two_clouds}}
+  \caption{\small [a] Simulated 3D aerosol distribution composed of
+    {\em Haze Blobs} and [b] its reconstruction. Color represents
+    aerosol density. The density units are $10^{6}~{\rm
+      particles}/{\rm m}^3.$}
+  \label{fig:two_clouds_sim}
+\end{figure}
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=\columnwidth]{images/front}}
   \caption{\small [a] Simulated 3D aerosol distribution composed of a
     {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
-    density. The density units are $10^{15}~{\rm particles}/{\rm
-      cm}^3.$}
-  \label{fig:simulation2}
+    density. The density units are $10^{6}~{\rm particles}/{\rm
+      m}^3.$}
+  \label{fig:front_sim}
 \end{figure}
@@
 part of which enters the volume). The haze front stretches across the
-width of the volume.  \cref{fig:simulation2}b visualizes the recovered
+width of the volume.  \cref{fig:front_sim}b visualizes the recovered
 3D distribution of this scene. For the {\em Haze Front},

### 2013-07-24 article.tex
Adde mike garay in correct style.

@@
 
+\newcommand\authnote[1]{\textsuperscript{\normalfont#1}}
+\newcommand\affilnote[1]{\textsuperscript{\normalfont#1}}
+\providecommand\textsuperscript[1]{$^{#1}$}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\author{Amit~Aides and Yoav~Y.~Schechner and Vadim~Holodovsky}
-
-\address{Electrical Engineering Dept., Technion - Israel Inst. Tech., \\ Haifa 32000, Israel}
-
-\email{amitibo@tx.technion.ac.il} %% email address is required
+\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1} Vadim~Holodovsky\authnote{1} and Michael~J.~Garay\authnote{2}}
+
+\address{\affilnote{1}Electrical Engineering Department, Technion - Israel Institute of Technology, Haifa 32000, Israel\\
+\affilnote{2}Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+
+\email{\authnote{*}amitibo@tx.technion.ac.il} %% email address is required
 

### 2013-07-25 article.tex
Copy for Yoav

@@
 \newcommand{\yoavcomment}[1]{}
-\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
+%\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
 
@@
 
-\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1} Vadim~Holodovsky\authnote{1} and Michael~J.~Garay\authnote{2}}
+\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1}
+  Vadim~Holodovsky\authnote{1} and Michael~J.~Garay\authnote{2}}
 
 \address{\affilnote{1}Electrical Engineering Department, Technion - Israel Institute of Technology, Haifa 32000, Israel\\
-\affilnote{2}Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+  \affilnote{2}Jet Propulsion Laboratory, California Institute of
+  Technology, Pasadena, CA 91109, USA}
 
@@
 
-\ocis{(000.0000) General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
+\ocis{(000.0000)
+  General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
 
@@
 
-\bibliography{article}{}
-\bibliographystyle{osajnl}
+\bibliography{article}{} \bibliographystyle{osajnl}
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
+    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
   \end{center}
@@
 recovery of refractive transparent objects~\cite{ihrke}, overcoming
-the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects
-was studied in horizontal, fixed
+the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects was
+studied in horizontal, fixed
 views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
@@
 Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
-space (\cref{fig:misr}), the Airborne Multiangle SpectroPolarimetric
+space, the Airborne Multiangle SpectroPolarimetric
 Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
 airborne instruments.
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.90\textwidth]{misr.pdf}
-  \caption{\small{[Left] NASA's MISR instrument, developed by the Jet
-      Propulsion Laboratory (JPL), provides multiangular,
-      multispectral images of Earth.  It scans Earth from 9 view
-      angles, at resolution of $\approx 300$m.  [Right] A series of
-      MISR images from different viewing angles showing an assortment
-      of clouds over Florida.}  }
-  \label{fig:misr}
-\end{figure}
 
@@
   Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-sky-cameras, looking upwards and capturing the sky lightfield.  This
+sky-cameras, looking upward and capturing the sky lightfield.  This
 paper takes the first step, of formulating this principle and
@@
 
-We simulate image acquisition using Monte Carlo simulations
-(\cref{sec:monte-carlo-simul}).  Monte carlo model multiple scattering
-and therefore enable simulating realistic scenarios. Our
-reconstruction algorithm is based on the Single-Scattering model
-(\cref{sec:single-scatt-model}). The Single-Scattering approximation
-enables state the solution to the Radiative Transform in a closed
-form. This closed is beneficial to us as it enables us to invert the
-model and thus recover the underlying atmosphere
-(\cref{sec:inverse-problem}).
+Our reconstruction algorithm is based on the
+Single-Scattering model (\cref{sec:single-scatt-model}). The
+Single-Scattering approximation enables stating an analytic solution
+to the Radiative Transfer in a closed form. This closed form is
+beneficial to us as it enables us to invert the model and thus recover
+the underlying atmosphere (\cref{sec:inverse-problem}). We validate
+our reconstruction method by applying it on 'Realistic' images.
+We simulate image acquisition using Monte Carlo (MC) simulations
+(\cref{sec:monte-carlo-simul}).  The monte carlo method models
+multiple scattering and therefore enables simulating realistic
+scenarios.
 
@@
       air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
-  [\tilde{\vect{\alpha}}^{\rm air}_c + 
-  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
+  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
+    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
+    n} ] \Big\} .
   \label{eq:bigIA}
@@
 As an example, we created a {\em Haze Blobs} scene using two ellipsoid
-blobs (\cref{fig:two_clouds_sim}a):
-the first is centered at altitude \SI{3.3}{\km}, and has horizontal
-width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
-second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
-lateral width of \SI{24}{\km} and vertical thickness of
-\SI{2.1}{\km}. Note that the horizontal widths are much larger than
-the vertical ones. This is consistent with scales of atmospheric
-aerosol distributions.
+blobs (\cref{fig:two_clouds_sim}a): the first is centered at altitude
+\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
+thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
+altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
+vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
+are much larger than the vertical ones. This is consistent with scales
+of atmospheric aerosol distributions.
 
@@
   \centering
-  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
+  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
   \caption{\small [a] Photograph of a sky that includes {\em Haze
@@
     angles.  [b] Photograph of the same sky and view point rendered
-    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
+    using the MCRT simulation (\cref{sec:monte-carlo-simul}).
+    [c] Cross section along the 
+  }
   \label{fig:simulation-results1}
@@
 that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
-with 8GB DDR3 memory per core. The number of cures used is depends
-on the size of the simulations. Each core was dedicated to rendering a
+with 8GB DDR3 memory per core. The number of cures used is depends on
+the size of the simulations. Each core was dedicated to rendering a
 modeled image.
@@
 An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in \cref{fig:two_clouds_sim}a, while the recovered
-3D distribution is visualized in \cref{fig:two_clouds_sim}b. The
-distributions appear consistent, though there are errors that stem
-from the random noise in the images. To quantify the results, we use a
-relative error measure based on the $\ell_1$ norm
+distribution is shown in \cref{fig:two_clouds_sim}a, while the
+recovered 3D distribution is visualized in
+\cref{fig:two_clouds_sim}b. The distributions appear consistent,
+though there are errors that stem from the random noise in the
+images. To quantify the results, we use a relative error measure based
+on the $\ell_1$ norm
 \begin{equation}

### 2013-07-25 article.tex
bookmark

@@
 \usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
+\usepackage{xfrac}
 
@@
 \newcommand{\OpCamera}{\bm{\mathcal{P}}}
+\newcommand{\Mask}{\bm{M}}
 \newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
@@
 \newcommand{\yoavcomment}[1]{}
-%\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
+\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
 
@@
   retrieval assumes a plane-parallel atmosphere and solely vertical
-  radiative transfer. We propose a principle to recover the atmosphere
+  radiative transfer (RT). We propose a principle to recover the atmosphere
   as it really is: a three dimensional (3D), volumetric, transparent
@@
   dominates the images.  We formulate an image formation model based
-  on 3D radiative transfer. Model inversion is done using optimization
+  on 3D RT. Model inversion is done using optimization
   methods, exploiting a closed-form gradient which we derive for the
@@
 discipline, the atmosphere is often assumed to be plane-parallel, for
-simplicity, using only 1D vertical radiative transfer. Consequently
+simplicity, using only 1D vertical RT. Consequently
 state-of-the-art aerosol retrieval is done in distinct large lateral
@@
   extinction cross section} $\sigma$ (units \si{\meter\squared}) for
-interacting with the irradiance. The volume includes many particles of
-this type. The denser the volume, the stronger is the extinction.  The
-density of the particles is $n$ (units
-\si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
-  extinction coefficient} $\beta$ (units \si{\per\meter}) is
+interacting with the irradiance. The density of the particles is $n$
+(units \si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
+  extinction coefficient} $\beta$ is
 \begin{align}
@@
 \begin{align}
-  t=\exp^{-\tau}
+  t=\exp(-\tau)
   \label{eq:beer-lambert}
@@
 unitless {\em single scattering albedo} $\varpi$ of the particle. The
-{\em scattering coefficient} $\alpha$ (units \si{\per\meter}) is
+{\em scattering coefficient} $\alpha$ is
 \begin{align}
@@
 \end{align}
-Scattering is generally anisotropic. Its angular distribution is
-determined by a {\em phase function} $P$. Part of the light scatters
-towards a camera's line of sight (LOS), as illustrated in
-\cref{fig:groundgrid}. The angle between the SR and LOS is the
-scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
-  scatter})$ is normalized: its integral over all solid angles is
-unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
-\si[sticky-per]{\per\meter\steradian}) is
+The angular distribution of scattering is determined by a {\em phase
+  function} $P$. Part of the light scatters towards a camera's LOS, as
+illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
+is the scattering angle $\Phi^{\rm scatter}$. The phase function
+$P(\Phi^{\rm scatter})$ is normalized: its integral over all solid
+angles is unit. The {\em angular scattering coefficient}
+$\tilde\alpha$ (units \si[sticky-per]{\per\meter\steradian}) is
 \begin{align}
@@
 \begin{align}
-  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
-    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
+  P_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 - g^2)(1+\mu^2)
+  (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
   \label{eq:aerosol_scatter}
 \end{align}
-where $g$ is an {\em anisotropy parameter} and
-\begin{align}
-  \mu\equiv \cos \Phi^{\rm scatter}.
-  \label{eq:mu}
-\end{align}
+where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos \Phi^{\rm scatter}$.
+\\
 
@@
 \begin{align}
-  P^{\rm air}\left[\mu(k)\right] &\approx \frac{3}{16\pi}(1+\mu^2)
+  P^{\rm air}\left[\mu(k)\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
   \label{eq:rayleighP}
@@
   \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
-  \frac{1.09 \times 10^{-3}}{\lambda^4}
+  1.09 \times 10^{-3}\lambda^{-4}
   \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
@@
 We believe that high resolution atmospheric recovery can be achieved
-by a large set of ground-based wide-angle~\cite{Cossairt2011,
+by a set of ground-based wide-angle~\cite{Cossairt2011,
   Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-sky-cameras, looking upward and capturing the sky lightfield.  This
-paper takes the first step, of formulating this principle and
+sky-cameras, looking upward, performing integral imaging of the sky.
+This paper takes the first step, of formulating this principle and
 demonstrating feasibility using realistic simulations. The formulation
@@
 
-Our reconstruction algorithm is based on the
-Single-Scattering model (\cref{sec:single-scatt-model}). The
-Single-Scattering approximation enables stating an analytic solution
-to the Radiative Transfer in a closed form. This closed form is
-beneficial to us as it enables us to invert the model and thus recover
-the underlying atmosphere (\cref{sec:inverse-problem}). We validate
-our reconstruction method by applying it on 'Realistic' images.
-We simulate image acquisition using Monte Carlo (MC) simulations
-(\cref{sec:monte-carlo-simul}).  The monte carlo method models
-multiple scattering and therefore enables simulating realistic
-scenarios.
+We simulate RT through the atmosphere using two models. The first is
+based on Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}) and
+models Multiple-Scattering. Therefore it enables simulating realistic
+scenarios.  The second model uses the Single-Scattering approximation
+(\cref{sec:single-scatt-model}). It is less accurate than the MC model
+but it enables stating an analytic solution to the RT in a closed
+form. This closed form is beneficial to us as it enables us to invert
+the model and thus recover the underlying atmosphere
+(\cref{sec:inverse-problem}). To mimic realistic scenarios, we apply
+the reconstruction algorithm on images simulated by the MC model.
 
@@
   = \sum_{c=1}^{N_{\rm views}}
-  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2 + \eta \cdot \Psi({\bm n})
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
 \end{equation}
@@
 \end{equation}
+We use $\Mask$ as a weight map to mask the influence of the sun and
+the horizon. These regions are prone to dominant multiple scattering.
 We solve~\cref{eq:minobjectiveA} using standard optimization tools.
@@
 increasing the number of photons.  Another advantage of the MC methods
-is that they are highly parallelable.
+is that they are highly parallelizable.
 

### 2013-07-26 article.tex
bookmark

@@
 \usepackage{xfrac}
+\usepackage{paralist}
 
@@
 \si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
-extinction and scattering by air molecules are modeled by
+extinction and scattering by air molecules can be modeled by
 \begin{align}
@@
 sky-cameras, looking upward, performing integral imaging of the sky.
-This paper takes the first step, of formulating this principle and
-demonstrating feasibility using realistic simulations. The formulation
-of this paper can also apply to multiview images that are captured
-from satellites, for future spaceborne instruments of this capacity.
-
-We simulate RT through the atmosphere using two models. The first is
-based on Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}) and
-models Multiple-Scattering. Therefore it enables simulating realistic
+Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
+capture the sky lightfield from below. Per viewpoint, the view azimuth
+and elevation angles (relative to the zenith and north) are
+encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
+  c}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
+any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
+measured radiance in all locations ${\bm x}$ and angles
+${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
+  x},{\bm{\Theta}})$.This paper takes the first step, of formulating
+this principle and demonstrating feasibility using realistic
+simulations.  We simulate RT through the atmosphere using two
+models. The first is based on Monte Carlo (MC) methods
+(\cref{sec:monte-carlo-simul}) and models
+Multiple-Scattering. Therefore it enables simulating realistic
 scenarios.  The second model uses the Single-Scattering approximation
@@
 A forward model takes as input the aerosol distribution, and outputs
-images as if captured at various viewpoints.  We use a
-\emph{single-scattering} model, in which any SR changes direction
-(scatters) only once on the way to the camera. This model is valid in
-atmospheres that are not very dense: inside fog and clouds this model
-does not apply.
-
-Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
-capture the sky lightfield from below. Per viewpoint, the view azimuth
-and elevation angles (relative to the zenith and north) are
-encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
-  x}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
-any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
-measured radiance in all locations ${\bm x}$ and angles
-${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
-  x},{\bm{\Theta}})$. Individual images are slices of the lightfield.
-
-Under single-scattering approximation, radiative transfer has three
-steps (\cref{fig:groundgrid}):
-\begin{enumerate}
-\item Attenuation of a SR propagating from the top of the atmosphere
-  (TOA) to voxel $k$.
-\item Light scattering at voxel $k$, towards a camera.
-\item Light attenuation on the LOS from voxel $k$ to the camera.
-\end{enumerate}
-
-Steps 1 and 3 involve the optical depth along the light path to and
-from voxel $k$, analyzed in \cref{sec:optical-depth}.  Step 2 involves
-the scattering coefficient at voxel $k$, described in
+images as if captured at various viewpoints.  In a
+\emph{single-scattering} model, any SR changes direction only once on
+the way to the camera. This model is valid in atmospheres that are not
+very dense: inside fog and clouds this model does not apply.  Under
+single-scattering approximation, radiative transfer has three steps
+(\cref{fig:groundgrid}):
+\begin{inparaenum}[\hfill\bfseries a\upshape)]
+\item \label{itm:first} Attenuation of a SR propagating from the top
+  of the atmosphere (TOA) to voxel $k$.
+\item \label{itm:second} Light scattering at voxel $k$, towards a
+  camera.
+\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
+  the camera.
+\end{inparaenum}
+Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
+along the light path to and from voxel $k$, analyzed in
+\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
+scattering coefficient at voxel $k$, described in
 \cref{sec:scattering}.

### 2013-07-26 article.tex
bookmark

@@
 
-A forward model takes as input the aerosol distribution, and outputs
-images as if captured at various viewpoints.  In a
-\emph{single-scattering} model, any SR changes direction only once on
-the way to the camera. This model is valid in atmospheres that are not
-very dense: inside fog and clouds this model does not apply.  Under
-single-scattering approximation, radiative transfer has three steps
-(\cref{fig:groundgrid}):
+The atmosphere is discretized into a grid of volume elements (voxels).
+A forward model takes as input the aerosol distribution over the grid
+of voxels, and outputs images as if captured at various viewpoints.
+In a \emph{single-scattering} model, any SR changes direction only
+once on the way to the camera. This model is valid in atmospheres that
+are not very dense: inside fog and clouds this model does not apply.
+Under single-scattering approximation, radiative transfer has three
+steps (\cref{fig:groundgrid}):
 \begin{inparaenum}[\hfill\bfseries a\upshape)]
@@
 
-An infinitesimal volume contains aerosols. The extinction and
-scattering coefficients due to aerosols in this volume are,
-respectively
-\begin{equation}
-  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
-  \;\;,\;\;
-  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
-  \;.
-  \label{eq:betaer}
-\end{equation}
-The infinitesimal volume contain also air molecules. Hence, the
-overall extinction and scattering coefficients in this small volume
-are, respectively
-\begin{equation}
-  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
-  \;\;,\;\;
-  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
-  \;.
-  \label{eq:betair}
-\end{equation}
-
 Any voxel generally contains both air molecules and aerosols. Voxels
-are indexed by $k$ or $q$. As approximation, assume that within any
-voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
-  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
-  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
-constants, e.g., corresponding to the value at each voxel
-center. These parameters may change between voxels.
+are indexed by $k$ or $q$. We assume that within any voxel, the
+molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
+the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
+  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
+corresponding to the value at each voxel center.
 

### 2013-07-26 article.tex
bookmark

@@
 
+\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
+
 %
@@
 %
-\newcommand{\OpSphere}{\bm{\mathcal{S}}}
-\newcommand{\OpRot}{\bm{\mathcal{R}}}
-\newcommand{\OpDistance}{\bm{\mathcal{D}}}
-\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
-\newcommand{\OpInt}{\bm{\mathcal{I}}}
-\newcommand{\OpCamera}{\bm{\mathcal{P}}}
+\newcommand{\OpSphere}{\mathbfcal{S}}
+\newcommand{\OpRot}{\mathbfcal{R}}
+\newcommand{\OpDistance}{\mathbfcal{D}}
+\newcommand{\OpCumsum}{\mathbfcal{C}}
+\newcommand{\OpInt}{\mathbfcal{I}}
+\newcommand{\OpCamera}{\mathbfcal{P}}
 \newcommand{\Mask}{\bm{M}}
@@
 
-The atmosphere is discretized into a grid of volume elements (voxels).
-A forward model takes as input the aerosol distribution over the grid
-of voxels, and outputs images as if captured at various viewpoints.
-In a \emph{single-scattering} model, any SR changes direction only
-once on the way to the camera. This model is valid in atmospheres that
-are not very dense: inside fog and clouds this model does not apply.
-Under single-scattering approximation, radiative transfer has three
-steps (\cref{fig:groundgrid}):
+The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
+elements (voxels).  A forward model takes as input the aerosol
+distribution over the grid of voxels, and outputs images as if
+captured at various viewpoints.  In a \emph{single-scattering} model,
+any SR changes direction only once on the way to the camera. This
+model is valid in atmospheres that are not very dense: inside fog and
+clouds this model does not apply.  Under single-scattering
+approximation, radiative transfer has three steps
+(\cref{fig:groundgrid}):
 \begin{inparaenum}[\hfill\bfseries a\upshape)]
@@
 angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
-the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
-$q$. The geometric length of this intersection line segment is $l_{\rm
-  SR}(q)$ which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.
-Following \cref{eq:tau,eq:betair}, the optical depth between the TOA
-and voxel $k$ is
-\begin{equation}
-  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
-  \label{eq:lSRn}
-\end{equation}
-Based on \cref{eq:betaer,eq:betair,eq:lSRn},
-\begin{equation}
-  \tau_{\rm SR}(k)=
-  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
-  \;\;,
-  \label{eq:lSRaa}
-\end{equation}
-where
-\begin{equation}
-  \tau_{\rm SR}^{\rm air}(k)=
-  \sum_{q \in[{\rm SR},k]}
-  \beta^{\rm air}(q)  l_{\rm SR}(q)
-  \label{eq:lSRair}
-\end{equation}
-and
-\begin{equation}
-  \tau_{\rm SR}^{\rm aerosol}(k)
-  \sum_{q \in[{\rm SR},k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm SR}(q)
-  \label{eq:lSRaeros}
-\end{equation}
-
-The number of voxels is $N_{\rm voxels}$. All their associated
-variables are concatenated into columns stack vectors, each $N_{\rm
-  voxels}$ long. Aerosol densities and cross sections in all voxels
-are stored in the respective vectors ${\bm n}$ and
-$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
-matrix ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
-$(k,q)$ is
-\begin{equation}
-  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
+the center of voxel $k$ by $[{\rm SR},k]$ (See
+\cref{fig:groundgrid}). This SR intersects voxel $q$. The geometric
+length of this intersection line segment is $l_{\rm SR}(q)$ which
+depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  We now define a
+$N_{\rm voxels}\times N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun
+    \rightarrow voxel}}$, whose element $(k,q)$ represents $l_{\rm
+  SR}(q)$:
+\begin{equation}
+  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
   \left\{
@@
   \right.
-  .
   \hspace{-0.05cm}
 \end{equation}
-\cref{eq:lSRaeros,eq:Dsv} lead to a vector of SR optical depths due to
-aerosols (See \cref{fig:projection})a:
-\begin{equation}
-  \vect{\tau}_{\rm SR}^{\rm aerosol}=
-  {\bm D}^{\mathrm{Sun \rightarrow voxel}}
-  (\vect{\sigma} \odot {\bm n})
-  \label{eq:tauSRvec1}
-\end{equation}
-where the operator $\odot$ denotes the Hadamard (element-wise)
-product. Similarly, \cref{eq:lSRair} leads to a vector of SR optical
-depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.
+Note that matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
+sparse.  Following \cref{eq:tau}, the optical depth between the TOA
+and voxel $k$ is
+\begin{equation}
+  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
+  \label{eq:lSRn}
+\end{equation}
+We can write \cref{eq:lSRn} using matrix notation
+\begin{equation}
+  \vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}
+  \label{eq:tau_matrix}
+\end{equation}
+Here $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
+representation of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively.
 
 Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
-between the camera and the center of voxel $k$. The LOS zenith angle
-is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
-length of this intersection line segment is $l_{\rm LOS_c}(q)$which
-depends on $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
-\cref{eq:lSRaa,eq:lSRair,eq:lSRaeros}, the optical depth along a LOS
-to $k$ is
-\begin{equation}
-  \tau_{{\rm LOS}_c}(k)=
-  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
-  \;\;,
-  \label{eq:lLOSaerot}
-\end{equation}
-where
-\begin{equation}
-  \tau_{{\rm LOS}_c}^{\rm air}(k)=
-  \sum_{q \in[{\rm LOS}_c,k]}
-  \beta^{\rm air}(q)  l_{\rm LOS_c}(q)
-  \label{eq:lLOSair}
-\end{equation}
-and
-\begin{align}
-  \label{eq:lLOSaeros}
-  \tau_{{\rm LOS}_c}^{\rm aerosol}(k) = \sum_{q \in[{\rm LOS}_c,k]}
-  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm LOS_c}(q).
-\end{align}
-\cref{eq:lLOSaeros} leads to a vector of LOS optical depths due to
-aerosols:
-\begin{equation}
-  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
-  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
-  (\vect{\sigma} \odot {\bm n})
-  \label{eq:tauLOSvec1}
-\end{equation}
-Here ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
-  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
-\begin{equation}
-  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
+between the camera and the center of voxel $k$ (see
+\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
+This LOS intersects voxel $q$. The geometric length of this
+intersection line segment is $l_{\rm LOS_c}(q)$which depends on
+$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
+\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
+sparse matrix whose element $(k,q)$ is
+\begin{equation}
+  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
   \left\{
     \begin{array}{ll}
-      l_{\rm LOS_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
+      l_{{\rm LOS}_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
       0  & \mbox{ otherwise}
@@
 \end{equation}
-Similarly, \cref{eq:lSRair} leads to a vector of LOS optical depths
-due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.
-
-The fixed sparse matrices ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$
-and ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
-single matrix
+The optical depth along a LOS to $k$ is
+\begin{equation}
+  \vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
+      cam}} \vect{\beta}
+  \label{eq:lLOSn}
+\end{equation}
+Here $\vect{\tau}_{\rm SR}$ is a column stack vector representation of
+$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths of each voxel $k$ can
+be joined to a single path from the TOA to camera $c$ giving
 \begin{equation}
@@
   {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
+  \quad\text{ and }\quad
+  \vect{\tau}_c=
+  \vect{\tau}_{\rm SR}+
+  \vect{\tau}_{{\rm LOS}_c}
   \;\;.
-  \label{eq:Dtotal}
-\end{equation}
-Similarly, the molecular optical depths along all trajectories between
-the sun, each voxel and camera $c$ are compounded to a vector
-\begin{equation}
-  \vect{\tau}_c^{\rm air}=
-  \vect{\tau}_{\rm SR}^{\rm air}+
-  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
-  \;\;.
-  \label{eq:tauairtotal}
-\end{equation}
-Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in all voxels, the
-vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus $\vect{\tau}_c^{\rm
-  air}$ can be calculated once, per sun zenith angle.
-
-Using
-\cref{eq:lSRaa,eq:tauSRvec1,eq:lLOSair,eq:tauLOSvec1,eq:Dtotal,eq:tauairtotal},
-the total optical depths corresponding to LOSs (of camera $c$) and SRs
-that cross all voxels comprise the vector
+  \label{eq:D_tau_total}
+\end{equation}
+
+We discern between air molecules and other aerosols and therefore
+write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
+  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
+all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
+$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
+angle. Given \cref{eq:extinctc}, the total optical depths
+corresponding to LOSs (of camera $c$) and SRs that cross all voxels
+comprise the vector
 \begin{equation}
@@
 \end{equation}
-This vector depends on the variables $\vect{\sigma}$ and ${\bm n}$
-(See~\cref{fig:projection}a).
+where the operator $\odot$ denotes the Hadamard (element-wise)
+product. This vector depends on the variables $\vect{\sigma}$ and
+${\bm n}$, the aerosol extinction and density at each voxel
+respectively.
 
@@
 Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
-  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
-which is pre-calculated.  Column-stacking all voxels yields the vector
-representation of all scattering angles in the domain,
-$\vect{\Phi}^{\rm scatter}_c$ per camera $c$. Similarly, the
-single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are
-stacked to vector $\vect{\varpi}$.  Using
-\cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the angular
-scattering coefficients across the domain are expressed in vector form
-by
+  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
+Column-stacking all voxels yields the vector representation of all
+scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
+camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
+  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
+Using \cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the
+angular scattering coefficients across the domain are expressed in
+vector form by
 \begin{align}

### 2013-07-26 article.tex
bookmark

@@
   aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
-Using \cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the
+Using \cref{eq:alphabasic,eq:rayleighP}, the
 angular scattering coefficients across the domain are expressed in
 vector form by
-\begin{align}
-  \tilde{\vect{\alpha}}^{\rm air}_c &=
-  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c) \nonumber \\
-  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
+\begin{equation}
+  \tilde{\vect{\alpha}}^{\rm air}_c =
+  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
+  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
   \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
@@
   \label{eq:alpha_matrix}
-\end{align}
+\end{equation}
 The vector ${\bm g}$ column-stacks the anisotropy parameter of the

### 2013-07-26 article.tex
bookmark

@@
 \newcommand{\OpCamera}{\mathbfcal{P}}
-\newcommand{\Mask}{\bm{M}}
+\newcommand{\Mask}{\mathbfcal{M}}
+\newcommand{\Laplacian}{\mathbfcal{L}}
 \newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
@@
 
-\section{Inverse Problem}
-\label{sec:inverse-problem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Unknowns and Prior Knowledge}
-\label{sec:prior}
-
-In general terms, the variables are the set
-\begin{equation}
-  {\cal V}\equiv
-  \left\{
-    {\bm n},
-    \left\{
-      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
-    \right\}_{\lambda}
-  \right\}
-  \;\;,
-  \label{eq:calV}
-\end{equation}
-where $\lambda$ denotes the spectral (color) channel.  There are
-$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
-variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
-    spectral})$}.
-
-Prior knowledge reduces the unknowns. For simplicity we assume a
-single aerosol type dominates a scene. Furthermore, in the following
-section we assume that we know the type of the particle. Hence, we
-focus here on retrieving ${\bm n}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Objective Function}
-\label{sec:objective-function}
-
-The recovery task is phrased as optimization of an objective function,
-that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
-    views}}$:
-\begin{equation}
-  \label{eq:minobjectiveA}
-  \hat{\bm n} =
-  \argmin_{{\bm n}} F({\bm n})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bm n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
-\end{equation}
-Here $\Psi({\bm n})$ is a regularization term that expresses some
-prior knowledge on the solution and $\eta$ is the regularization
-coefficient.  We enforce smoothness of the solution by using the
-\emph{Laplacian} operator.
-\begin{equation}
-  \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
-\end{equation}
-We use $\Mask$ as a weight map to mask the influence of the sun and
-the horizon. These regions are prone to dominant multiple scattering.
-We solve~\cref{eq:minobjectiveA} using standard optimization tools.
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \nabla^2\nabla^2{\bm n} \;.
-  \label{eq:gradient1}
-\end{align}
-Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
-symmetry of the \emph{Laplacian} operator. A close-form expression of
-our Jacobian is
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
-  ,
-  \label{eq:gradient2}
-\end{align}
-where
-\begin{align}
-  \label{eq:gradient3}
-  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
-  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
-  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}
-    ]} \nonumber \\
-  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
-For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
-refer the reader to \cref{sec:gradient-derivation}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Monte Carlo RT}
@@
 use the local estimation (LE) method.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inverse Problem}
+\label{sec:inverse-problem}
+
+In general terms, the variables are the set \mbox{$\left\{{\bm
+      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
+        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
+denotes the spectral (color) channel.  There are $N_{\rm spectral}$
+spectral channels.  Thus, the number of unknown variables is in
+principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm spectral})$}.
+
+Prior knowledge reduces the unknowns. For simplicity we assume a
+single aerosol type dominates a scene. Furthermore, in the following
+section we assume that we know the type of the particle. Hence, we
+focus here on retrieving ${\bm n}$.
+
+The recovery task is phrased as optimization of an objective function,
+that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
+measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
+    views}}$:
+\begin{equation}
+  \label{eq:minobjectiveA}
+  \hat{\bm n} =
+  \argmin_{{\bm n}} F({\bm n})
+\end{equation}
+where
+\begin{equation}
+  \label{eq:objectiveA}
+  F({\bm n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
+\end{equation}
+Here $\Psi({\bm n})$ is a regularization term that expresses some
+prior knowledge on the solution and $\eta$ is the regularization
+coefficient.  We enforce smoothness of the solution by using the
+\emph{Laplacian} operator.
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
+\end{equation}
+We use $\Mask$ as a weight map to mask the influence of the sun and
+the horizon. These regions are prone to dominant multiple scattering.
+We solve~\cref{eq:minobjectiveA} using standard optimization tools.
+The gradient of $F$ with respect to ${\bm n}$ is
+\begin{align}
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
+  \nabla^2\nabla^2{\bm n} \;.
+  \label{eq:gradient1}
+\end{align}
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
+symmetry of the \emph{Laplacian} operator. A close-form expression of
+our Jacobian is
+\begin{align}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
+  ,
+  \label{eq:gradient2}
+\end{align}
+where
+\begin{align}
+  \label{eq:gradient3}
+  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
+  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bm n}
+    ]} \nonumber \\
+  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+\end{align}
+For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
+refer the reader to \cref{sec:gradient-derivation}.
 

### 2013-07-26 article.tex
bookmark

@@
   [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
-  e^{-\tau_c(k)}
+  \exp\{-\tau_c(k)\}
   \;\;,
@@
   [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
-  \odot e^{-\vect{\tau}_c}
+  \odot \exp\{-\vect{\tau}_c\}
   \;\;.
@@
     (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
-      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
-      (\vect{\sigma} \odot {\bm n})]} \right\}
+      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
+      (\vect{\sigma} \odot {\bm n})]\} \right\}
   \label{eq:bigIc}
@@
 \begin{align}
-  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
-      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ \exp\{-(\vect{\tau}_c^{\rm
+      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})\}\odot
   [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
@@
 spectral channels.  Thus, the number of unknown variables is in
-principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm spectral})$}.
+principle \mbox{$N_{\rm voxels}(1+3N_{\rm spectral})$}.
 
@@
 single aerosol type dominates a scene. Furthermore, in the following
-section we assume that we know the type of the particle. Hence, we
-focus here on retrieving ${\bm n}$.
+section we assume that we know the type of the particle
+\cite{Martonchik2009}. Hence, we focus here on retrieving ${\bm n}$.
 
@@
 that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
-    views}}$:
+$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
+measured}_c\}_{c=1}^{N_{\rm views}}$:
 \begin{equation}

### 2013-07-26 article.tex
bookmark

@@
 prior knowledge on the solution and $\eta$ is the regularization
-coefficient.  We enforce smoothness of the solution by using the
-\emph{Laplacian} operator.
-\begin{equation}
-  \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
-\end{equation}
+coefficient. 
 We use $\Mask$ as a weight map to mask the influence of the sun and
 the horizon. These regions are prone to dominant multiple scattering.
+One common measurement of smoothness are the second order derivatives.
+These can be calculated using the \emph{Laplacian} operator, $\nabla^2$.
+We enforce smoothness of the solution by minimizing the signal energy
+of the \emph{Laplacian} of the signal
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
+\end{equation}
+where $\Laplacian$ is a matrix representation of the \emph{Laplacian} operator.
+
 We solve~\cref{eq:minobjectiveA} using standard optimization tools.
@@
     measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \nabla^2\nabla^2{\bm n} \;.
+  \Laplacian^T\Laplacian{\bm n} \;.
   \label{eq:gradient1}
@@
 Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
-symmetry of the \emph{Laplacian} operator. A close-form expression of
+vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
 our Jacobian is

### 2013-07-26 article.tex
Yoavs bookmark

--- 2013-07-26 article.tex
@@
 \newcommand{\OpCamera}{\mathbfcal{P}}
-\newcommand{\Mask}{\mathbfcal{M}}
-\newcommand{\Laplacian}{\mathbfcal{L}}
+\newcommand{\Mask}{\bm{M}}
 \newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
@@
 that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
-interacting with the irradiance. The density of the particles is $n$
-(units \si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
-  extinction coefficient} $\beta$ is
-\begin{align}
-  \beta= \sigma n \;.
-  \label{eq:extinctc}
-\end{align}
+  extinction cross section} $\sigma$ for
+interacting with the irradiance. The density of the particles is $n$. Per unit volume, the {\em extinction coefficient} is $\beta= \sigma n$.
 The volume has infinitesimal length $dl$. Then, the relative portion
-of extinct SR irradiance is the unitless differential {\em optical
-  depth}
-\begin{align}
-  d\tau= \beta dl=\sigma n dl \;.
-  \label{eq:extinct}
-\end{align}
-The optical depth aggregates in extended propagation:
+of extinct SR irradiance is the unitless differential optical
+  depth, $d\tau= \beta dl=\sigma n dl$.
+The {\em optical depth} aggregates in extended propagation:
 \begin{align}
@@
 The angular distribution of scattering is determined by a {\em phase
-  function} $P$. Part of the light scatters towards a camera's LOS, as
+  function} $P$, which is normalized: its integral over all solid
+angles is unit. Part of the light scatters towards a camera's LOS, as
 illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
-is the scattering angle $\Phi^{\rm scatter}$. The phase function
-$P(\Phi^{\rm scatter})$ is normalized: its integral over all solid
-angles is unit. The {\em angular scattering coefficient}
-$\tilde\alpha$ (units \si[sticky-per]{\per\meter\steradian}) is
+is the scattering angle $\Phi^{\rm scatter}$. The {\em angular scattering coefficient}
+$\tilde\alpha$ is
 \begin{align}
@@
 \noindent {\bf Air molecules}: Scattering by air molecules follows the
-{\em Rayleigh} model:
-\begin{align}
-  P^{\rm air}\left[\mu(k)\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
+{\em Rayleigh} model. The phase function is
+\begin{align}
+  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
   \label{eq:rayleighP}
 \end{align}
-and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
+and the single scattering albedo is $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
 off approximately exponentially with altitude, with a
 characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
-\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
+\si{\km}$. Thus~\cite{Levi1980}, the coefficients for
 extinction and scattering by air molecules can be modeled by
@@
   1.09 \times 10^{-3}\lambda^{-4}
-  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
+  \exp(-h/H^\mathrm{air}) 
+  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
   \label{eq:rayleighbeta}
 \end{align}
+where $\lambda$ is the wavelength, in microns.
 
@@
 
-We believe that high resolution atmospheric recovery can be achieved
-by a set of ground-based wide-angle~\cite{Cossairt2011,
-  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-sky-cameras, looking upward, performing integral imaging of the sky.
-Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
-capture the sky lightfield from below. Per viewpoint, the view azimuth
-and elevation angles (relative to the zenith and north) are
-encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
-  c}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
-any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
-measured radiance in all locations ${\bm x}$ and angles
-${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
-  x},{\bm{\Theta}})$.This paper takes the first step, of formulating
-this principle and demonstrating feasibility using realistic
-simulations.  We simulate RT through the atmosphere using two
-models. The first is based on Monte Carlo (MC) methods
-(\cref{sec:monte-carlo-simul}) and models
-Multiple-Scattering. Therefore it enables simulating realistic
-scenarios.  The second model uses the Single-Scattering approximation
-(\cref{sec:single-scatt-model}). It is less accurate than the MC model
-but it enables stating an analytic solution to the RT in a closed
-form. This closed form is beneficial to us as it enables us to invert
-the model and thus recover the underlying atmosphere
-(\cref{sec:inverse-problem}). To mimic realistic scenarios, we apply
-the reconstruction algorithm on images simulated by the MC model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Single-Scattering Model}
+Consider a set of ground-based wide-angle cameras
+ %~\cite{Cossairt2011, Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
+looking upwards (\cref{fig:groundgrid}). The set performs {\em integral imaging}~\cite{integral} of the sky. Per viewpoint, the view azimuth and elevation angles (relative to the zenith and north) are
+encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a distinct fixed location ${\bm x}$, capturing raw image $i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
+a principle of recovering the 3D atmospheric aerosols distribution, using such data. To show feasibility, we perform radiative transfer using two different forward models, enabling cross-validation.
+A forward model takes as input the 3D aerosol distribution, and outputs images as if
+captured at various viewpoints.
+One model uses Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally expresses multiple-scattering.
+Hence, this approach simulates realistic
+scenes of arbitrary complexity.  The second model uses the single-Scattering approximation
+(\cref{sec:single-scatt-model}). It is less accurate than MC, but derives an analytic closed
+form solution to the radiative transfer. This closed form enables simple inversion of 
+the model, to estimate the underlying atmosphere (\cref{sec:inverse-problem}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Single-Scattering Forward Model}
 \label{sec:single-scatt-model}
@@
 The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
-elements (voxels).  A forward model takes as input the aerosol
-distribution over the grid of voxels, and outputs images as if
-captured at various viewpoints.  In a \emph{single-scattering} model,
-any SR changes direction only once on the way to the camera. This
+elements (voxels), indexed by $k$ or $q$. In a \emph{single-scattering} model,
+any SR changes direction only once on the way to a camera. This
 model is valid in atmospheres that are not very dense: inside fog and
-clouds this model does not apply.  Under single-scattering
-approximation, radiative transfer has three steps
-(\cref{fig:groundgrid}):
-\begin{inparaenum}[\hfill\bfseries a\upshape)]
-\item \label{itm:first} Attenuation of a SR propagating from the top
-  of the atmosphere (TOA) to voxel $k$.
-\item \label{itm:second} Light scattering at voxel $k$, towards a
-  camera.
-\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
-  the camera.
-\end{inparaenum}
-Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
-along the light path to and from voxel $k$, analyzed in
-\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
-scattering coefficient at voxel $k$, described in
+clouds this model does not apply. In this model, radiative transfer has three steps
+(\cref{fig:groundgrid}): ({\tt i}) Attenuation of a SR propagating from the top
+  of the atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel $k$, towards a
+  camera. ~({\tt iii}) Light attenuation on the LOS from voxel $k$ to
+  the camera.~~
+Steps~{\tt i},{\tt iii} involve the optical depth along the light path to and from voxel $k$, as analyzed in \cref{sec:optical-depth}.
+Step~{\tt ii} involves the scattering coefficient at voxel $k$, described in
 \cref{sec:scattering}.
@@
 \label{sec:optical-depth}
-
-Any voxel generally contains both air molecules and aerosols. Voxels
-are indexed by $k$ or $q$. We assume that within any voxel, the
-molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
-the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
-  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
-corresponding to the value at each voxel center.
 
@@
 the center of voxel $k$ by $[{\rm SR},k]$ (See
-\cref{fig:groundgrid}). This SR intersects voxel $q$. The geometric
-length of this intersection line segment is $l_{\rm SR}(q)$ which
-depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  We now define a
+\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection line segment has geometric
+length $l_{\rm SR}(q)$, which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a
 $N_{\rm voxels}\times N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun
@@
 \end{equation}
-Note that matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
-sparse.  Following \cref{eq:tau}, the optical depth between the TOA
-and voxel $k$ is
-\begin{equation}
-  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
-  \label{eq:lSRn}
-\end{equation}
-We can write \cref{eq:lSRn} using matrix notation
-\begin{equation}
-  \vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}
-  \label{eq:tau_matrix}
-\end{equation}
-Here $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
-representation of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively.
-
+The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
+sparse.  
 Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
@@
 \cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
-This LOS intersects voxel $q$. The geometric length of this
-intersection line segment is $l_{\rm LOS_c}(q)$which depends on
+Suppose this LOS intersects voxel $q$. The geometric length of this
+intersection line segment is $l_{\rm LOS_c}(q)$ which depends on
 $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
@@
 \end{equation}
-The optical depth along a LOS to $k$ is
-\begin{equation}
-  \vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
-      cam}} \vect{\beta}
-  \label{eq:lLOSn}
-\end{equation}
-Here $\vect{\tau}_{\rm SR}$ is a column stack vector representation of
-$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths of each voxel $k$ can
-be joined to a single path from the TOA to camera $c$ giving
+
+Any voxel generally contains both air molecules and aerosols.  We assume that within any voxel, the
+molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
+the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
+  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
+corresponding to the value at each voxel center.
+Following \cref{eq:tau}, the optical depth between the TOA
+and voxel $k$ is
+\begin{equation}
+  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
+  \label{eq:lSRn}
+\end{equation}
+We can write \cref{eq:lSRn} using matrix notation,
+  $\vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
+where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
+representations of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively. Similarly, 
+the optical depth along a LOS to voxel $k$ is expressed by element $k$ of 
+  $\vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
+      cam}} \vect{\beta}$
+Here $\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
+$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel can
+form a single path from the TOA to camera $c$, yielding
 \begin{equation}
@@
 product. This vector depends on the variables $\vect{\sigma}$ and
-${\bm n}$, the aerosol extinction and density at each voxel
+${\bm n}$, the aerosol extinction and density at each voxel,
 respectively.
@@
   \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
-    g}(\vect{\Phi}^{\rm scatter}_c)
+    g}(\vect{\Phi}^{\rm scatter}_c) \;.
   \label{eq:alpha_matrix}
 \end{equation}
-The vector ${\bm g}$ column-stacks the anisotropy parameter of the
-phase function, in all voxels. We use this notation, to indicate a
+The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of the
+phase function, in all voxels. This notation indicates a
 parametric phase function as in \cref{eq:aerosol_scatter}.
@@
 
+\section{Inverse Problem}
+\label{sec:inverse-problem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Unknowns and Prior Knowledge}
+\label{sec:prior}
+
+In general terms, the variables are the set
+\begin{equation}
+  {\cal V}\equiv
+  \left\{
+    {\bm n},
+    \left\{
+      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
+    \right\}_{\lambda}
+  \right\}
+  \;\;,
+  \label{eq:calV}
+\end{equation}
+where $\lambda$ denotes the spectral (color) channel.  There are
+$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
+variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
+    spectral})$}.
+
+Prior knowledge reduces the unknowns. For simplicity we assume a
+single aerosol type dominates a scene. Furthermore, in the following
+section we assume that we know the type of the particle. Hence, we
+focus here on retrieving ${\bm n}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Objective Function}
+\label{sec:objective-function}
+
+The recovery task is phrased as optimization of an objective function,
+that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
+measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
+    views}}$:
+\begin{equation}
+  \label{eq:minobjectiveA}
+  \hat{\bm n} =
+  \argmin_{{\bm n}} F({\bm n})
+\end{equation}
+where
+\begin{equation}
+  \label{eq:objectiveA}
+  F({\bm n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
+\end{equation}
+Here $\Psi({\bm n})$ is a regularization term that expresses some
+prior knowledge on the solution and $\eta$ is the regularization
+coefficient.  We enforce smoothness of the solution by using the
+\emph{Laplacian} operator.
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
+\end{equation}
+We use $\Mask$ as a weight map to mask the influence of the sun and
+the horizon. These regions are prone to dominant multiple scattering.
+We solve~\cref{eq:minobjectiveA} using standard optimization tools.
+The gradient of $F$ with respect to ${\bm n}$ is
+\begin{align}
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
+  \nabla^2\nabla^2{\bm n} \;.
+  \label{eq:gradient1}
+\end{align}
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
+symmetry of the \emph{Laplacian} operator. A close-form expression of
+our Jacobian is
+\begin{align}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
+  ,
+  \label{eq:gradient2}
+\end{align}
+where
+\begin{align}
+  \label{eq:gradient3}
+  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
+  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bm n}
+    ]} \nonumber \\
+  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+\end{align}
+For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
+refer the reader to \cref{sec:gradient-derivation}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Monte Carlo RT}
@@
 use the local estimation (LE) method.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inverse Problem}
-\label{sec:inverse-problem}
-
-In general terms, the variables are the set \mbox{$\left\{{\bm
-      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
-        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
-denotes the spectral (color) channel.  There are $N_{\rm spectral}$
-spectral channels.  Thus, the number of unknown variables is in
-principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm spectral})$}.
-
-Prior knowledge reduces the unknowns. For simplicity we assume a
-single aerosol type dominates a scene. Furthermore, in the following
-section we assume that we know the type of the particle. Hence, we
-focus here on retrieving ${\bm n}$.
-
-The recovery task is phrased as optimization of an objective function,
-that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
-    views}}$:
-\begin{equation}
-  \label{eq:minobjectiveA}
-  \hat{\bm n} =
-  \argmin_{{\bm n}} F({\bm n})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bm n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
-\end{equation}
-Here $\Psi({\bm n})$ is a regularization term that expresses some
-prior knowledge on the solution and $\eta$ is the regularization
-coefficient.  We enforce smoothness of the solution by using the
-\emph{Laplacian} operator.
-\begin{equation}
-  \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
-\end{equation}
-We use $\Mask$ as a weight map to mask the influence of the sun and
-the horizon. These regions are prone to dominant multiple scattering.
-We solve~\cref{eq:minobjectiveA} using standard optimization tools.
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \nabla^2\nabla^2{\bm n} \;.
-  \label{eq:gradient1}
-\end{align}
-Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
-symmetry of the \emph{Laplacian} operator. A close-form expression of
-our Jacobian is
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
-  ,
-  \label{eq:gradient2}
-\end{align}
-where
-\begin{align}
-  \label{eq:gradient3}
-  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
-  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
-  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}
-    ]} \nonumber \\
-  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
-For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
-refer the reader to \cref{sec:gradient-derivation}.
 

### 2013-07-26 article.tex

@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inverse Problem}
-\label{sec:inverse-problem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Unknowns and Prior Knowledge}
-\label{sec:prior}
-
-In general terms, the variables are the set
-\begin{equation}
-  {\cal V}\equiv
-  \left\{
-    {\bm n},
-    \left\{
-      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
-    \right\}_{\lambda}
-  \right\}
-  \;\;,
-  \label{eq:calV}
-\end{equation}
-where $\lambda$ denotes the spectral (color) channel.  There are
-$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
-variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
-    spectral})$}.
-
-Prior knowledge reduces the unknowns. For simplicity we assume a
-single aerosol type dominates a scene. Furthermore, in the following
-section we assume that we know the type of the particle. Hence, we
-focus here on retrieving ${\bm n}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Objective Function}
-\label{sec:objective-function}
-
-The recovery task is phrased as optimization of an objective function,
-that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
-    views}}$:
-\begin{equation}
-  \label{eq:minobjectiveA}
-  \hat{\bm n} =
-  \argmin_{{\bm n}} F({\bm n})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bm n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
-\end{equation}
-Here $\Psi({\bm n})$ is a regularization term that expresses some
-prior knowledge on the solution and $\eta$ is the regularization
-coefficient.  We enforce smoothness of the solution by using the
-\emph{Laplacian} operator.
-\begin{equation}
-  \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
-\end{equation}
-We use $\Mask$ as a weight map to mask the influence of the sun and
-the horizon. These regions are prone to dominant multiple scattering.
-We solve~\cref{eq:minobjectiveA} using standard optimization tools.
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \nabla^2\nabla^2{\bm n} \;.
-  \label{eq:gradient1}
-\end{align}
-Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
-symmetry of the \emph{Laplacian} operator. A close-form expression of
-our Jacobian is
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
-  ,
-  \label{eq:gradient2}
-\end{align}
-where
-\begin{align}
-  \label{eq:gradient3}
-  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
-  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
-  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}
-    ]} \nonumber \\
-  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
-For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
-refer the reader to \cref{sec:gradient-derivation}.
 
@@
 use the local estimation (LE) method.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inverse Problem}
+\label{sec:inverse-problem}
+
+In general terms, the variables are the set \mbox{$\left\{{\bm
+      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
+        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
+denotes the spectral (color) channel.  There are $N_{\rm spectral}$
+spectral channels.  Thus, the number of unknown variables is in
+principle \mbox{$N_{\rm voxels}(1+3N_{\rm spectral})$}.
+
+Prior knowledge reduces the unknowns. For simplicity we assume a
+single aerosol type dominates a scene. Furthermore, in the following
+section we assume that we know the type of the particle
+\cite{Martonchik2009}. Hence, we focus here on retrieving ${\bm n}$.
+
+The recovery task is phrased as optimization of an objective function,
+that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
+$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
+measured}_c\}_{c=1}^{N_{\rm views}}$:
+\begin{equation}
+  \label{eq:minobjectiveA}
+  \hat{\bm n} =
+  \argmin_{{\bm n}} F({\bm n})
+\end{equation}
+where
+\begin{equation}
+  \label{eq:objectiveA}
+  F({\bm n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
+\end{equation}
+Here $\Psi({\bm n})$ is a regularization term that expresses some
+prior knowledge on the solution and $\eta$ is the regularization
+coefficient. 
+We use $\Mask$ as a weight map to mask the influence of the sun and
+the horizon. These regions are prone to dominant multiple scattering.
+One common measurement of smoothness are the second order derivatives.
+These can be calculated using the \emph{Laplacian} operator, $\nabla^2$.
+We enforce smoothness of the solution by minimizing the signal energy
+of the \emph{Laplacian} of the signal
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
+\end{equation}
+where $\Laplacian$ is a matrix representation of the \emph{Laplacian} operator.
+
+We solve~\cref{eq:minobjectiveA} using standard optimization tools.
+The gradient of $F$ with respect to ${\bm n}$ is
+\begin{align}
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
+  \Laplacian^T\Laplacian{\bm n} \;.
+  \label{eq:gradient1}
+\end{align}
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
+our Jacobian is
+\begin{align}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
+  ,
+  \label{eq:gradient2}
+\end{align}
+where
+\begin{align}
+  \label{eq:gradient3}
+  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
+  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bm n}
+    ]} \nonumber \\
+  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+\end{align}
+For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
+refer the reader to \cref{sec:gradient-derivation}.
 

### 2013-07-26 article.tex
bookmark

@@
 
+%An infinitesimal volume contains aerosols. The extinction and
+%scattering coefficients due to aerosols in this volume are,
+%respectively
+%\begin{equation}
+%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
+%  \;\;,\;\;
+%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
+%  \;.
+%  \label{eq:betaer}
+%\end{equation}
+%The infinitesimal volume contain also air molecules. Hence, the
+%overall extinction and scattering coefficients in this small volume
+%are, respectively
+%\begin{equation}
+%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
+%  \;\;,\;\;
+%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
+%  \;.
+%  \label{eq:betair}
+%\end{equation}
+
 \noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
@@
 voxels, and oblivious to all the rest~(\cref{fig:projection}b).
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
-  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
-    above it on a SR. The scattered radiance from voxel $k$ is then
-    attenuated by voxels below it on a LOS to camera $c$.  [b] An
-    image pixel captures light emanating in a cone in space. Voxels
-    that fully or partially fall in this cone are sensed by the
-    pixel.}
-  \label{fig:projection}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
+%  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
+%    above it on a SR. The scattered radiance from voxel $k$ is then
+%    attenuated by voxels below it on a LOS to camera $c$.  [b] An
+%    image pixel captures light emanating in a cone in space. Voxels
+%    that fully or partially fall in this cone are sensed by the
+%    pixel.}
+%  \label{fig:projection}
+%\end{figure}
 Thus light power captured at a pixel is a weighted sum of the power

### 2013-07-26 article.tex
bookmark

@@
 Consider a set of ground-based wide-angle cameras
- %~\cite{Cossairt2011, Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
-looking upwards (\cref{fig:groundgrid}). The set performs {\em integral imaging}~\cite{integral} of the sky. Per viewpoint, the view azimuth and elevation angles (relative to the zenith and north) are
-encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a distinct fixed location ${\bm x}$, capturing raw image $i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
-a principle of recovering the 3D atmospheric aerosols distribution, using such data. To show feasibility, we perform radiative transfer using two different forward models, enabling cross-validation.
-A forward model takes as input the 3D aerosol distribution, and outputs images as if
-captured at various viewpoints.
-One model uses Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally expresses multiple-scattering.
-Hence, this approach simulates realistic
-scenes of arbitrary complexity.  The second model uses the single-Scattering approximation
-(\cref{sec:single-scatt-model}). It is less accurate than MC, but derives an analytic closed
-form solution to the radiative transfer. This closed form enables simple inversion of
-the model, to estimate the underlying atmosphere (\cref{sec:inverse-problem}).
+% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
+% Koppal:2011:WMS:2191740.2192152}
+looking upwards (\cref{fig:groundgrid}). The set performs {\em
+  integral imaging}~\cite{integral} of the sky. Per viewpoint, the
+view azimuth and elevation angles (relative to the zenith and north)
+are encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a
+distinct fixed location ${\bm x}$, capturing raw image
+$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
+a principle of recovering the 3D atmospheric aerosols distribution,
+using such data. To show feasibility, we perform radiative transfer
+using two different forward models, enabling cross-validation.  A
+forward model takes as input the 3D aerosol distribution, and outputs
+images as if captured at various viewpoints. One model uses Monte
+Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
+slow but naturally expresses multiple-scattering. Hence, this approach
+simulates realistic scenes of arbitrary complexity.  The second model
+uses the single-Scattering approximation
+(\cref{sec:single-scatt-model}). It is less accurate than MC, but
+derives an analytic closed form solution to the radiative
+transfer. This closed form enables simple inversion of the model, to
+estimate the underlying atmosphere (\cref{sec:inverse-problem}).
 
@@
 The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
-elements (voxels), indexed by $k$ or $q$. In a \emph{single-scattering} model,
-any SR changes direction only once on the way to a camera. This
-model is valid in atmospheres that are not very dense: inside fog and
-clouds this model does not apply. In this model, radiative transfer has three steps
-(\cref{fig:groundgrid}): ({\tt i}) Attenuation of a SR propagating from the top
-  of the atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel $k$, towards a
-  camera. ~({\tt iii}) Light attenuation on the LOS from voxel $k$ to
-  the camera.~~
-Steps~{\tt i},{\tt iii} involve the optical depth along the light path to and from voxel $k$, as analyzed in \cref{sec:optical-depth}.
-Step~{\tt ii} involves the scattering coefficient at voxel $k$, described in
-\cref{sec:scattering}.
+elements (voxels), indexed by $k$ or $q$. In a
+\emph{single-scattering} model, any SR changes direction only once on
+the way to a camera. This model is valid in atmospheres that are not
+very dense: inside fog and clouds this model does not apply. In this
+model, radiative transfer has three steps (\cref{fig:groundgrid}):
+({\tt i}) Attenuation of a SR propagating from the top of the
+atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
+$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
+voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
+depth along the light path to and from voxel $k$, as analyzed in
+\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
+coefficient at voxel $k$, described in \cref{sec:scattering}.
 
@@
 the center of voxel $k$ by $[{\rm SR},k]$ (See
-\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection line segment has geometric
-length $l_{\rm SR}(q)$, which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a
-$N_{\rm voxels}\times N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun
-    \rightarrow voxel}}$, whose element $(k,q)$ represents $l_{\rm
-  SR}(q)$:
+\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection
+line segment has geometric length $l_{\rm SR}(q)$, which depends on
+$\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a $N_{\rm voxels}\times
+N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$,
+whose element $(k,q)$ represents $l_{\rm SR}(q)$:
 \begin{equation}
@@
 \end{equation}
-The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
-sparse.
+The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
 Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
@@
 
-Any voxel generally contains both air molecules and aerosols.  We assume that within any voxel, the
-molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
-the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
-  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
-corresponding to the value at each voxel center.
-Following \cref{eq:tau}, the optical depth between the TOA
-and voxel $k$ is
+Any voxel generally contains both air molecules and aerosols.  We
+assume that within any voxel, the molecular parameters $\{ \beta^{\rm
+  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol parameters $\{
+\sigma^{\rm aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm
+  aerosol}(k),g(k)\}$ are constants, e.g., corresponding to the value
+at each voxel center.  Following \cref{eq:tau}, the optical depth
+between the TOA and voxel $k$ is
 \begin{equation}
@@
 \end{equation}
-We can write \cref{eq:lSRn} using matrix notation,
-  $\vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
-where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
-representations of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively. Similarly,
-the optical depth along a LOS to voxel $k$ is expressed by element $k$ of
-  $\vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
-      cam}} \vect{\beta}$
-Here $\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
-$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel can
-form a single path from the TOA to camera $c$, yielding
+We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
+  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
+where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
+vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
+respectively. Similarly, the optical depth along a LOS to voxel $k$ is
+expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
+\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
+$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
+$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
+can form a single path from the TOA to camera $c$, yielding
 \begin{equation}
@@
   aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
-Using \cref{eq:alphabasic,eq:rayleighP}, the
-angular scattering coefficients across the domain are expressed in
-vector form by
+Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
+coefficients across the domain are expressed in vector form by
 \begin{equation}
@@
 \end{equation}
-The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of the
-phase function, in all voxels. This notation indicates a
+The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
+the phase function, in all voxels. This notation indicates a
 parametric phase function as in \cref{eq:aerosol_scatter}.
@@
 voxels, and oblivious to all the rest~(\cref{fig:projection}b).
-%\begin{figure}
+% \begin{figure}
 %   \centering
 %   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
-%  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
-%    above it on a SR. The scattered radiance from voxel $k$ is then
-%    attenuated by voxels below it on a LOS to camera $c$.  [b] An
+%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
+%   voxels above it on a SR. The scattered radiance from voxel $k$ is
+%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
 %   image pixel captures light emanating in a cone in space. Voxels
@@
 %   \label{fig:projection}
-%\end{figure}
+% \end{figure}
 Thus light power captured at a pixel is a weighted sum of the power
@@
 \begin{align}
-  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ \exp\{-(\vect{\tau}_c^{\rm
-      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})\}\odot
-  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
-    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
-    n} ] \Big\} .
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
+  \exp\{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c
+  {\bm n})\}\odot [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+    scatter}_c) \odot{\bm n} ] \Big\} .
   \label{eq:bigIA}
@@
 prior knowledge on the solution and $\eta$ is the regularization
-coefficient.
-We use $\Mask$ as a weight map to mask the influence of the sun and
-the horizon. These regions are prone to dominant multiple scattering.
-One common measurement of smoothness are the second order derivatives.
-These can be calculated using the \emph{Laplacian} operator, $\nabla^2$.
-We enforce smoothness of the solution by minimizing the signal energy
-of the \emph{Laplacian} of the signal
+coefficient.  We use $\Mask$ as a weight map to mask the influence of
+the sun and the horizon. These regions are prone to dominant multiple
+scattering.  One common measurement of smoothness are the second order
+derivatives.  These can be calculated using the \emph{Laplacian}
+operator, $\nabla^2$.  We enforce smoothness of the solution by
+minimizing the signal energy of the \emph{Laplacian} of the signal
 \begin{equation}
@@
 \end{equation}
-where $\Laplacian$ is a matrix representation of the \emph{Laplacian} operator.
+where $\Laplacian$ is a matrix representation of the \emph{Laplacian}
+operator.
 
@@
 Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
-our Jacobian is
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
-  ,
-  \label{eq:gradient2}
-\end{align}
-where
-\begin{align}
-  \label{eq:gradient3}
-  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
-  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
-  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}
-    ]} \nonumber \\
-  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
-For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
-refer the reader to \cref{sec:gradient-derivation}.
+vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
+this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
+viewpoint $c$) with variation of the density at voxel $k$, i.e.,
+$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.  A
+close-form expression of our Jacobian and its detailed derivation is
+given in \cref{sec:gradient-derivation}.
 
@@
 
-Here we detail the derivation of the gradient of the objective
-function:
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bm n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
-\end{equation}
-Here ${\bm i}^{\rm measured}_c$ is the image captured by camera $c$
-and ${\bm i}_c({\bm n})$ is an image modeled from the viewpoint of
-camera $c$ according to the density distribution ${\bm n}$. In
-\cref{sec:captured-image} article we show that ${\bm i}_c({\bm n})$
-can be expressed by
-\begin{align}
-  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
-      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
-  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
-  \nonumber \\
-  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
-  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
-  \label{eq:bigIA}
-\end{align}
-
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] \;.
-  \label{eq:gradient1}
-\end{align}
-Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$. Element $(\Theta,k)$ of
-this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
-viewpoint $c$) with variation of the density at voxel $k$, i.e.,
-$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.
-
-In order to describe the derivation of the Jacobian ${\bm J}_{{\bm
-    i}_c}({\bm n})$, we first show some results relating to
+Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
+    i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
 differentiation. Let $\vect{n}$ be a vector of length $q$. Let

### 2013-07-26 article.tex
bookmark

@@
   [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
-  \exp\{-\tau_c(k)\}
+  \exp[-\tau_c(k)]
   \;\;,
@@
   [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
-  \odot \exp\{-\vect{\tau}_c\}
+  \odot \exp(-\vect{\tau}_c)
   \;\;.
@@
 A camera pixel collects light from a narrow cone in the
-atmosphere. The cone includes some voxels, intersects with some other
-voxels, and oblivious to all the rest~(\cref{fig:projection}b).
+atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
 % \begin{figure}
@@
 % \end{figure}
-Thus light power captured at a pixel is a weighted sum of the power
-$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
-operation over ${\bm p}_c$. The measured image is column-stacked to a
-vector $N_{\rm pix}$ long. It is given by
+Overall, light power captured at a pixel is a weighted sum of the power
+$p_c(k)$ from all voxels.  This sum is formulated by a matrix
+operation over ${\bm p}_c$:
 \begin{equation}
   {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
-  \;\;.
+  \;\;,
   \label{eq:IcP}
 \end{equation}
+where ${\bm i}_c$ is the image, column-stacked to a
+vector $N_{\rm pix}$ long.
 
@@
 
-To simplify the case in study, let us assume there is only a single
+To simplify the case in study, we focus on situations in which there is only a single
 type of aerosol over a scene. Hence, the three-element vector

### 2013-07-27 article.tex
Bookmark after fixing Appendix

--- 2013-07-26 article.tex
@@
 %
+% Note:
+% Nice curly font is {\bm{\mathcal{D}}}
+%
 \newcommand{\OpSphere}{\mathbfcal{S}}
@@
 \newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
+\newcommand{\abbrev}[1]{\rm{#1}}
 \newcommand{\argmin}{\mathrm{arg}\min}
@@
     measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \Laplacian^T\Laplacian{\bm n} \;.
+  \transpose{\Laplacian}\Laplacian{\bm n} \;.
   \label{eq:gradient1}
@@
     i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
-differentiation. Let $\vect{n}$ be a vector of length $q$. Let
-$\vect{g}(\vect{n})$ be a vector function: it outputs a vector of
-length $r$. Let $\mat{B}$ be a $q \times r$ matrix and
-\begin{align}
-  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
+differentiation. Let $\vect{n}$ be a vector of length $m$. Let
+$\vect{a}(\vect{n})$ be a vector function: it outputs a vector of
+length $r$. Let $\mat{C}$ be a $m \times r$ matrix and
+\begin{align}
+  \vect{a}(\vect{n}) = \exp[-\transpose{\mat{C}}\vect{n}].
   \label{eq:example1}
@@
   \label{eq:partial2}
-  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
-  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
+  \PartDeriv{\vect{a}}{\vect{n}} &= - \mat{C} \,
+  \OpDiag{\exp[-\transpose{\mat{C}}\vect{n}]}
 \end{align}
@@
   \label{eq:partial4}
-  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
-      {\bm D}_c {\bm n})}}
+  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
   {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
-      {\bm D}_c {\bm n})}}
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
 \end{align}
@@
 we first note the following: Let $\vect{u}(\vect{n})$ be a vector
-function that outputs a vector of length $r$. Let $\mat{B}$ be a $r
-\times q$ matrix. Then,
+function that outputs a vector of length $r$. Let $\mat{C}$ be a $r
+\times m$ matrix. Then,
 \begin{align}
   \label{eq:partial1}
-  \PartDeriv{\transpose{\mat{B}} (\vect{g} \odot \vect{u})}{\vect{n}}
-  = \left[ \PartDeriv{\vect{g}}{\vect{n}} \OpDiag{\vect{u}} +
-    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{g}} \right] \mat{B}.
+  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
+  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
+    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
 \end{align}
@@
 Based on \cref{eq:partial4,eq:partial1,eq:partial3} we can derive a
-close-form expression for the Jacobian of \cref{eq:bigIA}:
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
+close-form expression for the Jacobian of \cref{eq:bigIA},
+\begin{align}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
   ,
@@
   \label{eq:gradient3}
-  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
+  \abbrev{A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
+  \abbrev{B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
   & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
@@
     ]} \nonumber \\
-  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+  \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
       aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}

### 2013-07-27 article.tex
bookmark

--- 2013-07-26 article.tex
@@
 \noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
-that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} $\sigma$ for
-interacting with the irradiance. The density of the particles is $n$. Per unit volume, the {\em extinction coefficient} is $\beta= \sigma n$.
+that includes particles of a certain type.
+Each particle has an {\em extinction cross section} for
+interacting with the irradiance. For an aerosol the cross section is denoted $\sigma^{\rm aerosol}$.
+The aerosol density is $n$. Per unit volume, the {\em extinction coefficient} due to aerosols is
+$\beta^{\rm aerosol}= \sigma^{\rm aerosol} n$. In addition, the atmosphere contains air molecules.
+The extinction coefficient due to the molecules is $\beta^{\rm air}$.
 The volume has infinitesimal length $dl$. Then, the relative portion
 of extinct SR irradiance is the unitless differential optical
-  depth, $d\tau= \beta dl=\sigma n dl$.
+  depth, $d\tau= (\beta^{\rm aerosol}+\beta^{\rm air}) dl$.
 The {\em optical depth} aggregates in extended propagation:
 \begin{align}
-  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
+  \tau= \int d\tau=\int (\beta^{\rm aerosol}+\beta^{\rm air}) dl
+       =\int (\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
+       = \tau^{\rm air}+ \int \sigma^{\rm aerosol} n dl \;,
   \label{eq:tau}
 \end{align}
-Through an attenuating volume, the {\em transmittance} exponentially
+where $\tau^{\rm air}=\int \beta^{\rm air} dl$.
+Through an attenuating atmosphere, the {\em transmittance} exponentially
 decays with the optical depth:
 \begin{align}
-  t=\exp(-\tau)
+  t=\exp(-\tau) \;.
   \label{eq:beer-lambert}
@@
 (to all directions), relative to the total extinction is given by the
-unitless {\em single scattering albedo} $\varpi$ of the particle. The
-{\em scattering coefficient} $\alpha$ is
-\begin{align}
-  \alpha= \varpi\beta=\varpi \sigma n \;.
+unitless {\em single scattering albedo} of the particle. For an aerosol,
+the single scattering albedo is denoted $\varpi^{\rm aerosol}$.
+The {\em scattering coefficient} due to aerosols in the volume is
+\begin{align}
+  \alpha^{\rm aerosol}= \varpi^{\rm aerosol}\beta^{\rm aerosol}
+                       =\varpi^{\rm aerosol} \sigma^{\rm aerosol} n \;.
   \label{eq:alph}
 \end{align}
-The angular distribution of scattering is determined by a {\em phase
-  function} $P$, which is normalized: its integral over all solid
-angles is unit. Part of the light scatters towards a camera's LOS, as
+The angular distribution of scattering by an aerosol is determined by a {\em phase function} $P^{\rm aerosol}$, which is normalized: its integral over all solid angles is unit.
+Part of the light scatters towards a camera's LOS, as
 illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
-is the scattering angle $\Phi^{\rm scatter}$. The {\em angular scattering coefficient}
-$\tilde\alpha$ is
-\begin{align}
-  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
-  = \varpi \sigma n P(\Phi^{\rm scatter}).
+is the scattering angle $\Phi^{\rm scatter}$. The {\em angular scattering coefficient} due to aerosols is
+\begin{align}
+  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) 
+  =  \alpha^{\rm aerosol} P^{\rm aerosol}(\Phi^{\rm scatter})
+  = \varpi^{\rm aerosol} \sigma^{\rm aerosol} n 
+        P^{\rm aerosol}(\Phi^{\rm scatter}).
   \label{eq:alphabasic}
 \end{align}
-
 The phase function is often approximated by a parametric expression,
@@
 \begin{align}
-  P_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 - g^2)(1+\mu^2)
+  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 - g^2)(1+\mu^2)
   (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
@@
 where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos \Phi^{\rm scatter}$.
-\\
-
-\noindent {\bf Air molecules}: Scattering by air molecules follows the
+
+Scattering by air molecules follows the
 {\em Rayleigh} model. The phase function is
@@
 \end{align}
-and the single scattering albedo is $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
-off approximately exponentially with altitude, with a
-characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
+and the single scattering albedo in visible light is $\varpi^{\rm air}$=1.
+Air molecular density falls off approximately exponentially with altitude $h$, with a characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
 \si{\km}$. Thus~\cite{Levi1980}, the coefficients for
@@
 view azimuth and elevation angles (relative to the zenith and north)
-are encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a
+are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
 distinct fixed location ${\bm x}$, capturing raw image
 $i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
-a principle of recovering the 3D atmospheric aerosols distribution,
+a principle of estimating the 3D atmospheric aerosols distribution,
 using such data. To show feasibility, we perform radiative transfer
@@
 simulates realistic scenes of arbitrary complexity.  The second model
-uses the single-Scattering approximation
+uses the single-scattering approximation
 (\cref{sec:single-scatt-model}). It is less accurate than MC, but
-derives an analytic closed form solution to the radiative
-transfer. This closed form enables simple inversion of the model, to
+solves radiative transfer in an analytic, closed form. This form enables simple inversion of the model, to
 estimate the underlying atmosphere (\cref{sec:inverse-problem}).
@@
   air}(k),\alpha^{\rm air}(k)\}$ and the aerosol parameters $\{
-\sigma^{\rm aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm
-  aerosol}(k),g(k)\}$ are constants, e.g., corresponding to the value
+\sigma^{\rm aerosol}(k),\varpi^{\rm aerosol}(k), n(k),g(k)\}$ are constants, e.g., corresponding to the value
 at each voxel center.  Following \cref{eq:tau}, the optical depth
@@
 \end{align}
-
-To simplify the case in study, we focus on situations in which there is only a single
+We focus on situations where there is only a single
 type of aerosol over a scene. Hence, the three-element vector
@@
   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
-  \exp\{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c
-  {\bm n})\}\odot [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
     aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-    scatter}_c) \odot{\bm n} ] \Big\} .
+    scatter}_c) \odot{\bm n} ] 
+  \odot   
+  \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c{\bm n})]
+    \Big\} .
   \label{eq:bigIA}
@@
 
-In general terms, the variables are the set \mbox{$\left\{{\bm
-      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
-        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
-denotes the spectral (color) channel.  There are $N_{\rm spectral}$
-spectral channels.  Thus, the number of unknown variables is in
-principle \mbox{$N_{\rm voxels}(1+3N_{\rm spectral})$}.
-
-Prior knowledge reduces the unknowns. For simplicity we assume a
-single aerosol type dominates a scene. Furthermore, in the following
-section we assume that we know the type of the particle
-\cite{Martonchik2009}. Hence, we focus here on retrieving ${\bm n}$.
+We seek to estimate the aerosol distribution. Most generally, this is the set 
+$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
+        g}_{\lambda}\right\}_{\lambda}\right\}$
+where some of the parameters depend on the spectral channel $\lambda$.
+Usually, however, a single aerosol type dominates a scene.
+Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}.
+Hence, we focus on estimating the density distribution ${\bm n}$.
 
@@
   = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
-\end{equation}
-Here $\Psi({\bm n})$ is a regularization term that expresses some
-prior knowledge on the solution and $\eta$ is the regularization
-coefficient.  We use $\Mask$ as a weight map to mask the influence of
-the sun and the horizon. These regions are prone to dominant multiple
-scattering.  One common measurement of smoothness are the second order
-derivatives.  These can be calculated using the \emph{Laplacian}
-operator, $\nabla^2$.  We enforce smoothness of the solution by
-minimizing the signal energy of the \emph{Laplacian} of the signal
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 
+  + \eta \Psi({\bm n})
+\end{equation}
+where $\Mask$ is a map that masks the areas around 
+the sun, which are overwhelmingly bright. %and the horizon.
+%These regions are prone to dominant multiple scattering. 
+In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term that expresses some prior knowledge on the distribution, while $\eta$ is a regularization weight.
+Since aerosol distributions are usually fuzzy,
+it can be beneficial that regularization be a {\em smoothness term}, which penalized energy in second order spatial derivatives (3D Laplacian). Hende, we use
 \begin{equation}
@@
 \end{equation}
-where $\Laplacian$ is a matrix representation of the \emph{Laplacian}
+where $\Laplacian$ is a matrix representation of the 3D \emph{Laplacian}
 operator.
@@
   \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
-  \Laplacian^T\Laplacian{\bm n} \;.
+    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \Laplacian^T\Laplacian{\bm n} \;.
   \label{eq:gradient1}
@@
 this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
-viewpoint $c$) with variation of the density at voxel $k$, i.e.,
-$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.  A
-close-form expression of our Jacobian and its detailed derivation is
+viewpoint $c$) with variation of the aerosol density at voxel $k$, i.e.,
+$\partial i_c({\bm \Theta})/\partial{n(k)}$.  A
+close-form expression of the Jacobian and its detailed derivation is
 given in \cref{sec:gradient-derivation}.

### 2013-07-27 article.tex

@@
   \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \Laplacian^T\Laplacian{\bm n} \;.
+    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \transpose{\Laplacian}\Laplacian{\bm n} \;.
   \label{eq:gradient1}

### 2013-07-27 article.tex
bookmark DOESNT COMPILE

@@
 \newcommand{\OpRot}{\mathbfcal{R}}
-\newcommand{\OpDistance}{\mathbfcal{D}}
+%\newcommand{\OpDistance}{\mathbfcal{D}}
+\newcommand{\OpDistance}{\bm{D}}
 \newcommand{\OpCumsum}{\mathbfcal{C}}
@@
 
-Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
-    i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
-differentiation. Let $\vect{n}$ be a vector of length $m$. Let
-$\vect{a}(\vect{n})$ be a vector function: it outputs a vector of
-length $r$. Let $\mat{C}$ be a $m \times r$ matrix and
-\begin{align}
-  \vect{a}(\vect{n}) = \exp[-\transpose{\mat{C}}\vect{n}].
-  \label{eq:example1}
-\end{align}
-In \cref{eq:example1}, the exponential is element-wise (not raising an
-operator to some power). Then
-\begin{align}
-  \label{eq:partial2}
-  \PartDeriv{\vect{a}}{\vect{n}} &= - \mat{C} \,
-  \OpDiag{\exp[-\transpose{\mat{C}}\vect{n}]}
-\end{align}
-Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
-into a diagonal matrix, whose main diagonal elements correspond to the
-elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
-\begin{align}
-  \label{eq:partial4}
-  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
-  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
-\end{align}
-In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
-known and constant.
-
-To calculate the derivative of the Hadamard product in \cref{eq:bigIA}
-we first note the following: Let $\vect{u}(\vect{n})$ be a vector
-function that outputs a vector of length $r$. Let $\mat{C}$ be a $r
-\times m$ matrix. Then,
+Here we detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to differentiation.  Let
+$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
+length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
+Then,
 \begin{align}
@@
 \end{align}
-Then,
+Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector $\vect{v}$
+into a diagonal matrix, whose main diagonal elements correspond to the
+elements of $\vect{v}$. Now, let
+\begin{align}
+  \vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n}).
+  \label{eq:example1}
+\end{align}
+In \cref{eq:example1}, the exponent is element-wise (not raising an
+operator to some power). Then
+\begin{align}
+  \label{eq:partial2}
+  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
+  \OpDiag{\exp(-{\mat{C}}\vect{n})}
+\end{align}
+Using \cref{eq:partial2},
+\begin{align}
+  \label{eq:partial4}
+  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
+  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
+\end{align}
+where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
 \begin{align}
   \label{eq:partial3}
-  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}}{\vect{n}}
+  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
   =
-  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
-  \nonumber \\
   \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
-  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
-\end{align}
-
-Based on \cref{eq:partial4,eq:partial1,eq:partial3} we can derive a
-close-form expression for the Jacobian of \cref{eq:bigIA},
-\begin{align}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
+\end{align}
+Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
+in close-form,
+\begin{align}
+%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
    ,
@@
   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  \abbrev{B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
-  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+  \abbrev{B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} %\nonumber\\
+%  & \;\;\; 
+      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
       aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
       scatter}_c) \odot{\bm n}
-    ]} \nonumber \\
-  \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
+    ]} 
+    %\nonumber \\
+  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+\end{align}
+
+%$\mathbb{D}$
 

### 2013-07-27 iccp2013.tex
added the iccp2013 article

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccp}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}

\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

%\iccpfinalcopy % *** Uncomment this line for the final submission

\def\iccpPaperID{19} % *** Enter the ICCP Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcpfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Sky Tomography for 3D Aerosol Distribution Recovery}

\author{Amit~Aides\\
  Electrical Engineering Dept.\\
  Technion - Israel Inst. Tech.\\
  Haifa 32000, Israel\\
  {\tt\small amitibo@tx.technion.ac.il} \and
  Yoav~Y.~Schechner\\
  Electrical Engineering Dept.\\
  Technion - Israel Inst. Tech.\\
  Haifa 32000, Israel\\
  {\tt\small yoav@ee.technion.ac.il} \and
  Michael~J.~Garay\\
  Jet Propulsion Laboratory\\
  California Inst. Tech.\\
  CA 91011, United States\\
  {\tt\small Michael.J.Garay@jpl.nasa.gov}
  % \and
  % Vadim~Holodovsky\\
  % Electrical Engineering Dept.\\
  % Technion - Israel Inst. Tech.\\
  % Haifa 32000, Israel\\
  % {\tt\small vholod@tx.technion.ac.il}
}

\maketitle
\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Aerosols effect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer. We propose a principle to recover the atmosphere
  as it really is: a three dimensional (3D), volumetric, transparent
  huge object. Tomography is the key to recovery. The process involves
  acquiring the sky lightfield by multi-view wide-angle photography on
  a very large scale. The tomography model is distinct, as the light
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.  We formulate an image formation model based
  on 3D radiative transfer. Model inversion is done using optimization
  methods, exploiting a closed-form gradient which we derive for the
  model-fit cost function. The problem is complex but tractable and
  parallelizable, eventually estimating the 3D aerosol distribution.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Lightfield and integral
imaging~\cite{bishop,horstmeyer,kim,levoy,Perwass} samples the optical
radiance distribution in location and direction. It is mainly used in
small-scale setups. This paper deals with a huge scale, up to Earth's
size.  The atmosphere allows light to pass through in multiple
locations and directions. Light is affected by this medium. Therefore,
in this paper we lay out a principle to recover this 3D medium using
measured and modeled lightfields (Fig.~\ref{fig:front}).
\begin{figure}[t!]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/front_img.pdf}}
  \caption{\small The sky is photographed from multiple viewpoints
    using wide angle (hemispherical) cameras, in a very wide area. The
    three dimensional distribution of aerosols in the atmosphere
    affects the images. This distribution is then recovered by a
    dedicated tomography formulation.}
  \label{fig:front}
\end{figure}

Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS~\cite{Seidel}.  The model turns
out to be {\em nonlinear, yet tractable}.

We do not deal with clouds here. Clouds scatter sunlight very strongly
and are easily observed. Hence they are directly recovered using
common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
On the other hand, aerosols have much more subtle visual effects and
are thus more difficult to recover. We focus on them.  In remote
sensing~\cite{diner}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}. In this
discipline, the atmosphere is often assumed to be plane-parallel, for
simplicity, using only 1D vertical radiative transfer. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{matronchik} with limited height
resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
recovery. Computational photography offers new ways to peer into
media. In addition to active
descattering~\cite{fuchs,kim,levoy,Marschner} and recovery of
refractive transparent objects~\cite{ihrke, Saito}, overcoming the
atmosphere~\cite{Joshi2,Milanfar} to view ground objects was studied
in horizontal, fixed
views~\cite{fattal,he,kopf,kratz,narasimhan2,oakley,Hschechner2,tan}. In
this paper, however, the medium itself, at all relevant altitudes is
the object of interest.

3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{dayan,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths. To keep safe, today's coarse sensing limits flight
capacity. A prominent example is the 2010 eruption of Iceland's
Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
much of Europe's airspace, grounding $\approx 100,000$
flights. Knowing the 3D distribution of aerosol density may indicate
safe 3D corridors to safely pass through, enhancing airspace
use. Viewing beyond the medium, atmospheric correction is needed, for
example, in satellite tracking of chlorophyll
distributions~\cite{johnsen}. Additional bodies in the solar system
have atmospheres. These objects can be viewed from multiple directions
by probes.  The approach described here may be helpful there.

We model passive optical tomographic imaging of 3D atmospheric
scatterer distributions in cloudless conditions. Then, we solve this
tomography problem, to recover the distribution. Recovery is
formulated as an optimization that minimizes a cost function. We
derive the gradient of this cost function, to enable efficient
optimization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Theoretical Background}
\label{sec:back}
\vspace{-0.2cm}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
$1/({\rm m}\cdot{{\rm strad}})$) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein function,
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Image Acquisition Principle}
\label{sec:setup} \vspace{-0.2cm}

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
\begin{figure*}[t!]
  \begin{center}
    \vspace{-0.4cm}
    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
  \end{center}\vspace{-1.5cm}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}

Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,matronchik,vanMol}. However, current multiview
spaceborne systems are very coarse. For example, aerosol retrieval in
the most complex instrument, MISR, requires spatial blocks that are
about $17\times 17$km wide, each observed from just 9 views
along-track. This practically leads to vertical radiative transfer
analysis, degenerating atmospheric analysis to 1D. Experimental
airborne instruments under development~\cite{baxter,dinerDavis10} may
provide better, if still coarse resolution once they are operational.

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{oliver, Peleg, kopal}
sky-cameras, looking upwards and capturing the sky lightfield.
Moreover, satellites image close to the orbit track (a 1D array of
viewpoints). In contrast, land-based cameras can form a 2D set of
viewpoints~\cite{Snavely} as easy or hard as a 1D
grid~\cite{Joshi}. However, before designing and setting up such a
very large scale system requires assessment of many details that had
not been explored. These include camera specifications needed to
recover typical distributions. Hence, a major theoretic and numerical
research phase is ahead.

This paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Forward Model}
\label{sec:skymodel} \vspace{-0.2cm}

This section describes models for image formation. In the consecutive
section, we describe how the image formation is inverted to recover
the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
Ground-based wide-angle sky-cameras capture the sky lightfield from
below. Per viewpoint, the view azimuth and elevation angles (relative
to the zenith and north) are encapsulated in the vector
${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
camera's location ${\bf x}$ is fixed, while any pixel in a frame
represents an angle ${\bf{\Theta}}$.  The measured radiance in all
locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
lightfield.
% Alternatively, several ground-based cameras can be mounted on moving
% vehicles, assuming that the aerosol distribution does not change
% much during the time-lapse of the camera trajectory.

Sunlight is scattered in the medium, creating {\em
  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
generally different, depending on the distribution of aerosols both
along a LOS, and along the SRs that hit the LOS.  As
Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
  x},{\bf{\Theta}}$) cut through different sets atmospheric
voxels. Thus, for each view, the radiance scattered from a voxel is
attenuated differently, depending on the distribution of aerosols
along the LOS~\cite{hansen}.

A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints. The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics. We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera. This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply. Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\

\vspace{-0.35cm}
\noindent
1. Attenuation of a SR propagating from the top of the atmosphere
(TOA) to voxel $k$. \\

\vspace{-0.35cm}
\noindent
2. Light scattering at voxel $k$, towards a camera.\\

\vspace{-0.35cm}
\noindent
3. Light attenuation on the LOS from voxel $k$ to the camera.

\noindent
Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
involves the scattering coefficient at voxel $k$, described in
Sec.~\ref{sec:scattering}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optical Depth}
\label{sec:optical-depth}

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
In addition, the infinitesimal volume contain also air
molecules. Hence, the overall extinction and scattering coefficients
in this small volume are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. As approximation, assume that within any
voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
constants, e.g., corresponding to the value at each voxel
center. These parameters may change between voxels.

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
$q$. The geometric length of this intersection line segment is $\Delta
z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
  [0,1]$} expresses how much of the vertical thickness of $q$ is
crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
optical depth between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta(q)\Delta z  f_{\rm SR}(q)
  \;\;.
  \label{eq:lSRn}
\end{equation}
Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
\begin{equation}
  \tau_{\rm SR}(k)=
  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lSRaa}
\end{equation}
where
\begin{equation}
  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta^{\rm air}(q)  f_{\rm SR}(q)
  \label{eq:lSRair}
\end{equation}
and
\begin{equation}
  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
  \label{eq:lSRaeros}
\end{equation}

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
      & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
depths due to aerosols (See Fig.~\ref{fig:optidepth}):
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$. The overall
    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
    optical depth affecting $k$. It is formalized in matrix-vector
    operations. }
  \label{fig:optidepth}
\end{figure}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $\Delta z f_{\rm
  LOS_c}(q)/\cos\Phi^{\rm LOS}_c$: the factor $f_{\rm LOS_c}(q)\in
[0,1]$ expresses how much of the vertical thickness of $q$ is crossed
by the LOS.  Analogously to
Eqs.~(\ref{eq:lSRaa},\ref{eq:lSRair},\ref{eq:lSRaeros}), The optical
depth %path length
along a LOS to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm LOS}_c}
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  f_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)=
  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~%\nonumber
  ~~~~~
  \\
  % ~~~~
  \frac{\Delta z}{\cos\Phi^{\rm LOS}_c} \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm LOS_c}(q).
  \nonumber
\end{align}
Eq.~(\ref{eq:lLOSaeros}) leads to a vector of LOS optical depths due
to aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta z f_{\rm LOS_c}(q)}{\cos\Phi^{\rm LOS}_c}
      & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of LOS optical
depths due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bf D}_c=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using Eq.~(\ref{eq:rayleighbeta}) for $\beta^{\rm air}$ in all voxels,
the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle.

Using
Eqs.~(\ref{eq:lSRaa},\ref{eq:tauSRvec1},\ref{eq:lLOSair},\ref{eq:tauLOSvec1},\ref{eq:Dtotal},\ref{eq:tauairtotal}),
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
(See Fig.~\ref{fig:optidepth}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scattering}
\label{sec:scattering}

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
which is pre-calculated.
% Eq.~(\ref{eq:mu}) yields its cosine, $\mu_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using
Eqs.~(\ref{eq:alphabasic},\ref{eq:rayleighP},\ref{eq:betaer},\ref{eq:betair}),
the angular scattering coefficients across the domain are expressed in
vector form by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)   \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bf g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in Eq.~(\ref{eq:aerosol_scatter}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Image Capture}
\label{sec:captured-image}

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(Eqs.~\ref{eq:beer-lambert},\ref{eq:betair},\ref{eq:tautotal}), the
radiant power contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  e^{-[\tau_c(k)]}
  \;\;.
  \label{eq:ick}
\end{equation}
A column-stack vector of all voxel contributions is
\begin{equation}
  {\bf p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot e^{-\vect{\tau}_c}
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest.  Thus light power captured at a
pixel is weighted sum of the power $p_c(k)$ from all voxels: most
voxels have null weight, since they fall outside the pixels's conic
field of view, while the rest of the voxels are aggregated.

This linear sum is formulated by a matrix operation over ${\bf
  p}_c$. The measured image is column-stacked to a vector $N_{\rm
  pix}$ long. It is given by
\begin{equation}
  {\bf i}_c= {\vect{\Pi}}_c{\bf p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}
The $N_{\rm pix}\times N_{\rm voxels}$ sparse matrix ${\vect{\Pi}}_c$
expresses {\em projection} of light into camera $c$. For pixel
$\Theta$ and voxel $k$, there is an {\em intersection} volume ${\bf
  V}_c(\Theta,k)$ between the cone volume of the pixel's field of
view, and the voxel, as illustrated in Fig.~\ref{fig:projection}.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/sensor.pdf_tex}}
  \caption{\small An image pixel captures light emanating in a cone in
    space. Voxels that fully or partially fall in this cone are sensed
    by the pixel. Factoring out scattering and attenuation (which are
    dealt elsewhere in our analysis), the relative contribution of
    each voxel depends on its distance and intersection with the
    cone. This is formalized a matrix-vector operation.}
  \label{fig:projection}
\end{figure}
The corresponding element in the matrix ${\vect{\Pi}}_c$ is
\begin{equation}
  \Pi_c(\Theta,k)=
  % \frac{a}{|{\bf V}(k)|}
  a
  \iiint_{{\bf V}_c(\Theta,k)}
  \frac{1}{[R({\bf v})]^2} d{\bf v}
  \;\;,
  \label{eq:Pc}
\end{equation}
where $a$ is the effective area of the camera lens.
% and $|{\bf V}(k)|$ is the volume of voxel $k$.
The distance $R({\bf v})$ is measured between the camera and an
infinitesimal volume element at ${\bf v}\in {\bf V}_c(\Theta,k)$.

Combining Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the
captured image is thus
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bf D}_c
      (\vect{\sigma} \odot {\bf n})]} \right\}
  \label{eq:bigIc}
\end{align}
Most often, there is only a single type of aerosol over a
scene. Hence, the three-element vector $[{\sigma}^{\rm
  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
the density distribution ${\bf n}$ is variable. Then,
Eq.~(\ref{eq:bigIc}) degenerates to
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inverse Problem}
\label{sec:inverse-problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unknowns and Prior Knowledge}
\label{sec:prior}

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bf n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bf g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

Prior knowledge reduces the unknowns. Sec.~\ref{sec:captured-image}
mentions a prior: in many cases a single aerosol type dominates a
scene. Then, the three-element vector $[\varpi^{\rm
  aerosol},{\sigma}^{\rm aerosol},g]$ is rather spatially uniform. In
such cases, the set of unknowns reduces to $ {\cal V}= \left\{ {\bf
    n}, \left\{ {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
      aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda} \right\} $ and
\mbox{$|{\cal V}|=N_{\rm voxels}+3N_{\rm spectral}$}.

Furthermore, the elements in the aerosol characteristics set $\left\{
  {\varpi}^{\rm aerosol}_{\lambda},{\sigma}^{\rm
    aerosol}_{\lambda},g_{\lambda} \right\}_{\lambda}$ is not
arbitrary, since all these characteristics have physical origins. This
set is constrained to comply with what nature allows (aerosol
classes).  This significantly constrains the unknown
characteristics. State-of-the-art aerosol retrieval, as used by NASA's
MISR products indeed employ an aerosol-class prior. Types of aerosol
mixtures are discretized to $N_{\rm models}=74$
classes~\cite{matronchik}, called {\em models}. Each class $m$
represents aerosols having a distinct characteristics set.  State of
the art retrieval is 1D (only vertical radiative transfer per large
areas). Nevertheless, we use this prior in our 3D problem. Then, the
set of unknowns reduces to $ {\cal V}= \left\{ {\bf n},m \right\}$ and
\mbox{$|{\cal V}|=N_{\rm voxels}+N_{\rm models}$}.

The atmosphere is photographed from $N_{\rm views}$ viewpoints. Each
photograph provides $N_{\rm pix}$ measurements (pixels), {\em
  including} their possible division to color channels. Hence, the
data at our disposal comprises $N_{\rm views}N_{\rm pix}$
measurements.  For the recovery task to be well-posed, it is necessary
that $N_{\rm views}N_{\rm pix}>|{\cal V}|$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Objective Function}
\label{sec:objective-function}

The inverse problem (tomography) seeks recovery of the 3D aerosol
distribution in the atmosphere. From
Eqs.~(\ref{eq:alpha_matrix},\ref{eq:bigIc},\ref{eq:bigIA},\ref{eq:calV}),
the images $\{ {\bf i}_c\}_{c=1}^{N_{\rm views}}$ depend on the
variables set ${\cal V}$, particularly on the unknown field ${\bf
  n}$. The recovery task is phrased as optimization of an objective
function, that fits the image-formation
model~(\ref{eq:bigIc},\ref{eq:bigIA}) to measured photographs $\{ {\bf
  i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:mingenobjective}
  \hat{\cal V} = \argmin_{{\cal V}\in {\cal C}} F({\cal V})
\end{equation}
where
\begin{equation}
  \label{eq:genobjective}
  F({\cal V}) = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\cal V})\| + {\rm Regularization}({\cal V})
  \;.
\end{equation}
Here ${\cal C}$ is a constraints set, which encapsulates part of the
prior knowledge, as well as nonnegativity bounds, while $\|~\|$ is
some error-distance measure.  Here ${\rm Regularization}({\cal V})$
describes spatial regularization terms of the variables, such as
smoothness, or a blobby or layered structure.

Spatial regularization can help overcome lack of data, if $N_{\rm
  views}$ is too small, and it is definitely helpful. In this work,
however, we formulate and demonstrate the basic principle of our
tomography task, hence we proceed without regularization. Relying on
prior knowledge described in Sec.~\ref{sec:prior}, the problem
complexity is by far dominated by the $N_{\rm voxels}$-large array
${\bf n}$, which is continuously valued. Hence, we focus here on
retrieving ${\bf n}$ through continuous optimization. Relying on the
least-squares measure, we seek:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bf n} =
  \argmin_{{\bf n}} F({\bf n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bf n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
\end{equation}
This is solved using standard optimization tools. Fast optimization
that leads to to local minima ($F$ is not convex) exploits the
gradient of $F$.

Since our model uses close-form expressions, $F$ is
differentiable. The gradient of $F$ with respect to ${\bf n}$ is
\begin{align}
  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
    measured}_c - {\bf i}_c({\bf n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.

Denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$ into a
diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$.  A close-form expression of our Jacobian is
\begin{align}
  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bf n}
    ]} \nonumber \\
  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of
Eqs.~(\ref{eq:gradient2},\ref{eq:gradient3}), we refer the reader to
the supplementary material.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations}
\label{sec:simul}

To test the model, we made simulations based on atmospheric models in the literature. Here are the details.\\

\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$. Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of
$L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm B}=255:236:224$.\\

\noindent{\bf Dimensions}: The domain of sky we simulate and recover has area of $50\times 50$km, and it extends from the ground up to altitude of 10km. This volume is divided to a $50\times50\times100$ grid, where each voxel has area of $1\times1$km and vertical thickness of 100 meters. The dimension of the problem is thus $250,000$ variables.\\

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm B}]=[16.5,16.2,15.9][1/\mu m^2]$.  Its
single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all channels.

We simulated various spatial distributions. All were set as a product
of two functions. The first function is an exponential
decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {\sigma^{\rm aerosol}_{\rm G} \mathrm{MFP^{sea
        level}}} \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2\ km$. This expresses a general trend of
reduced atmospheric density with height. Here the mean free path (MFP)
of the aerosols layer at sea level was set to $\mathrm{MFP^{sea
    level}}=1/5~{\rm[1/km]}$.
% is a typical characteristic thickness of the aerosol
% layer~\cite{Levi1980}.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bf n}^{\rm true}={\bf w}_1\odot {\bf w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene
(Fig.~\ref{fig:simulation1}) using two ellipsoid blobs: \begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small Simulated 3D aerosol distribution composed of {\em
      Haze Blobs}. Its reconstruction is shown in
    Fig.~\ref{fig:front}. Color represents aerosol density. The
    density units are $10^{15}~{\rm particles}/{\rm cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude $3.3km$, and has horizontal width of $32km$ and vertical thickness of $2.8km$. The second ellipsoid is centered at altitude $6.6km$, and has lateral width of $24km$ and vertical thickness of $2.1km$. Note that the horizontal widths are much larger than the vertical ones. This is consistent with scales of atmospheric aerosol distributions.\\

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used 95
viewpoints on a grid, each view $\approx 4.4$km from its neighbors.
The resolution of each camera is low: $128\times 128$ pixels,
expressing the fact that cloudless (yet hazy) sky images are rather
smooth, hence there is no need for high image resolution. Each pixel
has full-well depth of 40000 electrons, which corresponds to the
brightest pixel value. Each measurement has photon noise, which is
Poissonian distributed, according to each image-pixel value $i_c$ and
the full-well depth. For example, Fig.~\ref{fig:simulation-results1}
shows two modeled photographs
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/ref_images.pdf}}
  \caption{\small Rendered photographs (contrast enhanced)
    corresponding to different viewpoints, of sky that includes {\em
      Haze Blobs}. A yellow dot marks the Sun location. Dashed white
    circles mark elevation angles.}
  \label{fig:simulation-results1}
\end{figure}
of the  {\em Haze Blobs} scene that corresponds to Fig.~\ref{fig:simulation1}.\\

\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
with 8GB
DDR3 memory per core. Out of it, we used 8 nodes, corresponding to 96 cores. Each core was dedicated to rendering a modeled image (in each interaction) as if captured by one of the 95 cameras. Each iteration (varying the model according to the gradient-based algorithm and varying all the rendered images) took $\approx 7$sec.\\

\noindent{\bf Optimization}: We used the L-BFGS-B
algorithm~\cite{BFGS}. The algorithm was initialized by ${\bf
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total. For
example, Fig.~\ref{fig:objective} shows
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/objective.pdf}}
  % \includegraphics[width=\columnwidth]{images/objective.pdf}
  \caption{\small The decay of $\log F({\bf n})$ with the iteration
    index.}
  \label{fig:objective}
\end{figure}
the progression of the objective as a function of the iteration
number, when recovering the the {\em Haze Blobs} scene.

% 26, 48, 1320, 590
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Results}
\label{sec:optimization-results}

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in Fig.~\ref{fig:simulation1}, while the
recovered 3D distribution is visualized in Fig.~\ref{fig:front}. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bf n}  - {\bf n}^{\rm true} \|_1}
  {\| {\bf n}^{\rm true} \|_1} ,
  \hspace{-0.05cm}
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

We created a {\em Haze Front} scene. Fig.~\ref{fig:simulation2}a shows
an iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation2}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of a
    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation2}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude $5km$, has
vertical thickness of $4km$ and length of $32km$ (only part of which
enters the volume). The haze front stretches across the width of the
volume.  Fig.~\ref{fig:simulation2}b visualizes the recovered 3D
distribution of this scene. For the {\em Haze Front},
$\epsilon=0.198$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}

We describe a new way to sense the 3D atmosphere. We show feasibility
of departing from common 1D aerosol distribution models, in favor of
detailed 3D analysis.  The paper describes both a novel data
acquisition system concept for this recovery task, and a dedicated
algorithm for reconstructing aerosol distributions.

Even without regularization, the reconstruction algorithm handles
arbitrary density distributions. Using more prior knowledge,
e.g. spatial smoothness will improve the recovery.  The algorithm uses
a single scattering model. This approximation is valid when the
optical depth is small, which is common. To handle dense atmospheric
conditions (smoke, clouds), multi-scattering must be incorporated.

The goal, of coarse, is to deploy such a system on a very large
scale. However, this must first ensure that camera units are both cost
effective and field-robust, and that their positioning density is
proper. This will require a long-term engineering effort. Camera
specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research and development phase.  The new sensing modality and object
of interest offer a new domain for computational photography
problems. For example, how can compressed sensing principles be
employed here? How can priors be used to make data acquisition more
efficient? How can such a system be calibrated over time? Many such
questions and solutions would rise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\small
  % \bibliographystyle{ieee} \bibliography{atmosphere}

  \begin{thebibliography}{10}\itemsep=-1pt

  \bibitem{baxter} B.~Baxter, B.~Hooper, J.~Williams, and J.~Dugan.
    \newblock Polarimetric remote sensing of ocean waves.  \newblock
    Proc. MTS/IEEE OCEANS 2009.

  \bibitem{bishop} T.~E. Bishop, S.~Zanetti, and P.~Favaro.  \newblock
    Light field superresolution.  Proc. IEEE ICCP 2009.

  \bibitem{breon} F.~Br\'{e}on.  \newblock An analytical model for the
    cloud-free atmosphere/ocean system reflectance.  \newblock {\em
      Remote Sensing of Environment}, 43:179 -- 192, 1993.

    % \bibitem{chang} G.~C. Chang and R.~W. Gould.  \newblock
    %   Comparisons of optical properties of the coastal ocean derived
    %   from satellite ocean color and in situ measurements.
    %   \newblock {\em Opt. Express}, 14:10149--10163, 2006.

  \bibitem{BBradiance} M.~Charity.  \newblock Blackbody color
    datafile, 2001.  \newblock [Online; accessed 6-August-2012].

    % \bibitem{chud} A.~Chudnovsky, A.~Kostinski, L.~Herrmann,
    %   I.~Koren, G.~Nutesku, and E.~Ben-Dor.  \newblock Hyperspectral
    %   spaceborne imaging of dust-laden flows: Anatomy of saharan
    %   dust storm from the Bod\'{e}l\'{e} depression.  \newblock {\em
    %   Remote Sensing of Environment}, 115:1013 -- 1024, 2011.

  \bibitem{oliver} O. Cossairt, D. Miau, and S.K. Nayar.  \newblock
    Gigapixel Computational Imaging.  \newblock Proc. IEEE ICCP 2011.

  \bibitem{matronchik} J.~M. David, D.~J. Diner, R.~Kahn,
    T.~P. Ackerman, M.~M. Verstraete, B.~Pinty, and H.~R. Gordon.
    \newblock Techniques for the retrieval of aerosol properties over
    land and ocean using multi-angle imaging.  \newblock {\em IEEE
      Trans. Geoscience and Remote Sensing}, 36:1212--1227, 1998.

    % \bibitem{martonchikBook} J.~M. David, D.~J. Diner, R.~Kahn,
    %   T.~P. Ackerman, M.~M. Verstraete, B.~Pinty, and H.~R. Gordon.
    %   \newblock Techniques for the retrieval of aerosol properties
    %   over land and ocean using multi-angle imaging.  \newblock {\em
    %   IEEE Trans. Geoscience and Remote Sensing}, 36:1212--1227,
    %   1998.

  \bibitem{dayan} U.~{Dayan}, B.~{Ziv}, T.~{Shoob}, and Y.~{Enzel}.
    \newblock {Suspended dust over southeastern Mediterranean and its
      relation to atmospheric circulations}.  \newblock {\em
      Int. J. Climatology}, 28:915--924, 2008.

  \bibitem{dinerDavis10} D.~J. Diner, A.~Davis, B.~Hancock, S.~Geier,
    B.~Rheingans, V.~Jovanovic, M.~Bull, D.~M. Rider, R.~A. Chipman,
    A.-B. Mahler, and S.~C. McClain.  \newblock First results from a
    dual photoelastic-modulator-based polarimetric camera.  \newblock
    {\em Appl. Opt.}, 49:2929--2946, 2010.

    % \bibitem{dinerDavis07} D.~J. Diner, A.~Davis, B.~Hancock,
    %   G.~Gutt, R.~A. Chipman, and B.~Cairns.  \newblock
    %   Dual-photoelastic-modulator-based polarimetric imaging concept
    %   for aerosol remote sensing.  \newblock {\em Appl. Opt.},
    %   46(35):8428--8445, 2007.

  \bibitem{diner} D.~J. Diner and J.~V. Martonchik.  \newblock
    Atmospheric transmittance from spacecraft using multiple view
    angle imagery.  \newblock {\em Appl. Opt.}, 24:3503--3511, 1985.

  \bibitem{fattal} R.~Fattal.  \newblock Single image dehazing.
    \newblock In {\em ACM SIGGRAPH}, 72:1--72:9, 2008.

  \bibitem{fuchs} C.~Fuchs, M.~Heinz, M.~Levoy, H.-P. Seidel, and
    H.~P.~A. Lensch.  \newblock Combining confocal imaging and
    descattering.  \newblock {\em Computer Graphics Forum},
    27:1245--1253, 2008.

  \bibitem{gorbunov} M.~Gorbunov, S.~Sokolovsky,
    L.~Bengtsson, %and M.-P.-I. f{\"u}r Meteorologie.
    \newblock {\em Space Refractive Tomography of the Atmosphere:
      Modeling of Direct and Inverse Problems}.  \newblock
    Max-Planck-Institut f{\"u}r Meteorologie report, 1996.

  \bibitem{gregson} J.~Gregson, M.~Krimerman, M.~B. Hullin, and
    W.~Heidrich.  \newblock Stochastic tomography and its applications
    in 3D imaging of mixing fluids.  \newblock {\em ACM TOG},
    31:52:1--52:10, 2012.

  \bibitem{hansen} J.~Hansen and L.~Travis.  \newblock Light
    scattering in planetary atmospheres.  \newblock {\em Space Science
      Reviews}, 16:527--610, 1974.

  \bibitem{he} K.~He, J.~Sun, and X.~Tang.  \newblock Single image
    haze removal using dark channel prior.  \newblock {\em IEEE
      Trans. PAMI}, 33(12):2341 --2353, 2011.

  \bibitem{horstmeyer} R.~Horstmeyer, G.~Euliss, R.~Athale, and
    M.~Levoy.  \newblock Flexible multimodal camera using a light
    field architecture.  \newblock Proc. IEEE ICCP, 2009.

  \bibitem{ihrke} I.~Ihrke, K.~N. Kutulakos, H.~P.~A. Lensch,
    M.~Magnor, and W.~Heidrich.  \newblock State of the art in
    transparent and specular object reconstruction, 2008.

  \bibitem{johnsen} S.~Johnsen and H.~M. Sosik.  \newblock Shedding
    light on light in the ocean.  \newblock {\em Oceanus}, 43:24--28,
    2004.

  \bibitem{Joshi} N. Joshi, W. Matusik, and S. Avidan.  \newblock
    Natural Video Matting using Camera Arrays.  \newblock {\em ACM
      TOG} 25, 2006

  \bibitem{Joshi2} N. Joshi, and M. Cohen.  \newblock Seeing
    Mt. Rainier: Lucky Imaging for Multi-Image Denoising, Sharpening,
    and Haze Removal.  \newblock IEEE ICCP 2010.

  \bibitem{kalashnikova} O.~V. Kalashnikova, M.~J. Garay, A.~B. Davis,
    D.~J. Diner, and J.~V.  Martonchik.  \newblock Sensitivity of
    multi-angle photo-polarimetry to vertical layering and mixing of
    absorbing aerosols: Quantifying measurement uncertainties.
    \newblock {\em J. Quantitative Spectroscopy and Radiative
      Transfer}, 112:2149 -- 2163, 2011.

  \bibitem{kim} J.~Kim, D.~Lanman, Y.~Mukaigawa, and R.~Raskar.
    \newblock Descattering transmission via angular filtering.
    \newblock In. Proc. ECCV, 86--99, 2010.

    % \bibitem{kokhan} A.~Kokhanovsky.  \newblock {\em Light
    %   Scattering Media Optics}.  \newblock Springer Praxis Books /
    %   Environmental Sciences, 2005.

  \bibitem{kopal} S.~J. Koppal, I. Gkioulekas, T. Zickler, and
    G. Barrows \newblock Wide-angle micro sensors for vision on a
    tight budget \newblock In {\em Proc. IEEE CVPR}, 2011

  \bibitem{kopf} J.~Kopf, B.~Neubert, B.~Chen, M.~F. Cohen,
    D.~Cohen-Or, O.~Deussen, M.~Uyttendaele, and D.~Lischinski.
    \newblock Deep photo: Model-based photograph enhancement and
    viewing.  \newblock {\em ACM TOG}, 27:116:1--116:10, 2008.

  \bibitem{kratz} L.~Kratz and K.~Nishino.  \newblock Factorizing
    scene albedo and depth from a single foggy image.  \newblock In
    {\em Proc. IEEE ICCV}, 2009.

  \bibitem{Levi1980} L.~Levi.  \newblock {\em Applied Optics},
    volume~2.  \newblock Jhon Wiley \& Sons, Inc, 1980.

  \bibitem{levoy} M.~Levoy, B.~Chen, V.~Vaish, M.~Horowitz,
    I.~McDowall, and M.~Bolas.  \newblock Synthetic aperture confocal
    imaging.  \newblock {\em ACM TOG}, 23(3):825--834, Aug. 2004.

    % \bibitem{levy} M.~Levy, Y.~Lehahn, J.-M. Andre, L.~Memery,
    %   H.~Loisel, and E.~Heifetz.  \newblock {Production regimes in
    %   the northeast Atlantic: A study based on Sea-viewing Wide
    %   Field-of-view Sensor (SeaWiFS) chlorophyll and ocean general
    %   circulation model mixed layer depth}.  \newblock {\em
    %   J. Geophys. Res.}, 110(C7):C07S10, 2005.

  \bibitem{Seidel} A. Lintu, L. Hoffmann, M. Magnor, H.~P.~A. Lensch,
    H. Seidel \newblock 3D Reconstruction of Reflection Nebulae from a
    Single Image \newblock Proc. Vision, Modeling, and Visualization,
    2007

  \bibitem{Martonchik2009} J.~V. Martonchik, R.~A. Kahn, and
    D.~J. Diner.  \newblock {Retrieval of aerosol properties over land
      using MISR observations}.  \newblock In A.~A. Kokhanovsky and
    G.~Leeuw, editors, {\em Satellite Aerosol Remote Sensing over
      Land}, pages 267--293, Springer Praxis Books, Berlin 2009.

  \bibitem{messer} H.~Messer, A.~Zinevich, and P.~Alpert.  \newblock
    Environmental sensor networks using existing wireless
    communication systems for rainfall and wind velocity measurements.
    \newblock {\em IEEE Instrumentation Measurement Mag.}, 15:32 --38,
    2012.

  \bibitem{Saito} D. Miyazaki, M. Saito, Y. Sato, and K. Ikeuchi.
    \newblock Determining surface orientations of transparent objects
    based on polarization degress in visible and infrared wavelengths.
    \newblock {\em JOSA A}, 19:687-694, 2002.

  \bibitem{vanMol} B.~van Mol and K.Ruddick.  \newblock The compact
    high resolution imaging spectrometer (CHRIS): the future of
    hyperspectral satellite sensors.  \newblock Airborne Imaging
    Spectros. Worksh., 2004.

  \bibitem{Marschner} J.~T. Moon, B. Walter, and S.~R. Marschner.
    \newblock Rendering Discrete Random Media Using Precomputed
    Scattering Solutions \newblock Eurographics Symposium on Rendering
    2007

    % \bibitem{moses} W.~J. Moses, A.~A. Gitelson, S.~Berdnikov, and
    %   V.~Povazhnyy.  \newblock Estimation of chlorophyll- a
    %   concentration in case ii waters using modis and meris
    %   data-successes and challenges.  \newblock {\em Environmental
    %   Research Letters}, 4:045005, 2009.

  \bibitem{narasimhan2} S.~G. Narasimhan and S.~K. Nayar.  \newblock
    Vision and the atmosphere.  \newblock {\em
      Int. J. Comput. Vision}, 48:233--254, 2002.

  \bibitem{oakley} J.~P. Oakley and B.~L. Satherley.  \newblock
    Improving image quality in poor visibility conditions using a
    physical model for contrast degradation.  \newblock {\em
      Trans. Img. Proc.}, 7:167--179, 1998.

  \bibitem{Peleg} S. Peleg, M. Ben-Ezra, and Y. Pritch.  \newblock
    OmniStereo: Panoramic Stereo Imaging \newblock {\em IEEE
      Trans. PAMI}, 279-290, 2001.

  \bibitem{Perwass} C. Perwass and L. Wietzke.  \newblock Single lens
    3D-camera with extended depth-of-field.  \newblock SPIE 8291,
    Human Vision and Electronic Imaging XVII, 2012

  \bibitem{Hschechner2} Y.~Y. Schechner, S.~G. Narasimhan, and
    S.~K. Nayar.  \newblock Polarization-based vision through haze.
    \newblock {\em Appl. Opt.}, 42:511--525, 2003.

  \bibitem{seiz} G. Seiz, E. P. Balsavias and A. Gruen.  Cloud mapping
    from the ground: use of photogrammetric methods.  {\em
      Photogrammetric Eng. Rem. Sense} 68:941-951, 2002.

  \bibitem{Snavely} \newblock N. Snavely, I. Simon, M. Goesele,
    R. Szeliski, S.~M. Seitz.  \newblock Scene Reconstruction and
    Visualization From Community Photo Collections.  {\em Proceedings
      of IEEE}, 2010.

  \bibitem{tan} R.~Tan.  \newblock Visibility in bad weather from a
    single image.  \newblock In {\em Proc. IEEE CVPR}, 2008.

  \bibitem{sun_composition} Wikipedia.  \newblock Sunlight ---
    wikipedia{,} the free encyclopedia, 2012.  \newblock [Online;
    accessed 6-August-2012].

  \bibitem{wright} T.~E. Wright, M.~Burton, D.~M. Pyle, and
    T.~Caltabiano.  \newblock {Scanning tomography of SO2 distribution
      in a volcanic gas plume}.  \newblock {\em Geophys. Res. Lett.},
    35:L17811, 2008.

  \bibitem{BFGS} C.~Zhu, R.~H. Byrd, P.~Lu, and J.~Nocedal.  \newblock
    Algorithm 778: L-BFGS-B: Fortran subroutines for large-scale
    bound-constrained optimization.  \newblock {\em ACM
      Trans. Math. Softw.}, 23:550--560, 1997.

  \bibitem{Milanfar} X. Zhu and P. Milanfar.  \newblock Removing
    atmospheric turbulence via space-invariant deconvolution.
    \newblock {\em IEEE Trans. PAMI} 35:157-170, 2013

  \end{thebibliography}

}

\end{document}

%
% David brady
% Sing Bing Kang
%
% keep article 20 and remove all other citations
%

### 2013-07-27 article.tex
bookmark

@@
 \newcommand{\Laplacian}{\mathbfcal{L}}
-\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
+%\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
+\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
 \newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
@@
 
-Any voxel generally contains both air molecules and aerosols.  We
+Any voxel generally contains both air molecules and aerosols.
+We focus on situations where there is only a single type of aerosol over a scene. Hence, the three-element vector
+$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
+the scene, but the density distribution ${\bm n}$ is variable. As a numerical approximation,
 assume that within any voxel, the molecular parameters $\{ \beta^{\rm
-  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol parameters $\{
-\sigma^{\rm aerosol}(k),\varpi^{\rm aerosol}(k), n(k),g(k)\}$ are constants, e.g., corresponding to the value
+  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density $n(k)$ are constants, e.g., corresponding to the value
 at each voxel center.  Following \cref{eq:tau}, the optical depth
@@
   \vect{\tau}_c= \vect{\tau}_c^{\rm air}
-  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
+  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
   \;\;.
@@
 \end{equation}
-where the operator $\odot$ denotes the Hadamard (element-wise)
-product. This vector depends on the variables $\vect{\sigma}$ and
-${\bm n}$, the aerosol extinction and density at each voxel,
-respectively.
 
@@
 scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
-camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
-  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
+camera $c$. 
+%Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
 Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
@@
   \tilde{\vect{\alpha}}^{\rm air}_c =
-  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
-  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
-  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
-    g}(\vect{\Phi}^{\rm scatter}_c) \;.
+      \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
+      \quad
+%  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
+%  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
+%    g}(\vect{\Phi}^{\rm scatter}_c) \;.
+  \tilde{\vect{\alpha}}^{\rm aerosol}_c = 
+       \varpi^{\rm aerosol} \sigma^{\rm aerosol} 
+        {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
   \label{eq:alpha_matrix}
 \end{equation}
-The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
-the phase function, in all voxels. This notation indicates a
-parametric phase function as in \cref{eq:aerosol_scatter}.
+%The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
+%the phase function, in all voxels. This notation indicates a
+%parametric phase function as in \cref{eq:aerosol_scatter}.
+Here the operator $\odot$ denotes the Hadamard (element-wise)
+product.
 
@@
   {\bm p}_c= L^{\rm TOA}
-  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
+  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
   \odot \exp(-\vect{\tau}_c)
@@
 vector $N_{\rm pix}$ long.
-
 Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
-\begin{align}
-  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
-    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
-      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
-    (\vect{\sigma} \odot {\bm n})]\} \right\}
-  \label{eq:bigIc}
-\end{align}
-We focus on situations where there is only a single
-type of aerosol over a scene. Hence, the three-element vector
-$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
-the scene, but the density distribution ${\bm n}$ is variable. Then,
-\cref{eq:bigIc} degenerates to
+%\begin{align}
+%  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
+%    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
+%      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
+%    (\vect{\sigma} \odot {\bm n})]\} \right\}
+%  \label{eq:bigIc}
+%\end{align}
+%We focus on situations where there is only a single
+%type of aerosol over a scene. Hence, the three-element vector
+%$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
+%the scene, but the density distribution ${\bm n}$ is variable. Then,
+%\cref{eq:bigIc} degenerates to
 \begin{align}
@@
 
-We seek to estimate the aerosol distribution. Most generally, this is the set
-$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
-        g}_{\lambda}\right\}_{\lambda}\right\}$
-where some of the parameters depend on the spectral channel $\lambda$.
-Usually, however, a single aerosol type dominates a scene.
+In this paper, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
+%Most generally, this is the set
+%$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
+%        g}_{\lambda}\right\}_{\lambda}\right\}$
+%where some of the parameters depend on the spectral channel $\lambda$. 
+%Usually, a single aerosol type dominates a scene.
 Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}.
 Hence, we focus on estimating the density distribution ${\bm n}$.
-
-The recovery task is phrased as optimization of an objective function,
-that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
-$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
-  measured}_c\}_{c=1}^{N_{\rm views}}$:
+At hand, we have $N_{\rm views}$ measured photographs 
+ $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased as
+optimization of an objective function that fits the image-formation model to the measured photographs:
 \begin{equation}
@@
 viewpoint $c$) with variation of the aerosol density at voxel $k$, i.e.,
-$\partial i_c({\bm \Theta})/\partial{n(k)}$.  A
-close-form expression of the Jacobian and its detailed derivation is
-given in \cref{sec:gradient-derivation}.
+$\partial i_c({\bm \Theta})/\partial{n(k)}$.
+
+We now detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$. First, we provide some results relating to differentiation.  Let
+$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
+length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
+Then,
+\begin{align}
+  \label{eq:partial1}
+  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
+  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
+    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
+\end{align}
+Here $\OpDiag{\vect{v}}$ is a conversion of a general vector $\vect{v}$
+into a diagonal matrix, whose main diagonal elements correspond to the
+elements of $\vect{v}$. Now, let
+%\begin{align}
+  $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
+%  \label{eq:example1}
+%\end{align}
+%In \cref{eq:example1},
+where the exponent is element-wise (not raising an
+operator to some power). Then
+\begin{align}
+  \label{eq:partial2}
+  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
+  \OpDiag{\exp(-{\mat{C}}\vect{n})}.
+\end{align}
+Using \cref{eq:partial2},
+\begin{align}
+  \label{eq:partial4}
+  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
+  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
+\end{align}
+where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
+\begin{align}
+  \label{eq:partial3}
+  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
+  =
+  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
+\end{align}
+Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
+in close-form,
+\begin{align}
+%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm aerosol}({\bf A}-{\bf B})
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+   ,
+  \label{eq:gradient2}
+\end{align}
+where
+%\begin{align}
+%  \label{eq:gradient3}
+%  {\bf A} &= \varpi^{\rm aerosol}
+%  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+%  {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
+%%  & \;\;\;
+%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+%      scatter}_c) \odot{\bm n}
+%    ]}
+%    %\nonumber \\
+%  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+%\end{align}
+\begin{equation}
+  \label{eq:gradient3}
+  {\bf A} = \varpi^{\rm aerosol}
+       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
+  ,\;\;\;
+  {\bf B} = \transpose{{\bm D}_c}
+      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bm n}    ]}
+\end{equation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gradient Derivation}
-\label{sec:gradient-derivation}
-
-Here we detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to differentiation.  Let
-$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
-length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
-Then,
-\begin{align}
-  \label{eq:partial1}
-  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
-  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
-    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
-\end{align}
-Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector $\vect{v}$
-into a diagonal matrix, whose main diagonal elements correspond to the
-elements of $\vect{v}$. Now, let
-\begin{align}
-  \vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n}).
-  \label{eq:example1}
-\end{align}
-In \cref{eq:example1}, the exponent is element-wise (not raising an
-operator to some power). Then
-\begin{align}
-  \label{eq:partial2}
-  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
-  \OpDiag{\exp(-{\mat{C}}\vect{n})}
-\end{align}
-Using \cref{eq:partial2},
-\begin{align}
-  \label{eq:partial4}
-  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
-  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
-\end{align}
-where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
-\begin{align}
-  \label{eq:partial3}
-  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
-  =
-  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
-\end{align}
-Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
-in close-form,
-\begin{align}
-%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})
-  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-   ,
-  \label{eq:gradient2}
-\end{align}
-where
-\begin{align}
-  \label{eq:gradient3}
-  \abbrev{A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
-  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-  \abbrev{B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} %\nonumber\\
-%  & \;\;\; 
-      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}
-    ]} 
-    %\nonumber \\
-  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+\%appendix
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\section{Gradient Derivation}
+%\label{sec:gradient-derivation}
+%
+%Here we detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to differentiation.  Let
+%$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
+%length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
+%Then,
+%\begin{align}
+%  \label{eq:partial1}
+%  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
+%  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
+%    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
+%\end{align}
+%Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector $\vect{v}$
+%into a diagonal matrix, whose main diagonal elements correspond to the
+%elements of $\vect{v}$. Now, let
+%%\begin{align}
+%  $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
+%%  \label{eq:example1}
+%%\end{align}
+%%In \cref{eq:example1},
+%where the exponent is element-wise (not raising an
+%operator to some power). Then
+%\begin{align}
+%  \label{eq:partial2}
+%  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
+%  \OpDiag{\exp(-{\mat{C}}\vect{n})}.
+%\end{align}
+%Using \cref{eq:partial2},
+%\begin{align}
+%  \label{eq:partial4}
+%  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
+%  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+%  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
+%\end{align}
+%where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
+%\begin{align}
+%  \label{eq:partial3}
+%  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+%      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
+%  =
+%  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+%      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
+%\end{align}
+%Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
+%in close-form,
+%\begin{align}
+%%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm aerosol}({\bf A}-{\bf B})
+%  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
 %      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-\end{align}
-
-%$\mathbb{D}$
+%   ,
+%  \label{eq:gradient2}
+%\end{align}
+%where
+%%\begin{align}
+%%  \label{eq:gradient3}
+%%  {\bf A} &= \varpi^{\rm aerosol}
+%%  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+%%  {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
+%%%  & \;\;\;
+%%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+%%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+%%      scatter}_c) \odot{\bm n}
+%%    ]}
+%%    %\nonumber \\
+%%  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+%%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+%%\end{align}
+%\begin{equation}
+%  \label{eq:gradient3}
+%  {\bf A} = \varpi^{\rm aerosol}
+%       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
+%  ,\;\;\;
+%  {\bf B} = \transpose{{\bm D}_c}
+%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+%      scatter}_c) \odot{\bm n}    ]}
+%\end{equation}
 

### 2013-07-27 article.tex
bookmark

--- 2013-07-27 article.tex
@@
 
-%An infinitesimal volume contains aerosols. The extinction and
-%scattering coefficients due to aerosols in this volume are,
-%respectively
-%\begin{equation}
+% An infinitesimal volume contains aerosols. The extinction and
+% scattering coefficients due to aerosols in this volume are,
+% respectively
+% \begin{equation}
 %  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
@@
 %The infinitesimal volume contain also air molecules. Hence, the
-%overall extinction and scattering coefficients in this small volume
-%are, respectively
-%\begin{equation}
+% overall extinction and scattering coefficients in this small volume
+% are, respectively
+% \begin{equation}
 %  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
@@
 \noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
-that includes particles of a certain type.
-Each particle has an {\em extinction cross section} for
-interacting with the irradiance. For an aerosol the cross section is denoted $\sigma^{\rm aerosol}$.
-The aerosol density is $n$. Per unit volume, the {\em extinction coefficient} due to aerosols is
-$\beta^{\rm aerosol}= \sigma^{\rm aerosol} n$. In addition, the atmosphere contains air molecules.
+that includes particles of a certain type.  Each particle has an {\em
+  extinction cross section} for interacting with the irradiance. For
+an aerosol the cross section is denoted $\sigma^{\rm aerosol}$.  The
+aerosol density is $n$. Per unit volume, the {\em extinction
+  coefficient} due to aerosols is $\beta^{\rm aerosol}= \sigma^{\rm
+  aerosol} n$. In addition, the atmosphere contains air molecules.
 The extinction coefficient due to the molecules is $\beta^{\rm air}$.
 The volume has infinitesimal length $dl$. Then, the relative portion
-of extinct SR irradiance is the unitless differential optical
-  depth, $d\tau= (\beta^{\rm aerosol}+\beta^{\rm air}) dl$.
-The {\em optical depth} aggregates in extended propagation:
-\begin{align}
-  \tau= \int d\tau=\int (\beta^{\rm aerosol}+\beta^{\rm air}) dl
-       =\int (\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
-       = \tau^{\rm air}+ \int \sigma^{\rm aerosol} n dl \;,
+of extinct SR irradiance is the unitless differential optical depth,
+$d\tau= (\beta^{\rm aerosol}+\beta^{\rm air}) dl$.  The {\em optical
+  depth} aggregates in extended propagation:
+\begin{align}
+  \tau= \int d\tau=\int (\beta^{\rm aerosol}+\beta^{\rm air}) dl =\int
+  (\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm air}+ \int
+  \sigma^{\rm aerosol} n dl \;,
   \label{eq:tau}
 \end{align}
-where $\tau^{\rm air}=\int \beta^{\rm air} dl$.
-Through an attenuating atmosphere, the {\em transmittance} exponentially
-decays with the optical depth:
+where $\tau^{\rm air}=\int \beta^{\rm air} dl$.  Through an
+attenuating atmosphere, the {\em transmittance} exponentially decays
+with the optical depth:
 \begin{align}
@@
 (to all directions), relative to the total extinction is given by the
-unitless {\em single scattering albedo} of the particle. For an aerosol,
-the single scattering albedo is denoted $\varpi^{\rm aerosol}$.
-The {\em scattering coefficient} due to aerosols in the volume is
+unitless {\em single scattering albedo} of the particle. For an
+aerosol, the single scattering albedo is denoted $\varpi^{\rm
+  aerosol}$.  The {\em scattering coefficient} due to aerosols in the
+volume is
 \begin{align}
@@
 \end{align}
-The angular distribution of scattering by an aerosol is determined by a {\em phase function} $P^{\rm aerosol}$, which is normalized: its integral over all solid angles is unit.
-Part of the light scatters towards a camera's LOS, as
-illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
-is the scattering angle $\Phi^{\rm scatter}$. The {\em angular scattering coefficient} due to aerosols is
-\begin{align}
-  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter})
-  =  \alpha^{\rm aerosol} P^{\rm aerosol}(\Phi^{\rm scatter})
-  = \varpi^{\rm aerosol} \sigma^{\rm aerosol} n
-        P^{\rm aerosol}(\Phi^{\rm scatter}).
+The angular distribution of scattering by an aerosol is determined by
+a {\em phase function} $P^{\rm aerosol}$, which is normalized: its
+integral over all solid angles is unit. Part of the light scatters
+towards a camera's LOS, as illustrated in \cref{fig:groundgrid}. The
+angle between the SR and LOS is the scattering angle $\Phi^{\rm
+  scatter}$. The {\em angular scattering coefficient} due to aerosols
+is
+\begin{align}
+  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) = \alpha^{\rm
+    aerosol} P^{\rm aerosol}(\Phi^{\rm scatter}) = \varpi^{\rm
+    aerosol} \sigma^{\rm aerosol} n P^{\rm aerosol}(\Phi^{\rm
+    scatter}).
   \label{eq:alphabasic}
@@
 \begin{align}
-  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 - g^2)(1+\mu^2)
-  (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
+  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
+  g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
   \label{eq:aerosol_scatter}
 \end{align}
-where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos \Phi^{\rm scatter}$.
-
-Scattering by air molecules follows the
-{\em Rayleigh} model. The phase function is
+where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos
+\Phi^{\rm scatter}$.
+
+Scattering by air molecules follows the {\em Rayleigh} model. The
+phase function is
 \begin{align}
@@
 \end{align}
-and the single scattering albedo in visible light is $\varpi^{\rm air}$=1.
-Air molecular density falls off approximately exponentially with altitude $h$, with a characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
-\si{\km}$. Thus~\cite{Levi1980}, the coefficients for
-extinction and scattering by air molecules can be modeled by
+and the single scattering albedo in visible light is $\varpi^{\rm
+  air}$=1. Air molecular density falls off approximately exponentially
+with altitude $h$, with a characteristic~\cite{Levi1980} falloff
+height $H^\mathrm{air}=8\ \si{\km}$. Thus~\cite{Levi1980}, the
+coefficients for extinction and scattering by air molecules can be
+modeled by
 \begin{align}
   \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
-  1.09 \times 10^{-3}\lambda^{-4}
-  \exp(-h/H^\mathrm{air})
+  1.09 \times 10^{-3}\lambda^{-4} \exp(-h/H^\mathrm{air})
   \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
@@
 where $\lambda$ is the wavelength, in microns.
+\\
+
+\noindent {\bf Inverse Transform Sampling}: Monte Carlo methods
+simulate probabilistic phenomena by sampling from their probability
+disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is a common method for generating
+sample numbers at random from any probability distribution given its
+cumulative distribution function (cdf).  Let $X$ be a random variable
+whose distribution can be described by the cumulative distribution
+function $F$.  First we generate a random number $u$ from the standard
+uniform distribution in the interval $[0,1]$.  Then to draw a random
+number from the distribution described by $F$ we need to calculate the
+value $x$ such that $x = F^{-1}(u)$.
 
@@
 coefficient at voxel $k$, described in \cref{sec:scattering}.
+\begin{figure}
+  \centering
+  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
+  \caption{\small [a] Photograph of a sky that includes {\em Haze
+      Blobs} rendered using the single-scattering model.  A yellow dot
+    marks the Sun location. Dashed white circles mark elevation
+    angles.  [b] Photograph of the same sky and view point rendered
+    using the MC simulation (\cref{sec:monte-carlo-simul}).
+    [c] Cross section along the
+  }
+  \label{fig:simulation-results1}
+\end{figure}
 
@@
 probability distributions which describe the distance travelled by the
-photon between scatterings and the angle of deflection at each
+photon in-between scatterings and the angle of deflection at each
 scatter.  This enables simulating multiple scattering and produce
@@
 \cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
-traced from the detector to the sun. Photons are emitted from each
-pixel of the camera in the direction determined by the camera
-model. The optical distance that the photon travels before scattering
-is determined according to the Beer-Lambert law~\cref{eq:beer-lambert}
-and the inversion sampling method. Once the optical distance is
-determined the ``real'' distance is determined by summing the optical
-depth of the discrete voxels (\cref{sec:optical-depth}) along the
-photon direction till the desired optical distance is reached.  At
-each scattering event, first the type of aerosol is determined by
-sampling the different aerosols distributions inside the voxel. The
-new direction is determined by inverse sampling the phase function of
-the relevant aerosols: Rayleigh, \cref{eq:rayleighP} or
-Henyey-Greenstein \cref{eq:aerosol_scatter}.  To accelerate the MC we
-use the local estimation (LE) method.
+traced from the detector, camera, to their source, sun. Photons are
+emitted from each pixel of the camera in the direction determined by
+the camera model, i.e. hemispherical camera. The quality of the
+simulations is proportional to the number of photons. To create the
+\cref{fig:simulation-results1}b \num{10000} photons were emitted from
+each pixel. The distance travelled by the photon till its first
+scattering is determined by inversion sampling the transmittance
+probability (\cref{sec:theor-backgr}) optical distance
+distribution. This is done using the inversion sampling method. Once
+the optical distance is determined the ``real'' distance is determined
+by summing the optical depth of the discrete voxels
+(\cref{sec:optical-depth}) along the photon direction till the desired
+optical distance is reached.  At each scattering event, first the type
+of aerosol is determined by sampling the different aerosols
+distributions inside the voxel. The new direction is determined by
+inverse sampling the phase function of the relevant aerosols:
+Rayleigh, \cref{eq:rayleighP} or Henyey-Greenstein
+\cref{eq:aerosol_scatter}.  To accelerate the MC we use the local
+estimation (LE) method.
 
@@
 where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
-\SI{100}{\metre} and down to num{10 x 10 x 20} grid, where each voxel
+\SI{100}{\metre} and down to \num{10 x 10 x 20} grid, where each voxel
 has area of \SI{5 x 5}{\km} and vertical thickness of
@@
 
-\noindent{\bf Cameras}: The cameras are created by the MC simulations.
+\noindent{\bf Cameras}: The acquired images are cresimulated using the the MC model.
 Each ground-based camera has a hemispherical field of view, capturing
@@
 photograph
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
-  \caption{\small [a] Photograph of a sky that includes {\em Haze
-      Blobs} rendered using the single-scattering model.  A yellow dot
-    marks the Sun location. Dashed white circles mark elevation
-    angles.  [b] Photograph of the same sky and view point rendered
-    using the MCRT simulation (\cref{sec:monte-carlo-simul}).
-    [c] Cross section along the
-  }
-  \label{fig:simulation-results1}
-\end{figure}
 of the {\em Haze Blobs} scene that corresponds to

### 2013-07-27 article.tex
bookmark

--- 2013-07-27 article.tex
@@
 
-\title{Sky Tomography for 3D Aerosol Distribution Recovery}
+\title{Mulit-view 3D Aerosol Distribution Recovery}
 
@@
   retrieval assumes a plane-parallel atmosphere and solely vertical
-  radiative transfer (RT). We propose a principle to recover the atmosphere
-  as it really is: a three dimensional (3D), volumetric, transparent
-  huge object. Tomography is the key to recovery. The process involves
-  acquiring the sky lightfield by multi-view wide-angle photography on
-  a very large scale. The tomography model is distinct, as the light
-  source is unidirectional and uncontrolled, while off-axis scattering
-  dominates the images.  We formulate an image formation model based
+  radiative transfer (RT). We propose a principle to estimate the aerosol  
+  distribution as it really is: a three dimensional (3D) volume, using visible light. 
+  The principle is a type of tomography. The process involves
+  wide angle integral imaging of the sky on a very large scale.  
+  We formulate an image formation model based
   on 3D RT. Model inversion is done using optimization
   methods, exploiting a closed-form gradient which we derive for the
-  model-fit cost function. The problem is complex but tractable and
-  parallelizable, eventually estimating the 3D aerosol distribution.
+  model-fit cost function.  The tomography model is distinct, as the radiation
+  source is unidirectional and uncontrolled, while off-axis scattering
+  dominates the images.  
 \end{abstract}
@@
 
-Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
+Optical lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
 samples the optical radiance distribution in location and
 direction. It is mainly used in small-scale setups. This paper deals
-with a huge scale, up to Earth's size.  The atmosphere allows light to
-pass through in multiple locations and directions. Light is affected
+with a far larger scale, to estimate scatterer 3D spatial distribution in the sky. 
+The atmosphere allows light to pass through in multiple locations and directions. Light is affected
 by this medium. Therefore, in this paper we lay out a principle to
-recover this 3D medium using measured and modeled lightfields
+recover this 3D distribution using measured and modeled light-fields
 (Fig.~\ref{fig:groundgrid}).
@@
 \end{figure*}
-Projecting this large object to various directions is similar to
-tomography in other scientific domains. However, the formulation here
-is distinct. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
-our source is the uncontrolled, unidirectional Sun. Moreover, typical
-tomography relies on a linear model~\cite{gregson}: the pixel value is
-a linear combination of components along a line of sight (LOS), or a
-multiplicative combination (linearized by a logarithm). Linear
-tomography can detect volcanic gas~\cite{wright}, which absorbs
-UV. Other gases in the atmosphere absorb IR. However, in visible
-light, atmospheric attenuation is typically dominated by {\em
-  scattering} by particles (aerosols), rather than absorption by
-gasses. Thus, in our problem, we cannot rely on direct illumination,
-but on sunlight scattered into the LOS.  The model turns out to be
-{\em nonlinear, yet tractable}.
-
-We do not deal with clouds here. Clouds scatter sunlight very strongly
-and are easily observed. Hence they are directly recovered using
-common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
-On the other hand, aerosols have much more subtle visual effects and
-are thus more difficult to recover. We focus on them.  In remote
-sensing~\cite{diner}, imaging through air is associated with {\em
-  atmospheric correction}, based on {\em aerosol retrieval}. In this
-discipline, the atmosphere is often assumed to be plane-parallel, for
-simplicity, using only 1D vertical RT. Consequently
-state-of-the-art aerosol retrieval is done in distinct large lateral
-blocks~\cite{Martonchikc} with limited height
-resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
-recovery. Computational photography offers new ways to peer into
-media. In addition to active descattering~\cite{fuchs,kim,Ng1948} and
-recovery of refractive transparent objects~\cite{ihrke}, overcoming
-the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects was
-studied in horizontal, fixed
-views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
-this paper, however, the medium itself, at all relevant altitudes is
-the object of interest.
-
 3D recovery of this medium has direct implications to various
@@
 which needs real time assessment of conditions and visibility around
-flight paths. To keep safe, today's coarse sensing limits flight
-capacity. A prominent example is the 2010 eruption of Iceland's
-Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
-much of Europe's airspace, grounding $\approx 100,000$
-flights. Knowing the 3D distribution of aerosol density may indicate
-safe 3D corridors to safely pass through, enhancing airspace
-use. Viewing beyond the medium, atmospheric correction is needed, for
-example, in satellite tracking of chlorophyll
-distributions~\cite{johnsen}. Additional bodies in the solar system
-have atmospheres. These objects can be viewed from multiple directions
-by probes.  The approach described here may be helpful there.
-
-We model passive optical tomographic imaging of 3D atmospheric
+flight paths.
+
+In remote sensing~\cite{diner}, imaging through air is associated with {\em
+  atmospheric correction}, based on {\em aerosol retrieval}. In this
+discipline, the atmosphere is often assumed to be plane-parallel, using one-dimensional vertical RT. Consequently state-of-the-art aerosol retrieval is done in distinct large lateral
+blocks~\cite{Martonchikc} with limited height
+resolution~\cite{kalashnikova}. We, however, seek 3D
+recovery. Atmospheric correction is related to dehazing~\cite{Joshi2010,Zhu2013}. In
+this paper, however, the medium itself, at all relevant altitudes is the object of interest.
+
+We rely on sky imaging from multiple directions and locations. Such projection is similar to
+tomography in other scientific domains~\cite{Arridge}. However, the situation here
+is distinct. Most tomography setups have a controlled and/or
+multidirectional radiation source~\cite{Boas2001,messer}. In contrast,
+our source is the uncontrolled, unidirectional Sun. Moreover, typical
+tomography relies on a linear model~\cite{gregson}: the pixel value is
+a linear combination of components along a line of sight (LOS), or a
+multiplicative combination (linearized by a logarithm). Linear
+tomography can detect gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
+UV or IR radiation. However, aerosol attenuation of visible
+light is typically dominated by {\em scattering}, rather than absorption.
+Since the radiation source is single and fixed in space and time, we cannot rely on direct illumination for tomographic recovery of attenuation fields~\cite{Aviles2011}.
+We may only use sunlight scattered into the LOS.
+The model is
+{\em nonlinear, yet tractable}. We model passive optical tomographic imaging of 3D atmospheric
 scatterer distributions in cloudless conditions. Then, we solve this
@@
 optimization.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Related Work}
-\label{sec:literature}
-
-{\em Lightfield}, or {\em integral}
-imaging~\cite{Ng2006,bishop,Ng1948}, samples the radiance distribution
-in location and direction. It has so far been used in small-scale
-setups. Our proposed research deals with huge scale, up to Earth's
-size. Capturing the lightfield in very large scales requires uncommon
-sensors. Sampling Earth both spatially and angularly is done by the
-Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
-space, the Airborne Multiangle SpectroPolarimetric
-Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
-airborne instruments.
-
-Dehazing strives to improve quality of images taken through a
-semi-transparent medium, be it murky liquid~\cite{kim,fuchs},
-haze~\cite{fattal,Hschechner2}, or fog~\cite{narasimhan2}.  In remote
-sensing~\cite{kokhan}, imaging through air is associated with {\em
-  atmospheric correction}, based on {\em aerosol retrieval}.  In this
-methods the medium is usually assumed to be uniform or at least
-plane-parallel.  We, however, seek 3D recovery.  Another major
-difference is that these methods see the translucent medium as a
-disturbance that algorithms need to overcome, while in our research it
-is the medium that we want to recover.
-
-Computed Tomography (CT) refers to the reconstruction of a 3D object
-from a collection of projections of the object using any kind of
-penetrating radiation. CT finds wide use in medical imaging but is
-also valuable in other scientific fields, like
-geophysics~\cite{Kazahaya2008}, material science~\cite{Baruchel2000},
-astrophysics, and more.  Imaging of gaseous materials is also the
-target of extensive CT research~\cite{Price2001,Cosofret2009}. CT is
-based on an image formation model that describes the physical process
-underlying the projected measurements.  Most image formation models
-assume either absorption or emission processes. Other image formation
-models assume dominant diffusion by scattering~\cite{Boas2001}.
-
-CT uses several different methods for reconstructing the underlying
-medium. Transform algorithms are based on the Fourier and Radon
-transforms. Both relate the projection (or its Fourier transform) to
-the medium (or its Fourier transform). Solving for the medium involves
-calculating the inverse transform in an iterative process.  These
-algorithms assume a linear image formation model and require large
-amount of projections to give reasonable results. The simultaneous
-algebraic reconstruction technique
-(SART)~\cite{KakAvinashC.andSlaney2001} is another common method which
-is used when the image formation model is too big for explicit matrix
-representation. Stochastic Tomography~\cite{gregson} uses a different
-approach where the reconstruction is done in the space of projections
-using a probabilistic process based on random walk. This bypasses the
-need to discretize the signal, usually represented over a grid, and
-the use of large matrices to represent the formation model.
-
-Our research topic is closely related to optical
-tomography~\cite{Arridge}. Optical tomography uses light to visualize
-tissue, usually from close range.  Due to the highly scattering nature
-of biological tissue, optical tomography uses diffusive approximation
-in the image formation model.  Another method, based on scattering, is
-the X-Ray Scatter CT~\cite{Aviles2011} which measures the absorption
-and scattering coefficients of the medium separately.
-
-However, the formulation of our problem is {\em different} than prior
-situations. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{messer}. In contrast, our
-source is the uncontrolled, unidirectional Sun. Moreover, typical
-tomography relies on a linear model: the pixel value is a linear
-combination of components along a line of sight (LOS), or a
-multiplicative combination which is linearized by a logarithm.
-However, photographs of the atmosphere are a mixture of {\em
-  scattering}, and absorption. The model turns out to be {\em
-  nonlinear, yet tractable}.
 

### 2013-07-27 article.tex

@@
 
-\title{Mulit-view 3D Aerosol Distribution Recovery}
+\title{Multi-view 3D Aerosol Distribution Recovery}
 

### 2013-07-27 article.tex
bookmark

@@
   retrieval assumes a plane-parallel atmosphere and solely vertical
-  radiative transfer (RT). We propose a principle to estimate the aerosol  
-  distribution as it really is: a three dimensional (3D) volume, using visible light. 
-  The principle is a type of tomography. The process involves
-  wide angle integral imaging of the sky on a very large scale.  
-  We formulate an image formation model based
-  on 3D RT. Model inversion is done using optimization
-  methods, exploiting a closed-form gradient which we derive for the
-  model-fit cost function.  The tomography model is distinct, as the radiation
+  radiative transfer (RT). We propose a principle to estimate the
+  aerosol distribution as it really is: a three dimensional (3D)
+  volume, using visible light.  The principle is a type of
+  tomography. The process involves wide angle integral imaging of the
+  sky on a very large scale.  We formulate an image formation model
+  based on 3D RT. Model inversion is done using optimization methods,
+  exploiting a closed-form gradient which we derive for the model-fit
+  cost function.  The tomography model is distinct, as the radiation
   source is unidirectional and uncontrolled, while off-axis scattering
@@
 
-Optical lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
-samples the optical radiance distribution in location and
-direction. It is mainly used in small-scale setups. This paper deals
-with a far larger scale, to estimate scatterer 3D spatial distribution in the sky. 
-The atmosphere allows light to pass through in multiple locations and directions. Light is affected
-by this medium. Therefore, in this paper we lay out a principle to
-recover this 3D distribution using measured and modeled light-fields
-(Fig.~\ref{fig:groundgrid}).
+Optical lightfield and integral
+imaging~\cite{bishop,horstmeyer,kim,Ng1948} samples the optical
+radiance distribution in location and direction. It is mainly used in
+small-scale setups. This paper deals with a far larger scale, to
+estimate scatterer 3D spatial distribution in the sky.  The atmosphere
+allows light to pass through in multiple locations and
+directions. Light is affected by this medium. Therefore, in this paper
+we lay out a principle to recover this 3D distribution using measured
+and modeled light-fields (Fig.~\ref{fig:groundgrid}).
 \begin{figure*}[t!]
@@
 
-In remote sensing~\cite{diner}, imaging through air is associated with {\em
-  atmospheric correction}, based on {\em aerosol retrieval}. In this
-discipline, the atmosphere is often assumed to be plane-parallel, using one-dimensional vertical RT. Consequently state-of-the-art aerosol retrieval is done in distinct large lateral
+In remote sensing~\cite{diner}, imaging through air is associated with
+{\em atmospheric correction}, based on {\em aerosol retrieval}. In
+this discipline, the atmosphere is often assumed to be plane-parallel,
+using one-dimensional vertical RT. Consequently state-of-the-art
+aerosol retrieval is done in distinct large lateral
 blocks~\cite{Martonchikc} with limited height
 resolution~\cite{kalashnikova}. We, however, seek 3D
-recovery. Atmospheric correction is related to dehazing~\cite{Joshi2010,Zhu2013}. In
-this paper, however, the medium itself, at all relevant altitudes is the object of interest.
-
-We rely on sky imaging from multiple directions and locations. Such projection is similar to
-tomography in other scientific domains~\cite{Arridge}. However, the situation here
-is distinct. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{Boas2001,messer}. In contrast,
-our source is the uncontrolled, unidirectional Sun. Moreover, typical
-tomography relies on a linear model~\cite{gregson}: the pixel value is
-a linear combination of components along a line of sight (LOS), or a
+recovery. Atmospheric correction is related to
+dehazing~\cite{Joshi2010,Zhu2013}. In this paper, however, the medium
+itself, at all relevant altitudes is the object of interest.
+
+We rely on sky imaging from multiple directions and locations. Such
+projection is similar to tomography in other scientific
+domains~\cite{Arridge}. However, the situation here is distinct. Most
+tomography setups have a controlled and/or multidirectional radiation
+source~\cite{Boas2001,messer}. In contrast, our source is the
+uncontrolled, unidirectional Sun. Moreover, typical tomography relies
+on a linear model~\cite{gregson}: the pixel value is a linear
+combination of components along a line of sight (LOS), or a
 multiplicative combination (linearized by a logarithm). Linear
-tomography can detect gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
-UV or IR radiation. However, aerosol attenuation of visible
-light is typically dominated by {\em scattering}, rather than absorption.
-Since the radiation source is single and fixed in space and time, we cannot rely on direct illumination for tomographic recovery of attenuation fields~\cite{Aviles2011}.
-We may only use sunlight scattered into the LOS.
-The model is
-{\em nonlinear, yet tractable}. We model passive optical tomographic imaging of 3D atmospheric
-scatterer distributions in cloudless conditions. Then, we solve this
-tomography problem, to recover the distribution. Recovery is
-formulated as an optimization that minimizes a cost function. We
-derive the gradient of this cost function, to enable efficient
-optimization.
+tomography can detect
+gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
+UV or IR radiation. However, aerosol attenuation of visible light is
+typically dominated by {\em scattering}, rather than absorption. Since
+the radiation source is single and fixed in space and time, we cannot
+rely on direct illumination for tomographic recovery of attenuation
+fields~\cite{Aviles2011}. We may only use sunlight scattered into the
+LOS. The model is {\em nonlinear, yet tractable}. We model passive
+optical tomographic imaging of 3D atmospheric scatterer distributions
+in cloudless conditions. Then, we solve this tomography problem, to
+recover the distribution. Recovery is formulated as an optimization
+that minimizes a cost function. We derive the gradient of this cost
+function, to enable efficient optimization.
 
@@
 simulate probabilistic phenomena by sampling from their probability
-disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is a common method for generating
-sample numbers at random from any probability distribution given its
-cumulative distribution function (cdf).  Let $X$ be a random variable
-whose distribution can be described by the cumulative distribution
-function $F$.  First we generate a random number $u$ from the standard
-uniform distribution in the interval $[0,1]$.  Then to draw a random
-number from the distribution described by $F$ we need to calculate the
-value $x$ such that $x = F^{-1}(u)$.
+disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is
+a common method for generating sample numbers at random from any
+probability distribution given its cumulative distribution function
+(cdf).  Let $X$ be a random variable whose distribution can be
+described by the cumulative distribution function $F$.  First we
+generate a random number $u$ from the standard uniform distribution in
+the interval $[0,1]$.  Then to draw a random number from the
+distribution described by $F$ we need to calculate the value $x$ such
+that $x = F^{-1}(u)$.
 
@@
 looking upwards (\cref{fig:groundgrid}). The set performs {\em
-  integral imaging}~\cite{integral} of the sky. Per viewpoint, the
+  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
 view azimuth and elevation angles (relative to the zenith and north)
@@
 (\cref{sec:single-scatt-model}). It is less accurate than MC, but
-solves radiative transfer in an analytic, closed form. This form enables simple inversion of the model, to
-estimate the underlying atmosphere (\cref{sec:inverse-problem}).
+solves radiative transfer in an analytic, closed form. This form
+enables simple inversion of the model, to estimate the underlying
+atmosphere (\cref{sec:inverse-problem}).
 
@@
 coefficient at voxel $k$, described in \cref{sec:scattering}.
-\begin{figure}
-  \centering
-  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
-  \caption{\small [a] Photograph of a sky that includes {\em Haze
-      Blobs} rendered using the single-scattering model.  A yellow dot
-    marks the Sun location. Dashed white circles mark elevation
-    angles.  [b] Photograph of the same sky and view point rendered
-    using the MC simulation (\cref{sec:monte-carlo-simul}).
-    [c] Cross section along the
-  }
-  \label{fig:simulation-results1}
-\end{figure}
 
@@
 
-Any voxel generally contains both air molecules and aerosols.
-We focus on situations where there is only a single type of aerosol over a scene. Hence, the three-element vector
-$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
-the scene, but the density distribution ${\bm n}$ is variable. As a numerical approximation,
-assume that within any voxel, the molecular parameters $\{ \beta^{\rm
-  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density $n(k)$ are constants, e.g., corresponding to the value
-at each voxel center.  Following \cref{eq:tau}, the optical depth
-between the TOA and voxel $k$ is
+Any voxel generally contains both air molecules and aerosols.  We
+focus on situations where there is only a single type of aerosol over
+a scene. Hence, the three-element vector $[{\sigma}^{\rm
+  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
+the density distribution ${\bm n}$ is variable. As a numerical
+approximation, assume that within any voxel, the molecular parameters
+$\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density
+$n(k)$ are constants, e.g., corresponding to the value at each voxel
+center.  Following \cref{eq:tau}, the optical depth between the TOA
+and voxel $k$ is
 \begin{equation}
@@
 $\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
-angle. Given \cref{eq:extinctc}, the total optical depths
+angle. Given \cref{eq:tau}, the total optical depths
 corresponding to LOSs (of camera $c$) and SRs that cross all voxels
@@
 camera $c$.
-%Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
+% Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in
+% all voxels are stacked to vector $\vect{\varpi}$.
 Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
@@
 \end{equation}
-%The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
-%the phase function, in all voxels. This notation indicates a
-%parametric phase function as in \cref{eq:aerosol_scatter}.
-Here the operator $\odot$ denotes the Hadamard (element-wise)
-product.
+% The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter
+% of the phase function, in all voxels. This notation indicates a
+% parametric phase function as in \cref{eq:aerosol_scatter}.
+Here the operator $\odot$ denotes the Hadamard (element-wise) product.
 
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
+(\cref{eq:beer-lambert,eq:tautotal}) the radiant power
 contributed by the voxel is
@@
 A camera pixel collects light from a narrow cone in the
-atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
-% \begin{figure}
-%   \centering
-%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
-%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
-%   voxels above it on a SR. The scattered radiance from voxel $k$ is
-%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
-%   image pixel captures light emanating in a cone in space. Voxels
-%   that fully or partially fall in this cone are sensed by the
-%   pixel.}
-%   \label{fig:projection}
-% \end{figure}
-Overall, light power captured at a pixel is a weighted sum of the power
-$p_c(k)$ from all voxels.  This sum is formulated by a matrix
+atmosphere. The cone contains or intersects some voxels, while being
+oblivious to all the rest.
+Overall, light power captured at a pixel is a weighted sum of the
+power $p_c(k)$ from all voxels.  This sum is formulated by a matrix
 operation over ${\bm p}_c$:
@@
 \end{equation}
-where ${\bm i}_c$ is the image, column-stacked to a
-vector $N_{\rm pix}$ long.
-Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
-%\begin{align}
+where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
+  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
+image is thus
+% \begin{align}
 %   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
@@
 %   \label{eq:bigIc}
-%\end{align}
-%We focus on situations where there is only a single
-%type of aerosol over a scene. Hence, the three-element vector
-%$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
-%the scene, but the density distribution ${\bm n}$ is variable. Then,
-%\cref{eq:bigIc} degenerates to
+% \end{align}
+% We focus on situations where there is only a single type of aerosol
+% over a scene. Hence, the three-element vector $[{\sigma}^{\rm
+% aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
+% the density distribution ${\bm n}$ is variable. Then,
+% \cref{eq:bigIc} degenerates to
 \begin{align}
   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
-  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-    scatter}_c) \odot{\bm n} ]
-  \odot
-  \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c{\bm n})]
-    \Big\} .
+  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
+    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
+    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+  {\bm D}_c{\bm n})] \Big\} .
   \label{eq:bigIA}
@@
 Monte Carlo (MC) methods enable rigorous modeling of photon
-propagation in the atmosphere. The radiative transfer is expressed as
-probability distributions which describe the distance travelled by the
-photon in-between scatterings and the angle of deflection at each
-scatter.  This enables simulating multiple scattering and produce
-realistic results.  MC simulations can be made arbitrarily accurate by
-increasing the number of photons.  Another advantage of the MC methods
-is that they are highly parallelizable.
-
-The MC simulations use the same atmosphere grid described in
-\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
-traced from the detector, camera, to their source, sun. Photons are
-emitted from each pixel of the camera in the direction determined by
-the camera model, i.e. hemispherical camera. The quality of the
-simulations is proportional to the number of photons. To create the
-\cref{fig:simulation-results1}b \num{10000} photons were emitted from
-each pixel. The distance travelled by the photon till its first
-scattering is determined by inversion sampling the transmittance
-probability (\cref{sec:theor-backgr}) optical distance
-distribution. This is done using the inversion sampling method. Once
-the optical distance is determined the ``real'' distance is determined
-by summing the optical depth of the discrete voxels
-(\cref{sec:optical-depth}) along the photon direction till the desired
-optical distance is reached.  At each scattering event, first the type
-of aerosol is determined by sampling the different aerosols
-distributions inside the voxel. The new direction is determined by
-inverse sampling the phase function of the relevant aerosols:
-Rayleigh, \cref{eq:rayleighP} or Henyey-Greenstein
-\cref{eq:aerosol_scatter}.  To accelerate the MC we use the local
-estimation (LE) method.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inverse Problem}
-\label{sec:inverse-problem}
-
-In this paper, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
-%Most generally, this is the set
-%$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
-%        g}_{\lambda}\right\}_{\lambda}\right\}$
-%where some of the parameters depend on the spectral channel $\lambda$.
-%Usually, a single aerosol type dominates a scene.
-Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}.
-Hence, we focus on estimating the density distribution ${\bm n}$.
-At hand, we have $N_{\rm views}$ measured photographs
- $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased as
-optimization of an objective function that fits the image-formation model to the measured photographs:
-\begin{equation}
-  \label{eq:minobjectiveA}
-  \hat{\bm n} =
-  \argmin_{{\bm n}} F({\bm n})
-\end{equation}
-where
-\begin{equation}
-  \label{eq:objectiveA}
-  F({\bm n})
-  = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
-  + \eta \Psi({\bm n})
-\end{equation}
-where $\Mask$ is a map that masks the areas around
-the sun, which are overwhelmingly bright. %and the horizon.
-%These regions are prone to dominant multiple scattering.
-In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term that expresses some prior knowledge on the distribution, while $\eta$ is a regularization weight.
-Since aerosol distributions are usually fuzzy,
-it can be beneficial that regularization be a {\em smoothness term}, which penalized energy in second order spatial derivatives (3D Laplacian). Hende, we use
-\begin{equation}
-  \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
-\end{equation}
-where $\Laplacian$ is a matrix representation of the 3D \emph{Laplacian}
-operator.
-
-We solve~\cref{eq:minobjectiveA} using standard optimization tools.
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
-  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
-    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \transpose{\Laplacian}\Laplacian{\bm n} \;.
-  \label{eq:gradient1}
-\end{align}
-Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
-vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
-this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
-viewpoint $c$) with variation of the aerosol density at voxel $k$, i.e.,
-$\partial i_c({\bm \Theta})/\partial{n(k)}$.
-
-We now detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$. First, we provide some results relating to differentiation.  Let
-$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
-length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
-Then,
-\begin{align}
-  \label{eq:partial1}
-  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
-  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
-    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
-\end{align}
-Here $\OpDiag{\vect{v}}$ is a conversion of a general vector $\vect{v}$
-into a diagonal matrix, whose main diagonal elements correspond to the
-elements of $\vect{v}$. Now, let
-%\begin{align}
-  $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
-%  \label{eq:example1}
-%\end{align}
-%In \cref{eq:example1},
-where the exponent is element-wise (not raising an
-operator to some power). Then
-\begin{align}
-  \label{eq:partial2}
-  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
-  \OpDiag{\exp(-{\mat{C}}\vect{n})}.
-\end{align}
-Using \cref{eq:partial2},
-\begin{align}
-  \label{eq:partial4}
-  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
-  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
-\end{align}
-where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
-\begin{align}
-  \label{eq:partial3}
-  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
-  =
-  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
-      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
-\end{align}
-Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
-in close-form,
-\begin{align}
-%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
-  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm aerosol}({\bf A}-{\bf B})
-  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-   ,
-  \label{eq:gradient2}
-\end{align}
-where
-%\begin{align}
-%  \label{eq:gradient3}
-%  {\bf A} &= \varpi^{\rm aerosol}
-%  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-%  {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
-%%  & \;\;\;
-%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-%      scatter}_c) \odot{\bm n}
-%    ]}
-%    %\nonumber \\
-%  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-%\end{align}
-\begin{equation}
-  \label{eq:gradient3}
-  {\bf A} = \varpi^{\rm aerosol}
-       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
-  ,\;\;\;
-  {\bf B} = \transpose{{\bm D}_c}
-      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-      scatter}_c) \odot{\bm n}    ]}
-\end{equation}
+propagation in the atmosphere.  MC simulations can be made arbitrarily
+accurate by increasing the number of launched photons. MC methods are
+highly parallelizable. When applied to the RT problem, they enable
+simulating multiple scattering and produce realistic results.
+
+The MC simulations use the same atmospheric grid described in
+\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
+traced from the detector, camera, to their source, the Sun, in a
+direction determined by the camera model, i.e. hemispherical
+camera. The quality of the simulations is proportional to the number
+of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
+photons were emitted from each pixel. The distance travelled by the
+photon till its first scattering is determined by sampling from the
+transmittance distribution using the inverse transform sampling
+(\cref{sec:theor-backgr}).  The CDF of the transmittance distribution
+is given by,
+\begin{equation}
+  \label{eq:1}
+  F=\int_{0}^{1}\exp(-\tau)\derivsym{\tau}=1-\exp(-\tau)
+\end{equation}
+Given a uniformly distributed random number $u$ a random transmittance
+is given by
+\begin{equation}
+  \label{eq:2}
+  t=F^{-1}(u)=-\ln(1-u)
+\end{equation}
+If the scattering occurs outside the atmospheric grid, the photon is
+dropped. If not, the voxel in which the scattering occurs is
+calculated.  The type of scattering, either by air molecule or aerosol
+particle, is determined randomly according to their relative densities
+in the voxel.  The new direction of the photon is determined by
+inverse sampling the phase function of the scattering particle:
+Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
+\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
+used for calculating the amount of light reaching the sun at each
+scattering.  This process is repeated till the photon escapes the
+atmosphere grid or it reaches a predetermined number of scatterings.
 
@@
 
-To test the model, we made simulations based on atmospheric models in
-the literature. Here are the details.
+\begin{figure}
+  \centering
+  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
+  \caption{\small [a] Photograph of a sky that includes {\em Haze
+      Blobs} rendered using the single-scattering model.  A yellow dot
+    marks the Sun location. Dashed white circles mark elevation
+    angles.  [b] Photograph of the same sky and view point rendered
+    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
+    section along the }
+  \label{fig:simulation-results1}
+\end{figure}
+To test the model, we simulated several atmospheric models. Here are
+the details.
 
@@
 
-\noindent{\bf Dimensions}: The domain of sky we simulate and recover
-has area of \SI{50 x 50}{\km}, and it extends from the ground up to
-altitude of \SI{10}{\km}. This volume is divided into a rectilinear
-grid. We used different grid sizes from \num{50 x 50 x 100} grid,
-where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
-\SI{100}{\metre} and down to \num{10 x 10 x 20} grid, where each voxel
-has area of \SI{5 x 5}{\km} and vertical thickness of
-\SI{500}{\metre}. The different grid sizes determine the number of
-variables.
+\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
+  50}{\km} extending from the ground up to altitude of
+\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
+different grid sizes from \num{50 x 50 x 100} grid, where each voxel
+has area of \SI{1 x 1}{\km} and vertical thickness of \SI{100}{\metre}
+and down to \num{10 x 10 x 20} grid, where each voxel has area of
+\SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}.
 
@@
   aerosol}_{\rm
-  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.
-Its single-scattering albedo is $\varpi^{\rm aerosol}=1$ at all
-channels.
-
-We simulated various spatial distributions. All were set as a product
-of two functions. The first function is an exponential
-decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
+  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
+all channels, $\varpi^{\rm aerosol}=1$.
+
+We simulated various spatial distributions, as a product of two
+functions. The first function is an exponential decay~\cite{Levi1980}
+with altitude $h(k)$ of voxel $k$,
 \begin{align}
@@
 
-\noindent{\bf Cameras}: The acquired images are cresimulated using the the MC model.
-Each ground-based camera has a hemispherical field of view, capturing
-the entire sky from its viewpoint. Again, we used different numbers of
-cameras ranging from 100 viewpoints to 12. The cameras are arranged on
-a grid.  The resolution of each camera is low, expressing the fact
-that cloudless (yet hazy) sky images are rather smooth, hence there is
-no need for high image resolution.  For example,
+\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
+field of view, capturing the entire sky from its viewpoint. We used
+different numbers of cameras ranging from 12 viewpoints to 100, on a
+grid.  The resolution of each camera is low, expressing the fact that
+cloudless (yet hazy) sky images are rather smooth.  For example,
 \cref{fig:simulation-results1}b shows an example of a modeled
-photograph
-of the {\em Haze Blobs} scene that corresponds to
+photograph of the {\em Haze Blobs} scene that corresponds to
 \cref{fig:two_clouds_sim}a.
 
-\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
-that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
-with 8GB DDR3 memory per core. The number of cures used is depends on
-the size of the simulations. Each core was dedicated to rendering a
-modeled image.
-
-\noindent{\bf Optimization}: We used the L-BFGS-B
-algorithm~\cite{BFGS}. The algorithm was initialized by ${\bm
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inverse Problem}
+\label{sec:inverse-problem}
+
+In this paper, we assume that the type of the aerosol above an area is
+known~\cite{Martonchik2009}. Hence, we focus on estimating the density
+distribution ${\bm n}$.
+% Most generally, this is the set $\left\{{\bm
+%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
+%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
+% parameters depend on the spectral channel $\lambda$.  Usually, a
+% single aerosol type dominates a scene. Furthermore, we assume that
+% the type of the aerosol above an area is
+% known~\cite{Martonchik2009}. Hence, we focus on estimating the
+% density distribution ${\bm n}$.
+At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
+  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
+as optimization of an objective function that fits the image-formation
+model to the measured photographs:
+\begin{equation}
+  \label{eq:minobjectiveA}
+  \hat{\bm n} =
+  \argmin_{{\bm n}} F({\bm n})
+\end{equation}
+where
+\begin{equation}
+  \label{eq:objectiveA}
+  F({\bm n})
+  = \sum_{c=1}^{N_{\rm views}}
+  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
+  + \eta \Psi({\bm n})
+\end{equation}
+where $\Mask$ is a map that masks the areas around the sun, which are
+overwhelmingly bright. %and the horizon.
+% These regions are prone to dominant multiple scattering.
+In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
+that expresses some prior knowledge on the distribution, while $\eta$
+is a regularization weight.  Since aerosol distributions are usually
+fuzzy, it can be beneficial that regularization be a {\em smoothness
+  term}, which penalized energy in second order spatial derivatives
+(3D Laplacian). Hende, we use
+\begin{equation}
+  \label{eq:regularizer}
+  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
+\end{equation}
+where $\Laplacian$ is a matrix representation of the 3D
+\emph{Laplacian} operator.
+
+We solve~\cref{eq:minobjectiveA} using standard optimization tools.
+The gradient of $F$ with respect to ${\bm n}$ is
+\begin{align}
+  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
+    measured}_c - {\bm i}_c({\bm n})] + 2 \eta
+  \transpose{\Laplacian}\Laplacian{\bm n} \;.
+  \label{eq:gradient1}
+\end{align}
+Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
+vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
+this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
+viewpoint $c$) with variation of the aerosol density at voxel $k$,
+i.e., $\partial i_c({\bm \Theta})/\partial{n(k)}$.
+
+We now detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm
+  n})$. First, we provide some results relating to differentiation.
+Let $\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each
+outputs a vector of length $r$. Let $\mat{C}$ be a $r \times N_{\rm
+  voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
+Then,
+\begin{align}
+  \label{eq:partial1}
+  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
+  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
+    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
+\end{align}
+Here $\OpDiag{\vect{v}}$ is a conversion of a general vector
+$\vect{v}$ into a diagonal matrix, whose main diagonal elements
+correspond to the elements of $\vect{v}$. Now, let
+% \begin{align}
+$\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
+% \label{eq:example1}
+% \end{align}
+% In \cref{eq:example1},
+where the exponent is element-wise (not raising an operator to some
+power). Then
+\begin{align}
+  \label{eq:partial2}
+  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
+  \OpDiag{\exp(-{\mat{C}}\vect{n})}.
+\end{align}
+Using \cref{eq:partial2},
+\begin{align}
+  \label{eq:partial4}
+  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+      aerosol}{\bm D}_c {\bm n})]}
+  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
+  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm
+      D}_c {\bm n})]},
+\end{align}
+where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using
+\cref{eq:partial1},
+\begin{align}
+  \label{eq:partial3}
+  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
+  = \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
+\end{align}
+Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the
+Jacobian of \cref{eq:bigIA} in close-form,
+\begin{align}
+  % {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm
+  % TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm
+    aerosol}({\bf A}-{\bf B}) \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
+    {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})]}
+  \transpose{{\vect{\Pi}}_c} ,
+  \label{eq:gradient2}
+\end{align}
+where
+% \begin{align}
+%   \label{eq:gradient3}
+%   {\bf A} &= \varpi^{\rm aerosol}
+%   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
+%   {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
+%%   & \;\;\;
+%   \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+%   aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+%   scatter}_c) \odot{\bm n} ]}
+%    %   \nonumber \\
+%  %   \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
+%  %   {\sigma}^{\rm
+%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
+% \end{align}
+\begin{equation}
+  \label{eq:gradient3}
+  {\bf A} = \varpi^{\rm aerosol}
+  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
+  ,\;\;\;
+  {\bf B} = \transpose{{\bm D}_c}
+  \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
+      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
+      scatter}_c) \odot{\bm n}    ]}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+\label{sec:optimization-results}
+
+We applied the reconstruction algorithm \cref{sec:inverse-problem} to
+the images simulated in \cref{sec:simul}. We used the L-BFGS-B
+algorithm~\cite{BFGS} on a computer cluster. Each core was dedicated
+to rendering a modeled image. The algorithm was initialized by ${\bm
   n}=0$. Satisfactory convergence occurred in several thousand
 iterations, taking a couple of hours to complete in total.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:optimization-results}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\%appendix
+%\appendix
 %
@@
 %
-%\section{Gradient Derivation}
-%\label{sec:gradient-derivation}
+% \section{Gradient Derivation}
+% \label{sec:gradient-derivation}
 %
-%Here we detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to differentiation.  Let
-%$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
-%length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
-%Then,
-%\begin{align}
+% Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
+% i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results
+% relating to differentiation.  Let
+% $\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each
+% outputs a vector of length $r$. Let $\mat{C}$ be a $r \times N_{\rm
+% voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
+% Then,
+% \begin{align}
 %   \label{eq:partial1}
-%  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
+%   \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot
+%   \vect{u})}{\vect{n}}
 %   = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
-%    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
-%\end{align}
-%Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector $\vect{v}$
-%into a diagonal matrix, whose main diagonal elements correspond to the
-%elements of $\vect{v}$. Now, let
-%%\begin{align}
+%     \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right]
+%   \mat{C}.
+% \end{align}
+% Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector
+% $\vect{v}$ into a diagonal matrix, whose main diagonal elements
+% correspond to the elements of $\vect{v}$. Now, let
+%% \begin{align}
 %   $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
 %%   \label{eq:example1}
-%%\end{align}
-%%In \cref{eq:example1},
-%where the exponent is element-wise (not raising an
-%operator to some power). Then
-%\begin{align}
+%% \end{align}
+%% In \cref{eq:example1},
+% where the exponent is element-wise (not raising an operator to some
+% power). Then
+% \begin{align}
 %   \label{eq:partial2}
@@
 %   \OpDiag{\exp(-{\mat{C}}\vect{n})}.
-%\end{align}
-%Using \cref{eq:partial2},
-%\begin{align}
+% \end{align}
+% Using \cref{eq:partial2},
+% \begin{align}
 %   \label{eq:partial4}
-%  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
+%   \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+%   aerosol}{\bm D}_c {\bm n})]}
 %   {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-%  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
-%\end{align}
-%where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
-%\begin{align}
+%   \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+%   aerosol}{\bm D}_c {\bm n})]},
+% \end{align}
+% where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using
+% \cref{eq:partial1},
+% \begin{align}
 %   \label{eq:partial3}
@@
 %   aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
-%  =
-%  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
+%   = \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
 %   aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
-%\end{align}
-%Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
-%in close-form,
-%\begin{align}
-%%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
-%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm aerosol}({\bf A}-{\bf B})
-%  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-%      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-%   ,
+% \end{align}
+% Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the
+% Jacobian of \cref{eq:bigIA} in close-form,
+% \begin{align}
+%%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm
+%%   TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
+%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm
+%   aerosol}({\bf A}-{\bf B}) \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
+%   {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})]}
+%   \transpose{{\vect{\Pi}}_c} ,
 %   \label{eq:gradient2}
-%\end{align}
-%where
-%%\begin{align}
+% \end{align}
+% where
+%% \begin{align}
 %%   \label{eq:gradient3}
@@
 %%   aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-%%      scatter}_c) \odot{\bm n}
-%%    ]}
-%%    %\nonumber \\
-%%  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
+%%   scatter}_c) \odot{\bm n} ]}
+%%    %   \nonumber \\
+%%  %   \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
+%%  %   {\sigma}^{\rm
 %%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-%%\end{align}
-%\begin{equation}
+%% \end{align}
+% \begin{equation}
 %  \label{eq:gradient3}

### 2013-07-28 article.tex
bookmark

@@
 \end{figure}
-To test the model, we simulated several atmospheric models. Here are
-the details.
+To test the models, we simulated several atmospheric scenarios. Here
+are the details.
 
@@
 \SI{10}{\km}. This volume is divided into a rectilinear grid. We used
-different grid sizes from \num{50 x 50 x 100} grid, where each voxel
-has area of \SI{1 x 1}{\km} and vertical thickness of \SI{100}{\metre}
-and down to \num{10 x 10 x 20} grid, where each voxel has area of
-\SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}.
+different grid sizes from \num{10 x 10 x 20} grid, where each voxel
+has area of \SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}
+and up to \num{50 x 50 x 100} grid, where each voxel has area of \SI{1
+  x 1}{\km} and vertical thickness of \SI{100}{\metre}.
 
@@
 \begin{align}
-  w_1[h(k)] = \frac{1} {n^{sea level}}
-  \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
+  w_1[h(k)] = \sfrac{1} {n^{sea level}}
+  \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
 \end{align}
@@
 As an example, we created a {\em Haze Blobs} scene using two ellipsoid
-blobs (\cref{fig:two_clouds_sim}a): the first is centered at altitude
+blobs (\cref{fig:results}a): the first is centered at altitude
 \SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
@@
 cloudless (yet hazy) sky images are rather smooth.  For example,
-\cref{fig:simulation-results1}b shows an example of a modeled
-photograph of the {\em Haze Blobs} scene that corresponds to
-\cref{fig:two_clouds_sim}a.
+\cref{fig:simulation-results1}a and \cref{fig:simulation-results1}b
+show example photographs of the {\em Haze Blobs} scene as simulated by
+the Single Scattering model and MC model, respectively, from the same
+viewing point.  \cref{fig:simulation-results1}c compares a cross section
+of the photographs along the horizontal Axis.
 
@@
 An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in \cref{fig:two_clouds_sim}a, while the
-recovered 3D distribution is visualized in
-\cref{fig:two_clouds_sim}b. The distributions appear consistent,
-though there are errors that stem from the random noise in the
-images. To quantify the results, we use a relative error measure based
-on the $\ell_1$ norm
+distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
+the reconstructed scene based on images simulated by the Single
+Scattering model. \cref{fig:results}e visualizes the reconstructed
+scene based on images simulated by the MC model. The distributions
+appear consistent, though there are errors that stem from the random
+noise in the images. To quantify the results, we use a relative error
+measure based on the $\ell_1$ norm
 \begin{equation}
@@
 in all voxels, relative to the total aerosol mass in the scene.  In
-the {\em Haze Blobs} case, $\epsilon=0.202$.
-
-We created a {\em Haze Front} scene. \cref{fig:front_sim}a shows an
+the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
+the reconstructions based on the Single-Scattering images and MC
+images respectively.
+
+We created a {\em Haze Front} scene. \cref{fig:results}b shows an
 iso-surface visualization of this distribution.
@@
   \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/two_clouds}}
-  \caption{\small [a] Simulated 3D aerosol distribution composed of
-    {\em Haze Blobs} and [b] its reconstruction. Color represents
-    aerosol density. The density units are $10^{6}~{\rm
-      particles}/{\rm m}^3.$}
-  \label{fig:two_clouds_sim}
-\end{figure}
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/front}}
-  \caption{\small [a] Simulated 3D aerosol distribution composed of a
-    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
-    density. The density units are $10^{6}~{\rm particles}/{\rm
-      m}^3.$}
-  \label{fig:front_sim}
+  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
+  \caption{\small [a] and [b] Simulated 3D aerosol distribution
+    composed of a {\em Haze Front} and {\em Haze Front}
+    respectively. [c] and [d] Reconstruction of the same scenes when
+    using Single-Scattering simulated images as input.  [e] and [f]
+    Reconstruction of the scenes when using MC simulated images as
+    input.  Color represents aerosol density. The density units are
+    $10^{6}~{\rm particles}/{\rm m}^3.$}
+  \label{fig:results}
 \end{figure}
@@
 part of which enters the volume). The haze front stretches across the
-width of the volume.  \cref{fig:front_sim}b visualizes the recovered
-3D distribution of this scene. For the {\em Haze Front},
-$\epsilon=0.198$.
+width of the volume.  \cref{fig:results}d and \cref{fig:results}f
+visualizes the recovered 3D distribution of this scene. For the {\em
+  Haze Front}, $\epsilon=0.46$ and $\epsilon=0.62$ for the
+reconstructions based on the Single-Scattering images and MC images
+respectively.
 

### 2013-07-28 article.tex
bookmark

@@
     using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
-    section along the }
+    section along the X-Axis of the MC simulation, Single-Scattering
+    simulation and a Single-Scattering image created from the
+    reconstructed distribution (\cref{sec:optimization-results}).}
   \label{fig:simulation-results1}
@@
 the Single Scattering model and MC model, respectively, from the same
-viewing point.  \cref{fig:simulation-results1}c compares a cross section
-of the photographs along the horizontal Axis.
+viewing point.  \cref{fig:simulation-results1}c compares a cross
+section of the photographs along the horizontal Axis.
 
@@
 the reconstructions based on the Single-Scattering images and MC
-images respectively.
+images respectively. We used the distribution reconstructed based on
+the MC images to create images using the Single-Scattering
+model. \cref{fig:simulation-results1}c shows a cross of such an image
+compared to the original MC image.
 

### 2013-07-28 article.tex
Added corrections by Vadim

@@
 transmittance distribution using the inverse transform sampling
-(\cref{sec:theor-backgr}).  The CDF of the transmittance distribution
-is given by,
+(\cref{sec:theor-backgr}).  The CDF of the optical depth
+(transmittance) distribution is given by,
 \begin{equation}
   \label{eq:1}
-  F=\int_{0}^{1}\exp(-\tau)\derivsym{\tau}=1-\exp(-\tau)
-\end{equation}
-Given a uniformly distributed random number $u$ a random transmittance
+  F=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau)
+\end{equation}
+Given a uniformly distributed random number $u$ a random optical depth
 is given by
@@
 \end{equation}
-If the scattering occurs outside the atmospheric grid, the photon is
-dropped. If not, the voxel in which the scattering occurs is
+The actual distance travelled by the photon is calculated by
+accumulating the discrete optical depths of each voxel along the
+photon's path till the target optical path, drawn by \cref{eq:2}, is
+reached.  If the scattering occurs outside the atmospheric grid, the
+photon is dropped. If not, the voxel in which the scattering occurs is
 calculated.  The type of scattering, either by air molecule or aerosol

### 2013-07-28 article.tex
work on citations

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Optical lightfield and integral
-imaging~\cite{bishop,horstmeyer,kim,Ng1948} samples the optical
+imaging~\cite{Stern2006,kim,Ng1948} samples the optical
 radiance distribution in location and direction. It is mainly used in
@@
 
-In remote sensing~\cite{diner}, imaging through air is associated with
+In remote sensing~\cite{Mishchenko2007}, imaging through air is associated with
 {\em atmospheric correction}, based on {\em aerosol retrieval}. In
@@
 recovery. Atmospheric correction is related to
-dehazing~\cite{Joshi2010,Zhu2013}. In this paper, however, the medium
+dehazing~\cite{Namer2009,Zhu2013}. In this paper, however, the medium
 itself, at all relevant altitudes is the object of interest.
@@
 projection is similar to tomography in other scientific
-domains~\cite{Arridge}. However, the situation here is distinct. Most
+domains~\cite{Bluestone2001}. However, the situation here is distinct. Most
 tomography setups have a controlled and/or multidirectional radiation

### 2013-07-30 article.tex
reviewing Yoav changes

@@
 \usepackage{paralist}
+\usepackage{cite}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% body %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% body %%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Optical lightfield and integral
-imaging~\cite{Stern2006,kim,Ng1948} samples the optical
-radiance distribution in location and direction. It is mainly used in
+imaging~\cite{Stern2006,kim,Ng1948} sample the optical
+radiance distribution in location and direction. These are mainly used in
 small-scale setups. This paper deals with a far larger scale, to
@@
 To test the models, we simulated several atmospheric scenarios. Here
-are the details.
+are the details:
+\\
 
@@
   B}=255:236:224$.
+\\
 
@@
   x 1}{\km} and vertical thickness of \SI{100}{\metre}.
+\\
 
@@
 of atmospheric aerosol distributions.
+\\
 
@@
 fuzzy, it can be beneficial that regularization be a {\em smoothness
-  term}, which penalized energy in second order spatial derivatives
-(3D Laplacian). Hende, we use
+  term}, which penalizes energy in second order spatial derivatives
+(3D Laplacian). Hence, we use
 \begin{equation}
@@
 The goal, of coarse, is to deploy such a system on a very large
-scale. However, this must first ensure that camera units are both cost
-effective and field-robust, and that their positioning density is
+scale. However, it must be first ensured that camera units are both
+cost effective and field-robust, and that their positioning density is
 proper. This will require a long-term engineering effort. Camera
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%% Appendix %%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\appendix
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% \section{Gradient Derivation}
-% \label{sec:gradient-derivation}
-%
-% Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
-% i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results
-% relating to differentiation.  Let
-% $\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each
-% outputs a vector of length $r$. Let $\mat{C}$ be a $r \times N_{\rm
-% voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
-% Then,
-% \begin{align}
-%   \label{eq:partial1}
-%   \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot
-%   \vect{u})}{\vect{n}}
-%   = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
-%     \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right]
-%   \mat{C}.
-% \end{align}
-% Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector
-% $\vect{v}$ into a diagonal matrix, whose main diagonal elements
-% correspond to the elements of $\vect{v}$. Now, let
-%% \begin{align}
-%   $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
-%%   \label{eq:example1}
-%% \end{align}
-%% In \cref{eq:example1},
-% where the exponent is element-wise (not raising an operator to some
-% power). Then
-% \begin{align}
-%   \label{eq:partial2}
-%   \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
-%   \OpDiag{\exp(-{\mat{C}}\vect{n})}.
-% \end{align}
-% Using \cref{eq:partial2},
-% \begin{align}
-%   \label{eq:partial4}
-%   \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-%   aerosol}{\bm D}_c {\bm n})]}
-%   {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
-%   \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
-%   aerosol}{\bm D}_c {\bm n})]},
-% \end{align}
-% where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using
-% \cref{eq:partial1},
-% \begin{align}
-%   \label{eq:partial3}
-%   \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
-%   aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
-%   = \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
-%   aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
-% \end{align}
-% Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the
-% Jacobian of \cref{eq:bigIA} in close-form,
-% \begin{align}
-%%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm
-%%   TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
-%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm
-%   aerosol}({\bf A}-{\bf B}) \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
-%   {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})]}
-%   \transpose{{\vect{\Pi}}_c} ,
-%   \label{eq:gradient2}
-% \end{align}
-% where
-%% \begin{align}
-%%   \label{eq:gradient3}
-%%   {\bf A} &= \varpi^{\rm aerosol}
-%%   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-%%   {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
-%%%   & \;\;\;
-%%   \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-%%   aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-%%   scatter}_c) \odot{\bm n} ]}
-%%    %   \nonumber \\
-%%  %   \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
-%%  %   {\sigma}^{\rm
-%%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-%% \end{align}
-% \begin{equation}
-%  \label{eq:gradient3}
-%  {\bf A} = \varpi^{\rm aerosol}
-%       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
-%  ,\;\;\;
-%  {\bf B} = \transpose{{\bm D}_c}
-%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-%      scatter}_c) \odot{\bm n}    ]}
-%\end{equation}
-
 \end{document}

### 2013-07-30 article.tex
Cleanup of redundnat references

@@
 recovery. Atmospheric correction is related to
-dehazing~\cite{Namer2009,Zhu2013}. In this paper, however, the medium
+dehazing~\cite{Namer2009}. In this paper, however, the medium
 itself, at all relevant altitudes is the object of interest.
@@
 tomography setups have a controlled and/or multidirectional radiation
-source~\cite{Boas2001,messer}. In contrast, our source is the
+source~\cite{Bluestone2001,messer}. In contrast, our source is the
 uncontrolled, unidirectional Sun. Moreover, typical tomography relies
@@
 tomography can detect
-gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
+gases~\cite{Cosofret2009}, which absorb
 UV or IR radiation. However, aerosol attenuation of visible light is

### 2013-07-30 article.tex
pasted the bib text into the tex file. Fixed the url of two references.

@@
 
-\bibliography{article}{} \bibliographystyle{osajnl}
+%\bibliography{article}{} \bibliographystyle{osajnl}
+
+\begin{thebibliography}{10}
+\newcommand{\enquote}[1]{``#1''}
+
+\bibitem{Stern2006}
+A.~Stern and B.~Javidi, \enquote{{Three-dimensional image sensing,
+  visualization, and processing using integral imaging},} Proceedings of the
+  IEEE \textbf{94} (2006).
+
+\bibitem{kim}
+J.~Kim, D.~Lanman, Y.~Mukaigawa, and R.~Raskar, \enquote{{Descattering
+  transmission via angular filtering},} in \enquote{Proc. ECCV' 10,}
+  (Springer-Verlag, Berlin, Heidelberg, 2010), pp. 86--99.
+
+\bibitem{Ng1948}
+M.~Levoy, R.~Ng, A.~Adams, M.~Footer, and M.~Horowitz, \enquote{{Light field
+  microscopy},} ACM Transactions on Graphics (TOG) \textbf{25}, 924----934
+  (2006).
+
+\bibitem{Dayan2008}
+U.~Dayan, B.~Ziv, T.~Shoob, and Y.~Enzel, \enquote{{Suspended dust over
+  southeastern Mediterranean and its relation to atmospheric circulations},}
+  International Journal of Climatology \textbf{924}, 915--924 (2008).
+
+\bibitem{kalashnikova}
+O.~V. Kalashnikova, M.~J. Garay, A.~B. Davis, D.~J. Diner, and J.~V.
+  Martonchik, \enquote{{Sensitivity of multi-angle photo-polarimetry to
+  vertical layering and mixing of absorbing aerosols: Quantifying measurement
+  uncertainties},} Journal of Quantitative Spectroscopy and Radiative Transfer
+  \textbf{112}, 2149--2163 (2011).
+
+\bibitem{Mishchenko2007}
+M.~I. Mishchenko and I.~V. Geogdzhayev, \enquote{{Satellite remote sensing
+  reveals regional tropospheric aerosol trends.}} Optics express \textbf{15},
+  7423--38 (2007).
+
+\bibitem{Martonchikc}
+J.~Martonchik, D.~D.~J. Diner, J.~M. David, R.~Kahn, T.~P. Ackerman, M.~M.
+  Verstraete, B.~Pinty, and H.~R. Gordon, \enquote{{Techniques for the
+  Retrieval of Aerosol Properties over Land and Ocean Using Multi-angle
+  Imaging},} IEEE Trans. on Geoscience and Remote Sensing \textbf{36},
+  1212--1227 (1998).
+
+\bibitem{Namer2009}
+E.~Namer, S.~Shwartz, and Y.~Y. Schechner, \enquote{{Skyless polarimetric
+  calibration and visibility enhancement.}} Optics express \textbf{17}, 472--93
+  (2009).
+
+\bibitem{Bluestone2001}
+a.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
+  \enquote{{Three-dimensional optical tomography of hemodynamics in the human
+  head},} Optics express \textbf{9}, 272--86 (2001).
+
+\bibitem{messer}
+H.~Messer, A.~Zinevich, and P.~Alpert, \enquote{{Environmental sensor networks
+  using existing wireless communication systems for rainfall and wind velocity
+  measurements},} IEEE Instrumentation \& Measurement Magazine \textbf{15},
+  32--38 (2012).
+
+\bibitem{gregson}
+J.~Gregson, M.~Krimerman, M.~B. Hullin, and W.~Heidrich, \enquote{{Stochastic
+  tomography and its applications in 3D imaging of mixing fluids},} ACM Trans.
+  Graph. \textbf{31}, 52:1----52:10 (2012).
+
+\bibitem{Cosofret2009}
+B.~R. Cosofret, D.~Konno, A.~Faghfouri, H.~S. Kindle, C.~M. Gittins, M.~L.
+  Finson, T.~E. Janov, M.~J. Levreault, R.~K. Miyashiro, and W.~J. Marinelli,
+  \enquote{{Imaging sensor constellation for tomographic chemical cloud
+  mapping},} Applied optics \textbf{48}, 1837--52 (2009).
+
+\bibitem{Aviles2011}
+J.~A. Aviles, \enquote{{The Development and Validation of a First Generation
+  X-Ray Scatter Computed Tomography Algorithm for the Reconstruction of
+  Electron Density Breast Images Using Monte Carlo Simulation},} Ph.D. thesis
+  (2011).
+
+\bibitem{Cornette1995}
+W.~M. Cornette and J.~G. Shanks, \enquote{{Physically reasonable analytic
+  expression for the single-scattering phase function: errata.}} Applied optics
+  \textbf{34}, 641 (1995).
+
+\bibitem{Levi1980}
+L.~Levi, \emph{{Applied Optics}} (John Wiley \& Sons, Inc., 1980).
+
+\bibitem{devroye1986sample}
+L.~Devroye, \enquote{{Sample-based non-uniform random variate generation},} in
+  \enquote{Proceedings of the 18th conference on Winter simulation,}  (ACM,
+  1986), pp. 260--265.
+
+\bibitem{Hong2004}
+S.-H. Hong, J.-S. Jang, and B.~Javidi, \enquote{{Three-dimensional volumetric
+  object reconstruction using computational integral imaging.}} Optics express
+  \textbf{12}, 483--91 (2004).
+
+\bibitem{marshak20053d}
+A.~Marshak and A.~Davis, \emph{{3D Radiative Transfer in Cloudy Atmospheres}},
+  Physics of Earth and Space Environments (Springer, 2005).
+
+\bibitem{BBradiance}
+M.~Charity, \enquote{{Blackbody color datafile},}  (2001), \url{http://www.vendian.org/mncharity/dir3/blackbody/UnstableURLs/bbr\_color.html}.
+
+\bibitem{sun_composition}
+Wikipedia, \enquote{{Sunlight --- Wikipedia\{,\} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.
+
+\bibitem{Martonchik2009}
+J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
+  properties over land using MISR observations},} in \enquote{Satellite Aerosol
+  Remote Sensing over Land,} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
+  Berlin Heidelberg, 2009), pp. 267--293.
+
+\bibitem{BFGS}
+C.~Zhu, R.~H. Byrd, P.~Lu, and J.~Nocedal, \enquote{{Algorithm 778: L-BFGS-B:
+  Fortran subroutines for large-scale bound-constrained optimization},} ACM
+  Trans. Math. Softw. \textbf{23}, 550--560 (1997).
+
+\end{thebibliography}
 

### 2013-07-31 article.tex
bookmark

@@
+ 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\noindent {\bf Inverse Transform Sampling}: Monte Carlo methods
-simulate probabilistic phenomena by sampling from their probability
-disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is
-a common method for generating sample numbers at random from any
-probability distribution given its cumulative distribution function
-(cdf).  Let $X$ be a random variable whose distribution can be
-described by the cumulative distribution function $F$.  First we
-generate a random number $u$ from the standard uniform distribution in
-the interval $[0,1]$.  Then to draw a random number from the
-distribution described by $F$ we need to calculate the value $x$ such
-that $x = F^{-1}(u)$.
+\noindent {\bf Inverse Transform Sampling}: We use a Monte-Carlo (MC)
+method as a tool for RT. MC considers scattering and attenuation as
+random phenomena, that are sampled from their probability
+distributions.  Sample random numbers that comply with any known
+probability density function can be generated using inverse transform
+sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
+from a uniform distribution in the interval $[0,1]$. The number $u$
+can be transformed into a random variable $X$, whose cumulative
+distribution function (CDF) is $F(X)$. The transform is $X =
+F^{-1}(u)$.
 
@@
   \centering
-  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
+  \yoavcomment{\includegraphics[width=\linewidth]{images/ref_images.pdf}}
   \caption{\small [a] Photograph of a sky that includes {\em Haze

### 2013-07-31 article.tex
bookmark

@@
 The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
-elements (voxels), indexed by $k$ or $q$. In a
+elements (voxels), indexed by $k$, $m$ or $q$. In a
 \emph{single-scattering} model, any SR changes direction only once on
@@
 Suppose this LOS intersects voxel $q$. The geometric length of this
-intersection line segment is $l_{\rm LOS_c}(q)$ which depends on
-$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
+intersection line segment is $l_{\rm LOS_c}(m)$ which depends on
+$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $m$.  Analogously to
 \cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
-sparse matrix whose element $(k,q)$ is
-\begin{equation}
-  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
+sparse matrix whose element $(k,m)$ is
+\begin{equation}
+  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,m) =
   \left\{
     \begin{array}{ll}
-      l_{{\rm LOS}_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
+      l_{{\rm LOS}_c}(m) & \mbox{ if $m \in[{\rm LOS}_c,k]$} \\
       0  & \mbox{ otherwise}
@@
 \begin{align}
-  w_1[h(k)] = \sfrac{1} {n^{sea level}}
+  f_1[h(k)] = \sfrac{1} {n^{sea level}}
   \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
@@
 
-The second function, $w_2$, expresses a clustered nature of aerosol
+The second function, $f_2$, expresses a clustered nature of aerosol
 ``clouds''. We define blobs in the form of 3D ellipsoids. There may be
@@
 \begin{equation}
-  w_2(k) =
+  f_2(k) =
   \left\{
@@
   \label{eq:ntrue}
-  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
+  {\bm n}^{\rm true}={\bm f}_1\odot {\bm f}_2  .
   \hspace{-0.05cm}

### 2013-07-31 article.tex
bookmark

@@
 %
-\newcommand{\OpSphere}{\mathbfcal{S}}
-\newcommand{\OpRot}{\mathbfcal{R}}
-%\newcommand{\OpDistance}{\mathbfcal{D}}
-\newcommand{\OpDistance}{\bm{D}}
-\newcommand{\OpCumsum}{\mathbfcal{C}}
-\newcommand{\OpInt}{\mathbfcal{I}}
-\newcommand{\OpCamera}{\mathbfcal{P}}
-\newcommand{\Mask}{\mathbfcal{M}}
-\newcommand{\Laplacian}{\mathbfcal{L}}
-%\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
-\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
 \newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
@@
 
+%
+% Used symbols (only partial for now...)
+%
+\newcommand{\OpSphere}{\mathbfcal{S}}
+\newcommand{\OpRot}{\mathbfcal{R}}
+\newcommand{\OpDistance}{\bm{D}}
+\newcommand{\OpCumsum}{\mathbfcal{C}}
+\newcommand{\OpInt}{\mathbfcal{I}}
+\newcommand{\OpCamera}{\mathbfcal{P}}
+\newcommand{\MaskSun}{\mathbfcal{M}}
+\newcommand{\Laplacian}{\mathbfcal{L}}
+\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
+\newcommand{\DistSet}{\mathcal{C}}
+\newcommand{\DistUnknown}{\vect{n}}
+\newcommand{\DistEstimated}{\hat{\vect{n}}}
+\newcommand{\CostFunc}[1]{E(#1)}
+
+%
+% For the title
+%
 \newcommand\authnote[1]{\textsuperscript{\normalfont#1}}
@@
   aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
-the density distribution ${\bm n}$ is variable. As a numerical
+the density distribution ${\DistUnknown}$ is variable. As a numerical
 approximation, assume that within any voxel, the molecular parameters
@@
 known~\cite{Martonchik2009}. Hence, we focus on estimating the density
-distribution ${\bm n}$.
-% Most generally, this is the set $\left\{{\bm
-%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
-%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
-% parameters depend on the spectral channel $\lambda$.  Usually, a
-% single aerosol type dominates a scene. Furthermore, we assume that
-% the type of the aerosol above an area is
-% known~\cite{Martonchik2009}. Hence, we focus on estimating the
-% density distribution ${\bm n}$.
+distribution $\DistUnknown$.
 At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
@@
 as optimization of an objective function that fits the image-formation
-model to the measured photographs:
+model to the measured photographs, under constraints. Let $\DistSet$
+be the set of all legitimate distributions, according to constraints.
+Particularly, $\DistEstimated$ is non-negative, and it has limited spatial
+support between the ground and the TOA. The optimization problem is,
 \begin{equation}
   \label{eq:minobjectiveA}
-  \hat{\bm n} =
-  \argmin_{{\bm n}} F({\bm n})
+  \DistEstimated =
+  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
 \end{equation}
@@
   \label{eq:objectiveA}
-  F({\bm n})
+  \CostFunc{\DistUnknown}
   = \sum_{c=1}^{N_{\rm views}}
-  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
+  \| \MaskSun \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
   + \eta \Psi({\bm n})
 \end{equation}
-where $\Mask$ is a map that masks the areas around the sun, which are
+where $\MaskSun$ is a map that masks the areas around the sun, which are
 overwhelmingly bright. %and the horizon.

### 2013-07-31 article.tex
Modifications by Yoav

@@
- 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Multi-view 3D Aerosol Distribution Recovery}
+\title{Multi sky-view\\ 3D aerosol distribution recovery}
 
@@
 
-% An infinitesimal volume contains aerosols. The extinction and
-% scattering coefficients due to aerosols in this volume are,
-% respectively
-% \begin{equation}
-%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
-%  \;\;,\;\;
-%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
-%  \;.
-%  \label{eq:betaer}
-%\end{equation}
-%The infinitesimal volume contain also air molecules. Hence, the
-% overall extinction and scattering coefficients in this small volume
-% are, respectively
-% \begin{equation}
-%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
-%  \;\;,\;\;
-%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
-%  \;.
-%  \label{eq:betair}
-%\end{equation}
-
 \noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
@@
 
-\noindent {\bf Inverse Transform Sampling}: We use a Monte-Carlo (MC)
-method as a tool for RT. MC considers scattering and attenuation as
+\noindent {\bf Inverse Transform Sampling}: A tool for RT is Monte-Carlo (MC)
+simulation. MC considers scattering and extinction as
 random phenomena, that are sampled from their probability
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
+For example, consider a photon propagating in the atmosphere.
+The photon has high probability of propagating as long as $t$ is high, 
+and the probability diminishes as $t\rightarrow 0$. Thus Eq.~(\ref{eq:beer-lambert}) can be viewed as a probability density function, whose CDF is 
+\begin{equation}
+  \label{eq:Ftau}
+  F(\tau)=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau).
+\end{equation}
+Thus a photon propagates to a random optical depth 
+\begin{equation}
+  \label{eq:taurand}
+  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u).
+\end{equation}
+If the atmosphere is uniform, then from Eq.~(\ref{eq:tau}) the photon reaches a random distance
+\begin{equation}
+  \label{eq:lrand}
+  l^{\rm random}= (\beta^{\rm aerosol}+\beta^{\rm air})^{-1} \tau^{\rm random}
+                = -(\beta^{\rm aerosol}+\beta^{\rm air})^{-1}\ln(1-u),
+\end{equation}
+before interacting with a particle. If the number of photons launched is very high, their average number falls off in consistency with Eqs.~(\ref{eq:tau},\ref{eq:beer-lambert}). 
+Analogous transforms generate scattering at random angles, according to the phase function.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{3D recovery approach and its assessment}
 \label{sec:methodology}
 
-Consider a set of ground-based wide-angle cameras
-% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
-% Koppal:2011:WMS:2191740.2192152}
-looking upwards (\cref{fig:groundgrid}). The set performs {\em
+A set of ground-based wide-angle cameras
+looks upwards (\cref{fig:groundgrid}), performing {\em
   integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
@@
 are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
-distinct fixed location ${\bm x}$, capturing raw image
-$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
-a principle of estimating the 3D atmospheric aerosols distribution,
-using such data. To show feasibility, we perform radiative transfer
-using two different forward models, enabling cross-validation.  A
-forward model takes as input the 3D aerosol distribution, and outputs
-images as if captured at various viewpoints. One model uses Monte
-Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
-slow but naturally expresses multiple-scattering. Hence, this approach
-simulates realistic scenes of arbitrary complexity.  The second model
-uses the single-scattering approximation
+distinct fixed location, capturing raw image
+$i_c({\bm{\Theta}})$. This paper takes a first step of formulating
+a principle for estimating the 3D atmospheric aerosols distribution,
+using such data. To study the feasibility and cross validate it, we perform RT
+using two different forward models. A forward model takes as input a 3D aerosol distribution, and outputs images as if captured at various viewpoints. 
+One model uses MC (\cref{sec:monte-carlo-simul}): it is stochastic,
+slow but naturally expresses multiple-scattering. Hence, MC
+rigorously simulates realistic scenes of arbitrary complexity. 
+%MC simulations can be made arbitrarily accurate by increasing the number of launched %photons. MC methods are highly parallelizable. 
+The second model uses the single-scattering approximation
 (\cref{sec:single-scatt-model}). It is less accurate than MC, but
-solves radiative transfer in an analytic, closed form. This form
+solves RT in an analytic, closed form. This form
 enables simple inversion of the model, to estimate the underlying
-atmosphere (\cref{sec:inverse-problem}).
+aerosol distribution (\cref{sec:inverse-problem}).
 
@@
 very dense: inside fog and clouds this model does not apply. In this
-model, radiative transfer has three steps (\cref{fig:groundgrid}):
+model, RT has three steps (\cref{fig:groundgrid}):
 ({\tt i}) Attenuation of a SR propagating from the top of the
@@
   \quad
-  % \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
-  % \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
-  % g}(\vect{\Phi}^{\rm scatter}_c) \;.
   \tilde{\vect{\alpha}}^{\rm aerosol}_c =
@@
 \end{equation}
-% The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter
-% of the phase function, in all voxels. This notation indicates a
-% parametric phase function as in \cref{eq:aerosol_scatter}.
 Here the operator $\odot$ denotes the Hadamard (element-wise) product.
@@
 image is thus
-% \begin{align}
-%   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
-%     (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
-%     aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
-%     (\vect{\sigma} \odot {\bm n})]\} \right\}
-%   \label{eq:bigIc}
-% \end{align}
-% We focus on situations where there is only a single type of aerosol
-% over a scene. Hence, the three-element vector $[{\sigma}^{\rm
-% aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
-% the density distribution ${\bm n}$ is variable. Then,
-% \cref{eq:bigIc} degenerates to
 \begin{align}
@@
 
-\section{Monte Carlo RT}
+\section{Multiple-Scattering Forward Model by Monte Carlo}
 \label{sec:monte-carlo-simul}
 
-Monte Carlo (MC) methods enable rigorous modeling of photon
-propagation in the atmosphere.  MC simulations can be made arbitrarily
-accurate by increasing the number of launched photons. MC methods are
-highly parallelizable. When applied to the RT problem, they enable
-simulating multiple scattering and produce realistic results.
-
-The MC simulations use the same atmospheric grid described in
-\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
-traced from the detector, camera, to their source, the Sun, in a
-direction determined by the camera model, i.e. hemispherical
-camera. The quality of the simulations is proportional to the number
-of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
-photons were emitted from each pixel. The distance travelled by the
-photon till its first scattering is determined by sampling from the
-transmittance distribution using the inverse transform sampling
-(\cref{sec:theor-backgr}).  The CDF of the optical depth
-(transmittance) distribution is given by,
-\begin{equation}
-  \label{eq:1}
-  F=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau)
-\end{equation}
-Given a uniformly distributed random number $u$ a random optical depth
-is given by
-\begin{equation}
-  \label{eq:2}
-  t=F^{-1}(u)=-\ln(1-u)
-\end{equation}
-The actual distance travelled by the photon is calculated by
-accumulating the discrete optical depths of each voxel along the
-photon's path till the target optical path, drawn by \cref{eq:2}, is
-reached.  If the scattering occurs outside the atmospheric grid, the
-photon is dropped. If not, the voxel in which the scattering occurs is
-calculated.  The type of scattering, either by air molecule or aerosol
-particle, is determined randomly according to their relative densities
-in the voxel.  The new direction of the photon is determined by
-inverse sampling the phase function of the scattering particle:
-Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
-\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
-used for calculating the amount of light reaching the sun at each
-scattering.  This process is repeated till the photon escapes the
-atmosphere grid or it reaches a predetermined number of scatterings.
+The MC simulations rely on the same grid as Sec.~\ref{sec:single-scatt-model}.
+We use backward MC: from a detector pixel, photons are `launched' via the camera lens; then the photons are traced back through the atmosphere.
+Photons that happen to be back-traced to the Sun are counted, per pixel.
+In this model, RT takes the following steps, per launched photon (\cref{fig:mcgrid}):\\
+({\tt i}) Launch a photon from camera $c$ to direction ${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.\\
+Per iteration $i$\\
+({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon propagates.
+To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm random}$.
+Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm random}$ s.t.
+\begin{align}
+  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm random}
+  \label{eq:MCextinct}
+\end{align}
+Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf X}_{i}$.
+If  ${\bf X}_{i}$ is outside the atmospheric grid, the photon is terminated. If, in addition,  ${\cal R}_{i}\parallel {\rm SR}$ , the photon is counted as contributing to the image pixel.\\
+({\tt iii}) The type of particle (air molecule or aerosol) the photon interacts with at ${\bf X}_{i}$ is determined randomly according to their relative densities at the voxel containing ${\bf X}_{i}$.\\
+({\tt iv}) If it is an aerosol, the photon is terminated with probability 
+$1-\varpi^{\rm aerosol}$.\\
+({\tt v}) The photon is scattered to a new direction, determined by inverse transform sampling, according to the phase function of the particle: \cref{eq:aerosol_scatter}
+or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)  proceeds.\\
+Local Estimation~\cite{marshak20053d} is used for calculating the amount of light back-traced to the sun at each scattering.
+
+The quality of the simulations is proportional to the number of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
+photons were emitted from each pixel.
 
@@
 be the set of all legitimate distributions, according to constraints.
-Particularly, $\DistEstimated$ is non-negative, and it has limited spatial
-support between the ground and the TOA. The optimization problem is,
+Particularly, $\DistUnknown$ is non-negative, and its spatial
+support is bounded between the ground and the TOA. The optimization problem is
 \begin{equation}
@@
   = \sum_{c=1}^{N_{\rm views}}
-  \| \MaskSun \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
+  \left\| 
+     \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
+  \right\|^2_2
   + \eta \Psi({\bm n})
 \end{equation}
-where $\MaskSun$ is a map that masks the areas around the sun, which are
-overwhelmingly bright. %and the horizon.
+Here $\MaskSun$ masks the area around the sun, which in real-world photographs is indeed blocked. %and the horizon.
 % These regions are prone to dominant multiple scattering.
@@
 that expresses some prior knowledge on the distribution, while $\eta$
-is a regularization weight.  Since aerosol distributions are usually
-fuzzy, it can be beneficial that regularization be a {\em smoothness
-  term}, which penalizes energy in second order spatial derivatives
-(3D Laplacian). Hence, we use
+is a regularization weight.
+
+Since aerosol distributions are usually fuzzy, useful regularization is by a {\em smoothness term}, which penalizes energy in second order spatial derivatives
+(3D Laplacian), $\| \nabla^2{\bm n}\|^2_2$.
+Regularization is not required when data is sufficient and reliable.
+As seen in Fig.~\ref{fig:groundgrid}, voxels at high altitude have good coverage by many cameras at multiple directions, while at low altitude voxels are mainly observed by local cameras.
+Hence, regularization can be weakened with altitude.
+We accomplished this weakening using a weight
+$w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
 \begin{equation}
   \label{eq:regularizer}
-  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
-\end{equation}
-where $\Laplacian$ is a matrix representation of the 3D
-\emph{Laplacian} operator.
+  \Psi({\bm n}) = \| {\bf W} \Laplacian{\bm n}\|^2_2
+\end{equation}
+where $\Laplacian$ is a matrix representation of the 3D Laplacian operator, and matrix
+${\bf W}$ is diagonal, whose elements are $w(k)$.
 
@@
     measured}_c - {\bm i}_c({\bm n})] + 2 \eta
-  \transpose{\Laplacian}\Laplacian{\bm n} \;.
+  \transpose{\Laplacian}\transpose{{\bf W}}{\bf W}\Laplacian{\bm n} \;.
   \label{eq:gradient1}

### 2013-07-31 article.tex
Fixed results image.

@@
 
-Optical lightfield and integral
-imaging~\cite{Stern2006,kim,Ng1948} sample the optical
-radiance distribution in location and direction. These are mainly used in
-small-scale setups. This paper deals with a far larger scale, to
-estimate scatterer 3D spatial distribution in the sky.  The atmosphere
-allows light to pass through in multiple locations and
-directions. Light is affected by this medium. Therefore, in this paper
-we lay out a principle to recover this 3D distribution using measured
-and modeled light-fields (Fig.~\ref{fig:groundgrid}).
+Optical lightfield and integral imaging~\cite{Stern2006,kim,Ng1948}
+sample the optical radiance distribution in location and
+direction. These are mainly used in small-scale setups. This paper
+deals with a far larger scale, to estimate scatterer 3D spatial
+distribution in the sky.  The atmosphere allows light to pass through
+in multiple locations and directions. Light is affected by this
+medium. Therefore, in this paper we lay out a principle to recover
+this 3D distribution using measured and modeled light-fields
+(Fig.~\ref{fig:groundgrid}).
 \begin{figure*}[t!]
@@
 
-In remote sensing~\cite{Mishchenko2007}, imaging through air is associated with
-{\em atmospheric correction}, based on {\em aerosol retrieval}. In
-this discipline, the atmosphere is often assumed to be plane-parallel,
-using one-dimensional vertical RT. Consequently state-of-the-art
-aerosol retrieval is done in distinct large lateral
+In remote sensing~\cite{Mishchenko2007}, imaging through air is
+associated with {\em atmospheric correction}, based on {\em aerosol
+  retrieval}. In this discipline, the atmosphere is often assumed to
+be plane-parallel, using one-dimensional vertical RT. Consequently
+state-of-the-art aerosol retrieval is done in distinct large lateral
 blocks~\cite{Martonchikc} with limited height
@@
 recovery. Atmospheric correction is related to
-dehazing~\cite{Namer2009}. In this paper, however, the medium
-itself, at all relevant altitudes is the object of interest.
+dehazing~\cite{Namer2009}. In this paper, however, the medium itself,
+at all relevant altitudes is the object of interest.
 
@@
 projection is similar to tomography in other scientific
-domains~\cite{Bluestone2001}. However, the situation here is distinct. Most
-tomography setups have a controlled and/or multidirectional radiation
-source~\cite{Bluestone2001,messer}. In contrast, our source is the
-uncontrolled, unidirectional Sun. Moreover, typical tomography relies
-on a linear model~\cite{gregson}: the pixel value is a linear
-combination of components along a line of sight (LOS), or a
-multiplicative combination (linearized by a logarithm). Linear
-tomography can detect
-gases~\cite{Cosofret2009}, which absorb
-UV or IR radiation. However, aerosol attenuation of visible light is
-typically dominated by {\em scattering}, rather than absorption. Since
-the radiation source is single and fixed in space and time, we cannot
-rely on direct illumination for tomographic recovery of attenuation
+domains~\cite{Bluestone2001}. However, the situation here is
+distinct. Most tomography setups have a controlled and/or
+multidirectional radiation source~\cite{Bluestone2001,messer}. In
+contrast, our source is the uncontrolled, unidirectional
+Sun. Moreover, typical tomography relies on a linear
+model~\cite{gregson}: the pixel value is a linear combination of
+components along a line of sight (LOS), or a multiplicative
+combination (linearized by a logarithm). Linear tomography can detect
+gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
+aerosol attenuation of visible light is typically dominated by {\em
+  scattering}, rather than absorption. Since the radiation source is
+single and fixed in space and time, we cannot rely on direct
+illumination for tomographic recovery of attenuation
 fields~\cite{Aviles2011}. We may only use sunlight scattered into the
@@
 
-\noindent {\bf Inverse Transform Sampling}: A tool for RT is Monte-Carlo (MC)
-simulation. MC considers scattering and extinction as
+\noindent {\bf Inverse Transform Sampling}: A tool for RT is
+Monte-Carlo (MC) simulation. MC considers scattering and extinction as
 random phenomena, that are sampled from their probability
@@
 
-For example, consider a photon propagating in the atmosphere.
-The photon has high probability of propagating as long as $t$ is high, 
-and the probability diminishes as $t\rightarrow 0$. Thus Eq.~(\ref{eq:beer-lambert}) can be viewed as a probability density function, whose CDF is 
+For example, consider a photon propagating in the atmosphere.  The
+photon has high probability of propagating as long as $t$ is high, and
+the probability diminishes as $t\rightarrow 0$. Thus
+Eq.~(\ref{eq:beer-lambert}) can be viewed as a probability density
+function, whose CDF is
 \begin{equation}
@@
 \end{equation}
-If the atmosphere is uniform, then from Eq.~(\ref{eq:tau}) the photon reaches a random distance
+If the atmosphere is uniform, then from Eq.~(\ref{eq:tau}) the photon
+reaches a random distance
 \begin{equation}
@@
 \end{equation}
-before interacting with a particle. If the number of photons launched is very high, their average number falls off in consistency with Eqs.~(\ref{eq:tau},\ref{eq:beer-lambert}). 
-Analogous transforms generate scattering at random angles, according to the phase function.
+before interacting with a particle. If the number of photons launched
+is very high, their average number falls off in consistency with
+Eqs.~(\ref{eq:tau},\ref{eq:beer-lambert}).  Analogous transforms
+generate scattering at random angles, according to the phase function.
 
@@
 
-A set of ground-based wide-angle cameras
-looks upwards (\cref{fig:groundgrid}), performing {\em
-  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
-view azimuth and elevation angles (relative to the zenith and north)
-are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
+A set of ground-based wide-angle cameras looks upwards
+(\cref{fig:groundgrid}), performing {\em integral
+  imaging}~\cite{Hong2004} of the sky. Per viewpoint, the view azimuth
+and elevation angles (relative to the zenith and north) are
+encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
 distinct fixed location, capturing raw image
-$i_c({\bm{\Theta}})$. This paper takes a first step of formulating
-a principle for estimating the 3D atmospheric aerosols distribution,
-using such data. To study the feasibility and cross validate it, we perform RT
-using two different forward models. A forward model takes as input a 3D aerosol distribution, and outputs images as if captured at various viewpoints. 
-One model uses MC (\cref{sec:monte-carlo-simul}): it is stochastic,
-slow but naturally expresses multiple-scattering. Hence, MC
-rigorously simulates realistic scenes of arbitrary complexity. 
-%MC simulations can be made arbitrarily accurate by increasing the number of launched %photons. MC methods are highly parallelizable. 
+$i_c({\bm{\Theta}})$. This paper takes a first step of formulating a
+principle for estimating the 3D atmospheric aerosols distribution,
+using such data. To study the feasibility and cross validate it, we
+perform RT using two different forward models. A forward model takes
+as input a 3D aerosol distribution, and outputs images as if captured
+at various viewpoints.  One model uses MC
+(\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally
+expresses multiple-scattering. Hence, MC rigorously simulates
+realistic scenes of arbitrary complexity.
+% MC simulations can be made arbitrarily accurate by increasing the
+% number of launched %photons. MC methods are highly parallelizable.
 The second model uses the single-scattering approximation
 (\cref{sec:single-scatt-model}). It is less accurate than MC, but
-solves RT in an analytic, closed form. This form
-enables simple inversion of the model, to estimate the underlying
-aerosol distribution (\cref{sec:inverse-problem}).
+solves RT in an analytic, closed form. This form enables simple
+inversion of the model, to estimate the underlying aerosol
+distribution (\cref{sec:inverse-problem}).
 
@@
 
-The MC simulations rely on the same grid as Sec.~\ref{sec:single-scatt-model}.
-We use backward MC: from a detector pixel, photons are `launched' via the camera lens; then the photons are traced back through the atmosphere.
-Photons that happen to be back-traced to the Sun are counted, per pixel.
-In this model, RT takes the following steps, per launched photon (\cref{fig:mcgrid}):\\
-({\tt i}) Launch a photon from camera $c$ to direction ${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.\\
-Per iteration $i$\\
-({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon propagates.
-To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm random}$.
-Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm random}$ s.t.
-\begin{align}
-  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm random}
+The MC simulations rely on the same grid as
+Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
+pixel, photons are `launched' via the camera lens; then the photons
+are traced back through the atmosphere. Photons that happen to be
+back-traced to the Sun are counted, per pixel. In this model, RT takes
+the following steps, per launched photon (\cref{fig:mcgrid}):
+
+\noindent ({\tt i}) Launch a photon from camera $c$ to direction
+${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.
+
+\noindent Per iteration $i$
+
+\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon
+propagates. To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm
+  random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform
+atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm
+  random}$ s.t.
+\begin{align}
+  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
+  = \tau^{\rm random}
   \label{eq:MCextinct}
 \end{align}
-Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf X}_{i}$.
-If  ${\bf X}_{i}$ is outside the atmospheric grid, the photon is terminated. If, in addition,  ${\cal R}_{i}\parallel {\rm SR}$ , the photon is counted as contributing to the image pixel.\\
-({\tt iii}) The type of particle (air molecule or aerosol) the photon interacts with at ${\bf X}_{i}$ is determined randomly according to their relative densities at the voxel containing ${\bf X}_{i}$.\\
-({\tt iv}) If it is an aerosol, the photon is terminated with probability 
-$1-\varpi^{\rm aerosol}$.\\
-({\tt v}) The photon is scattered to a new direction, determined by inverse transform sampling, according to the phase function of the particle: \cref{eq:aerosol_scatter}
-or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)  proceeds.\\
-Local Estimation~\cite{marshak20053d} is used for calculating the amount of light back-traced to the sun at each scattering.
-
-The quality of the simulations is proportional to the number of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
+Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf
+  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
+photon is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
+  SR}$ , the photon is counted as contributing to the image pixel.
+
+\noindent ({\tt iii}) The type of particle (air molecule or aerosol) the photon
+interacts with at ${\bf X}_{i}$ is determined randomly according to
+their relative densities at the voxel containing ${\bf X}_{i}$.
+
+\noindent ({\tt iv}) If it is an aerosol, the photon is terminated with
+probability $1-\varpi^{\rm aerosol}$.
+
+\noindent ({\tt v}) The photon is scattered to a new direction, determined by
+inverse transform sampling, according to the phase function of the
+particle: \cref{eq:aerosol_scatter} or~\cref{eq:rayleighP}. This
+yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf
+  X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)
+proceeds.
+
+\noindent Local Estimation~\cite{marshak20053d} is used for calculating the
+amount of light back-traced to the sun at each scattering.
+
+The quality of the simulations is proportional to the number of
+photons. To create the \cref{fig:simulation-results1}b, \num{10000}
 photons were emitted from each pixel.
@@
 known~\cite{Martonchik2009}. Hence, we focus on estimating the density
-distribution $\DistUnknown$.
-At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
-  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
-as optimization of an objective function that fits the image-formation
-model to the measured photographs, under constraints. Let $\DistSet$
-be the set of all legitimate distributions, according to constraints.
-Particularly, $\DistUnknown$ is non-negative, and its spatial
-support is bounded between the ground and the TOA. The optimization problem is
+distribution $\DistUnknown$.  At hand, we have $N_{\rm views}$
+measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
+    views}}$. The recovery task is phrased as optimization of an
+objective function that fits the image-formation model to the measured
+photographs, under constraints. Let $\DistSet$ be the set of all
+legitimate distributions, according to constraints.  Particularly,
+$\DistUnknown$ is non-negative, and its spatial support is bounded
+between the ground and the TOA. The optimization problem is
 \begin{equation}
@@
 \end{equation}
-Here $\MaskSun$ masks the area around the sun, which in real-world photographs is indeed blocked. %and the horizon.
+Here $\MaskSun$ masks the area around the sun, which in real-world
+photographs is indeed blocked. %and the horizon.
 % These regions are prone to dominant multiple scattering.
@@
 
-Since aerosol distributions are usually fuzzy, useful regularization is by a {\em smoothness term}, which penalizes energy in second order spatial derivatives
-(3D Laplacian), $\| \nabla^2{\bm n}\|^2_2$.
-Regularization is not required when data is sufficient and reliable.
-As seen in Fig.~\ref{fig:groundgrid}, voxels at high altitude have good coverage by many cameras at multiple directions, while at low altitude voxels are mainly observed by local cameras.
-Hence, regularization can be weakened with altitude.
-We accomplished this weakening using a weight
+Since aerosol distributions are usually fuzzy, useful regularization
+is by a {\em smoothness term}, which penalizes energy in second order
+spatial derivatives (3D Laplacian), $\| \nabla^2{\bm
+  n}\|^2_2$. Regularization is not required when data is sufficient
+and reliable. As seen in Fig.~\ref{fig:groundgrid}, voxels at high
+altitude have good coverage by many cameras at multiple directions,
+while at low altitude voxels are mainly observed by local
+cameras. Hence, regularization can be weakened with altitude. We
+accomplished this weakening using a weight
 $w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
@@
 \end{equation}
-where $\Laplacian$ is a matrix representation of the 3D Laplacian operator, and matrix
-${\bf W}$ is diagonal, whose elements are $w(k)$.
+where $\Laplacian$ is a matrix representation of the 3D Laplacian
+operator, and matrix ${\bf W}$ is diagonal, whose elements are $w(k)$.
 
@@
     measured}_c - {\bm i}_c({\bm n})] + 2 \eta
-  \transpose{\Laplacian}\transpose{{\bf W}}{\bf W}\Laplacian{\bm n} \;.
+  \transpose{\Laplacian}\transpose{{\bf W}}{\bf W}\Laplacian{\bm n}
+  \;.
   \label{eq:gradient1}
@@
 in all voxels, relative to the total aerosol mass in the scene.  In
-the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
+the {\em Haze Blobs} case, $\epsilon=0.143$ and $\epsilon=0.646$ for
 the reconstructions based on the Single-Scattering images and MC
@@
 visualizes the recovered 3D distribution of this scene. For the {\em
-  Haze Front}, $\epsilon=0.46$ and $\epsilon=0.62$ for the
+  Haze Front}, $\epsilon=0.199$ and $\epsilon=0.654$ for the
 reconstructions based on the Single-Scattering images and MC images

### 2013-08-01 article.tex
Added Monte Carlo image
Bookmark

@@
 \bibitem{Bluestone2001}
-a.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
+A.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
   \enquote{{Three-dimensional optical tomography of hemodynamics in the human
   head},} Optics express \textbf{9}, 272--86 (2001).
+
+\bibitem{Boas2001}
+D.~A. Boas, D.~H. Brooks, E.~L. Miller, C.~A. DiMarzio, M.~Kilmer, R.~J.
+  Gaudette, and Q.~Zhang, \enquote{{Imaging the body with diffuse optical
+  tomography},} Sig.Proc. Magazine \textbf{18}, 57--75 (2001).
 
@@
 \bibitem{sun_composition}
-Wikipedia, \enquote{{Sunlight --- Wikipedia\{,\} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.
+Wikipedia, \enquote{{Sunlight --- {W}ikipedia{,} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.
 
@@
 J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
-  properties over land using MISR observations},} in \enquote{Satellite Aerosol
-  Remote Sensing over Land,} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
+  properties over land using MISR observations},} in \emph{{Satellite Aerosol
+  Remote Sensing over Land,}} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
   Berlin Heidelberg, 2009), pp. 267--293.
@@
 (Fig.~\ref{fig:groundgrid}).
-\begin{figure*}[t!]
-  \begin{center}
-    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
-  \end{center}
-  \caption{\small Lightfield imaging through a volumetric distribution
-    in the atmosphere, using ground-based cameras.}
-  \label{fig:groundgrid}
-\end{figure*}
 3D recovery of this medium has direct implications to various
@@
 distinct. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{Bluestone2001,messer}. In
+multidirectional radiation source~\cite{Boas2001,messer}. In
 contrast, our source is the uncontrolled, unidirectional
@@
 function, to enable efficient optimization.
+\begin{figure*}[t!]
+  \begin{center}
+    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
+  \end{center}
+  \caption{\small Lightfield imaging through a volumetric distribution
+    in the atmosphere, using ground-based cameras.}
+  \label{fig:groundgrid}
+\end{figure*}
 
@@
 The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
-elements (voxels), indexed by $k$, $m$ or $q$. In a
-\emph{single-scattering} model, any SR changes direction only once on
-the way to a camera. This model is valid in atmospheres that are not
-very dense: inside fog and clouds this model does not apply. In this
-model, RT has three steps (\cref{fig:groundgrid}):
+elements (voxels), indexed by $k$, $m$ or $q$. \cref{fig:distributions}.
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
+  \caption{\small [a] and [b] Simulated 3D aerosol distribution
+    composed of a {\em Haze Front} and {\em Haze Front}
+    respectively. The density units are $10^{6}~{\rm particles}/{\rm
+      m}^3.$}
+  \label{fig:distributions}
+\end{figure}
+In a \emph{single-scattering} model, any SR changes direction only
+once on the way to a camera. This model is valid in atmospheres that
+are not very dense: inside fog and clouds this model does not
+apply. In this model, RT has three steps (\cref{fig:groundgrid}):
 ({\tt i}) Attenuation of a SR propagating from the top of the
@@
 $\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
-angle. Given \cref{eq:tau}, the total optical depths
-corresponding to LOSs (of camera $c$) and SRs that cross all voxels
-comprise the vector
+angle. Given \cref{eq:tau}, the total optical depths corresponding to
+LOSs (of camera $c$) and SRs that cross all voxels comprise the vector
 \begin{equation}
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal}) the radiant power
-contributed by the voxel is
+(\cref{eq:beer-lambert,eq:tautotal}) the radiant power contributed by
+the voxel is
 \begin{equation}
@@
 atmosphere. The cone contains or intersects some voxels, while being
-oblivious to all the rest.
-Overall, light power captured at a pixel is a weighted sum of the
-power $p_c(k)$ from all voxels.  This sum is formulated by a matrix
-operation over ${\bm p}_c$:
+oblivious to all the rest.  Overall, light power captured at a pixel
+is a weighted sum of the power $p_c(k)$ from all voxels.  This sum is
+formulated by a matrix operation over ${\bm p}_c$:
 \begin{equation}
@@
 \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Multiple-Scattering Forward Model by Monte Carlo}
-\label{sec:monte-carlo-simul}
-
-The MC simulations rely on the same grid as
-Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
-pixel, photons are `launched' via the camera lens; then the photons
-are traced back through the atmosphere. Photons that happen to be
-back-traced to the Sun are counted, per pixel. In this model, RT takes
-the following steps, per launched photon (\cref{fig:mcgrid}):
-
-\noindent ({\tt i}) Launch a photon from camera $c$ to direction
-${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.
-
-\noindent Per iteration $i$
-
-\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon
-propagates. To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm
-  random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform
-atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm
-  random}$ s.t.
-\begin{align}
-  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
-  = \tau^{\rm random}
-  \label{eq:MCextinct}
-\end{align}
-Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf
-  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
-photon is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
-  SR}$ , the photon is counted as contributing to the image pixel.
-
-\noindent ({\tt iii}) The type of particle (air molecule or aerosol) the photon
-interacts with at ${\bf X}_{i}$ is determined randomly according to
-their relative densities at the voxel containing ${\bf X}_{i}$.
-
-\noindent ({\tt iv}) If it is an aerosol, the photon is terminated with
-probability $1-\varpi^{\rm aerosol}$.
-
-\noindent ({\tt v}) The photon is scattered to a new direction, determined by
-inverse transform sampling, according to the phase function of the
-particle: \cref{eq:aerosol_scatter} or~\cref{eq:rayleighP}. This
-yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf
-  X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)
-proceeds.
-
-\noindent Local Estimation~\cite{marshak20053d} is used for calculating the
-amount of light back-traced to the sun at each scattering.
-
-The quality of the simulations is proportional to the number of
-photons. To create the \cref{fig:simulation-results1}b, \num{10000}
-photons were emitted from each pixel.
 
@@
 As an example, we created a {\em Haze Blobs} scene using two ellipsoid
-blobs (\cref{fig:results}a): the first is centered at altitude
+blobs (\cref{fig:distributions}a): the first is centered at altitude
 \SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
@@
 section of the photographs along the horizontal Axis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Multiple-Scattering Forward Model by Monte Carlo}
+\label{sec:monte-carlo-simul}
+
+The MC simulations rely on the same grid as
+Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
+pixel, photons are `launched' via the camera lens; then the photons
+are traced back through the atmosphere. Photons that happen to be
+back-traced to the Sun are counted, per pixel. In this model, RT takes
+the following steps, per launched photon (\cref{fig:mcgrid}):
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=0.5\linewidth]{images/mcgrid.pdf}}
+  \caption{\small Monte Carlo simulation of multiple-scattering
+    radiative transfer.}
+  \label{fig:mcgrid}
+\end{figure}
+
+\noindent ({\tt i}) Launch a photon from camera $c$ to direction
+${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.
+
+\noindent Per iteration $i$
+
+\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which
+the photon propagates. To do this, Eq.~(\ref{eq:taurand}) yields
+$\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a
+non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek
+$l^{\rm random}$ s.t.
+\begin{align}
+  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
+  = \tau^{\rm random}
+  \label{eq:MCextinct}
+\end{align}
+Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf
+  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
+photon is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
+  SR}$ , the photon is counted as contributing to the image pixel.
+
+\noindent ({\tt iii}) The type of particle (air molecule or aerosol)
+the photon interacts with at ${\bf X}_{i}$ is determined randomly
+according to their relative densities at the voxel containing ${\bf
+  X}_{i}$.
+
+\noindent ({\tt iv}) If it is an aerosol, the photon is terminated
+with probability $1-\varpi^{\rm aerosol}$.
+
+\noindent ({\tt v}) The photon is scattered to a new direction,
+determined by inverse transform sampling, according to the phase
+function of the particle: \cref{eq:aerosol_scatter}
+or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal
+  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
+Estimation~\cite{marshak20053d} is used for calculating the amount of
+light back-traced to the sun at each scattering. The next iteration of
+propagation (denoted {\tt ii} above) proceeds.
+
+The quality of the simulations is proportional to the number of
+photons. To create the \cref{fig:simulation-results1}b, \num{10000}
+photons were emitted from each pixel.
 
@@
 
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
+  \caption{\small [a] and [b] Reconstruction of the scenes shown in
+    \cref{fig:distributions} when using Single-Scattering simulated
+    images as input.  [c] and [d] Reconstruction of the same scenes
+    when using MC simulated images as input.  Color represents aerosol
+    density. The density units are $10^{6}~{\rm particles}/{\rm
+      m}^3.$}
+  \label{fig:results}
+\end{figure}
 We applied the reconstruction algorithm \cref{sec:inverse-problem} to
@@
 An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
-the reconstructed scene based on images simulated by the Single
-Scattering model. \cref{fig:results}e visualizes the reconstructed
-scene based on images simulated by the MC model. The distributions
-appear consistent, though there are errors that stem from the random
-noise in the images. To quantify the results, we use a relative error
-measure based on the $\ell_1$ norm
-\begin{equation}
-  \label{eq:ndiff}
-  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
-  {\| {\bm n}^{\rm true} \|_1} ,
-\end{equation}
-It is equivalent to the aerosol mass that is over and under-estimated
-in all voxels, relative to the total aerosol mass in the scene.  In
-the {\em Haze Blobs} case, $\epsilon=0.143$ and $\epsilon=0.646$ for
-the reconstructions based on the Single-Scattering images and MC
-images respectively. We used the distribution reconstructed based on
-the MC images to create images using the Single-Scattering
+distribution is shown in
+\cref{fig:distributions}a. \cref{fig:results}a show the reconstructed
+scene based on images simulated by the Single Scattering
+model. \cref{fig:results}c visualizes the reconstructed scene based on
+images simulated by the MC model. The distributions appear consistent,
+though there are errors that stem from the random noise in the
+images. To quantify the results, we use a relative error measure based
+on the $\ell_1$ norm: $\epsilon=\sfrac{\| \hat{\bm n} - {\bm n}^{\rm
+    true} \|_1} {\| {\bm n}^{\rm true} \|_1}$.  It is equivalent to
+the aerosol mass that is over and under-estimated in all voxels,
+relative to the total aerosol mass in the scene.  In the {\em Haze
+  Blobs} case, $\epsilon=0.14$ and $\epsilon=0.65$ for the
+reconstructions based on the Single-Scattering images and MC images
+respectively. We used the distribution reconstructed based on the MC
+images to create images using the Single-Scattering
 model. \cref{fig:simulation-results1}c shows a cross of such an image
@@
 
-We created a {\em Haze Front} scene. \cref{fig:results}b shows an
-iso-surface visualization of this distribution.
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
-  \caption{\small [a] and [b] Simulated 3D aerosol distribution
-    composed of a {\em Haze Front} and {\em Haze Front}
-    respectively. [c] and [d] Reconstruction of the same scenes when
-    using Single-Scattering simulated images as input.  [e] and [f]
-    Reconstruction of the scenes when using MC simulated images as
-    input.  Color represents aerosol density. The density units are
-    $10^{6}~{\rm particles}/{\rm m}^3.$}
-  \label{fig:results}
-\end{figure}
+We created a {\em Haze Front} scene. \cref{fig:distributions}b shows
+an iso-surface visualization of this distribution.
 Here an ellipsoid degenerated to an elliptic cylinder that partly
@@
 part of which enters the volume). The haze front stretches across the
-width of the volume.  \cref{fig:results}d and \cref{fig:results}f
+width of the volume.  \cref{fig:results}b and \cref{fig:results}d
 visualizes the recovered 3D distribution of this scene. For the {\em
-  Haze Front}, $\epsilon=0.199$ and $\epsilon=0.654$ for the
+  Haze Front}, $\epsilon=0.20$ and $\epsilon=0.65$ for the
 reconstructions based on the Single-Scattering images and MC images
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% Acknowledgments %%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Acknowledgments}
+\label{sec:acknowledgments}
+
+We thank Anthony~B. Davis and David~J. Diner for useful
+discussions. Yoav Schechner is a Landau Fellow - supported by the Taub
+Foundation. This work was conducted in the Ollendorff Minerva
+Center. Minerva is funded through the BMBF.
+
 \end{document}

### 2013-08-04 article.tex
Added OCIS codes.
Yoav fixes with small updates by me.

@@
 
-\ocis{(000.0000)
-  General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
+\ocis{
+(100.3190)   Inverse problems;
+(100.3200)   Inverse scattering;
+(280.1100)   Aerosol detection;
+(280.1310)   Atmospheric scattering;
+(280.4991)   Passive remote sensing.
+}
 
@@
   \textbf{12}, 483--91 (2004).
+
+\bibitem{Iwabuchi2006}
+H.~Iwabuchi, \enquote{{Efficient Monte Carlo Methods for Radiative Transfer
+  Modeling},} Journal of the Atmospheric Sciences \textbf{63}, 2324--2339
+  (2006).
 
@@
   \end{center}
-  \caption{\small Lightfield imaging through a volumetric distribution
+  \caption{\small Integral (lightfield) imaging through a volumetric distribution
     in the atmosphere, using ground-based cameras.}
@@
 
-\section{Theoretical Background}
+\section{Theoretical background}
 \label{sec:theor-backgr}
@@
 that includes particles of a certain type.  Each particle has an {\em
-  extinction cross section} for interacting with the irradiance. For
-an aerosol the cross section is denoted $\sigma^{\rm aerosol}$.  The
-aerosol density is $n$. Per unit volume, the {\em extinction
+  extinction cross section} for interacting with the irradiance. An
+aerosol extinction cross section is denoted $\sigma^{\rm aerosol}$.
+The aerosol density is $n$. Per unit volume, the {\em extinction
   coefficient} due to aerosols is $\beta^{\rm aerosol}= \sigma^{\rm
@@
 \end{align}
-The phase function is often approximated by a parametric expression,
-as the Henyey-Greenstein~\cite{Cornette1995} function,
+% Let $\mu\equiv \cos\Phi^{\rm scatter}$.
+The phase function is often approximated by a parametric
+expression. Specifically, the Henyey-Greenstein~\cite{Cornette1995}
+function is governed by an {\em anisotropy parameter} $g$:
 \begin{align}
   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
-  g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
+  g^2)(1+\cos^2\Phi^{\rm scatter}) (2+g^2)^{-1}(1 + g^2 -
+  2g\cos\Phi^{\rm scatter})^{-1.5}.
   \label{eq:aerosol_scatter}
 \end{align}
-where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos
-\Phi^{\rm scatter}$.
+% \begin{align}
+%   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
+%   g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}.
+%   \label{eq:aerosol_scatter}
+% \end{align}
 
@@
 \begin{align}
-  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
+  P^{\rm air}(\Phi^{\rm scatter}) &\approx
+  \sfrac{3}{16\pi}(1+\cos^2\Phi^{\rm scatter})
   \label{eq:rayleighP}
@@
 
-\noindent {\bf Inverse Transform Sampling}: A tool for RT is
+\noindent {\bf Inverse transform sampling}: A tool for RT is
 Monte-Carlo (MC) simulation. MC considers scattering and extinction as
 random phenomena, that are sampled from their probability
-distributions.  Sample random numbers that comply with any known
+distributions.  Sample random numbers that comply with a specified
 probability density function can be generated using inverse transform
@@
 distinct fixed location, capturing raw image
-$i_c({\bm{\Theta}})$. This paper takes a first step of formulating a
-principle for estimating the 3D atmospheric aerosols distribution,
-using such data. To study the feasibility and cross validate it, we
-perform RT using two different forward models. A forward model takes
-as input a 3D aerosol distribution, and outputs images as if captured
-at various viewpoints.  One model uses MC
-(\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally
-expresses multiple-scattering. Hence, MC rigorously simulates
-realistic scenes of arbitrary complexity.
+$i_c({\bm{\Theta}})$. This paper reports a first step: formulating a
+principle for estimating 3D atmospheric aerosols distributions, using
+such data. To theoretically study the feasibility and cross validate
+it, we perform RT using two different forward models. A forward model
+takes as input a 3D aerosol distribution, and outputs images as if
+captured at various viewpoints.  One model uses MC
+(Sec.~\ref{sec:monte-carlo-simul}): it is stochastic, slow but
+naturally expresses multiple-scattering. Hence, MC rigorously
+simulates realistic scenes of arbitrary complexity.
 % MC simulations can be made arbitrarily accurate by increasing the
@@
 The second model uses the single-scattering approximation
-(\cref{sec:single-scatt-model}). It is less accurate than MC, but
+(Sec.~\ref{sec:single-scatt-model}). It is less accurate than MC, but
 solves RT in an analytic, closed form. This form enables simple
 inversion of the model, to estimate the underlying aerosol
-distribution (\cref{sec:inverse-problem}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Single-Scattering Forward Model}
+distribution (Sec.~\ref{sec:inverse-problem}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Single-scattering forward model}
 \label{sec:single-scatt-model}
 
-The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
-elements (voxels), indexed by $k$, $m$ or $q$. \cref{fig:distributions}.
+As illustrated in Figs.~\ref{fig:groundgrid},\ref{fig:distributions},
+The sky is discretized into a grid of $N_{\rm voxels}$ volume elements
+(voxels), indexed by $k$, $m$ or $q$.
 \begin{figure}
@@
   \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
-  \caption{\small [a] and [b] Simulated 3D aerosol distribution
-    composed of a {\em Haze Front} and {\em Haze Front}
-    respectively. The density units are $10^{6}~{\rm particles}/{\rm
-      m}^3.$}
+  \caption{\small Simulated 3D aerosol distributions: {\em Haze blobs}
+    [a] and {\em Haze Front}.  Here, an aerosol density unit is
+    $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
+    area of $50\times 50{\rm km}^2$, extending from the ground up to
+    altitude of 10km. The domain is divided into a rectilinear grid
+    having $N_{\rm voxels}$ voxels.}
   \label{fig:distributions}
@@
 depth along the light path to and from voxel $k$, as analyzed in
-\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
-coefficient at voxel $k$, described in \cref{sec:scattering}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Optical Depth}
+Sec.~\ref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
+coefficient at voxel $k$, described in Sec.~\ref{sec:scattering}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Optical depth}
 \label{sec:optical-depth}
 
-A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
-angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
-the center of voxel $k$ by $[{\rm SR},k]$ (See
-\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection
-line segment has geometric length $l_{\rm SR}(q)$, which depends on
-$\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a $N_{\rm voxels}\times
-N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$,
-whose element $(k,q)$ represents $l_{\rm SR}(q)$:
+Denote a SR line segment between the TOA and the center of voxel $k$
+by $[{\rm SR},k]$ (See \cref{fig:groundgrid}). This SR intersects
+voxel $q$. The intersection line segment has geometric length $l_{\rm
+  SR}(q|\Delta z,\Phi^{\rm SR})$, where $\Delta z$ is a voxel's
+vertical geometric thickness, and $\Phi^{\rm SR}$ is the Sun
+angle. Define a \mbox{$N_{\rm voxels}\times N_{\rm voxels}$} matrix
+$\OpDistance^{\mathrm{Sun \rightarrow voxel}}$, whose element $(k,q)$
+represents $l_{\rm SR}(q)$:
 \begin{equation}
@@
 \end{equation}
-The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
+Matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
 Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
@@
 Suppose this LOS intersects voxel $q$. The geometric length of this
-intersection line segment is $l_{\rm LOS_c}(m)$ which depends on
-$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $m$.  Analogously to
-\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
-sparse matrix whose element $(k,m)$ is
+intersection line segment is $l_{\rm LOS_c}(m|\Delta z,\Phi^{\rm
+  LOS}_c)$.  As in~(\ref{eq:Dsv}), define a $N_{\rm voxels}\times
+N_{\rm voxels}$ sparse matrix whose element $(k,m)$ is
 \begin{equation}
@@
 
-Any voxel generally contains both air molecules and aerosols.  We
-focus on situations where there is only a single type of aerosol over
-a scene. Hence, the three-element vector $[{\sigma}^{\rm
-  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
-the density distribution ${\DistUnknown}$ is variable. As a numerical
-approximation, assume that within any voxel, the molecular parameters
-$\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density
-$n(k)$ are constants, e.g., corresponding to the value at each voxel
-center.  Following \cref{eq:tau}, the optical depth between the TOA
-and voxel $k$ is
-\begin{equation}
-  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
+We focus on situations where, in addition to air molecules, there is a
+single type of aerosol over a scene. Hence, the three-element vector
+$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
+the scene, but the density distribution ${\DistUnknown}$ is
+variable. As a numerical approximation, assume that within any voxel,
+the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
+and the aerosol density $n(k)$ are constants, e.g., corresponding to
+the value at each voxel center.  Following \cref{eq:tau}, the optical
+depth between the TOA and voxel $k$ is
+% \begin{equation}
+%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
+%  \label{eq:lSRn}
+%\end{equation}
+\begin{equation}
+  \tau_{\rm SR}(k)=
+  \sum_{q \in[{\rm SR},k]}
+  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] l_{\rm SR}(q)
+  =\tau_{\rm SR}^{\rm air}(k)+  \sigma^{\rm aerosol}\sum_{q \in[{\rm SR},k]} l_{\rm SR}(q) n(q)
+  ,
   \label{eq:lSRn}
 \end{equation}
-We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
-  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
-where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
-vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
-respectively. Similarly, the optical depth along a LOS to voxel $k$ is
-expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
-\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
-$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
-$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
-can form a single path from the TOA to camera $c$, yielding
+where $\tau_{\rm SR}^{\rm air}(k)=\sum_{q \in[{\rm SR},k]}\beta^{\rm
+  air}(q)l_{\rm SR}(q)$.  Let $\vect{\tau}_{\rm SR}$ and
+$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
+representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
+  air}(k)$, respectively. Then, we can write \cref{eq:lSRn} using
+matrix notation: \mbox{$\vect{\tau}_{\rm SR}=\vect{\tau}_{\rm SR}^{\rm
+    air} + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow
+      voxel}} {\DistUnknown}$}.
+
+A similar analysis yields the optical depth along a LOS to voxel $k$,
+$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
+\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
+  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
+  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
+form a single path from the TOA to camera $c$, yielding
 \begin{equation}
@@
 \end{equation}
-
-We discern between air molecules and other aerosols and therefore
-write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
-  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
-all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
-$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
-angle. Given \cref{eq:tau}, the total optical depths corresponding to
-LOSs (of camera $c$) and SRs that cross all voxels comprise the vector
+Hence, in matrix notation, \cref{eq:tau} yields the total optical
+depths corresponding to LOSs (of camera $c$) and SRs that cross all
+voxels:
 \begin{equation}
@@
 
-\subsection{Image Capture}
+\subsection{Image capture}
 \label{sec:captured-image}
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal}) the radiant power contributed by
-the voxel is
+(Eqs.~\ref{eq:beer-lambert},\ref{eq:tautotal}) the radiant power
+contributed by the voxel is
 \begin{equation}
@@
 where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
-  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
-image is thus
+  pix}$ long.  Combining
+Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the captured image
+is thus
 \begin{align}
@@
 
-\section{Simulations}
+\section{Examples}
 \label{sec:simul}
@@
 \end{figure}
-To test the models, we simulated several atmospheric scenarios. Here
-are the details:
-\\
-
-\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
+To demonstrate the model, we simulated some scenarios, whose details are as follows.\\
+\noindent{\bf Geometry}: The sun is at zenith angle $\Phi^{\rm
   SR}=45^o$.  Its $L^{\rm TOA}$ is obtained
@@
   B}=255:236:224$.
-\\
-
-\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
-  50}{\km} extending from the ground up to altitude of
-\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
-different grid sizes from \num{10 x 10 x 20} grid, where each voxel
-has area of \SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}
-and up to \num{50 x 50 x 100} grid, where each voxel has area of \SI{1
-  x 1}{\km} and vertical thickness of \SI{100}{\metre}.
-\\
+
+The atmospheric domain is described in Fig.~\ref{fig:distributions}.
+We tested domain division to various grids, from $10\times10 \times
+20$ voxels, up to $50\times50 \times 1000$. The corresponding voxels
+had width, length and thickness of $5{\rm km}\times 5{\rm km} \times
+0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.  Each
+ground-based camera has nearly a hemispherical field of view, and low
+resolution, $128 \rm{px} \times 128 \rm{px}$, as cloudless (yet hazy)
+sky images are rather smooth.
 
@@
   B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
-all channels, $\varpi^{\rm aerosol}=1$.
-
-We simulated various spatial distributions, as a product of two
-functions. The first function is an exponential decay~\cite{Levi1980}
-with altitude $h(k)$ of voxel $k$,
-\begin{align}
-  f_1[h(k)] = \sfrac{1} {n^{sea level}}
-  \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
-\end{align}
-where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
-of reduced atmospheric density with height.
-
-The second function, $f_2$, expresses a clustered nature of aerosol
-``clouds''. We define blobs in the form of 3D ellipsoids. There may be
-multiple ellipsoids suspended.  Then
+all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
+distributions using a product of two functions. To express the general
+trend of reduced density with altitude $h(k)$ of voxel $k$, we follow
+Ref.~\cite{Levi1980} and set the first function as
+\begin{align}
+  f_1[h(k)] = \sfrac{1} {n^{\rm sealevel}}
+  \exp[-h(k)/H^\mathrm{aerosol}],
+\end{align}
+where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
+of aerosol distributions (as clouds), we define blobs in the form of
+3D ellipsoids. There may be multiple ellipsoids suspended.  Then
 \begin{equation}
@@
 \end{equation}
-The true aerosol distribution is then
-\begin{equation}
-  \label{eq:ntrue}
-  {\bm n}^{\rm true}={\bm f}_1\odot {\bm f}_2  .
-  \hspace{-0.05cm}
-\end{equation}
-As an example, we created a {\em Haze Blobs} scene using two ellipsoid
-blobs (\cref{fig:distributions}a): the first is centered at altitude
-\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
-thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
-altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
-vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
-are much larger than the vertical ones. This is consistent with scales
-of atmospheric aerosol distributions.
-\\
-
-\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
-field of view, capturing the entire sky from its viewpoint. We used
-different numbers of cameras ranging from 12 viewpoints to 100, on a
-grid.  The resolution of each camera is low, expressing the fact that
-cloudless (yet hazy) sky images are rather smooth.  For example,
-\cref{fig:simulation-results1}a and \cref{fig:simulation-results1}b
-show example photographs of the {\em Haze Blobs} scene as simulated by
-the Single Scattering model and MC model, respectively, from the same
-viewing point.  \cref{fig:simulation-results1}c compares a cross
-section of the photographs along the horizontal Axis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Multiple-Scattering Forward Model by Monte Carlo}
+The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
+  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
+smoothing, obtained by narrow 3D Gaussian filtering. It expresses
+non-sharp boundaries of typical distributions. The {\em Haze Blobs}
+scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
+wide, 2.8km thick and centered at altitude 3.3km; the other is 24km
+wide, 2.1km thick and centered at altitude 6.6km. Horizontal widths
+are much larger than the vertical thickness, in consistency with
+atmospheric scales. Fig.~\ref{fig:simulation-results1}a shows one
+photographs of the {\em Haze Blobs} scene, as simulated by
+Eq.~(\ref{eq:bigIA}).
+
+The {\em Haze Front} scene in \cref{fig:distributions}b uses an
+ellipsoid degenerated to an elliptic cylinder that partly enters the
+analyzed volume. It is 32km long (only part of which enters the
+volume), 4km thick and centered at altitude 5km. The front stretches
+across the domain width.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Multiple-scattering forward model by Monte Carlo}
 \label{sec:monte-carlo-simul}
@@
 back-traced to the Sun are counted, per pixel. In this model, RT takes
-the following steps, per launched photon (\cref{fig:mcgrid}):
+the following steps, per pixel (\cref{fig:mcgrid}):
 \begin{figure}
@@
 
-\noindent ({\tt i}) Launch a photon from camera $c$ to direction
-${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.
+\noindent ({\tt i}) Launch a photon-packet from camera $c$ to
+direction ${\bm{\Theta}}$. This is the initial {\em ray}, denoted
+${\cal R}_0$. The packet has intensity $I_0$.
 
@@
 \noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which
-the photon propagates. To do this, Eq.~(\ref{eq:taurand}) yields
-$\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a
-non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek
+the photon-packet propagates. To do this, Eq.~(\ref{eq:taurand})
+yields $\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to
+a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek
 $l^{\rm random}$ s.t.
@@
   X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
-photon is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
-  SR}$ , the photon is counted as contributing to the image pixel.
+packet is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
+  SR}$ , the packet is counted as contributing to the image pixel.
 
 \noindent ({\tt iii}) The type of particle (air molecule or aerosol)
-the photon interacts with at ${\bf X}_{i}$ is determined randomly
-according to their relative densities at the voxel containing ${\bf
-  X}_{i}$.
-
-\noindent ({\tt iv}) If it is an aerosol, the photon is terminated
-with probability $1-\varpi^{\rm aerosol}$.
-
-\noindent ({\tt v}) The photon is scattered to a new direction,
+the photon-packet interacts with at ${\bf X}_{i}$ is determined
+randomly according to their relative densities at the voxel containing
+${\bf X}_{i}$.
+
+\noindent ({\tt iv}) If it is an aerosol, the photon-packet intensity
+is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
+lower than a threshold, the packet is stochastically terminated,
+following~\cite{Iwabuchi2006}.
+
+\noindent ({\tt v}) The photon-packet is scattered to a new direction,
 determined by inverse transform sampling, according to the phase
-function of the particle: \cref{eq:aerosol_scatter}
-or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal
+function of the particle (Eqs.~\ref{eq:aerosol_scatter}
+or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
@@
 
-The quality of the simulations is proportional to the number of
-photons. To create the \cref{fig:simulation-results1}b, \num{10000}
-photons were emitted from each pixel.
+The quality of MC increases with the number of photons launched.
+Fig.~\ref{fig:simulation-results1}b shows a photographs of the {\em
+  Haze Blobs} scene, derived by the MC process, using \num{10000}
+photons per pixel, from the same viewpoint as
+Fig.~\ref{fig:simulation-results1}a.  A comparison of a sample
+horizontal cross section is shown in \cref{fig:simulation-results1}c.
 
@@
 
-In this paper, we assume that the type of the aerosol above an area is
-known~\cite{Martonchik2009}. Hence, we focus on estimating the density
-distribution $\DistUnknown$.  At hand, we have $N_{\rm views}$
-measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
-    views}}$. The recovery task is phrased as optimization of an
-objective function that fits the image-formation model to the measured
-photographs, under constraints. Let $\DistSet$ be the set of all
-legitimate distributions, according to constraints.  Particularly,
-$\DistUnknown$ is non-negative, and its spatial support is bounded
-between the ground and the TOA. The optimization problem is
+When the type of aerosol above an area is known~\cite{Martonchik2009},
+estimation of the density distribution $\DistUnknown$ is needed. The
+data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
+  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
+optimization of a cost function that fits the image-formation model to
+the data. Let $\DistSet$ be the set of all distributions complying
+with some constraints.  Particularly, $\DistUnknown$ is non-negative,
+and its spatial support is bounded between the ground and the TOA. The
+optimization problem is
 \begin{equation}
@@
     \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
-  \right\|^2_2
-  + \eta \Psi({\bm n})
-\end{equation}
-Here $\MaskSun$ masks the area around the sun, which in real-world
-photographs is indeed blocked. %and the horizon.
-% These regions are prone to dominant multiple scattering.
-In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
-that expresses some prior knowledge on the distribution, while $\eta$
-is a regularization weight.
+  \right\|^2_2  + \eta \Psi({\bm n}).
+\end{equation}
+Here $\MaskSun$ masks the area around the sun, as in real-world images
+it is indeed blocked.  In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$
+is a regularization term that expresses some prior knowledge on the
+distribution, while $\eta$ is a regularization weight.
 
@@
 We solve~\cref{eq:minobjectiveA} using standard optimization tools.
-The gradient of $F$ with respect to ${\bm n}$ is
-\begin{align}
-  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
+The gradient of $E$ with respect to ${\bm n}$ is
+\begin{align}
+  \Grad{{\bm n}} E = -2\sum_{c=1}^{N_{\rm views}}
   \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
@@
 \end{align}
-Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the
-Jacobian of \cref{eq:bigIA} in close-form,
+Based on Eqs.~(\ref{eq:partial4},\ref{eq:partial1},\ref{eq:partial3}),
+we derive the Jacobian of \cref{eq:bigIA} in close-form,
 \begin{align}
@@
 
+Sec.~\ref{sec:simul} describes simulates scenes at various grid
+resolution.  Depending directly on the area grid finesse, $N_{\rm
+  views}$ varied from 12 to 100.
 \begin{figure}
@@
 \end{figure}
-We applied the reconstruction algorithm \cref{sec:inverse-problem} to
-the images simulated in \cref{sec:simul}. We used the L-BFGS-B
-algorithm~\cite{BFGS} on a computer cluster. Each core was dedicated
-to rendering a modeled image. The algorithm was initialized by ${\bm
-  n}=0$. Satisfactory convergence occurred in several thousand
-iterations, taking a couple of hours to complete in total.
-
-An iso-surface visualization of the original {\em Haze Blobs}
-distribution is shown in
-\cref{fig:distributions}a. \cref{fig:results}a show the reconstructed
-scene based on images simulated by the Single Scattering
-model. \cref{fig:results}c visualizes the reconstructed scene based on
-images simulated by the MC model. The distributions appear consistent,
-though there are errors that stem from the random noise in the
-images. To quantify the results, we use a relative error measure based
-on the $\ell_1$ norm: $\epsilon=\sfrac{\| \hat{\bm n} - {\bm n}^{\rm
-    true} \|_1} {\| {\bm n}^{\rm true} \|_1}$.  It is equivalent to
-the aerosol mass that is over and under-estimated in all voxels,
-relative to the total aerosol mass in the scene.  In the {\em Haze
-  Blobs} case, $\epsilon=0.14$ and $\epsilon=0.65$ for the
-reconstructions based on the Single-Scattering images and MC images
-respectively. We used the distribution reconstructed based on the MC
-images to create images using the Single-Scattering
-model. \cref{fig:simulation-results1}c shows a cross of such an image
-compared to the original MC image.
-
-We created a {\em Haze Front} scene. \cref{fig:distributions}b shows
-an iso-surface visualization of this distribution.
-Here an ellipsoid degenerated to an elliptic cylinder that partly
-enters the analyzed volume. It is centered at altitude \SI{5}{\km},
-has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
-part of which enters the volume). The haze front stretches across the
-width of the volume.  \cref{fig:results}b and \cref{fig:results}d
-visualizes the recovered 3D distribution of this scene. For the {\em
-  Haze Front}, $\epsilon=0.20$ and $\epsilon=0.65$ for the
-reconstructions based on the Single-Scattering images and MC images
-respectively.
+We applied the reconstruction algorithm to images created as described
+in Secs.~\ref{sec:simul} and~\ref{sec:monte-carlo-simul}. We used the
+L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
+dedicated to rendering a modeled image. The algorithm was initialized
+by ${\bm n}=0$.  Satisfactory convergence occurred in several thousand
+iterations. Depending on the resolution it took between minutes to a
+couple of hours to complete, in total.
+
+Fig.~\ref{fig:results} shows estimation results, corresponding to the
+original distributions of Fig.~\ref{fig:distributions}. In
+Figs.~\ref{fig:results}a,b, the single-scattering model was used both
+in rendering of the raw images, and in the estimation algorithm. In
+Figs.~\ref{fig:results}c,d, the MC model (multiple scattering)
+rendered the raw images, over which the estimation algorithm
+ran. Overall, the distributions, the density order of magnitude and
+values are consistent.
+% Using the recovered distribution shown in Figs.~\ref{fig:results}c
+% (originating from MC), we ran the single scattering model to create
+% images. \cref{fig:simulation-results1}c shows a cross of such an
+% image compared to the original MC image.
+Errors in Figs.~\ref{fig:results}a,b stem from random noise, which had
+been induced in the raw images. Errors are larger when MC is used to
+render the images, since high-order scattering is not accounted for in
+the algorithm of Sec.~\ref{sec:inverse-problem}. The total estimation
+error can be quantifies based on the $\ell_1$ norm: $\epsilon=\|
+\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
+It is equivalent to the aerosol mass that is over and under-estimated
+in all voxels, relative to the total aerosol mass in the scene.  In
+Figs.~\ref{fig:results}a,b, respectively $\epsilon=0.14$ and
+$\epsilon=0.20$.  In Figs.~\ref{fig:results}c,d, both cases have
+$\epsilon=0.65$.
 

### 2013-08-04 article.tex
bookmark

@@
 \usepackage[capitalise]{cleveref}
+\crefname{section}{Sec.}{Sec.}
 \makeatletter
@@
 \author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1}
-  Vadim~Holodovsky\authnote{1} and Michael~J.~Garay\authnote{2}}
+  Vadim~Holodovsky\authnote{1}, Michael~J.~Garay\authnote{2} and Anthony~B.~Davis\authnote{2}}
 
@@
   \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
-  \caption{\small Simulated 3D aerosol distributions: {\em Haze blobs}
-    [a] and {\em Haze Front}.  Here, an aerosol density unit is
-    $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
+  \caption{\small Simulated 3D aerosol distributions: [a] {\em Haze
+      blobs} and [b] {\em Haze Front}.  Here, an aerosol density unit
+    is $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
     area of $50\times 50{\rm km}^2$, extending from the ground up to
@@
   \centering
-  \yoavcomment{\includegraphics[width=\linewidth]{images/ref_images.pdf}}
-  \caption{\small [a] Photograph of a sky that includes {\em Haze
-      Blobs} rendered using the single-scattering model.  A yellow dot
-    marks the Sun location. Dashed white circles mark elevation
-    angles.  [b] Photograph of the same sky and view point rendered
-    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
-    section along the X-Axis of the MC simulation, Single-Scattering
-    simulation and a Single-Scattering image created from the
-    reconstructed distribution (\cref{sec:optimization-results}).}
+  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
+  \caption{\small Different view-points of a sky that includes {\em
+      Haze Blobs}. Images rendered using the single-scattering model.
+    A yellow dot marks the Sun location. Dashed white circles mark
+    zenith angles.}
   \label{fig:simulation-results1}
@@
   \centering
-  \yoavcomment{\includegraphics[width=0.5\linewidth]{images/mcgrid.pdf}}
-  \caption{\small Monte Carlo simulation of multiple-scattering
-    radiative transfer.}
+  \yoavcomment{\includegraphics[width=\linewidth]{images/mcgrid.pdf}}
+  \caption{\small [a] Multiple-scattering forward model by Monte
+    Carlo. [b] Photograph of the same sky and view point as in
+    \cref{fig:simulation-results1}, rendered using a MC model.
+    [c] Cross section along the $X$-Axis of the MC simulation,
+    Single-Scattering simulation and a Single-Scattering image created
+    from the reconstructed distribution
+    (\cref{sec:optimization-results}).}
   \label{fig:mcgrid}
@@
   \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
-  \caption{\small [a] and [b] Reconstruction of the scenes shown in
-    \cref{fig:distributions} when using Single-Scattering simulated
-    images as input.  [c] and [d] Reconstruction of the same scenes
-    when using MC simulated images as input.  Color represents aerosol
-    density. The density units are $10^{6}~{\rm particles}/{\rm
-      m}^3.$}
+  \caption{\small Reconstructions of the scenes shown in
+    \cref{fig:distributions}. Color represents aerosol density. The
+    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
+    Single-Scattering simulated images are used as input to the
+    recovery.  In [c,d], MC simulated images are used as input for the
+    recovery.  }
   \label{fig:results}

### 2013-08-04 article.tex
modifications by yoav

--- 2013-08-04 article.tex
@@
 the value at each voxel center.  Following \cref{eq:tau}, the optical
-depth between the TOA and voxel $k$ is
+depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$ are
 % \begin{equation}
@@
 %\end{equation}
-\begin{equation}
-  \tau_{\rm SR}(k)=
-  \sum_{q \in[{\rm SR},k]}
-  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] l_{\rm SR}(q)
-  =\tau_{\rm SR}^{\rm air}(k)+  \sigma^{\rm aerosol}\sum_{q \in[{\rm SR},k]} l_{\rm SR}(q) n(q)
-  ,
+\begin{align}
+  \tau_{\rm SR}(k)&=
+  \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
+  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \\
+  \tau_{{\rm LOS}_c}(k)&=
+  \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
+  [\beta^{\rm air}(m)+\sigma^{\rm aerosol} n(m)].
   \label{eq:lSRn}
-\end{equation}
-where $\tau_{\rm SR}^{\rm air}(k)=\sum_{q \in[{\rm SR},k]}\beta^{\rm
-  air}(q)l_{\rm SR}(q)$.  Let $\vect{\tau}_{\rm SR}$ and
-$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
-representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
-  air}(k)$, respectively. Then, we can write \cref{eq:lSRn} using
-matrix notation: \mbox{$\vect{\tau}_{\rm SR}=\vect{\tau}_{\rm SR}^{\rm
-    air} + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow
-      voxel}} {\DistUnknown}$}.
-
-A similar analysis yields the optical depth along a LOS to voxel $k$,
-$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
-\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
-  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
-  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
-form a single path from the TOA to camera $c$, yielding
-\begin{equation}
-  {\bm D}_c=
-  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
-  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
-  \quad\text{ and }\quad
-  \vect{\tau}_c=
-  \vect{\tau}_{\rm SR}+
-  \vect{\tau}_{{\rm LOS}_c}
-  \;\;.
-  \label{eq:D_tau_total}
-\end{equation}
+\end{align}
+Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be 
+column stack vector
+representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm air}(k)$, respectively.
+ Then, we can write \cref{eq:lSRn} using
+matrix notation: 
+   \mbox{$\vect{\tau}_{\rm SR}=
+   \OpDistance^{\mathrm{Sun \rightarrow voxel}}\vect{\beta}^{\rm air} 
+   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}} {\DistUnknown}$},\
+and
+    \mbox{$\vect{\tau}_{{\rm LOS}_c}=
+   \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air}
+   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}} {\DistUnknown}$}.
+The SR and LOS paths joining at each voxel 
+form a single path from the TOA to camera $c$.  
 Hence, in matrix notation, \cref{eq:tau} yields the total optical
@@
   + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
-  \;\;.
+  \;\;,
   \label{eq:tautotal}
 \end{equation}
+where   ${\bm D}_c=
+  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
+  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c$
+and $\vect{\tau}_c^{\rm air}= {\bm D}_c \vect{\beta}^{\rm air}$.
+
+%
+%
+%and
+%$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
+%representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
+%  air}(k)$, respectively.
+%
+%A similar analysis yields the optical depth along a LOS to voxel $k$,
+%$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
+%\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
+%  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
+%  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
+%form a single path from the TOA to camera $c$, yielding
+%\begin{equation}
+%  {\bm D}_c=
+%  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
+%  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
+%  \quad\text{ and }\quad
+%  \vect{\tau}_c=
+%  \vect{\tau}_{\rm SR}+
+%  \vect{\tau}_{{\rm LOS}_c}
+%  \;\;.
+%  \label{eq:D_tau_total}
+%\end{equation}
+%Hence, in matrix notation, \cref{eq:tau} yields the total optical
+%depths corresponding to LOSs (of camera $c$) and SRs that cross all
+%voxels:
+%\begin{equation}
+%  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
+%  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
+%  \;\;.
+%  \label{eq:tautotal}
+%\end{equation}
 
@@
 
-\section{Conclusions}
+\section{Discussion}
 \label{sec:conclusions}
 
-We describe a new way to sense the 3D atmosphere. We show feasibility
-of departing from common 1D aerosol distribution models, in favor of
-detailed 3D analysis.  The paper describes both a novel data
-acquisition system concept for this recovery task, and a dedicated
-algorithm for reconstructing aerosol distributions.
-
-Even without regularization, the reconstruction algorithm handles
-arbitrary density distributions. Using more prior knowledge,
-e.g. spatial smoothness will improve the recovery.  The algorithm uses
-a single scattering model. This approximation is valid when the
-optical depth is small, which is common. To handle dense atmospheric
-conditions (smoke, clouds), multi-scattering must be incorporated.
-
-The goal, of coarse, is to deploy such a system on a very large
-scale. However, it must be first ensured that camera units are both
-cost effective and field-robust, and that their positioning density is
-proper. This will require a long-term engineering effort. Camera
-specifications should be set to optimally recover a wide range of
+We describe a way to sense the 3D atmosphere. It can help 
+remote sensing departing from common 1D aerosol distribution models, in favor of detailed 3D RT analysis.  The paper describes both a novel data
+acquisition system concept for this recovery task (ground-based camera network), and a dedicated algorithm for reconstructing aerosol distributions.
+Using more prior knowledge on the nature of distributions will improve the recovery.
+The estimation algorithm uses a single scattering model.
+This approximation is valid when the
+optical depth is small.
+However, as the MC simulation show, it is important to generalize this algorithm so that it explicitly incorporates high-order scattering in the scene, including the ground.
+This will certainly be needed for dense distributions as clouds.
+
+To deploy such a system on a very large scale will require a long-term engineering effort. Camera specifications should be set to optimally recover a wide range of
 aerosol distributions. This requires a major theoretic and numerical
-research and development phase.  The new sensing modality and object
-of interest offer a new domain for computational photography
-problems. For example, how can compressed sensing principles be
-employed here? How can priors be used to make data acquisition more
-efficient? How can such a system be calibrated over time? Many such
-questions and solutions would rise.
+research.
 
@@
 
-We thank Anthony~B. Davis and David~J. Diner for useful
+We thank David~J. Diner for useful
 discussions. Yoav Schechner is a Landau Fellow - supported by the Taub

### 2013-08-04 article.tex
bookmark

@@
 the value at each voxel center.  Following \cref{eq:tau}, the optical
-depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$ are
+depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$
+are
 % \begin{equation}
@@
 \begin{align}
-  \tau_{\rm SR}(k)&=
-  \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
+  \tau_{\rm SR}(k)&= \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
   [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \\
-  \tau_{{\rm LOS}_c}(k)&=
-  \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
+  \tau_{{\rm LOS}_c}(k)&= \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
   [\beta^{\rm air}(m)+\sigma^{\rm aerosol} n(m)].
@@
 \end{align}
-Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be 
-column stack vector
-representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm air}(k)$, respectively.
- Then, we can write \cref{eq:lSRn} using
-matrix notation: 
-   \mbox{$\vect{\tau}_{\rm SR}=
-   \OpDistance^{\mathrm{Sun \rightarrow voxel}}\vect{\beta}^{\rm air} 
-   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}} {\DistUnknown}$},\
-and
-    \mbox{$\vect{\tau}_{{\rm LOS}_c}=
-   \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air}
-   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}} {\DistUnknown}$}.
-The SR and LOS paths joining at each voxel 
-form a single path from the TOA to camera $c$.  
-Hence, in matrix notation, \cref{eq:tau} yields the total optical
-depths corresponding to LOSs (of camera $c$) and SRs that cross all
-voxels:
+Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be column
+stack vector representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm
+  air}(k)$, respectively.  Then, we can write \cref{eq:lSRn} using
+matrix notation: \mbox{$\vect{\tau}_{\rm SR}= \OpDistance^{\mathrm{Sun
+      \rightarrow voxel}}\vect{\beta}^{\rm air} + \sigma^{\rm
+    aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}}
+  {\DistUnknown}$},\ and \mbox{$\vect{\tau}_{{\rm LOS}_c}=
+  \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air} +
+  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
+  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel form a
+single path from the TOA to camera $c$.  Hence, in matrix notation,
+\cref{eq:tau} yields the total optical depths corresponding to LOSs
+(of camera $c$) and SRs that cross all voxels:
 \begin{equation}
@@
 \end{equation}
-where   ${\bm D}_c=
-  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
-  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c$
-and $\vect{\tau}_c^{\rm air}= {\bm D}_c \vect{\beta}^{\rm air}$.
-
-%
-%
-%and
-%$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
-%representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
+where ${\bm D}_c= {\bm D}^{\mathrm{Sun \rightarrow voxel}}+ {\bm
+  D}^{\mathrm{voxel \rightarrow cam}}_c$ and $\vect{\tau}_c^{\rm air}=
+{\bm D}_c \vect{\beta}^{\rm air}$.
+
+%
+%
+% and $\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
+% representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
 % air}(k)$, respectively.
 %
-%A similar analysis yields the optical depth along a LOS to voxel $k$,
-%$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
-%\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
-%  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
+% A similar analysis yields the optical depth along a LOS to voxel
+% $k$, $\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
+% \mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air}
+% + \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
 % {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
-%form a single path from the TOA to camera $c$, yielding
-%\begin{equation}
+% form a single path from the TOA to camera $c$, yielding
+% \begin{equation}
 %  {\bm D}_c=
@@
 %Hence, in matrix notation, \cref{eq:tau} yields the total optical
-%depths corresponding to LOSs (of camera $c$) and SRs that cross all
-%voxels:
-%\begin{equation}
+% depths corresponding to LOSs (of camera $c$) and SRs that cross all
+% voxels:
+% \begin{equation}
 %  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
@@
 
-We describe a way to sense the 3D atmosphere. It can help 
-remote sensing departing from common 1D aerosol distribution models, in favor of detailed 3D RT analysis.  The paper describes both a novel data
-acquisition system concept for this recovery task (ground-based camera network), and a dedicated algorithm for reconstructing aerosol distributions.
-Using more prior knowledge on the nature of distributions will improve the recovery.
-The estimation algorithm uses a single scattering model.
-This approximation is valid when the
-optical depth is small.
-However, as the MC simulation show, it is important to generalize this algorithm so that it explicitly incorporates high-order scattering in the scene, including the ground.
-This will certainly be needed for dense distributions as clouds.
-
-To deploy such a system on a very large scale will require a long-term engineering effort. Camera specifications should be set to optimally recover a wide range of
-aerosol distributions. This requires a major theoretic and numerical
-research.
+We describe a way to sense the 3D atmosphere. It can help remote
+sensing departing from common 1D aerosol distribution models, in favor
+of detailed 3D RT analysis.  The paper describes both a novel data
+acquisition system concept for this recovery task (ground-based camera
+network), and a dedicated algorithm for reconstructing aerosol
+distributions. Using more prior knowledge on the nature of
+distributions will improve the recovery.  The estimation algorithm
+uses a single scattering model. This approximation is valid when the
+optical depth is small. However, as the MC simulation show, it is
+important to generalize this algorithm so that it explicitly
+incorporates high-order scattering in the scene, including the
+ground. This will certainly be needed for dense distributions as
+clouds.
+
+To deploy such a system on a very large scale will require a long-term
+engineering effort. Camera specifications should be set to optimally
+recover a wide range of aerosol distributions. This requires a major
+theoretic and numerical research.
 
@@
 
-We thank David~J. Diner for useful
-discussions. Yoav Schechner is a Landau Fellow - supported by the Taub
-Foundation. This work was conducted in the Ollendorff Minerva
-Center. Minerva is funded through the BMBF.
+We thank David~J. Diner for useful discussions. Yoav Schechner is a
+Landau Fellow - supported by the Taub Foundation. This work was
+conducted in the Ollendorff Minerva Center. Minerva is funded through
+the BMBF. Part of this work was per- formed at the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with
+NASA.
 

### 2013-08-04 article.tex
bookmark

@@
 \usepackage[capitalise]{cleveref}
-\crefname{section}{Sec.}{Sec.}
+\crefname{section}{Sec.}{Secs.}
 \makeatletter
@@
 
+\bibitem{BBradiance}
+M.~Charity, \enquote{{Blackbody color datafile},}  (2001), \url{http://www.vendian.org/mncharity/dir3/blackbody/UnstableURLs/bbr\_color.html}.
+
+\bibitem{sun_composition}
+Wikipedia, \enquote{{Sunlight --- {W}ikipedia{,} The Free Encyclopedia},}
+  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.
+
+\bibitem{Martonchik2009}
+J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
+  properties over land using MISR observations},} in \emph{Satellite Aerosol
+  Remote Sensing over Land,} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
+  Berlin Heidelberg, 2009), pp. 267--293.
+
 \bibitem{Iwabuchi2006}
@@
   Physics of Earth and Space Environments (Springer, 2005).
-
-\bibitem{BBradiance}
-M.~Charity, \enquote{{Blackbody color datafile},}  (2001), \url{http://www.vendian.org/mncharity/dir3/blackbody/UnstableURLs/bbr\_color.html}.
-
-\bibitem{sun_composition}
-Wikipedia, \enquote{{Sunlight --- {W}ikipedia{,} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.
-
-\bibitem{Martonchik2009}
-J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
-  properties over land using MISR observations},} in \emph{{Satellite Aerosol
-  Remote Sensing over Land,}} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
-  Berlin Heidelberg, 2009), pp. 267--293.
 
@@
   \tau_{\rm SR}(k)&= \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
-  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \\
+  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \nonumber \\
   \tau_{{\rm LOS}_c}(k)&= \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
@@
   \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
-  \caption{\small Different view-points of a sky that includes {\em
-      Haze Blobs}. Images rendered using the single-scattering model.
+  \caption{\small Different viewpoints of a sky that includes {\em
+      Haze Blobs}. Images are rendered using the single-scattering model.
     A yellow dot marks the Sun location. Dashed white circles mark
@@
 are much larger than the vertical thickness, in consistency with
-atmospheric scales. Fig.~\ref{fig:simulation-results1}a shows one
+atmospheric scales. \cref{fig:simulation-results1} shows
 photographs of the {\em Haze Blobs} scene, as simulated by
@@
   \centering
-  \yoavcomment{\includegraphics[width=\linewidth]{images/mcgrid.pdf}}
+  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
   \caption{\small [a] Multiple-scattering forward model by Monte
     Carlo. [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}, rendered using a MC model.
-    [c] Cross section along the $X$-Axis of the MC simulation,
+    \cref{fig:simulation-results1}, rendered using a MC model.  [c]
+    Cross section along the $X$-Axis of the MC simulation,
     Single-Scattering simulation and a Single-Scattering image created
@@
 The quality of MC increases with the number of photons launched.
-Fig.~\ref{fig:simulation-results1}b shows a photographs of the {\em
-  Haze Blobs} scene, derived by the MC process, using \num{10000}
-photons per pixel, from the same viewpoint as
-Fig.~\ref{fig:simulation-results1}a.  A comparison of a sample
-horizontal cross section is shown in \cref{fig:simulation-results1}c.
+Fig.~\ref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
+scene, derived by the MC process, using \num{10000} photons per pixel,
+from the same viewpoint as Fig.~\ref{fig:simulation-results1}[left].  A
+comparison of a sample horizontal cross section is shown in
+\cref{fig:mcgrid}c.
 
@@
 
-Sec.~\ref{sec:simul} describes simulates scenes at various grid
-resolution.  Depending directly on the area grid finesse, $N_{\rm
+Sec.~\ref{sec:simul} describes simulated scenes at various grid
+resolutions.  Depending directly on the area grid finesse, $N_{\rm
   views}$ varied from 12 to 100.
@@
 the algorithm of Sec.~\ref{sec:inverse-problem}. The total estimation
-error can be quantifies based on the $\ell_1$ norm: $\epsilon=\|
+error can be quantifies by the aerosol mass that is over and under-estimated
+in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
+the total mass relative difference is
+$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
+The overall mass is recovered, but for 6.5\% loss. For local errors,
+ $\epsilon=\|
 \hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
-It is equivalent to the aerosol mass that is over and under-estimated
-in all voxels, relative to the total aerosol mass in the scene.  In
+  In
 Figs.~\ref{fig:results}a,b, respectively $\epsilon=0.14$ and
@@
 conducted in the Ollendorff Minerva Center. Minerva is funded through
-the BMBF. Part of this work was per- formed at the Jet Propulsion
+the BMBF. Part of this work was performed at the Jet Propulsion
 Laboratory, California Institute of Technology, under contract with

### 2013-08-04 article.tex
bookmark

@@
 %
-\usepackage[capitalise]{cleveref}
+\usepackage[capitalise,poorman]{cleveref}
 \crefname{section}{Sec.}{Secs.}
@@
 
+\bibitem{Pust2011}
+N.~J. Pust, A.~R. Dahlberg, M.~J. Thomas, and J.~a. Shaw, \enquote{{Comparison
+  of full-sky polarization and radiance observations to radiative transfer
+  simulations which employ AERONET products.}} Optics express \textbf{19},
+  18602--13 (2011).
+
 \bibitem{Mishchenko2007}
@@
   head},} Optics express \textbf{9}, 272--86 (2001).
+
+\bibitem{ihrke}
+I.~Ihrke, K.~N. Kutulakos, H.~P. Lensch, M.~Magnor, and W.~Heidrich,
+  \enquote{{State of the art in transparent and specular object
+  reconstruction},} in \enquote{EUROGRAPHICS 2008 STAR--STATE OF THE ART
+  REPORT,}  (2008).
 
@@
 this 3D distribution using measured and modeled light-fields
-(Fig.~\ref{fig:groundgrid}).
+(\cref{fig:groundgrid}).
 3D recovery of this medium has direct implications to various
@@
 
-In remote sensing~\cite{Mishchenko2007}, imaging through air is
+In remote sensing~\cite{Pust2011, Mishchenko2007}, imaging through air is
 associated with {\em atmospheric correction}, based on {\em aerosol
@@
 projection is similar to tomography in other scientific
-domains~\cite{Bluestone2001}. However, the situation here is
+domains~\cite{Bluestone2001,ihrke}. However, the situation here is
 distinct. Most tomography setups have a controlled and/or
@@
 the probability diminishes as $t\rightarrow 0$. Thus
-Eq.~(\ref{eq:beer-lambert}) can be viewed as a probability density
+(\cref{eq:beer-lambert}) can be viewed as a probability density
 function, whose CDF is
@@
 \end{equation}
-If the atmosphere is uniform, then from Eq.~(\ref{eq:tau}) the photon
+If the atmosphere is uniform, then from \cref{eq:tau} the photon
 reaches a random distance
@@
 is very high, their average number falls off in consistency with
-Eqs.~(\ref{eq:tau},\ref{eq:beer-lambert}).  Analogous transforms
+\cref{eq:tau,eq:beer-lambert}.  Analogous transforms
 generate scattering at random angles, according to the phase function.
@@
 captured at various viewpoints.  One model uses MC
-(Sec.~\ref{sec:monte-carlo-simul}): it is stochastic, slow but
+(\cref{sec:monte-carlo-simul}): it is stochastic, slow but
 naturally expresses multiple-scattering. Hence, MC rigorously
@@
 The second model uses the single-scattering approximation
-(Sec.~\ref{sec:single-scatt-model}). It is less accurate than MC, but
+(\cref{sec:single-scatt-model}). It is less accurate than MC, but
 solves RT in an analytic, closed form. This form enables simple
 inversion of the model, to estimate the underlying aerosol
-distribution (Sec.~\ref{sec:inverse-problem}).
+distribution (\cref{sec:inverse-problem}).
 
@@
 
-As illustrated in Figs.~\ref{fig:groundgrid},\ref{fig:distributions},
+As illustrated in \cref{fig:groundgrid,fig:distributions},
 The sky is discretized into a grid of $N_{\rm voxels}$ volume elements
@@
 depth along the light path to and from voxel $k$, as analyzed in
-Sec.~\ref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
-coefficient at voxel $k$, described in Sec.~\ref{sec:scattering}.
+\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
+coefficient at voxel $k$, described in \cref{sec:scattering}.
 
@@
 intersection line segment is $l_{\rm LOS_c}(m|\Delta z,\Phi^{\rm
-  LOS}_c)$.  As in~(\ref{eq:Dsv}), define a $N_{\rm voxels}\times
+  LOS}_c)$.  As in \cref{eq:Dsv}, define a $N_{\rm voxels}\times
 N_{\rm voxels}$ sparse matrix whose element $(k,m)$ is
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(Eqs.~\ref{eq:beer-lambert},\ref{eq:tautotal}) the radiant power
+(\cref{eq:beer-lambert,eq:tautotal}) the radiant power
 contributed by the voxel is
@@
   pix}$ long.  Combining
-Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the captured image
-is thus
+\cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
 \begin{align}
@@
 
-The atmospheric domain is described in Fig.~\ref{fig:distributions}.
+The atmospheric domain is described in \cref{fig:distributions}.
 We tested domain division to various grids, from $10\times10 \times
@@
 photographs of the {\em Haze Blobs} scene, as simulated by
-Eq.~(\ref{eq:bigIA}).
+\cref{eq:bigIA}.
 
@@
 The MC simulations rely on the same grid as
-Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
+\cref{sec:single-scatt-model}. We use backward MC: from a detector
 pixel, photons are `launched' via the camera lens; then the photons
@@
 \noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which
-the photon-packet propagates. To do this, Eq.~(\ref{eq:taurand})
-yields $\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to
-a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek
+the photon-packet propagates. To do this, \cref{eq:taurand}
+yields $\tau^{\rm random}$. Then, \cref{eq:lrand} generalizes to
+a non-uniform atmosphere: using \cref{eq:tau}, numerically seek
 $l^{\rm random}$ s.t.
@@
 The quality of MC increases with the number of photons launched.
-Fig.~\ref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
+\cref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as Fig.~\ref{fig:simulation-results1}[left].  A
+from the same viewpoint as \cref{fig:simulation-results1}[left].  A
 comparison of a sample horizontal cross section is shown in
@@
 Here $\MaskSun$ masks the area around the sun, as in real-world images
-it is indeed blocked.  In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$
+it is indeed blocked.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
 is a regularization term that expresses some prior knowledge on the
@@
   n}\|^2_2$. Regularization is not required when data is sufficient
-and reliable. As seen in Fig.~\ref{fig:groundgrid}, voxels at high
+and reliable. As seen in \cref{fig:groundgrid}, voxels at high
 altitude have good coverage by many cameras at multiple directions,
@@
 \end{align}
-Based on Eqs.~(\ref{eq:partial4},\ref{eq:partial1},\ref{eq:partial3}),
+Based on \cref{eq:partial4,eq:partial1,eq:partial3},
 we derive the Jacobian of \cref{eq:bigIA} in close-form,
@@
 
-Sec.~\ref{sec:simul} describes simulated scenes at various grid
+\cref{sec:simul} describes simulated scenes at various grid
 resolutions.  Depending directly on the area grid finesse, $N_{\rm
@@
 We applied the reconstruction algorithm to images created as described
-in Secs.~\ref{sec:simul} and~\ref{sec:monte-carlo-simul}. We used the
+in \cref{sec:simul,sec:monte-carlo-simul}. We used the
 L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
@@
 
-Fig.~\ref{fig:results} shows estimation results, corresponding to the
-original distributions of Fig.~\ref{fig:distributions}. In
-Figs.~\ref{fig:results}a,b, the single-scattering model was used both
+\cref{fig:results} shows estimation results, corresponding to the
+original distributions of \cref{fig:distributions}. In
+\cref{fig:results}a,b, the single-scattering model was used both
 in rendering of the raw images, and in the estimation algorithm. In
-Figs.~\ref{fig:results}c,d, the MC model (multiple scattering)
+\cref{fig:results}c,d, the MC model (multiple scattering)
 rendered the raw images, over which the estimation algorithm
@@
 values are consistent.
-% Using the recovered distribution shown in Figs.~\ref{fig:results}c
-% (originating from MC), we ran the single scattering model to create
-% images. \cref{fig:simulation-results1}c shows a cross of such an
-% image compared to the original MC image.
-Errors in Figs.~\ref{fig:results}a,b stem from random noise, which had
+Errors in \cref{fig:results}a,b stem from random noise, which had
 been induced in the raw images. Errors are larger when MC is used to
 render the images, since high-order scattering is not accounted for in
-the algorithm of Sec.~\ref{sec:inverse-problem}. The total estimation
+the algorithm of \cref{sec:inverse-problem}. The total estimation
 error can be quantifies by the aerosol mass that is over and under-estimated
@@
   In
-Figs.~\ref{fig:results}a,b, respectively $\epsilon=0.14$ and
-$\epsilon=0.20$.  In Figs.~\ref{fig:results}c,d, both cases have
+\cref{fig:results}a,b, respectively $\epsilon=0.14$ and
+$\epsilon=0.20$.  In \cref{fig:results}c,d, both cases have
 $\epsilon=0.65$.

### 2013-08-04 article.tex

@@
 \begin{abstract}
-  Aerosols effect climate, health and aviation.  Currently, their
+  Aerosols affect climate, health and aviation.  Currently, their
   retrieval assumes a plane-parallel atmosphere and solely vertical
@@
   \enquote{{State of the art in transparent and specular object
-  reconstruction},} in \enquote{EUROGRAPHICS 2008 STAR--STATE OF THE ART
+  reconstruction},} in \emph{EUROGRAPHICS 2008 STAR--STATE OF THE ART
   REPORT,}  (2008).
@@
 this 3D distribution using measured and modeled light-fields
-(\cref{fig:groundgrid}).
-3D recovery of this medium has direct implications to various
-scientific communities that either rely on remotely-sensed imagery,
-study the atmosphere, or overcome the medium to see beyond. These
-include meteorology, atmospheric sciences, volcanology, and
-climatology.  Aerosol retrieval is important for understanding climate
-evolution~\cite{Dayan2008,kalashnikova} and monitoring air
-quality. Mapping aerosol density is significant to aviation safety,
-which needs real time assessment of conditions and visibility around
-flight paths.
-
-In remote sensing~\cite{Pust2011, Mishchenko2007}, imaging through air is
-associated with {\em atmospheric correction}, based on {\em aerosol
+(\cref{fig:groundgrid}).  3D recovery of this medium has direct
+implications to various scientific communities that either rely on
+remotely-sensed imagery, study the atmosphere, or overcome the medium
+to see beyond. These include meteorology, atmospheric sciences,
+volcanology, and climatology.  Aerosol retrieval is important for
+understanding climate evolution~\cite{Dayan2008,kalashnikova} and
+monitoring air quality. Mapping aerosol density is significant to
+aviation safety, which needs real time assessment of conditions and
+visibility around flight paths.
+
+In remote sensing~\cite{Pust2011, Mishchenko2007}, imaging through air
+is associated with {\em atmospheric correction}, based on {\em aerosol
   retrieval}. In this discipline, the atmosphere is often assumed to
@@
 distinct. Most tomography setups have a controlled and/or
-multidirectional radiation source~\cite{Boas2001,messer}. In
-contrast, our source is the uncontrolled, unidirectional
-Sun. Moreover, typical tomography relies on a linear
-model~\cite{gregson}: the pixel value is a linear combination of
-components along a line of sight (LOS), or a multiplicative
-combination (linearized by a logarithm). Linear tomography can detect
-gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
-aerosol attenuation of visible light is typically dominated by {\em
-  scattering}, rather than absorption. Since the radiation source is
-single and fixed in space and time, we cannot rely on direct
-illumination for tomographic recovery of attenuation
+multidirectional radiation source~\cite{Boas2001,messer}. In contrast,
+our source is the uncontrolled, unidirectional Sun. Moreover, typical
+tomography relies on a linear model~\cite{gregson}: the pixel value is
+a linear combination of components along a line of sight (LOS), or a
+multiplicative combination (linearized by a logarithm). Linear
+tomography can detect gases~\cite{Cosofret2009}, which absorb UV or IR
+radiation. However, aerosol attenuation of visible light is typically
+dominated by {\em scattering}, rather than absorption. Since the
+radiation source is single and fixed in space and time, we cannot rely
+on direct illumination for tomographic recovery of attenuation
 fields~\cite{Aviles2011}. We may only use sunlight scattered into the
-LOS. The model is {\em nonlinear, yet tractable}. We model passive
-optical tomographic imaging of 3D atmospheric scatterer distributions
-in cloudless conditions. Then, we solve this tomography problem, to
-recover the distribution. Recovery is formulated as an optimization
-that minimizes a cost function. We derive the gradient of this cost
-function, to enable efficient optimization.
+LOS. The model is {\em nonlinear}, yet {\em tractable}. We model
+passive optical tomographic imaging of 3D atmospheric scatterer
+distributions in cloudless conditions. Then, we solve this tomography
+problem, to recover the distribution. Recovery is formulated as an
+optimization that minimizes a cost function. We derive the gradient of
+this cost function, to enable efficient optimization.
 \begin{figure*}[t!]
@@
   \end{center}
-  \caption{\small Integral (lightfield) imaging through a volumetric distribution
-    in the atmosphere, using ground-based cameras.}
+  \caption{\small Integral (lightfield) imaging through a volumetric
+    distribution in the atmosphere, using ground-based cameras.}
   \label{fig:groundgrid}
@@
 \end{align}
-% Let $\mu\equiv \cos\Phi^{\rm scatter}$.
 The phase function is often approximated by a parametric
@@
 \begin{align}
-  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
-  g^2)(1+\cos^2\Phi^{\rm scatter}) (2+g^2)^{-1}(1 + g^2 -
-  2g\cos\Phi^{\rm scatter})^{-1.5}.
+  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -
+  g^2)(1+\mu^2)}{(2+g^2)(1 + g^2 - 2g\mu)^{\sfrac{3}{2}}}.
   \label{eq:aerosol_scatter}
 \end{align}
-% \begin{align}
-%   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
-%   g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}.
-%   \label{eq:aerosol_scatter}
-% \end{align}
 
@@
   P^{\rm air}(\Phi^{\rm scatter}) &\approx
-  \sfrac{3}{16\pi}(1+\cos^2\Phi^{\rm scatter})
+  \frac{3}{16\pi}(1+\cos^2\Phi^{\rm scatter})
   \label{eq:rayleighP}
@@
 with altitude $h$, with a characteristic~\cite{Levi1980} falloff
-height $H^\mathrm{air}=8\ \si{\km}$. Thus~\cite{Levi1980}, the
+height $H^\mathrm{air}=8\ \si{\km}$. Thus, the
 coefficients for extinction and scattering by air molecules can be
-modeled by
+modeled by~\cite{Levi1980},
 \begin{align}
@@
 
-\noindent {\bf Inverse transform sampling}: A tool for RT is
-Monte-Carlo (MC) simulation. MC considers scattering and extinction as
+\noindent {\bf Inverse transform sampling}: A tool for RT modeling is
+the Monte-Carlo (MC) method. MC considers scattering and extinction as
 random phenomena, that are sampled from their probability
-distributions.  Sample random numbers that comply with a specified
-probability density function can be generated using inverse transform
-sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
+distributions. 
+Inverse transform sampling~\cite{devroye1986sample} is used for 
+sampling random numbers that comply with a specified
+probability density function. Let $u$ be a random number drawn
 from a uniform distribution in the interval $[0,1]$. The number $u$
@@
 voxel $q$. The intersection line segment has geometric length $l_{\rm
-  SR}(q|\Delta z,\Phi^{\rm SR})$, where $\Delta z$ is a voxel's
+  SR}(q|\Delta z,\Phi^{\rm SR},k)$, where $\Delta z$ is a voxel's
 vertical geometric thickness, and $\Phi^{\rm SR}$ is the Sun
@@
 intersection line segment is $l_{\rm LOS_c}(m|\Delta z,\Phi^{\rm
-  LOS}_c)$.  As in \cref{eq:Dsv}, define a $N_{\rm voxels}\times
+  LOS}_c,k)$.  As in \cref{eq:Dsv}, define a $N_{\rm voxels}\times
 N_{\rm voxels}$ sparse matrix whose element $(k,m)$ is
@@
 $[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
-the scene, but the density distribution ${\DistUnknown}$ is
+the scene, but the density distribution $n(k)$ is
 variable. As a numerical approximation, assume that within any voxel,
@@
 are
-% \begin{equation}
-%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
-%  \label{eq:lSRn}
-%\end{equation}
 \begin{align}
@@
 \end{align}
-Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be column
-stack vector representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm
+Let ${\DistUnknown}$, $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be column
+stack vector representations of $n(k)$, $\tau_{\rm SR}(k)$ and $\beta^{\rm
   air}(k)$, respectively.  Then, we can write \cref{eq:lSRn} using
-matrix notation: \mbox{$\vect{\tau}_{\rm SR}= \OpDistance^{\mathrm{Sun
+matrix notation: 
+\begin{align}
+  \vect{\tau}_{\rm SR} &= \OpDistance^{\mathrm{Sun
       \rightarrow voxel}}\vect{\beta}^{\rm air} + \sigma^{\rm
     aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}}
-  {\DistUnknown}$},\ and \mbox{$\vect{\tau}_{{\rm LOS}_c}=
-  \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air} +
-  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
-  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel form a
+  {\DistUnknown} \nonumber \\
+  \vect{\tau}_{{\rm LOS}_c} &=
+  \OpDistance_c^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air} +
+  \sigma^{\rm aerosol}\OpDistance_c^{\mathrm{voxel \rightarrow cam}}
+  {\DistUnknown}.
+\end{align}
+
+The SR and LOS paths joining at each voxel form a
 single path from the TOA to camera $c$.  Hence, in matrix notation,
@@
 
-%
-%
-% and $\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
-% representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
-% air}(k)$, respectively.
-%
-% A similar analysis yields the optical depth along a LOS to voxel
-% $k$, $\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
-% \mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air}
-% + \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
-% {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
-% form a single path from the TOA to camera $c$, yielding
-% \begin{equation}
-%  {\bm D}_c=
-%  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
-%  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
-%  \quad\text{ and }\quad
-%  \vect{\tau}_c=
-%  \vect{\tau}_{\rm SR}+
-%  \vect{\tau}_{{\rm LOS}_c}
-%  \;\;.
-%  \label{eq:D_tau_total}
-%\end{equation}
-%Hence, in matrix notation, \cref{eq:tau} yields the total optical
-% depths corresponding to LOSs (of camera $c$) and SRs that cross all
-% voxels:
-% \begin{equation}
-%  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
-%  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
-%  \;\;.
-%  \label{eq:tautotal}
-%\end{equation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
-Column-stacking all voxels yields the vector representation of all
+Column-stacking all angles yields the vector representation of all
 scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal}) the radiant power
+(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the radiant power
 contributed by the voxel is
@@
 
-A camera pixel collects light from a narrow cone in the
+A camera sensor comprises $N_{\rm pix}$ pixels. Each pixel collects light from a narrow cone in the
 atmosphere. The cone contains or intersects some voxels, while being
-oblivious to all the rest.  Overall, light power captured at a pixel
-is a weighted sum of the power $p_c(k)$ from all voxels.  This sum is
-formulated by a matrix operation over ${\bm p}_c$:
+oblivious to all the rest.  Overall, light power captured at the pixel
+is a weighted sum of the power $p_c(k)$ radiating from all voxels.  This sum is
+formulated by a matrix operation ${\vect{\Pi}}_c$ over ${\bm p}_c$:
 \begin{equation}
@@
   pix}$ long.  Combining
-\cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
-\begin{align}
-  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
-  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
+\cref{eq:tautotal,eq:pc,eq:IcP,eq:alpha_matrix}, the captured image is thus
+\begin{align}
+  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
+  \left[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
     aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
-    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
-  {\bm D}_c{\bm n})] \Big\} .
+    n} \right] \odot \exp\left[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
+  {\bm D}_c{\bm n})\right] \right\} .
   \label{eq:bigIA}
@@
 \end{figure}
-To demonstrate the model, we simulated some scenarios, whose details are as follows.\\
+To demonstrate the model, we simulated some scenarios, whose details are as follows.
+\\
+
 \noindent{\bf Geometry}: The sun is at zenith angle $\Phi^{\rm
@@
 We tested domain division to various grids, from $10\times10 \times
-20$ voxels, up to $50\times50 \times 1000$. The corresponding voxels
+20$ voxels, up to $50\times50 \times 100$. The corresponding voxels
 had width, length and thickness of $5{\rm km}\times 5{\rm km} \times
 0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.  Each
-ground-based camera has nearly a hemispherical field of view, and low
+ground-based camera has a hemispherical field of view, and low
 resolution, $128 \rm{px} \times 128 \rm{px}$, as cloudless (yet hazy)
 sky images are rather smooth.
+\\
 
@@
 \begin{align}
-  f_1[h(k)] = \sfrac{1} {n^{\rm sealevel}}
+  f_1[h(k)] = n^{\rm sealevel}
   \exp[-h(k)/H^\mathrm{aerosol}],
@@
 scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
-wide, 2.8km thick and centered at altitude 3.3km; the other is 24km
-wide, 2.1km thick and centered at altitude 6.6km. Horizontal widths
+wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
+wide, 2.1km thick and centered at altitude 5km. Horizontal widths
 are much larger than the vertical thickness, in consistency with
@@
 back-traced to the Sun are counted, per pixel. In this model, RT takes
-the following steps, per pixel (\cref{fig:mcgrid}):
+the following steps, per pixel (\cref{fig:mcgrid}a):
 \begin{figure}
@@
   \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
-  \caption{\small [a] Multiple-scattering forward model by Monte
-    Carlo. [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}, rendered using a MC model.  [c]
-    Cross section along the $X$-Axis of the MC simulation,
-    Single-Scattering simulation and a Single-Scattering image created
+  \caption{\small [a] Multiple-scattering forward model by MC.
+    [b] Photograph of the same sky and view point as in
+    \cref{fig:simulation-results1}[left], rendered using MC.
+    [c] Cross section along the $X$-Axis of the MC simulation,
+    single-scattering simulation and a single-scattering image created
     from the reconstructed distribution
@@
 
-\noindent Per iteration $i$
+\noindent Per iteration $i$:
 
@@
 \end{align}
-Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf
+Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields the 3D position ${\bf
   X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
@@
 \noindent ({\tt iii}) The type of particle (air molecule or aerosol)
-the photon-packet interacts with at ${\bf X}_{i}$ is determined
+that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
 randomly according to their relative densities at the voxel containing
@@
 determined by inverse transform sampling, according to the phase
-function of the particle (Eqs.~\ref{eq:aerosol_scatter}
-or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
+function of the particle (Eqs.~(\ref{eq:aerosol_scatter})
+or~(\ref{eq:rayleighP})). This yields a new {\em ray}, denoted ${\cal
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
@@
 is a regularization term that expresses some prior knowledge on the
-distribution, while $\eta$ is a regularization weight.
+distribution, while $\eta$ is the regularization weight.
 
 Since aerosol distributions are usually fuzzy, useful regularization
-is by a {\em smoothness term}, which penalizes energy in second order
+is by a {\em smoothness term}, which penalizes for energy in the second order
 spatial derivatives (3D Laplacian), $\| \nabla^2{\bm
@@
 altitude have good coverage by many cameras at multiple directions,
-while at low altitude voxels are mainly observed by local
+while low altitude voxels are mainly observed by local
 cameras. Hence, regularization can be weakened with altitude. We
-accomplished this weakening using a weight
+accomplish this weakening using a weight
 $w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
@@
 vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
-this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
+the Jacobian differentiates the intensity in pixel ${\bm \Theta}$ (in
 viewpoint $c$) with variation of the aerosol density at voxel $k$,
@@
   views}$ varied from 12 to 100.
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
     density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
-    Single-Scattering simulated images are used as input to the
+    single-scattering simulated images are used as input to the
     recovery.  In [c,d], MC simulated images are used as input for the
@@
 dedicated to rendering a modeled image. The algorithm was initialized
-by ${\bm n}=0$.  Satisfactory convergence occurred in several thousand
+by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
 iterations. Depending on the resolution it took between minutes to a
@@
 the algorithm of \cref{sec:inverse-problem}. The total estimation
-error can be quantifies by the aerosol mass that is over and under-estimated
+error can be quantified by the aerosol mass that is over and under-estimated
 in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 

### 2013-08-04 article.tex
Final version

@@
 
-\bibitem{Pust2011}
-N.~J. Pust, A.~R. Dahlberg, M.~J. Thomas, and J.~a. Shaw, \enquote{{Comparison
-  of full-sky polarization and radiance observations to radiative transfer
-  simulations which employ AERONET products.}} Optics express \textbf{19},
-  18602--13 (2011).
-
 \bibitem{Mishchenko2007}
@@
   Trans. Math. Softw. \textbf{23}, 550--560 (1997).
+
+\bibitem{Pust2011}
+N.~J. Pust, A.~R. Dahlberg, M.~J. Thomas, and J.~a. Shaw, \enquote{{Comparison
+  of full-sky polarization and radiance observations to radiative transfer
+  simulations which employ AERONET products.}} Optics express \textbf{19},
+  18602--13 (2011).
 
@@
 
-In remote sensing~\cite{Pust2011, Mishchenko2007}, imaging through air
+In remote sensing~\cite{Mishchenko2007}, imaging through air
 is associated with {\em atmospheric correction}, based on {\em aerosol
@@
 To deploy such a system on a very large scale will require a long-term
-engineering effort. Camera specifications should be set to optimally
-recover a wide range of aerosol distributions. This requires a major
-theoretic and numerical research.
+engineering effort. Camera specifications~\cite{Pust2011} should be
+set to optimally recover a wide range of aerosol distributions. This
+requires a major theoretic and numerical research.
 

### 2013-09-22 article.tex
highlighted comments for resubmission

@@
 \usepackage{cite}
+\usepackage{soul}
 
@@
 \renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
+\newcommand{\fix}[2]{\st{#1}\hl{#2}}
 
@@
   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -
-  g^2)(1+\mu^2)}{(2+g^2)(1 + g^2 - 2g\mu)^{\sfrac{3}{2}}}.
+  g^2)(1+\mu^2)}{(2+g^2)(1 + g^2 - 2g\mu)^{\sfrac{3}{2}}}
   \label{eq:aerosol_scatter}
 \end{align}
+\hl{where $\mu\equiv \cos \Phi^{\rm scatter}$}
 
@@
 As illustrated in \cref{fig:groundgrid,fig:distributions},
-The sky is discretized into a grid of $N_{\rm voxels}$ volume elements
+The sky is discretized into a grid of $N_{\rm voxels}$ \fix{volume
+  elements}{rectangular cuboid elements}
 (voxels), indexed by $k$, $m$ or $q$.
@@
 \cref{fig:results} shows estimation results, corresponding to the
-original distributions of \cref{fig:distributions}. In
+original distributions of \cref{fig:distributions}. 
+\hl{
+In these simulations the atmosphere domain was defined over a
+$20\times20 \times 40$ grid. Thirty six cameras were placed
+$\sim7$km apart on a $6\times6$ grid.
+}
+In
 \cref{fig:results}a,b, the single-scattering model was used both
@@
 engineering effort. Camera specifications~\cite{Pust2011} should be
-set to optimally recover a wide range of aerosol distributions. This
-requires a major theoretic and numerical research.
+set to optimally recover a wide range of aerosol distributions.
+\hl{The relation between the quantity and spatial distribution of
+  cameras and the quality of reconstruction should also be determined.}
+\fix{This requires}{These open questions require} a major theoretic
+ and numerical research.
 

### 2013-09-22 article.tex
Fixed style corrections

--- 2013-08-04 article.tex
@@
 \author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1}
-  Vadim~Holodovsky\authnote{1}, Michael~J.~Garay\authnote{2} and Anthony~B.~Davis\authnote{2}}
+  Vadim~Holodovsky,\authnote{1} Michael~J.~Garay\authnote{2} and Anthony~B.~Davis\authnote{2}}
 
@@
   visualization, and processing using integral imaging},} Proceedings of the
-  IEEE \textbf{94} (2006).
+  IEEE \textbf{94.3} (2006).
 
@@
 J.~Kim, D.~Lanman, Y.~Mukaigawa, and R.~Raskar, \enquote{{Descattering
-  transmission via angular filtering},} in \enquote{Proc. ECCV' 10,}
+  transmission via angular filtering},} in \emph{Proc. ECCV' 10,}
   (Springer-Verlag, Berlin, Heidelberg, 2010), pp. 86--99.
@@
 M.~I. Mishchenko and I.~V. Geogdzhayev, \enquote{{Satellite remote sensing
-  reveals regional tropospheric aerosol trends.}} Optics express \textbf{15},
+  reveals regional tropospheric aerosol trends},} \opex \textbf{15},
   7423--38 (2007).
@@
 E.~Namer, S.~Shwartz, and Y.~Y. Schechner, \enquote{{Skyless polarimetric
-  calibration and visibility enhancement.}} Optics express \textbf{17}, 472--93
+  calibration and visibility enhancement},} \opex \textbf{17}, 472--93
   (2009).
@@
   \enquote{{Three-dimensional optical tomography of hemodynamics in the human
-  head},} Optics express \textbf{9}, 272--86 (2001).
+  head},} \opex \textbf{9}, 272--86 (2001).
 
@@
   \enquote{{Imaging sensor constellation for tomographic chemical cloud
-  mapping},} Applied optics \textbf{48}, 1837--52 (2009).
+  mapping},} \ao \textbf{48}, 1837--52 (2009).
 
@@
 W.~M. Cornette and J.~G. Shanks, \enquote{{Physically reasonable analytic
-  expression for the single-scattering phase function: errata.}} Applied optics
+  expression for the single-scattering phase function: errata},} \ao
   \textbf{34}, 641 (1995).
@@
 L.~Devroye, \enquote{{Sample-based non-uniform random variate generation},} in
-  \enquote{Proceedings of the 18th conference on Winter simulation,}  (ACM,
+  \emph{Proceedings of the 18th conference on Winter simulation,}  (ACM,
   1986), pp. 260--265.
@@
 S.-H. Hong, J.-S. Jang, and B.~Javidi, \enquote{{Three-dimensional volumetric
-  object reconstruction using computational integral imaging.}} Optics express
-  \textbf{12}, 483--91 (2004).
+  object reconstruction using computational integral imaging},} \opex
+  \textbf{12}, 483--491 (2004).
 
@@
   of full-sky polarization and radiance observations to radiative transfer
-  simulations which employ AERONET products.}} Optics express \textbf{19},
-  18602--13 (2011).
+  simulations which employ AERONET products},} \opex \textbf{19},
+  18602--18613 (2011).
 
@@
 \noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
-in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
+in~\cite{Martonchik2009}. This is a spherical non-absorbing
 sea-salt/organic particle, whose anisotropy parameter per color
@@
 distributions using a product of two functions. To express the general
-trend of reduced density with altitude $h(k)$ of voxel $k$, we follow
-Ref.~\cite{Levi1980} and set the first function as
+trend of reduced density with altitude $h(k)$ of voxel $k$, we
+follow~\cite{Levi1980} and set the first function as
 \begin{align}
@@
 non-sharp boundaries of typical distributions. The {\em Haze Blobs}
-scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
+scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
 wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
@@
 
-The {\em Haze Front} scene in \cref{fig:distributions}b uses an
+The {\em Haze Front} scene in \cref{fig:distributions}(b) uses an
 ellipsoid degenerated to an elliptic cylinder that partly enters the
@@
 back-traced to the Sun are counted, per pixel. In this model, RT takes
-the following steps, per pixel (\cref{fig:mcgrid}a):
+the following steps, per pixel (\cref{fig:mcgrid}(a)):
 \begin{figure}
@@
 The quality of MC increases with the number of photons launched.
-\cref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
+\cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
 scene, derived by the MC process, using \num{10000} photons per pixel,
@@
 comparison of a sample horizontal cross section is shown in
-\cref{fig:mcgrid}c.
+\cref{fig:mcgrid}(c).
 
@@
 
-\cref{fig:results} shows estimation results, corresponding to the
+\Cref{fig:results} shows estimation results, corresponding to the
 original distributions of \cref{fig:distributions}. In
-\cref{fig:results}a,b, the single-scattering model was used both
+Figs.~\ref{fig:results}(a) and (b), the single-scattering model was used both
 in rendering of the raw images, and in the estimation algorithm. In
-\cref{fig:results}c,d, the MC model (multiple scattering)
+Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
 rendered the raw images, over which the estimation algorithm
@@
 values are consistent.
-Errors in \cref{fig:results}a,b stem from random noise, which had
+Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
 been induced in the raw images. Errors are larger when MC is used to
@@
 \hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
-  In
-\cref{fig:results}a,b, respectively $\epsilon=0.14$ and
-$\epsilon=0.20$.  In \cref{fig:results}c,d, both cases have
+  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
+$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
 $\epsilon=0.65$.

### 2013-09-22 article.tex
Several more styling corrections

@@
 \crefname{section}{Sec.}{Secs.}
+\Crefname{section}{Section}{Sections}
 \makeatletter
@@
 are much larger than the vertical thickness, in consistency with
-atmospheric scales. \cref{fig:simulation-results1} shows
+atmospheric scales. \Cref{fig:simulation-results1} shows
 photographs of the {\em Haze Blobs} scene, as simulated by
@@
 The quality of MC increases with the number of photons launched.
-\cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
+\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
 scene, derived by the MC process, using \num{10000} photons per pixel,
@@
 
-\cref{sec:simul} describes simulated scenes at various grid
+\Cref{sec:simul} describes simulated scenes at various grid
 resolutions.  Depending directly on the area grid finesse, $N_{\rm

### 2013-09-23 article.tex

@@
 \Cref{fig:results} shows estimation results, corresponding to the
-original distributions of \cref{fig:distributions}. In
-Figs.~\ref{fig:results}(a) and (b), the single-scattering model was used both
+original distributions of \cref{fig:distributions}. 
+\hl{
+In these simulations the atmosphere domain was defined over a
+$20\times20 \times 40$ grid. Thirty six cameras were placed
+$\sim7$km apart on a $6\times6$ grid.
+}
+In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
+used both
 in rendering of the raw images, and in the estimation algorithm. In

### 2013-09-30 article.tex
Added section on error vs cameras.

@@
 where
-% \begin{align}
-%   \label{eq:gradient3}
-%   {\bf A} &= \varpi^{\rm aerosol}
-%   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
-%   {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
-%%   & \;\;\;
-%   \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
-%   aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
-%   scatter}_c) \odot{\bm n} ]}
-%    %   \nonumber \\
-%  %   \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
-%  %   {\sigma}^{\rm
-%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
-% \end{align}
 \begin{equation}
@@
 
+\hl{Optimal placement of cameras is an important aspect in realization
+of the suggested system. As a first step we would like to measure the effect of
+the distance between the cameras on the estimation quality. For this, we
+repeated the reconstruction algorithm, each time using a subset of varying size
+of the raw images. In each test the reconstruction algorithm was applied to $n_{views}$
+($<N_{views}$) images. The images were selected randomly from the total $N_{views}$ raw images.
+To eliminate the effect of incidental camera position, the test was repeated several
+times each time with a different $n_{views}$ subset.} \Cref{fig:error_vs_cameras}
+\hl{summarizes the results of these tests. In can be seen that a good estimation
+is achieved already when using $20$ cameras. Over an area of $50\times 50{\rm km}^2$,
+this quantity relates to placing the cameras $\sim11$km apart.}
+
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\def\svgwidth{0.6\linewidth}\small{\input{images/error_vs_cameras.pdf_tex}}}
+  \caption{\small Local error measure as function of cameras
+    quantity. The blue error bars represent the error standard
+    deviation. The dashed horizontal line marks the reconstruction
+    error when all thirty six cameras are used.}
+  \label{fig:error_vs_cameras}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-09-30 article.tex
Replaced pdf_tex images with pdf (to avoid text placement problems). Using textext extension in inkscape based on http://people.orie.cornell.edu/jmd388/design/
bookmark

@@
 \usepackage{soul}
+\usepackage{layouts}
 
@@
 \begin{document}
+%\printinunitsof{in}\prntlen{\linewidth}
 
@@
   \centering
-  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
+  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
   \caption{\small [a] Multiple-scattering forward model by MC.
     [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}[left], rendered using MC.
-    [c] Cross section along the $X$-Axis of the MC simulation,
-    single-scattering simulation and a single-scattering image created
-    from the reconstructed distribution
-    (\cref{sec:optimization-results}).}
+    \cref{fig:simulation-results1}[left], rendered using MC.}
   \label{fig:mcgrid}
@@
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}[left].  A
-comparison of a sample horizontal cross section is shown in
-\cref{fig:mcgrid}(c).
+from the same viewpoint as \cref{fig:simulation-results1}[left].
+Comparison of \hl{horizontal and vertical cross sections along 
+matching MC and single-scattering simulated images are} shown in
+\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
+\hl{The cross sections indicate fair correspondence between
+the MC and single-scattering simulations.}
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
+  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
+    a MC and single-scattering simulations. Overlay of the cross
+    sections on the MC simulated image is shown in [c]. }
+  \label{fig:cross_sections}
+\end{figure}
+
+\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
+scattering events to the MC image. The amount of light scattered
+in the direction of the sun due to the first scatter event of each photon
+is collected to create} \cref{fig:scatter_order}(a). \hl{This process
+is repeated for the second and third scatter events creating}
+\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
+\hl{respectively. It is conspicuous that the first scatter is responsible
+for most of the energy in the MC image. The effect of subsequent scatters
+is mostly evident at the horizon. The line of sight extending into the
+horizon crosses a larger volume of atmosphere then the line of sight extending
+in the direction of the zenith. This increases the probability of
+scattering events along the line of sight extending into the horizon.}
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\includegraphics{images/scatter_order2.pdf}}
+  \caption{\small Separation of a MC simulated image to (a) first
+   scattering order, (b) second scattering order and (c) third
+   scattering order. }
+  \label{fig:scatter_order}
+\end{figure}
 
@@
   \centering
-  \yoavcomment{\def\svgwidth{0.6\linewidth}\small{\input{images/error_vs_cameras.pdf_tex}}}
+  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
   \caption{\small Local error measure as function of cameras

### 2013-09-30 article.tex
bookmark

@@
 the MC and single-scattering simulations.}
-\begin{figure}[h]
+\begin{figure}[th]
   \centering
@@
   \centering
-  \yoavcomment{\includegraphics{images/scatter_order2.pdf}}
+  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
   \caption{\small Separation of a MC simulated image to (a) first
@@
 Here $\MaskSun$ masks the area around the sun, as in real-world images
-it is indeed blocked.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
+it is indeed blocked. \hl{It is also used for masking the areas in the image
+prone for multiple scattering events, e.g. the horizon area as evident in}
+\cref{fig:scatter_order}(b).  In \cref{eq:objectiveA}, $\Psi({\bm n})$
 is a regularization term that expresses some prior knowledge on the
@@
 this quantity relates to placing the cameras $\sim11$km apart.}
-
 \begin{figure}[h]
@@
 \end{figure}
+
+\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
+resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
+This admits to the fact that the single-scattering model, on which the reconstruction
+algorithm is based, is valid when the optical depth of the medium is small.}
+% \begin{figure}[h]
+%   \centering
+%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
+%   \caption{\small (a) and (b) show MC simulations of low and 
+%     high density scenes, respectively. (c) shows the reconstruction of
+%     the high density scene.}
+%   \label{fig:high_density}
+% \end{figure}
 
@@
 ground. This will certainly be needed for dense distributions as
-clouds.
+clouds. \Cref{fig:scatter_order}(b) \hl{suggests that incorporating
+the second order of scattering might be sufficient for most situations.}
 

### 2013-10-02 article.tex
Yoav Changes
work on graphics

@@
   \label{eq:taurand}
-  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u).
-\end{equation}
+  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u),
+\end{equation}
+where $F^{-1}$ denotes the inverse function of $F$.
 If the atmosphere is uniform, then from \cref{eq:tau} the photon
@@
   \caption{\small Separation of a MC simulated image to (a) first
-   scattering order, (b) second scattering order and (c) third
-   scattering order. }
+   scattering order, (b) second scattering order, (c) third
+   scattering order and (d) forth scattering order. }
   \label{fig:scatter_order}

### 2013-10-02 article.tex
bookmark

--- 2013-09-30 article.tex
@@
 \begin{align}
-  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -
-  g^2)(1+\mu^2)}{(2+g^2)(1 + g^2 - 2g\mu)^{\sfrac{3}{2}}}
+  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -g^2)
+  [1+(\cos \Phi^{\rm scatter})^2]}
+  {(2+g^2)(1 + g^2 - 2g\cos \Phi^{\rm scatter})^{\sfrac{3}{2}}}
   \label{eq:aerosol_scatter}
 \end{align}
-\hl{where $\mu\equiv \cos \Phi^{\rm scatter}$}
 
@@
 As illustrated in \cref{fig:groundgrid,fig:distributions},
-The sky is discretized into a grid of $N_{\rm voxels}$ \fix{volume
-  elements}{rectangular cuboid elements}
+The sky is discretized into a grid of $N_{\rm voxels}$ rectangular cuboid volume elements
 (voxels), indexed by $k$, $m$ or $q$.
@@
 
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
-  \caption{\small Different viewpoints of a sky that includes {\em
-      Haze Blobs}. Images are rendered using the single-scattering model.
-    A yellow dot marks the Sun location. Dashed white circles mark
-    zenith angles.}
-  \label{fig:simulation-results1}
-\end{figure}
 To demonstrate the model, we simulated some scenarios, whose details are as follows.
@@
 atmospheric scales. \Cref{fig:simulation-results1} shows
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
+  \caption{\small Different viewpoints of a sky that includes {\em
+      Haze Blobs}. Images are rendered using the single-scattering model.
+    A yellow dot marks the Sun location. Dashed white circles mark
+    zenith angles.}
+  \label{fig:simulation-results1}
+\end{figure}
 photographs of the {\em Haze Blobs} scene, as simulated by
@@
 back-traced to the Sun are counted, per pixel. In this model, RT takes
-the following steps, per pixel (\cref{fig:mcgrid}(a)):
+the following steps, per pixel (\cref{fig:mcgrid}a):
 \begin{figure}
@@
 determined by inverse transform sampling, according to the phase
-function of the particle (Eqs.~(\ref{eq:aerosol_scatter})
-or~(\ref{eq:rayleighP})). This yields a new {\em ray}, denoted ${\cal
+function of the particle (Eqs.~\ref{eq:aerosol_scatter}
+or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
@@
 from the same viewpoint as \cref{fig:simulation-results1}[left].
-Comparison of \hl{horizontal and vertical cross sections along 
-matching MC and single-scattering simulated images are} shown in
-\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
-\hl{The cross sections indicate fair correspondence between
-the MC and single-scattering simulations.}
-\begin{figure}[th]
+Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
+cross sections of the viewed field, extracted from the images in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).
+These plots demonstrate consistency in these cases, for most pixels.
+\begin{figure}[t]
   \centering
   \yoavcomment{\includegraphics{images/cross_sections.pdf}}
-  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
-    a MC and single-scattering simulations. Overlay of the cross
-    sections on the MC simulated image is shown in [c]. }
+  \caption{\small Cross sections along the $X$-axis [a] and $Y$-axis [b] of
+    and images rendered by either single-scattering and MC. The corresponding
+    images appear in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).}
   \label{fig:cross_sections}
@@
 
-\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
-scattering events to the MC image. The amount of light scattered
-in the direction of the sun due to the first scatter event of each photon
-is collected to create} \cref{fig:scatter_order}(a). \hl{This process
-is repeated for the second and third scatter events creating}
-\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
-\hl{respectively. It is conspicuous that the first scatter is responsible
-for most of the energy in the MC image. The effect of subsequent scatters
-is mostly evident at the horizon. The line of sight extending into the
-horizon crosses a larger volume of atmosphere then the line of sight extending
-in the direction of the zenith. This increases the probability of
-scattering events along the line of sight extending into the horizon.}
-\begin{figure}[h]
+\Cref{fig:scatter_order} shows the contribution by successive
+scattering orders. They are derived from the MC image. Photons contributing to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
+The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a).
+Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
+\cref{fig:scatter_order}(c). Clearly, first-order scatter is responsible
+for most of the energy in the MC image. Radiance by higher order scattering
+is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
+towards the horizon the probability of high order scattering increases.
+\begin{figure}[bt]
   \centering
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of a MC simulated image to (a) first
-   scattering order, (b) second scattering order and (c) third
-   scattering order. }
+  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first  order, (b) second order and (c) third scattering order.}
   \label{fig:scatter_order}
@@
 Here $\MaskSun$ masks the area around the sun, as in real-world images
-it is indeed blocked. \hl{It is also used for masking the areas in the image
-prone for multiple scattering events, e.g. the horizon area as evident in}
-\cref{fig:scatter_order}(b).  In \cref{eq:objectiveA}, $\Psi({\bm n})$
+it is indeed blocked.
+We mask the horizon, by using a camera whose field of view is a bit smaller than hemispherical.
+This reduces the influence of image regions that are more strongly affected by high-order scattering (\cref{fig:scatter_order}(b)).
+Consequently,
+the fit of the image formation model focuses on the bulk image region, where the single scattering model is more valid.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
 is a regularization term that expresses some prior knowledge on the
@@
 
-\section{Results}
+\section{Recovery simulations}
 \label{sec:optimization-results}
 
-\Cref{sec:simul} describes simulated scenes at various grid
-resolutions.  Depending directly on the area grid finesse, $N_{\rm
-  views}$ varied from 12 to 100.
+To demonstrate recovery, we performed simulations. We tested how results are affected by the following variations:
+$\{1\}$ Multiple or only single scatter in the forward model;
+$\{2\}$ Spatial distribution;
+$\{3\}$ Density of viewpoints;
+$\{4\}$ Aerosol characteristics;
+$\{5\}$ Density scale.
+
+In all cases, images were created as described
+in \cref{sec:simul,sec:monte-carlo-simul}.
+These images served as input to the reconstruction algorithm.
+The optimization used an L-BFGS-B solver~\cite{BFGS} on a computer cluster.
+Each computer core was dedicated to rendering a modeled image.
+The algorithm was initialized
+by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
+iterations. Depending on the resolution it took between minutes to a
+couple of hours to complete, in total. The total estimation
+error can be quantified by the aerosol mass that is over and under-estimated
+in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm,
+the total mass relative difference is
+$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$. 
+To also sense local errors, we use 
+ $\epsilon=\|
+\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
+%  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
+%$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
+%$\epsilon=0.65$.
+These results are listed in Table~\ref{tbl:mass}. \\
+
+\noindent{\bf Forward models and distributions}: 
+\Cref{fig:results} shows estimation results, corresponding to the
+original distributions of \cref{fig:distributions}.
 \begin{figure}[h]
@@
 \end{figure}
-We applied the reconstruction algorithm to images created as described
-in \cref{sec:simul,sec:monte-carlo-simul}. We used the
-L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
-dedicated to rendering a modeled image. The algorithm was initialized
-by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
-iterations. Depending on the resolution it took between minutes to a
-couple of hours to complete, in total.
-
-\Cref{fig:results} shows estimation results, corresponding to the
-original distributions of \cref{fig:distributions}. 
 \hl{
@@
 In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
-used both
-in rendering of the raw images, and in the estimation algorithm. In
+used both in rendering of the raw images, and in the estimation algorithm. In
 Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
@@
 render the images, since high-order scattering is not accounted for in
-the algorithm of \cref{sec:inverse-problem}. The total estimation
-error can be quantified by the aerosol mass that is over and under-estimated
-in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
-the total mass relative difference is
-$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
-The overall mass is recovered, but for 6.5\% loss. For local errors,
- $\epsilon=\|
-\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
-  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
-$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
-$\epsilon=0.65$.
-
-\hl{Optimal placement of cameras is an important aspect in realization
-of the suggested system. As a first step we would like to measure the effect of
-the distance between the cameras on the estimation quality. For this, we
-repeated the reconstruction algorithm, each time using a subset of varying size
-of the raw images. In each test the reconstruction algorithm was applied to $n_{views}$
-($<N_{views}$) images. The images were selected randomly from the total $N_{views}$ raw images.
-To eliminate the effect of incidental camera position, the test was repeated several
-times each time with a different $n_{views}$ subset.} \Cref{fig:error_vs_cameras}
-\hl{summarizes the results of these tests. In can be seen that a good estimation
-is achieved already when using $20$ cameras. Over an area of $50\times 50{\rm km}^2$,
-this quantity relates to placing the cameras $\sim11$km apart.}
-\begin{figure}[h]
+the algorithm of \cref{sec:inverse-problem}.
+The overall mass is recovered, but for 6.5\% loss. \\
+
+% at various grid
+%resolutions.  Depending directly on the area grid finesse, $N_{\rm
+%  views}$ varied from 12 to 100.
+%
+%
+%For local errors,
+% $\epsilon=\|
+%\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
+%  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
+%$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
+%$\epsilon=0.65$.
+
+\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
+repeated the reconstruction many times, each time using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
+of $N_{\rm views}< 36$. All rendered images used MC.
+\Cref{fig:error_vs_cameras} plots $\epsilon$ as a function $N_{\rm views}$. 
+\begin{figure}[t]
   \centering
   \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
-  \caption{\small Local error measure as function of cameras
-    quantity. The blue error bars represent the error standard
-    deviation. The dashed horizontal line marks the reconstruction
-    error when all thirty six cameras are used.}
+  \caption{\small Relative error $\epsilon$ measure as function of the number of
+    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
   \label{fig:error_vs_cameras}
 \end{figure}
-
-\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
-resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
-This admits to the fact that the single-scattering model, on which the reconstruction
-algorithm is based, is valid when the optical depth of the medium is small.}
+Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints.\\
+
+\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the  
+aerosol characteristics. Compared to the aerosol described in Sec.~\ref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
+$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is 
+$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
+[0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
+Sample results are shown in Fig.~\ref{fig:variations}(a,b,c,d) and in Table~\ref{tbl:mass}.\\
+
+\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution and characteristics as described in Sec.~\ref{sec:simul}, but increased the aerosol density tenfold everywhere.
+This significantly increases the effects of high order scattering, as shown in Fig.~\ref{fig:cross_sections}(b) and Fig.~\ref{fig:variations}(e).
+Consequently, $\epsilon$ increases, when using $N_{\rm views}=36$.
+Still, Fig.~\ref{fig:variations}(f) shows that the spatial distribution outlines are recovered similarly to the other tests.
+
+%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
+%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
+%This admits to the fact that the single-scattering model, on which the reconstruction
+%algorithm is based, is valid when the optical depth of the medium is small.}
 % \begin{figure}[h]

### 2013-10-02 article.tex
modifications to the graphics
bookmark

@@
 \usepackage{layouts}
+\usepackage{booktabs}
+\usepackage{colortbl}
 
@@
 \newcommand{\CostFunc}[1]{E(#1)}
+
+\definecolor{Gray}{gray}{0.9}
 
@@
   \centering
-  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
+  \yoavcomment{\includegraphics{images/results}}
   \caption{\small Reconstructions of the scenes shown in
@@
 \noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the  
-aerosol characteristics. Compared to the aerosol described in Sec.~\ref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
+aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
 $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is 
@@
 [0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
-Sample results are shown in Fig.~\ref{fig:variations}(a,b,c,d) and in Table~\ref{tbl:mass}.\\
-
-\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution and characteristics as described in Sec.~\ref{sec:simul}, but increased the aerosol density tenfold everywhere.
-This significantly increases the effects of high order scattering, as shown in Fig.~\ref{fig:cross_sections}(b) and Fig.~\ref{fig:variations}(e).
-Consequently, $\epsilon$ increases, when using $N_{\rm views}=36$.
-Still, Fig.~\ref{fig:variations}(f) shows that the spatial distribution outlines are recovered similarly to the other tests.
+Sample results are shown in Figs.~\ref{fig:simulation_particles}(a)--(d) and in Table~\ref{tbl:mass}.\\
+
+\newcolumntype{g}{>{\columncolor{Gray}}r}
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{cccccg}
+    \toprule
+    Haze Scene & Forward Model& Density & Isotropic PF & Absorbing & $\epsilon$ \\
+    \midrule
+    Front & Single & Low & & & 0.18 \\
+     & MC & Low & & & 0.65 \\
+    \cmidrule(r){1-5}
+    Blobs & Single & Low & & & 0.14 \\
+     & MC & Low & & & 0.65 \\
+     & MC & Low & $\surd$  & & 0.49 \\
+     & MC & Low & & $\surd$ & 0.83 \\
+     & MC & High & & & 0.98 \\
+    \bottomrule
+  \end{tabular}
+  \caption{Local error for the various simulations}
+  \label{tbl:mass}
+\end{table}
+
+\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
+and characteristics as described in Sec.~\ref{sec:simul}, but increased the
+aerosol density tenfold everywhere. This significantly increases the effects
+of high order scattering, as shown in \cref{fig:cross_sections}(b) and
+\cref{fig:simulation_particles}(c). Consequently, $\epsilon$ increases,
+when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
+that the spatial distribution outlines are recovered similarly to the other
+tests.
 
@@
 %algorithm is based, is valid when the optical depth of the medium is small.}
-% \begin{figure}[h]
-%   \centering
-%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
-%   \caption{\small (a) and (b) show MC simulations of low and
-%     high density scenes, respectively. (c) shows the reconstruction of
-%     the high density scene.}
-%   \label{fig:high_density}
-% \end{figure}
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
+  \caption{\small (a) and (b) show MC simulations of low and
+    high density scenes, respectively. (c) shows the reconstruction of
+    the high density scene.}
+  \label{fig:simulation_particles}
+\end{figure}
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
+  \caption{\small (a) and (b) show MC simulations of low and
+    high density scenes, respectively. (c) shows the reconstruction of
+    the high density scene.}
+  \label{fig:reconstructions}
+\end{figure}
 

### 2013-10-03 article.tex
bookmark

@@
     [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}[left], rendered using MC.}
+    \cref{fig:simulation-results1}(a), rendered using MC.}
   \label{fig:mcgrid}
@@
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}[left].
+from the same viewpoint as \cref{fig:simulation-results1}(a).
 Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
-cross sections of the viewed field, extracted from the images in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).
+cross sections of the viewed field, extracted from the images in
+\cref{fig:simulation-results1}(d) and the corresponding MC derived photograph.
 These plots demonstrate consistency in these cases, for most pixels.
@@
   \yoavcomment{\includegraphics{images/cross_sections.pdf}}
-  \caption{\small Cross sections along the $X$-axis [a] and $Y$-axis [b] of
-    and images rendered by either single-scattering and MC. The corresponding
-    images appear in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).}
+  \caption{\small Cross-sections along the $X$-axis of photographs rendered
+    by the single-scattering and MC forward models. 
+    (a) cross sections of low density simulations (\cref{fig:simulation-results1}(d)
+    and \cref{fig:simulation_particles}(a)). (b) cross sections of
+    high density simulations (\cref{fig:simulation_particles}(d)).
+  }
   \label{fig:cross_sections}
@@
 \Cref{fig:scatter_order} shows the contribution by successive
-scattering orders. They are derived from the MC image. Photons contributing to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
+scattering orders. They are derived from the MC image. Photons contributing
+to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
 The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a).
@@
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first  order, (b) second order and (c) third scattering order.}
+  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
   \label{fig:scatter_order}
@@
   \end{tabular}
-  \caption{Local error for the various simulations}
+  \caption{Local error for the various reconstruction simulations}
   \label{tbl:mass}

### 2013-10-03 article.tex
bookamrk

@@
 
+\begin{figure}
+  \centering
+  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
+  \caption{\small Different viewpoints of a sky that includes {\em
+      Haze Blobs}. Images are rendered using the single-scattering model.
+    A yellow dot marks the Sun location. Dashed white circles mark
+    zenith angles.}
+  \label{fig:simulation-results1}
+\end{figure}
 To demonstrate the model, we simulated some scenarios, whose details are as follows.
@@
 atmospheric scales. \Cref{fig:simulation-results1} shows
-\begin{figure}
-  \centering
-  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
-  \caption{\small Different viewpoints of a sky that includes {\em
-      Haze Blobs}. Images are rendered using the single-scattering model.
-    A yellow dot marks the Sun location. Dashed white circles mark
-    zenith angles.}
-  \label{fig:simulation-results1}
-\end{figure}
 photographs of the {\em Haze Blobs} scene, as simulated by
@@
 that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
-randomly according to their relative densities at the voxel containing
-${\bf X}_{i}$.
+randomly by the relative \hl{scattering coefficients
+($\vect{\alpha}^{\rm air}$ and $\vect{\alpha}^{\rm aerosol}$} respectively)
+at the voxel containing ${\bf X}_{i}$.
 
@@
     \cref{fig:distributions}. Color represents aerosol density. The
-    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
+    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
     single-scattering simulated images are used as input to the
-    recovery.  In [c,d], MC simulated images are used as input for the
+    recovery.  In (c) and (d), MC simulated images are used as input for the
     recovery.  }
@@
   \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
-  \caption{\small (a) and (b) show MC simulations of low and
-    high density scenes, respectively. (c) shows the reconstruction of
-    the high density scene.}
+  \caption{\small MC simulations of the {\em Haze Blobs} scene
+    with varying density scales and aerosol characteristics
+    (described in \cref{sec:optimization-results}). All images
+    correspond to the same viewpoint of
+    \ref{fig:simulation-results1}(d). (a) low density scale
+    (b) absorbing particle, (c) isotropic particle and (d) high
+    density scale.
+  }
   \label{fig:simulation_particles}
@@
   \yoavcomment{\includegraphics{images/reconstructions.pdf}}
-  \caption{\small (a) and (b) show MC simulations of low and
-    high density scenes, respectively. (c) shows the reconstruction of
-    the high density scene.}
+  \caption{\small 
+    Reconstructions of the scenes shown in
+    \cref{fig:simulation_particles}(b)--(d).
+    (1a absorbing particle, (b) isotropic particle and (c) high
+    density scale scenes, respectively.}
   \label{fig:reconstructions}
@@
 ground. This will certainly be needed for dense distributions as
-clouds. \Cref{fig:scatter_order}(b) \hl{suggests that incorporating
+clouds. \Cref{fig:scatter_order} \hl{suggests that incorporating
 the second order of scattering might be sufficient for most situations.}

### 2013-10-03 article.tex
bookmark

@@
     Reconstructions of the scenes shown in
-    \cref{fig:simulation_particles}(b)--(d).
-    (1a absorbing particle, (b) isotropic particle and (c) high
-    density scale scenes, respectively.}
+    Figs.~\ref{fig:simulation_particles}(b)--(d).
+    (a) absorbing particle scene, (b) isotropic particle scene
+    and (c) high density scale scene, respectively.}
   \label{fig:reconstructions}

### 2013-10-03 article.tex
Yoav modifications

--- 2013-10-03 article.tex
@@
     [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}(a), rendered using MC.}
+    \cref{fig:simulation-results1}[left], rendered using MC.}
   \label{fig:mcgrid}
@@
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}(a).
+from the same viewpoint as \cref{fig:simulation-results1}[left].
 Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
-cross sections of the viewed field, extracted from the images in
-\cref{fig:simulation-results1}(d) and the corresponding MC derived photograph.
+cross sections of the viewed field, extracted from the images in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).
 These plots demonstrate consistency in these cases, for most pixels.
@@
   \yoavcomment{\includegraphics{images/cross_sections.pdf}}
-  \caption{\small Cross-sections along the $X$-axis of photographs rendered
-    by the single-scattering and MC forward models. 
-    (a) cross sections of low density simulations (\cref{fig:simulation-results1}(d)
-    and \cref{fig:simulation_particles}(a)). (b) cross sections of
-    high density simulations (\cref{fig:simulation_particles}(d)).
-  }
+  \caption{\small Cross sections along the $X$-axis [a] and $Y$-axis [b] of
+    and images rendered by either single-scattering and MC. The corresponding
+    images appear in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).}
   \label{fig:cross_sections}
@@
 \Cref{fig:scatter_order} shows the contribution by successive
-scattering orders. They are derived from the MC image. Photons contributing
-to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
+scattering orders. They are derived from the MC image. Photons contributing to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
 The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a).
@@
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
+  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first  order, (b) second order and (c) third scattering order.}
   \label{fig:scatter_order}
@@
 
-To demonstrate recovery, we performed simulations. We tested how results are affected by the following variations:
+To demonstrate recovery, we performed simulations, and tested effects of the following variations:
 $\{1\}$ Multiple or only single scatter in the forward model;
@@
 Each computer core was dedicated to rendering a modeled image.
-The algorithm was initialized
+The optimization was initialized
 by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
@@
 \end{figure}
-\hl{
-In these simulations the atmosphere domain was defined over a
-$20\times20 \times 40$ grid. Thirty six cameras were placed
-$\sim7$km apart on a $6\times6$ grid.
-}
+Here, the atmosphere domain was defined over a
+$20\times20 \times 40$ grid. Cameras were placed
+$\sim 7$km apart on a $6\times6$ grid.
 In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
@@
 Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
-rendered the raw images, over which the estimation algorithm
-ran. Overall, the distributions, the density order of magnitude and
+rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
 values are consistent.
@@
 the algorithm of \cref{sec:inverse-problem}.
+\newcolumntype{g}{>{\columncolor{Gray}}r}
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{cccccg}
+    \toprule
+    Scene  & Forward & Aerosol & Isotropic     & Absorbing & $\epsilon$ \\
+           & model&   density & Phase function? & aerosol?   & \\
+     \midrule
+    Haze Front & Single scatter & Low & & & 0.18 \\
+          & Monte Carlo & Low & & & 0.65 \\
+    \cmidrule(r){1-5}
+    Haze Blobs & Single scatter & Low & & & 0.14 \\
+     & Monte Carlo & Low & & & 0.65 \\
+     & Monte Carlo & Low & $\surd$  & & 0.49 \\
+     & Monte Carlo & Low & & $\surd$ & 0.83 \\
+     & Monte Carlo & High & & & 0.98 \\
+    \bottomrule
+  \end{tabular}
+  \caption{Relative error measure in various simulations}
+  \label{tbl:mass}
+\end{table}
 The overall mass is recovered, but for 6.5\% loss. \\
-
-% at various grid
-%resolutions.  Depending directly on the area grid finesse, $N_{\rm
-%  views}$ varied from 12 to 100.
-%
-%
-%For local errors,
-% $\epsilon=\|
-%\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
-%  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
-%$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
-%$\epsilon=0.65$.
 
@@
   \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
-  \caption{\small Relative error $\epsilon$ measure as function of the number of
+  \caption{\small The relative error $\epsilon$ measure decreases with the number of
     cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
@@
 $[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
-[0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
-Sample results are shown in Figs.~\ref{fig:simulation_particles}(a)--(d) and in Table~\ref{tbl:mass}.\\
-
-\newcolumntype{g}{>{\columncolor{Gray}}r}
-\begin{table}[htbp]
+[0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
+\begin{figure}[h]
   \centering
-  \begin{tabular}{cccccg}
-    \toprule
-    Haze Scene & Forward Model& Density & Isotropic PF & Absorbing & $\epsilon$ \\
-    \midrule
-    Front & Single & Low & & & 0.18 \\
-     & MC & Low & & & 0.65 \\
-    \cmidrule(r){1-5}
-    Blobs & Single & Low & & & 0.14 \\
-     & MC & Low & & & 0.65 \\
-     & MC & Low & $\surd$  & & 0.49 \\
-     & MC & Low & & $\surd$ & 0.83 \\
-     & MC & High & & & 0.98 \\
-    \bottomrule
-  \end{tabular}
-  \caption{Local error for the various reconstruction simulations}
-  \label{tbl:mass}
-\end{table}
+  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
+  \caption{\small Images simulated by MC, from the same viewpoint, but different
+  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}.
+    high. (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
+  \label{fig:simulation_particles}
+\end{figure}
+Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b) 
+\begin{figure}[h]
+  \centering
+  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
+  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
+    isotropic (b) or highly dense (c).}
+  \label{fig:reconstructions}
+\end{figure}
+and in Table~\ref{tbl:mass}.\\
 
@@
 of high order scattering, as shown in \cref{fig:cross_sections}(b) and
-\cref{fig:simulation_particles}(c). Consequently, $\epsilon$ increases,
+\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases,
 when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
@@
 
-%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
-%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
-%This admits to the fact that the single-scattering model, on which the reconstruction
-%algorithm is based, is valid when the optical depth of the medium is small.}
-\begin{figure}[h]
-  \centering
-  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
-  \caption{\small (a) and (b) show MC simulations of low and
-    high density scenes, respectively. (c) shows the reconstruction of
-    the high density scene.}
-  \label{fig:simulation_particles}
-\end{figure}
-\begin{figure}[h]
-  \centering
-  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
-  \caption{\small (a) and (b) show MC simulations of low and
-    high density scenes, respectively. (c) shows the reconstruction of
-    the high density scene.}
-  \label{fig:reconstructions}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We describe a way to sense the 3D atmosphere. It can help remote
-sensing departing from common 1D aerosol distribution models, in favor
+sensing depart from common 1D aerosol distribution models, in favor
 of detailed 3D RT analysis.  The paper describes both a novel data
@@
 distributions. Using more prior knowledge on the nature of
-distributions will improve the recovery.  The estimation algorithm
+distributions will improve the recovery.
+
+The estimation algorithm
 uses a single scattering model. This approximation is valid when the
-optical depth is small. However, as the MC simulation show, it is
-important to generalize this algorithm so that it explicitly
-incorporates high-order scattering in the scene, including the
-ground. This will certainly be needed for dense distributions as
-clouds. \Cref{fig:scatter_order}(b) \hl{suggests that incorporating
-the second order of scattering might be sufficient for most situations.}
-
-To deploy such a system on a very large scale will require a long-term
-engineering effort. Camera specifications~\cite{Pust2011} should be
+optical depth is small. However, as MC simulations show, it is
+important to generalize the recovery algorithm so that high-order scattering 
+is included in it. Such generalization would be computationally complex: 
+in our tests, the MC forward model was slower by 2-3 orders of magnitude than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering model requires research into
+numerical schemes for increasing the solution efficiency of both forward and inverse problems.  
+The remote sensing community has devised several approaches to better approximate multiple-scattering problems, mainly in 1D scenes.
+These include successive orders of scattering, DISORT.....
+We may tap into some of these approaches.
+Deploying an experimental system will be needed: camera specifications~\cite{Pust2011} should be
 set to optimally recover a wide range of aerosol distributions.
@@
 \label{sec:acknowledgments}
+
+BSF!!!!
 

### 2013-10-03 article.tex
bookmark

@@
 from the same viewpoint as \cref{fig:simulation-results1}(a).
-Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
-cross sections of the viewed field, extracted from the images in
-\cref{fig:simulation-results1}(d) and the corresponding MC derived photograph.
-These plots demonstrate consistency in these cases, for most pixels.
+\Cref{fig:cross_sections} plots the intensity profile
+along a horizontal cross section of the viewed field, 
+comparing photographs simulated using the single-scattering and the  MC forward models.
+\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
+and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
+This plot demonstrates consistency in this scene, for most pixels.
+\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
+where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
+and the corresponding MC photograph \cref{fig:simulation_particles}(d)). 
+In this plot the single-scattering and MC cross sections diverge
+due to the effect of the high order scattering.
 \begin{figure}[t]
@@
     by the single-scattering and MC forward models. 
-    (a) cross sections of low density simulations (\cref{fig:simulation-results1}(d)
+    (a) cross sections of the low density scene (\cref{fig:simulation-results1}(d)
     and \cref{fig:simulation_particles}(a)). (b) cross sections of
-    high density simulations (\cref{fig:simulation_particles}(d)).
+    the high density scene (\cref{fig:simulation_particles}(d)).
   }
@@
 is included in it. Such generalization would be computationally complex: 
-in our tests, the MC forward model was slower by 2-3 orders of magnitude than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering model requires research into
-numerical schemes for increasing the solution efficiency of both forward and inverse problems.  
-The remote sensing community has devised several approaches to better approximate multiple-scattering problems, mainly in 1D scenes.
-These include successive orders of scattering, DISORT.....
-We may tap into some of these approaches.
-Deploying an experimental system will be needed: camera specifications~\cite{Pust2011} should be
-set to optimally recover a wide range of aerosol distributions.
+in our tests, the MC forward model was slower by 2-3 orders of magnitude
+than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
+model requires research into numerical schemes for increasing the solution
+efficiency of both forward and inverse problems.  
+The remote sensing community has devised several approaches to better approximate
+multiple-scattering problems, mainly in 1D scenes (e.g. successive
+orders of scattering and discrete ordinates method). We may tap into some of these approaches.
+Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
+should be set to optimally recover a wide range of aerosol distributions.
 \hl{The relation between the quantity and spatial distribution of

### 2013-10-03 opex2013_reply.tex
added reply

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{datetime}
\usepackage{nicefrac}

\topmargin      -0.0truein%do not change
\oddsidemargin   0.0truein%do not change
\evensidemargin  0.0truein%do not change
\textheight     8.5truein%do not change
\textwidth      6.3truein%do not change

\parskip 0.3cm
\parindent=0pt

%\pagestyle{empty}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{.5cm} \hrule

\def\sender{
  \it{Amit Aides}\\
  \scriptsize{Dept. of Electrical Engineering, Technion - Israel Inst.~Technology, Haifa 32000, Israel.}\\
  \scriptsize{Tel No.: (+972) 54-4526416}\hspace{5pt}\\
  \scriptsize{E-mail: amitibo@tx.technion.ac.il} } {\sender}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.5cm}
\noindent
To:\\
Dr. James Churnside,\\
Editor,\\
Associate Editor, Optics Express\\[0.6cm]

\begin{flushright}
  \today
\end{flushright}

\vspace{0.3cm} \noindent

Dear Dr. Churnside,

We are pleased to submit our revised manuscript {\em Multi sky-view 3D
  aerosol distribution recovery}, (195261).  We have addressed all the
requests made by the reviewers. The changes made to the manuscript are
detailed in the following pages. We thank the reviewers for their
helpful comments and hope that the paper in its current form satisfies
your requirements.

We look forward to hearing from you,\\

\vspace{0.2cm} Sincerely,

\vspace{0.6cm}
Amit Aides and Yoav Schechner\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% if the letter runs to a second page, or longer, the following lines
% must be inserted on the second page to prevent the heading and
% footer from appearing
\newpage

{\Large Changes Following the Comments by the Reviewers}\\

We would like to thank the reviewers for their general approval. In
the following we describe the changes made to the manuscript following
their remarks. Each reviewer's comment is summarized (colored in
blue), followed by our reply.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REVIEWER I
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \underline {\bf Reviewer 1}

We appreciate the reviewer's comment. We address it below.

\begin{enumerate}

\item \textcolor{blue}{ ``The paper can be devided in two parts, one
    for computing single scattering, the other for multiple
    scattering. While the first part can be treated by a simple
    inverse transformation sampling as presented by the authors, the
    second part should have a different more complex inversion. For
    this reason I think that larger errors arise in multiple
    scattering. I feel the authors should dedicate some time to review
    this second part, that is more realistic."}

  {}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REVIEWER II
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \underline {\bf Reviewer 2}

Reviewer 2 sees the paper as novel, highly relevant and well written.
The reviewer suggests that the paper is well worth publishing and
recommends accepting the paper after a minor revision.  We thank the
reviewer for his general approval. Below we address his/her comments:

\begin{enumerate}

%%%%%%%%%%%%%%%%
\item \textcolor{blue}{``I don’t understand Eq 9. If $F(u) =
    1-\exp(-u)$ how is $\nicefrac{1}{F} = -\ln(1-u)$?''}

  {There is no contradiction. The notation $F^{-1}$ refers to the
    inverse function of function $F$ and not to $\nicefrac{1}{F}$}

%%%%%%%%%%%%%%%%
\item \textcolor{blue}{ ``Maybe define $\mu$ and voxel''}

  {Following the reviewer's comment, we have defined $\mu$ after
    Eq.~5, and revised the definition of the term ``voxel''. }

%%%%%%%%%%%%%%%%

\item \textcolor{blue}{ ``How do you predefine the voxels
    vertically?''}

  {}

%%%%%%%%%%%%%%%%

\item \textcolor{blue}{ ``The result of the example (sec. 8) could be
    a little more precise in the sense that non-specialists get a
    clear idea of how your method works and which aerosol properties
    hinder or favor retrieval.''}

  {}

%%%%%%%%%%%%%%%%

\item \textcolor{blue}{ ``How many cameras in which distance do you
    need to obtain feasible results for the case of Sec. 5?''}

  {}

\end{enumerate}

\end{document}

### 2013-10-03 article.tex
bookmark.

@@
 had width, length and thickness of $5{\rm km}\times 5{\rm km} \times
-0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.  Each
+0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.
+\hl{We use finer vertical resolution to provide for higher variability
+of air and aerosols distribution in the vertical dimension.} Each
 ground-based camera has a hemispherical field of view, and low

### 2013-10-03 opex2013_reply.tex
bookmark.

@@
 
-\item \textcolor{blue}{ ``The paper can be devided in two parts, one
+\item \textcolor{blue}{ ``The paper can be divided in two parts, one
     for computing single scattering, the other for multiple
@@
 
-  {}
+  {
+    The reviewer raises a good point. Inverting the radiation transfer
+    in the presence of multiple-scattering is the ``Holy Grail''
+    of RT researchers. As far as we know there are no methods to
+    solve this problem in the general case of non-homogeneous 3D
+    atmosphere. Solutions are known only for a limited set of 
+    situations.
+
+    In this article we describe a novel data acquisition system
+    and suggest a method to recover the 3D atmosphere based on
+    the single-scattering approximation. Following the reviewer's
+    suggestion we checked the limitations of the approximation
+    by testing it in situations prone to high order of scatterings.
+    Figures~5(b), 9(d) and 10(c) shows the results of applying
+    out algorithm in a scene with dense aerosols distribution.
+    Section~8 further discusses this experiment.
+  }
 
@@
 
-  {There is no contradiction. The notation $F^{-1}$ refers to the
-    inverse function of function $F$ and not to $\nicefrac{1}{F}$}
+  {The notation $F^{-1}$ refers to the inverse function
+   of function $F$ and not to $\nicefrac{1}{F}$.}
 
@@
 
-  {Following the reviewer's comment, we have defined $\mu$ after
-    Eq.~5, and revised the definition of the term ``voxel''. }
+  {We thank the reviewer for turning our attention to this.
+   We replaced $\mu$ in Eq.~5 with its definition,
+   $\cos \Phi^{\rm scatter})$. We revised the definition
+   of the term ``voxel'', at the beginning of Sec.~4.}
 
@@
 
-  {}
+  {
+    We now explain our vertical division of the atmosphere at the
+    beginning of Sec.~5.
+  }
 
@@
 
-  {}
+  {
+    We appreciate the reviewer's comment. The issue raised by the
+    reviewer is now discussed in Sec.~8. We also added Table~1 and
+    Figs.~9 and 10, which show results of varying different properties
+    of the aerosols and their distribution.
+  }
 
@@
 
-  {}
+  {Following this comment, we tested  repeated the reconstruction
+   simulations many times, each time varying the distance between
+   cameras. The results are described in Sec.~8 and Fig.~8.}
 

### 2013-10-03 article.tex
bookmark

@@
     by the single-scattering and MC forward models. 
-    (a) cross sections of the low density scene (\cref{fig:simulation-results1}(d)
+    (a) cross sections of the {\em Haze Blobs} scene (\cref{fig:simulation-results1}(d)
     and \cref{fig:simulation_particles}(a)). (b) cross sections of
-    the high density scene (\cref{fig:simulation_particles}(d)).
+    the increased aerosol density scene (\cref{fig:simulation_particles}(d)).
   }
@@
 render the images, since high-order scattering is not accounted for in
-the algorithm of \cref{sec:inverse-problem}.
 \newcolumntype{g}{>{\columncolor{Gray}}r}
@@
   \centering
-  \begin{tabular}{cccccg}
+  \begin{tabular}{cccccgg}
     \toprule
-    Scene  & Forward & Aerosol & Isotropic     & Absorbing & $\epsilon$ \\
-           & model&   density & Phase function? & aerosol?   & \\
+    Scene      & Forward        & Aerosol density & Isotropic       & Absorbing & $\epsilon$ & Mass \\
+               & model          & order           & Phase function? & aerosol?  &            & diff. \\
      \midrule
-    Haze Front & Single scatter & Low & & & 0.18 \\
-          & Monte Carlo & Low & & & 0.65 \\
+    Haze Front & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
+               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
     \cmidrule(r){1-5}
-    Haze Blobs & Single scatter & Low & & & 0.14 \\
-     & Monte Carlo & Low & & & 0.65 \\
-     & Monte Carlo & Low & $\surd$  & & 0.49 \\
-     & Monte Carlo & Low & & $\surd$ & 0.83 \\
-     & Monte Carlo & High & & & 0.98 \\
+    Haze Blobs & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
+               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
+               & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\
+               & Monte Carlo    & $10^{6}$         &                 & $\surd$   & 0.83       & 9.6\%  \\
+               & Monte Carlo    & $10^{7}$         &                 &           & 0.98       & 23\%  \\
     \bottomrule
@@
 \end{table}
-The overall mass is recovered, but for 6.5\% loss. \\
+the algorithm of \cref{sec:inverse-problem}. \\
 

### 2013-10-03 article.tex
fixing the table size

@@
     \toprule
-    Scene      & Forward        & Aerosol density & Isotropic       & Absorbing & $\epsilon$ & Mass \\
-               & model          & order           & Phase function? & aerosol?  &            & diff. \\
+    Scene      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon$ & Mass \\
+               & model          & density order    & Phase function? & aerosol?  &            & diff. \\
      \midrule
-    Haze Front & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
-               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
+    Haze       & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
+    Front      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
     \cmidrule(r){1-5}
-    Haze Blobs & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
-               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
+    Haze       & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
+    Blobs      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
                & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\

### 2013-10-04 article.tex
bookmark

@@
 As illustrated in \cref{fig:groundgrid,fig:distributions},
-The sky is discretized into a grid of $N_{\rm voxels}$ rectangular cuboid volume elements
+the sky is discretized into a grid of $N_{\rm voxels}$ rectangular cuboid volume elements
 (voxels), indexed by $k$, $m$ or $q$.
@@
 once on the way to a camera. This model is valid in atmospheres that
-are not very dense: inside fog and clouds this model does not
-apply. In this model, RT has three steps (\cref{fig:groundgrid}):
-({\tt i}) Attenuation of a SR propagating from the top of the
-atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
-$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
+are not very dense (inside fog and clouds this model does not
+apply). Here, RT has three steps (\cref{fig:groundgrid}):
+({\tt i})~Attenuation of a SR propagating from the top of the
+atmosphere (TOA) to voxel $k$. ~({\tt ii})~Light scattering at voxel
+$k$, towards a camera. ~({\tt iii})~Light attenuation on the LOS from
 voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
-depth along the light path to and from voxel $k$, as analyzed in
-\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
-coefficient at voxel $k$, described in \cref{sec:scattering}.
+depth along the light path to and from voxel $k$ (analyzed in
+\cref{sec:optical-depth}).  Step~{\tt ii} involves the scattering
+coefficient at voxel $k$ (\cref{sec:scattering}).
 
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the radiant power
-contributed by the voxel is
+(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the voxel contributes radiant power
 \begin{equation}
@@
 0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.
-\hl{We use finer vertical resolution to provide for higher variability
-of air and aerosols distribution in the vertical dimension.} Each
+In all cases, the vertical resolution was higher than horizontal, via use
+of voxels that are vertically thin but laterally wide. This expresses the natural 
+higher variability of air and aerosols in the vertical dimension. Each
 ground-based camera has a hemispherical field of view, and low
@@
 \end{align}
-Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields the 3D position ${\bf
+Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields 3D position ${\bf
   X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
@@
 that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
-randomly by the relative \hl{scattering coefficients
-($\vect{\alpha}^{\rm air}$ and $\vect{\alpha}^{\rm aerosol}$} respectively)
-at the voxel containing ${\bf X}_{i}$.
-
-\noindent ({\tt iv}) If it is an aerosol, the photon-packet intensity
+randomly. The relative probabilities of this random step are set by the respective extinction coefficients
+($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.
+
+\noindent ({\tt iv}) If the particle is an aerosol, the photon-packet intensity
 is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
@@
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
-Estimation~\cite{marshak20053d} is used for calculating the amount of
+estimation~\cite{marshak20053d} derives the amount of
 light back-traced to the sun at each scattering. The next iteration of
@@
   \caption{\small Cross-sections along the $X$-axis of photographs rendered
-    by the single-scattering and MC forward models.
+    by the single-scattering (dotted) and MC (solid line) forward models.
     (a) cross sections of the {\em Haze Blobs} scene (\cref{fig:simulation-results1}(d)
-    and \cref{fig:simulation_particles}(a)). (b) cross sections of
-    the increased aerosol density scene (\cref{fig:simulation_particles}(d)).
+    and \cref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
+    when the scatterers are ten times denser, corresponding to \cref{fig:simulation_particles}(d).
   }
@@
 scattering orders. They are derived from the MC image. Photons contributing
-to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
+to any pixel are accumulated in steps {\tt ii},{\tt v} above.
 The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a).
 Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
-\cref{fig:scatter_order}(c). Clearly, first-order scatter is responsible
-for most of the energy in the MC image. Radiance by higher order scattering
+\cref{fig:scatter_order}(c). First-order scatter yields
+most of the energy in the MC image. Radiance by higher order scattering
 is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
@@
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
+  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
+   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
   \label{fig:scatter_order}
@@
 \end{equation}
-Here $\MaskSun$ masks the area around the sun, as in real-world images
+Here $\MaskSun$ masks the area around the sun: in real-world images
 it is indeed blocked.
-We mask the horizon, by using a camera whose field of view is a bit smaller than hemispherical.
-This reduces the influence of image regions that are more strongly affected by high-order scattering (\cref{fig:scatter_order}(b)).
+We mask the horizon, by using a camera whose field of view is a little narrower than hemispherical.
+This reduces the influence of LOSs that are more strongly affected by high-order scattering (\cref{fig:scatter_order}(b)).
 Consequently,
-the fit of the image formation model focuses on the bulk image region, where the single scattering model is more valid.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
+the fit of the imaging model focuses on the bulk image region, where the single scattering model is more valid.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
 is a regularization term that expresses some prior knowledge on the
@@
   n}\|^2_2$. Regularization is not required when data is sufficient
-and reliable. As seen in \cref{fig:groundgrid}, voxels at high
-altitude have good coverage by many cameras at multiple directions,
+and reliable.  Voxels at high
+altitude have good coverage by many cameras at multiple directions (\cref{fig:groundgrid}),
 while low altitude voxels are mainly observed by local
@@
 the total mass relative difference is
-$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
+$\delta_{\rm mass}=(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
 To also sense local errors, we use
@@
 original distributions of \cref{fig:distributions}.
-\begin{figure}[h]
+\begin{figure}[t]
   \centering
   \yoavcomment{\includegraphics{images/results}}
-  \caption{\small Reconstructions of the scenes shown in
-    \cref{fig:distributions}. Color represents aerosol density. The
-    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
-    single-scattering simulated images are used as input to the
+  \caption{\small Recoveries of scenes shown in
+    \cref{fig:distributions}. Color represents aerosol density, in
+    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
+    images simulated by single-scattering are used as input for the
     recovery.  In (c) and (d), MC simulated images are used as input for the
@@
 \newcolumntype{g}{>{\columncolor{Gray}}r}
-\begin{table}[htbp]
+\begin{table}[t]
   \centering
@@
     \toprule
-    Scene      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon$ & Mass \\
-               & model          & density order    & Phase function? & aerosol?  &            & diff. \\
+    Haze      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon~~$ & $\delta_{\rm mass}$ \\
+    scene     & model          & density [$1/{\rm m}^3$]    & phase function? & aerosol?  &            &  \\
      \midrule
-    Haze       & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
-    Front      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
+    Front       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 18\%       & 1.1\%  \\
+               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 14\%  \\
     \cmidrule(r){1-5}
-    Haze       & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
-    Blobs      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
-               & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\
-               & Monte Carlo    & $10^{6}$         &                 & $\surd$   & 0.83       & 9.6\%  \\
-               & Monte Carlo    & $10^{7}$         &                 &           & 0.98       & 23\%  \\
+     Blobs       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 14\%       & 0\%  \\
+               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 6.7\%  \\
+               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         & $\surd$         &           & 49\%       & 2\%  \\
+               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 & $\surd$   & 83\%       & 9.6\%  \\
+               & Monte Carlo    & ${\mathcal{O}}(10^{7})$         &                 &           & 98\%       & 23\%  \\
     \bottomrule
   \end{tabular}
-  \caption{Relative error measure in various simulations}
+  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
   \label{tbl:mass}
@@
 \noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
-repeated the reconstruction many times, each time using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
+repeated the reconstruction many times, each using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
 of $N_{\rm views}< 36$. All rendered images used MC.
-\Cref{fig:error_vs_cameras} plots $\epsilon$ as a function $N_{\rm views}$.
+\Cref{fig:error_vs_cameras} plots the performance.
 \begin{figure}[t]
@@
 \end{figure}
-Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints.\\
+Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints.
+These tests point to fundamental questions about spatial-angular sampling: how spatially dense should cameras be, and how dense should a camera's field of view be sampled (in pixels)?
+This likely depends on the finesse of atmospheric structure sought, and the level of optical diffusion achieved by various aerosols.
+The novel tomography domain introduced here thus raises new important questions that will   require extensive further research.\\
 
@@
 [0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
-\begin{figure}[h]
+\begin{figure}[b]
   \centering
@@
   aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
-    high. (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
+  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
   \label{fig:simulation_particles}
@@
 Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b)
-\begin{figure}[h]
+\begin{figure}[b]
   \centering
@@
   \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
-    isotropic (b) or highly dense (c).}
+    has isotropic phase function (b) or has high density (c).}
   \label{fig:reconstructions}
 \end{figure}
-and in Table~\ref{tbl:mass}.\\
+and in Table~\ref{tbl:mass}.
+The results indicate that if the aerosol's phase function has smaller anisotropy, recovery of the aerosol's density is easier.
+We hypothesise that tomography is better served by scattering isotropy, since then significant radiance from any voxel reach cameras in a wide range of directions.
+This may make back-projection (recovery from cameras to voxels) more accurate.
+On the other hand, if the phase function is strongly peaked around one direction, most cameras would not receive much radiance.
+
+ that have mo\\
 
@@
 The remote sensing community has devised several approaches to better approximate
-multiple-scattering problems, mainly in 1D scenes (e.g. successive
-orders of scattering and discrete ordinates method). We may tap into some of these approaches.
+multiple-scattering problems, mainly in one-dimensional models (e.g., successive
+orders of scattering and discrete ordinates methods). We may tap into some of these approaches.
 Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
 should be set to optimally recover a wide range of aerosol distributions.
-\hl{The relation between the quantity and spatial distribution of
-  cameras and the quality of reconstruction should also be determined.}
-\fix{This requires}{These open questions require} a major theoretic
- and numerical research.
+%\hl{The relation between the quantity and spatial distribution of
+%  cameras and the quality of reconstruction should also be determined.}
+%\fix{This requires}{These open questions require} a major theoretic
+% and numerical research.
 
@@
 
-BSF!!!!
-
-We thank David~J. Diner for useful discussions. Yoav Schechner is a
-Landau Fellow - supported by the Taub Foundation. This work was
-conducted in the Ollendorff Minerva Center. Minerva is funded through
-the BMBF. Part of this work was performed at the Jet Propulsion
-Laboratory, California Institute of Technology, under contract with
-NASA.
+We are grateful to David~J.
+Diner for fruitful discussions and his support at all levels.
+We thank the reviewers for useful comments.
+Yoav Schechner is a Landau Fellow - supported by the Taub Foundation.
+This work is supported by the US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the Ollendorff Minerva Center.
+Minerva is funded through the BMBF.
+Part of this work is performed at the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with NASA. 
+%The work in Caltech was partly supported by ONR-Global grant  N62909-10-1-4056.
 

### 2013-10-04 article.tex
bookmark

@@
 This likely depends on the finesse of atmospheric structure sought, and the level of optical diffusion achieved by various aerosols.
-The novel tomography domain introduced here thus raises new important questions that will   require extensive further research.\\
+The novel tomography domain introduced here thus raises new theoretical questions that will   require extensive further research.\\
 
@@
 This may make back-projection (recovery from cameras to voxels) more accurate.
-On the other hand, if the phase function is strongly peaked around one direction, most cameras would not receive much radiance.
-
- that have mo\\
+On the other hand, if the phase function is too strongly peaked around one direction, most cameras would not receive much scattered radiance from a voxel, undermining tomography.
+A very broad research is needed to verify and quantify such dependencies.\\
 
@@
 We describe a way to sense the 3D atmosphere. It can help remote
-sensing depart from common 1D aerosol distribution models, in favor
+sensing depart from common one-dimensional aerosol distribution models, in favor
 of detailed 3D RT analysis.  The paper describes both a novel data
@@
 multiple-scattering problems, mainly in one-dimensional models (e.g., successive
-orders of scattering and discrete ordinates methods). We may tap into some of these approaches.
+orders of scattering and the discrete ordinates method). We may tap into some of these approaches.
 Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}

### 2013-10-04 article.tex
bookmark

--- 2013-10-04 article.tex
@@
 photographs of the {\em Haze Blobs} scene, as simulated by
-\cref{eq:bigIA}.
+\cref{eq:bigIA}. \hl{Figs. 6.3 to Fig. 6.14 in every comparison, for display purposes both images underwent same contrast streching operations, and used the same colormap}.
 
@@
     \toprule
-    Haze      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon~~$ & $\delta_{\rm mass}$ \\
+    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
     scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
      \midrule                                                                                             
-    Front       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 18\%       & 1.1\%  \\
-               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 14\%  \\
+    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 1.1\%               & 18\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -14\%               & 65\%         \\
     \cmidrule(r){1-5}                                                                                     
-     Blobs       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 14\%       & 0\%  \\
-               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 6.7\%  \\
-               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         & $\surd$         &           & 49\%       & 2\%  \\
-               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 & $\surd$   & 83\%       & 9.6\%  \\
-               & Monte Carlo    & ${\mathcal{O}}(10^{7})$         &                 &           & 98\%       & 23\%  \\
+     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 6.7\%               & 65\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & -2\%                & 49\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & 9.6\%               & 83\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & 23\%                & 98\%         \\
     \bottomrule

### 2013-10-06 article.tex
Last fixes by Yoav and proof reading of the new sections by me.

@@
 \usepackage{colortbl}
+\usepackage{endnotes}
 
@@
 distribution function (CDF) is $F(X)$. The transform is $X =
-F^{-1}(u)$.
+F^{-1}(u)$, where $F^{-1}$ denotes the inverse function of $F$.
 
@@
 photographs of the {\em Haze Blobs} scene, as simulated by
-\cref{eq:bigIA}. \hl{Figs. 6.3 to Fig. 6.14 in every comparison, for display purposes both images underwent same contrast streching operations, and used the same colormap}.
+\cref{eq:bigIA}. \endnote{For clarity of display, the brightness of the
+displayed pictures in this paper underwent the same standard
+contrast enhancement (stretching), including gamma-correction.
+The recovery algorithms, of course, have used the raw (not brightness
+enhanced) images.}
 
@@
 scattering orders. They are derived from the MC image. Photons contributing
-to any pixel are accumulated in steps {\tt ii},{\tt v} above.
-The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a).
-Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
-\cref{fig:scatter_order}(c). First-order scatter yields
-most of the energy in the MC image. Radiance by higher order scattering
-is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
-towards the horizon the probability of high order scattering increases.
+to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
+The contributing photons that stem from just a single scattering event yield
+\cref{fig:scatter_order}(a). Similarly, contributing photons that had
+experienced exactly  two or three scattering events yield respectively
+\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
+scatter yields most of the energy in the MC image. Radiance by higher order scattering
+is mostly evident at the horizon. A horizontal LOS passes through a long
+and dense part of the atmosphere, while a vertical LOS cuts short through
+the dense, lower part. Hence, toward the horizon the probability of high
+order scattering increases.
 \begin{figure}[bt]
@@
 Here $\MaskSun$ masks the area around the sun: in real-world images
-it is indeed blocked.
-We mask the horizon, by using a camera whose field of view is a little narrower than hemispherical.
-This reduces the influence of LOSs that are more strongly affected by high-order scattering (\cref{fig:scatter_order}(b)).
-Consequently,
-the fit of the imaging model focuses on the bulk image region, where the single scattering model is more valid.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
-is a regularization term that expresses some prior knowledge on the
-distribution, while $\eta$ is the regularization weight.
+it is indeed blocked. We mask the horizon, by using a camera whose
+field of view is a little narrower than hemispherical. This reduces
+the influence of LOSs that are more strongly affected by high-order
+scattering (\cref{fig:scatter_order}(b)). Consequently,
+the fit of the imaging model focuses on the bulk image region, where
+the single scattering model is more valid.  In \cref{eq:objectiveA},
+$\Psi({\bm n})$ is a regularization term that expresses some prior
+knowledge on the distribution, while $\eta$ is the regularization weight.
 
@@
 $\sim 7$km apart on a $6\times6$ grid.
-In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
+In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
 used both in rendering of the raw images, and in the estimation algorithm. In
-Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
-rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
-values are consistent.
-Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
+Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
+rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
+Overall, the distributions, the density order of magnitude and values are consistent.
+Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
 been induced in the raw images. Errors are larger when MC is used to
@@
      \midrule                                                                                             
-    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 1.1\%               & 18\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -14\%               & 65\%         \\
+    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
     \cmidrule(r){1-5}                                                                                     
      Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 6.7\%               & 65\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & -2\%                & 49\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & 9.6\%               & 83\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & 23\%                & 98\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -9.6\%               & 83\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
     \bottomrule
@@
 \noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
-repeated the reconstruction many times, each using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
+repeated the reconstruction many times, each using a different subset of the above mentioned
+36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
 of $N_{\rm views}< 36$. All rendered images used MC.
@@
 \end{figure}
-Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints.
-These tests point to fundamental questions about spatial-angular sampling: how spatially dense should cameras be, and how dense should a camera's field of view be sampled (in pixels)?
-This likely depends on the finesse of atmospheric structure sought, and the level of optical diffusion achieved by various aerosols.
-The novel tomography domain introduced here thus raises new theoretical questions that will   require extensive further research.\\
+Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km
+separation between neighboring viewpoints. These tests point to fundamental questions about
+spatial-angular sampling: how spatially dense should cameras be, and how dense should a
+camera's field of view be sampled (in pixels)? This likely depends on the finesse of
+atmospheric structure sought, and the level of optical diffusion achieved by various
+aerosols. The novel tomography domain introduced here thus raises new theoretical questions
+that will   require extensive further research.\\
 
@@
 $[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
-[0.69,0.74,0.78]$.  All rendered images used MC (See Figs.~\ref{fig:simulation_particles}(a)--(c)).
+[0.69,0.74,0.78]$.  All rendered images used MC
+(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
 \begin{figure}[b]
@@
 \end{figure}
-Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a,b)
+Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
+and \ref{fig:reconstructions}(b)
 \begin{figure}[b]
@@
 \end{figure}
-and in Table~\ref{tbl:mass}.
-The results indicate that if the aerosol's phase function has smaller anisotropy, recovery of the aerosol's density is easier.
-We hypothesise that tomography is better served by scattering isotropy, since then significant radiance from any voxel reach cameras in a wide range of directions.
-This may make back-projection (recovery from cameras to voxels) more accurate.
-On the other hand, if the phase function is too strongly peaked around one direction, most cameras would not receive much scattered radiance from a voxel, undermining tomography.
-A very broad research is needed to verify and quantify such dependencies.\\
+and in \cref{tbl:mass}. The results indicate that if the aerosol's phase function
+has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesize that
+tomography is better served by scattering isotropy, since then significant radiance from
+any voxel reaches cameras in a wide range of directions. This may make back-projection
+(recovery from cameras to voxels) more accurate. On the other hand, if the phase function
+is too strongly peaked around one direction, most cameras would not receive much scattered
+radiance from a voxel, undermining tomography. A very broad research is needed to verify
+and quantify such dependencies.\\
 
@@
 of high order scattering, as shown in \cref{fig:cross_sections}(b) and
-\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases,
+\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases (\cref{tbl:mass}),
 when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
@@
 
-We are grateful to David~J.
-Diner for fruitful discussions and his support at all levels.
-We thank the reviewers for useful comments.
-Yoav Schechner is a Landau Fellow - supported by the Taub Foundation.
-This work is supported by the US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the Ollendorff Minerva Center.
-Minerva is funded through the BMBF.
-Part of this work is performed at the Jet Propulsion
-Laboratory, California Institute of Technology, under contract with NASA. 
-%The work in Caltech was partly supported by ONR-Global grant  N62909-10-1-4056.
+We are grateful to David~J. Diner for fruitful discussions and his support at all
+levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
+Fellow - supported by the Taub Foundation. This work is supported by the
+US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
+Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
+by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.
+
+\theendnotes
 

### 2013-10-07 opex2013_reply.tex
Last fixes by Yoav and proof reading of the new sections by me.
updated the reply to reviewers

--- 2013-10-03 opex2013_reply.tex
@@
 \usepackage{datetime}
+\usdate
 \usepackage{nicefrac}
+
+%% fonts
+\usepackage{mathptmx,courier,textcomp}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bm}
+\usepackage{xfrac}
+
+\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
+
+%
+% Some new commands I use in this text
+%
+% Note:
+% Nice curly font is {\bm{\mathcal{D}}}
+%
+\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
+\newcommand{\abbrev}[1]{\rm{#1}}
+\newcommand{\argmin}{\mathrm{arg}\min}
+\newcommand{\curly}[1]{\left\{#1\right\}}
+\newcommand{\roundy}[1]{\left(#1\right)}
+\newcommand{\recty}[1]{\left[#1\right]}
+\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
+\newcommand{\vect}[1]{\bm{#1}}
+\newcommand{\mat}[1]{\bm{#1}}
+\newcommand{\transpose}[1]{{#1}^\intercal}
+\newcommand{\derivsym}[1]{\,d{#1}}
+\newcommand{\yoavcomment}[1]{}
+\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
+\newcommand{\fix}[2]{\st{#1}\hl{#2}}
+
+%
+% Used symbols (only partial for now...)
+%
+\newcommand{\OpSphere}{\mathbfcal{S}}
+\newcommand{\OpRot}{\mathbfcal{R}}
+\newcommand{\OpDistance}{\bm{D}}
+\newcommand{\OpCumsum}{\mathbfcal{C}}
+\newcommand{\OpInt}{\mathbfcal{I}}
+\newcommand{\OpCamera}{\mathbfcal{P}}
+\newcommand{\MaskSun}{\mathbfcal{M}}
+\newcommand{\Laplacian}{\mathbfcal{L}}
+\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
+\newcommand{\DistSet}{\mathcal{C}}
+\newcommand{\DistUnknown}{\vect{n}}
+\newcommand{\DistEstimated}{\hat{\vect{n}}}
+\newcommand{\CostFunc}[1]{E(#1)}
 
@@
 Dr. James Churnside,\\
-Editor,\\
 Associate Editor, Optics Express\\[0.6cm]
@@
 \vspace{0.6cm}
-Amit Aides and Yoav Schechner\\
+Amit Aides, corresponding author.\\
 
@@
 
-We would like to thank the reviewers for their general approval. In
-the following we describe the changes made to the manuscript following
-their remarks. Each reviewer's comment is summarized (colored in
+We would like to thank the reviewers for their general approval and useful
+suggestions. In the following we describe the changes made to the manuscript
+following their remarks. Each comment is summarized (colored in
 blue), followed by our reply.
@@
 
-  {}
+  {
+    In this article we describe a novel data acquisition system
+    and suggest a method to recover the 3D atmosphere based on
+    the single-scattering approximation. Following the reviewer's
+    suggestion we expanded our reference to the implications
+    of high order scattering on our method.
+
+    We added the new Fig.~5. In this figure we visually demonstrate
+    the extents to which the single-scattering approximation is valid
+    and to which it is not.
+
+    The newly added Fig.~6 shows the contribution of each scattering order to
+    the final MC image. Figure~6 makes clear that there are regions in
+    the image that are affected by multiple scattering more than others.
+    The two new paragraphs at the end of Sec.~6 reference the issues
+    raised by Fig.~5 and Fig.~6.
+
+    In the top of p.~10 we added a new description of $MaskSun$. We use
+    $MaskSun$ to mask the regions in the image which are dominated 
+    by multi-scattering as shown by Fig.~6. This method improves the
+    results of the reconstruction algorithm.
+
+    We test our reconstruction algorithm on a new scene where we
+    increase the aerosol density tenfold. This significantly increases the
+    effects of high order scattering. The results are shown in 
+    Figs.~9(d) and 10(c), and reported in Table~1.
+    Paragraph ``Density scale'' in Sec.~8 summarizes this experiment.
+    Further discussion is given in Sec.~9.
+  }
 
 \end{enumerate}
+
+\newpage
 
@@
 
-  {There is no contradiction. The notation $F^{-1}$ refers to the
-    inverse function of function $F$ and not to $\nicefrac{1}{F}$}
+  {The notation $F^{-1}$ refers to the inverse function
+   of function $F$ and not to $\nicefrac{1}{F}$. Following the
+   reviewer's comment we added a clarification in the ``Inverse
+   transform sampling'' paragraph on p.~4. }
 
@@
 
-  {Following the reviewer's comment, we have defined $\mu$ after
-    Eq.~5, and revised the definition of the term ``voxel''. }
+  {We thank the reviewer for turning our attention to this.
+   We replaced $\mu$ in Eq.~5 with its definition,
+   $\cos \Phi^{\rm scatter}$. We revised the definition
+   of the term ``voxel'', at the beginning of Sec.~4 of the
+   article.}
 
@@
 
-  {}
+  {
+    We appreciate the reviewer's comment. We added new simulations to
+    test the effect of varying different properties of the aerosols.
+    These experiments are detailed in Sec.~8. The results are shown
+    in Figs.~9 and 10 and reported in Table.~1.
+  }
 
@@
 
-  {}
+  {Following this comment, we repeated the reconstruction
+   simulations many times, each time varying the distance between
+   cameras. These tests are described in the paragraph ``Density of viewpoints''
+   in Sec.~8. The results are shown in Fig.~8.}
 

### 2013-10-08 article.tex
Updated absorbtion error

@@
            & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -9.6\%               & 83\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
            & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\

### 2013-10-08 article.tex
Red-lined version of the article

@@
 \usepackage{endnotes}
+\usepackage{xcolor}
+\usepackage[normalem]{ulem}
 
@@
 \renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
-\newcommand{\fix}[2]{\st{#1}\hl{#2}}
-
+
+%
+% Red-lined version settings
+%
+\newcommand{\del}[1]{\sout{#1}}
+\newcommand{\rl}[1]{\uwave{#1}}
+\newcommand{\fix}[2]{\del{#1}\rl{#2}}
+\newcommand{\rleq}[1]{%
+  \colorbox{red!50}{$\displaystyle#1$}}
 %
@@
   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -g^2)
-  [1+(\cos \Phi^{\rm scatter})^2]}
-  {(2+g^2)(1 + g^2 - 2g\cos \Phi^{\rm scatter})^{\sfrac{3}{2}}}
+  [1+\rleq{(\cos \Phi^{\rm scatter})}^2]}
+  {(2+g^2)(1 + g^2 - 2g\rleq{\cos \Phi^{\rm scatter}})^{\sfrac{3}{2}}}
   \label{eq:aerosol_scatter}
@@
 distribution function (CDF) is $F(X)$. The transform is $X =
-F^{-1}(u)$, where $F^{-1}$ denotes the inverse function of $F$.
+F^{-1}(u)$, \rl{where $F^{-1}$ denotes the inverse function of $F$}.
 
@@
 As illustrated in \cref{fig:groundgrid,fig:distributions},
-the sky is discretized into a grid of $N_{\rm voxels}$ rectangular cuboid volume elements
+the sky is discretized into a grid of $N_{\rm voxels}$ \rl{rectangular cuboid} volume elements
 (voxels), indexed by $k$, $m$ or $q$.
@@
 are not very dense (inside fog and clouds this model does not
-apply). Here, RT has three steps (\cref{fig:groundgrid}):
+apply). \fix{In this model}{Here}, RT has three steps (\cref{fig:groundgrid}):
 ({\tt i})~Attenuation of a SR propagating from the top of the
@@
 voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
-depth along the light path to and from voxel $k$ (analyzed in
+depth along the light path to and from voxel $k$ \del{as} (analyzed in
 \cref{sec:optical-depth}).  Step~{\tt ii} involves the scattering
-coefficient at voxel $k$ (\cref{sec:scattering}).
+coefficient at voxel $k$ \del{described in} (\cref{sec:scattering}).
 
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the voxel contributes radiant power
+(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the \fix{the radiant power contributed by is}{voxel contributes} radiant power
 \begin{equation}
@@
 0.5{\rm km}$ and $1{\rm km}\times 1{\rm km} \times 0.1{\rm km}$.
-In all cases, the vertical resolution was higher than horizontal, via use
+\rl{In all cases, the vertical resolution was higher than horizontal, via use
 of voxels that are vertically thin but laterally wide. This expresses the natural 
-higher variability of air and aerosols in the vertical dimension. Each
+higher variability of air and aerosols in the vertical dimension.} Each
 ground-based camera has a hemispherical field of view, and low
@@
 photographs of the {\em Haze Blobs} scene, as simulated by
-\cref{eq:bigIA}. \endnote{For clarity of display, the brightness of the
+\cref{eq:bigIA}. \endnote{\rl{For clarity of display, the brightness of the
 displayed pictures in this paper underwent the same standard
@@
 The recovery algorithms, of course, have used the raw (not brightness
-enhanced) images.}
+enhanced) images.}}
 
@@
     [b] Photograph of the same sky and view point as in
-    \cref{fig:simulation-results1}(a), rendered using MC.}
+    \cref{fig:simulation-results1}(a), rendered using MC.
+    \del{[c] Cross section along the $X$-Axis of the MC simulation,
+    single-scattering simulation and a single-scattering image created
+    from the reconstructed distribution
+    (Sec.~\ref{sec:optimization-results})}.}
   \label{fig:mcgrid}
@@
 \end{align}
-Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields 3D position ${\bf
+Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields \del{the} 3D position ${\bf
   X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
@@
 that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
-randomly. The relative probabilities of this random step are set by the respective extinction coefficients
-($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.
-
-\noindent ({\tt iv}) If the particle is an aerosol, the photon-packet intensity
+randomly \fix{according to their relative densities at the voxel containing
+${\bf X}_{i}$.}{The relative probabilities of this random step are set by the respective extinction coefficients
+($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.}
+
+\noindent ({\tt iv}) If \fix{it}{the particle} is an aerosol, the photon-packet intensity
 is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
@@
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
-estimation~\cite{marshak20053d} derives the amount of
+estimation~\cite{marshak20053d} \fix{is used for calculating}{derives} the amount of
 light back-traced to the sun at each scattering. The next iteration of
@@
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}(a).
-\Cref{fig:cross_sections} plots the intensity profile
+from the same viewpoint as \cref{fig:simulation-results1}(a). \fix{A
+comparison of a sample horizontal cross section is shown in
+Fig.~\ref{fig:mcgrid}c.}
+{Figure~\ref{fig:cross_sections} plots the intensity profile
 along a horizontal cross section of the viewed field,
 comparing photographs simulated using the single-scattering and the  MC forward models.
-\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
-and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
+Figure~\ref{fig:cross_sections}(a) compares photographs Fig.~\ref{fig:simulation-results1}(d)
+and Fig.~\ref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
 This plot demonstrates consistency in this scene, for most pixels.
-\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
-where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
-and the corresponding MC photograph \cref{fig:simulation_particles}(d)).
+Figure~\ref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
+where the aerosol density was increased ten folds (see Fig.~\ref{sec:optimization-results}
+and the corresponding MC photograph Fig.~\ref{fig:simulation_particles}(d)).
 In this plot the single-scattering and MC cross sections diverge
-due to the effect of the high order scattering.
+due to the effect of the high order scattering.}
 \begin{figure}[t]
@@
   \yoavcomment{\includegraphics{images/cross_sections.pdf}}
-  \caption{\small Cross-sections along the $X$-axis of photographs rendered
+  \caption{\small \rl{Cross-sections along the $X$-axis of photographs rendered
     by the single-scattering (dotted) and MC (solid line) forward models.
-    (a) cross sections of the {\em Haze Blobs} scene (\cref{fig:simulation-results1}(d)
-    and \cref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
-    when the scatterers are ten times denser, corresponding to \cref{fig:simulation_particles}(d).
+    (a) cross sections of the {\em Haze Blobs} scene (Fig.~\ref{fig:simulation-results1}(d)
+    and Fig.~\ref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
+    when the scatterers are ten times denser, corresponding to Fig.~\ref{fig:simulation_particles}(d).}
   }
@@
 
-\Cref{fig:scatter_order} shows the contribution by successive
+\rl{Figure~\ref{fig:scatter_order} shows the contribution by successive
 scattering orders. They are derived from the MC image. Photons contributing
@@
 The contributing photons that stem from just a single scattering event yield
-\cref{fig:scatter_order}(a). Similarly, contributing photons that had
+Fig.~\ref{fig:scatter_order}(a). Similarly, contributing photons that had
 experienced exactly  two or three scattering events yield respectively
-\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
+Fig.~\ref{fig:scatter_order}(b) and Fig.~\ref{fig:scatter_order}(c). First-order
 scatter yields most of the energy in the MC image. Radiance by higher order scattering
@@
 the dense, lower part. Hence, toward the horizon the probability of high
-order scattering increases.
+order scattering increases.}
 \begin{figure}[bt]
@@
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
-   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
+  \caption{\small \rl{Separation of the image shown in Fig.~\ref{fig:mcgrid}(b) to contributions
+   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}}
   \label{fig:scatter_order}
@@
 \end{equation}
-Here $\MaskSun$ masks the area around the sun: in real-world images
-it is indeed blocked. We mask the horizon, by using a camera whose
+Here $\MaskSun$ masks the area around the sun: \del{as} in real-world images
+it is indeed blocked. \rl{We mask the horizon, by using a camera whose
 field of view is a little narrower than hemispherical. This reduces
 the influence of LOSs that are more strongly affected by high-order
-scattering (\cref{fig:scatter_order}(b)). Consequently,
+scattering (Fig.~\ref{fig:scatter_order}(b)). Consequently,
 the fit of the imaging model focuses on the bulk image region, where
-the single scattering model is more valid.  In \cref{eq:objectiveA},
+the single scattering model is more valid.}  In \cref{eq:objectiveA},
 $\Psi({\bm n})$ is a regularization term that expresses some prior
@@
   n}\|^2_2$. Regularization is not required when data is sufficient
-and reliable.  Voxels at high
+and reliable. \del{As seen in Fig.~\ref{fig:groundgrid},}Voxels at high
 altitude have good coverage by many cameras at multiple directions (\cref{fig:groundgrid}),
@@
 
-To demonstrate recovery, we performed simulations, and tested effects of the following variations:
+\rl{To demonstrate recovery, we performed simulations, and tested effects of the following variations:
 $\{1\}$ Multiple or only single scatter in the forward model;
@@
 $\{4\}$ Aerosol characteristics;
-$\{5\}$ Density scale.
-
-In all cases, images were created as described
-in \cref{sec:simul,sec:monte-carlo-simul}.
+$\{5\}$ Density scale.}
+
+\rl{In all cases, images were created as described
+in Secs.~\ref{sec:simul} and~\ref{sec:monte-carlo-simul}.
 These images served as input to the reconstruction algorithm.
-The optimization used an L-BFGS-B solver~\cite{BFGS} on a computer cluster.
+The optimization used an L-BFGS-B solver}~\cite{BFGS} \rl{on a computer cluster.
 Each computer core was dedicated to rendering a modeled image.
@@
 %$\epsilon=0.65$.
-These results are listed in Table~\ref{tbl:mass}. \\
-
-\noindent{\bf Forward models and distributions}:
-\Cref{fig:results} shows estimation results, corresponding to the
-original distributions of \cref{fig:distributions}.
+These results are listed in Table~\ref{tbl:mass}.} \\
+
+\rl{\noindent{\bf Forward models and distributions}:
+Figure~\ref{fig:results} shows estimation results, corresponding to the
+original distributions of Fig.~\ref{fig:distributions}.}
 \begin{figure}[t]
@@
   \yoavcomment{\includegraphics{images/results}}
-  \caption{\small Recoveries of scenes shown in
-    \cref{fig:distributions}. Color represents aerosol density, in
-    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
-    images simulated by single-scattering are used as input for the
+  \caption{\small \fix{Reconstructions of the}{Recoveries of} scenes shown in
+    \cref{fig:distributions}. Color represents aerosol density\fix{. The density units are}{, in
+    units of} $10^{6}~{\rm particles}/{\rm m}^3.$ In \fix{[a,b],
+    single-scattering simulated images}{(a) and (b)
+    images simulated by single-scattering} are used as input \fix{to}{for} the
     recovery.  In (c) and (d), MC simulated images are used as input for the
@@
 \end{figure}
-Here, the atmosphere domain was defined over a
+\rl{Here, the atmosphere domain was defined over a
 $20\times20 \times 40$ grid. Cameras were placed
@@
 been induced in the raw images. Errors are larger when MC is used to
-render the images, since high-order scattering is not accounted for in
+render the images, since high-order scattering is not accounted for in}
 \newcolumntype{g}{>{\columncolor{Gray}}r}
@@
   \end{tabular}
-  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
+  \caption{\rl{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}}
   \label{tbl:mass}
 \end{table}
-the algorithm of \cref{sec:inverse-problem}. \\
-
-\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
+\rl{the algorithm of} \cref{sec:inverse-problem}. \\
+
+\rl{\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
 repeated the reconstruction many times, each using a different subset of the above mentioned
@@
 of $N_{\rm views}< 36$. All rendered images used MC.
-\Cref{fig:error_vs_cameras} plots the performance.
+Figure~\ref{fig:error_vs_cameras} plots the performance.}
 \begin{figure}[t]
@@
   \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
-  \caption{\small The relative error $\epsilon$ measure decreases with the number of
-    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
+  \caption{\small \rl{The relative error $\epsilon$ measure decreases with the number of
+    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}}
   \label{fig:error_vs_cameras}
 \end{figure}
-Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km
+\rl{Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km
 separation between neighboring viewpoints. These tests point to fundamental questions about
@@
 aerosols. The novel tomography domain introduced here thus raises new theoretical questions
-that will   require extensive further research.\\
-
-\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
-aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
+that will   require extensive further research.}\\
+
+\rl{\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
+aerosol characteristics. Compared to the aerosol described in Sec.~\ref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
 $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
@@
 [0.69,0.74,0.78]$.  All rendered images used MC
-(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
+(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).}
 \begin{figure}[b]
@@
   \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
-  \caption{\small Images simulated by MC, from the same viewpoint, but different
+  \caption{\small \rl{Images simulated by MC, from the same viewpoint, but different
   aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
-  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
+  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}}
   \label{fig:simulation_particles}
 \end{figure}
-Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
-and \ref{fig:reconstructions}(b)
+\rl{Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
+and \ref{fig:reconstructions}(b)}
 \begin{figure}[b]
@@
   \yoavcomment{\includegraphics{images/reconstructions.pdf}}
-  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
-    has isotropic phase function (b) or has high density (c).}
+  \caption{\small  \rl{Recovered distributions when the aerosol is either party absorbing (a),
+    has isotropic phase function (b) or has high density (c).}}
   \label{fig:reconstructions}
 \end{figure}
-and in \cref{tbl:mass}. The results indicate that if the aerosol's phase function
+\rl{and in Table~\ref{tbl:mass}. The results indicate that if the aerosol's phase function
 has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesize that
@@
 radiance from a voxel, undermining tomography. A very broad research is needed to verify
-and quantify such dependencies.\\
-
-\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
+and quantify such dependencies.}\\
+
+\rl{\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
 and characteristics as described in Sec.~\ref{sec:simul}, but increased the
 aerosol density tenfold everywhere. This significantly increases the effects
-of high order scattering, as shown in \cref{fig:cross_sections}(b) and
-\cref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases (\cref{tbl:mass}),
-when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
+of high order scattering, as shown in Fig.~\ref{fig:cross_sections}(b) and
+Fig.~\ref{fig:simulation_particles}(d). Consequently, $\epsilon$ increases (Table~\ref{tbl:mass}),
+when using $N_{\rm views}=36$. Still, Fig.~\ref{fig:reconstructions}(c) shows
 that the spatial distribution outlines are recovered similarly to the other
-tests.
+tests.}
 
@@
 We describe a way to sense the 3D atmosphere. It can help remote
-sensing depart from common one-dimensional aerosol distribution models, in favor
+sensing depart from common \fix{1D}{one-dimensional} aerosol distribution models, in favor
 of detailed 3D RT analysis.  The paper describes both a novel data
@@
 uses a single scattering model. This approximation is valid when the
-optical depth is small. However, as MC simulations show, it is
-important to generalize the recovery algorithm so that high-order scattering
+optical depth is small. However, as \del{the} MC simulations show, it is
+important to generalize \st{is algorithm so that it explicitly
+incorporates high-order scattering in the scene, including the
+ground. This will certainly be needed for dense distributions as
+clouds.}
+
+\st{To deploy such a system on a very large scale will require a long-term
+engineering effort. Camera specifications}~\cite{Pust2011}\st{should be
+set to optimally recover a wide range of aerosol distributions. This
+requires a major theoretic and numerical research.}
+\rl{the recovery algorithm so that high-order scattering
 is included in it. Such generalization would be computationally complex:
@@
 orders of scattering and the discrete ordinates method). We may tap into some of these approaches.
-Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
-should be set to optimally recover a wide range of aerosol distributions.
+Deploying an experimental system will be needed: camera specifications}~\cite{Pust2011}
+\rl{should be set to optimally recover a wide range of aerosol distributions.}
 %\hl{The relation between the quantity and spatial distribution of
@@
 
-We are grateful to David~J. Diner for fruitful discussions and his support at all
+\fix{We thank David~J. Diner for useful discussions. Yoav Schechner is a
+Landau Fellow - supported by the Taub Foundation. This work was
+conducted in the Ollendorff Minerva Center. Minerva is funded through
+the BMBF. Part of this work was performed at the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with
+NASA.}{We are grateful to David~J. Diner for fruitful discussions and his support at all
 levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
@@
 Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
-by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.
+by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.}
 

### 2013-10-08 article.tex
Fix typo

--- 2013-10-08 article.tex
@@
   \yoavcomment{\includegraphics{images/scatter_order.pdf}}
-  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
+  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
    by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}

### 2013-10-08 article.tex
Removed the deleted parts

--- 2013-10-08 article.tex
@@
 are not very dense (inside fog and clouds this model does not
-apply). \fix{In this model}{Here}, RT has three steps (\cref{fig:groundgrid}):
+apply). \rl{Here}, RT has three steps (\cref{fig:groundgrid}):
 ({\tt i})~Attenuation of a SR propagating from the top of the
@@
 voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
-depth along the light path to and from voxel $k$ \del{as} (analyzed in
+depth along the light path to and from voxel $k$ (analyzed in
 \cref{sec:optical-depth}).  Step~{\tt ii} involves the scattering
-coefficient at voxel $k$ \del{described in} (\cref{sec:scattering}).
+coefficient at voxel $k$ (\cref{sec:scattering}).
 
@@
 and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
-(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the \fix{the radiant power contributed by is}{voxel contributes} radiant power
+(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the \rl{voxel contributes} radiant power
 \begin{equation}
@@
     \cref{fig:simulation-results1}(a), rendered using MC.
-    \del{[c] Cross section along the $X$-Axis of the MC simulation,
-    single-scattering simulation and a single-scattering image created
-    from the reconstructed distribution
-    (Sec.~\ref{sec:optimization-results})}.}
+    }
   \label{fig:mcgrid}
@@
 \end{align}
-Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields \del{the} 3D position ${\bf
+Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields 3D position ${\bf
   X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
@@
 that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
-randomly \fix{according to their relative densities at the voxel containing
-${\bf X}_{i}$.}{The relative probabilities of this random step are set by the respective extinction coefficients
+randomly \rl{The relative probabilities of this random step are set by the respective extinction coefficients
 ($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.}
 
-\noindent ({\tt iv}) If \fix{it}{the particle} is an aerosol, the photon-packet intensity
+\noindent ({\tt iv}) If \rl{the particle} is an aerosol, the photon-packet intensity
 is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
@@
   R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
-estimation~\cite{marshak20053d} \fix{is used for calculating}{derives} the amount of
+estimation~\cite{marshak20053d} \rl{derives} the amount of
 light back-traced to the sun at each scattering. The next iteration of
@@
 scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}(a). \fix{A
-comparison of a sample horizontal cross section is shown in
-Fig.~\ref{fig:mcgrid}c.}
-{Figure~\ref{fig:cross_sections} plots the intensity profile
+from the same viewpoint as \cref{fig:simulation-results1}(a). 
+\rl{Figure~\ref{fig:cross_sections} plots the intensity profile
 along a horizontal cross section of the viewed field,
@@
 \end{equation}
-Here $\MaskSun$ masks the area around the sun: \del{as} in real-world images
+Here $\MaskSun$ masks the area around the sun: in real-world images
 it is indeed blocked. \rl{We mask the horizon, by using a camera whose
@@
   n}\|^2_2$. Regularization is not required when data is sufficient
-and reliable. \del{As seen in Fig.~\ref{fig:groundgrid},}Voxels at high
+and reliable. Voxels at high
 altitude have good coverage by many cameras at multiple directions (\cref{fig:groundgrid}),
@@
   \yoavcomment{\includegraphics{images/results}}
-  \caption{\small \fix{Reconstructions of the}{Recoveries of} scenes shown in
-    \cref{fig:distributions}. Color represents aerosol density\fix{. The density units are}{, in
-    units of} $10^{6}~{\rm particles}/{\rm m}^3.$ In \fix{[a,b],
-    single-scattering simulated images}{(a) and (b)
-    images simulated by single-scattering} are used as input \fix{to}{for} the
+  \caption{\small \rl{Recoveries of} scenes shown in
+    \cref{fig:distributions}. Color represents aerosol density\rl{, in
+    units of} $10^{6}~{\rm particles}/{\rm m}^3.$ In \rl{(a) and (b)
+    images simulated by single-scattering} are used as input \rl{for} the
     recovery.  In (c) and (d), MC simulated images are used as input for the
@@
 We describe a way to sense the 3D atmosphere. It can help remote
-sensing depart from common \fix{1D}{one-dimensional} aerosol distribution models, in favor
+sensing depart from common \rl{one-dimensional} aerosol distribution models, in favor
 of detailed 3D RT analysis.  The paper describes both a novel data
@@
 uses a single scattering model. This approximation is valid when the
-optical depth is small. However, as \del{the} MC simulations show, it is
-important to generalize \st{is algorithm so that it explicitly
-incorporates high-order scattering in the scene, including the
-ground. This will certainly be needed for dense distributions as
-clouds.}
-
-\st{To deploy such a system on a very large scale will require a long-term
-engineering effort. Camera specifications}~\cite{Pust2011}\st{should be
-set to optimally recover a wide range of aerosol distributions. This
-requires a major theoretic and numerical research.}
+optical depth is small. However, as MC simulations show, it is
+important to generalize 
 \rl{the recovery algorithm so that high-order scattering
@@
 
-\fix{We thank David~J. Diner for useful discussions. Yoav Schechner is a
-Landau Fellow - supported by the Taub Foundation. This work was
-conducted in the Ollendorff Minerva Center. Minerva is funded through
-the BMBF. Part of this work was performed at the Jet Propulsion
-Laboratory, California Institute of Technology, under contract with
-NASA.}{We are grateful to David~J. Diner for fruitful discussions and his support at all
+\rl{We are grateful to David~J. Diner for fruitful discussions and his support at all
 levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau

### 2013-10-13 article.tex
Integrated the formatting comments, yoav and anthony modifications.

--- 2013-10-08 article.tex
@@
 
-\usepackage{hyperref}
-\hypersetup{pdfborder={0 0 0}}
+%\usepackage[bookmarks=false]{hyperref}
+%\hypersetup{pdfborder={0 0 0}}
 
@@
   retrieval assumes a plane-parallel atmosphere and solely vertical
-  radiative transfer (RT). We propose a principle to estimate the
+  radiative transfer. We propose a principle to estimate the
   aerosol distribution as it really is: a three dimensional (3D)
-  volume, using visible light.  The principle is a type of
+  volume.  The principle is a type of
   tomography. The process involves wide angle integral imaging of the
-  sky on a very large scale.  We formulate an image formation model
-  based on 3D RT. Model inversion is done using optimization methods,
+  sky on a very large scale. The sensing can use an array of cameras in visible light.
+  We formulate an image formation model
+  based on 3D radiative transfer. Model inversion is done using optimization methods,
   exploiting a closed-form gradient which we derive for the model-fit
@@
 
-\bibitem{Cornette1995}
+\bibitem{cornette1992physically}
 W.~M. Cornette and J.~G. Shanks, \enquote{{Physically reasonable analytic
-  expression for the single-scattering phase function: errata},} \ao
-  \textbf{34}, 641 (1995).
+  expression for the single-scattering phase function},} \ao
+  \textbf{31}, 3152--3160 (1992).
 
@@
   retrieval}. In this discipline, the atmosphere is often assumed to
-be plane-parallel, using one-dimensional vertical RT. Consequently
+be plane-parallel, using one-dimensional vertical radiative transfer (RT). Consequently
 state-of-the-art aerosol retrieval is done in distinct large lateral
@@
 The phase function is often approximated by a parametric
-expression. Specifically, the Henyey-Greenstein~\cite{Cornette1995}
+expression. Specifically, the Henyey-Greenstein~\cite{cornette1992physically}
 function is governed by an {\em anisotropy parameter} $g$:
@@
 photographs of the {\em Haze Blobs} scene, as simulated by
-\cref{eq:bigIA}. \endnote{For clarity of display, the brightness of the
+\cref{eq:bigIA}. For clarity of display, the brightness of the
 displayed pictures in this paper underwent the same standard
@@
 The recovery algorithms, of course, have used the raw (not brightness
-enhanced) images.}
+enhanced) images.
 
@@
 comparing photographs simulated using the single-scattering and the  MC forward models.
-\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
-and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
+\Cref{fig:cross_sections}(a) compares photographs of the {\em Haze Blobs} scene described in \cref{sec:simul}.
 This plot demonstrates consistency in this scene, for most pixels.
 \Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
-where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
-and the corresponding MC photograph \cref{fig:simulation_particles}(d)).
+where the aerosol density was increased ten folds (see \cref{sec:optimization-results}).
 In this plot the single-scattering and MC cross sections diverge
@@
     by the single-scattering (dotted) and MC (solid line) forward models.
-    (a) cross sections of the {\em Haze Blobs} scene (\cref{fig:simulation-results1}(d)
-    and \cref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
-    when the scatterers are ten times denser, corresponding to \cref{fig:simulation_particles}(d).
+    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
+    The difference between the models is much more pronounced (b) 
+    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
   }
@@
 
-\section{Inverse Problem}
+\section{Inverse problem}
 \label{sec:inverse-problem}
@@
 
-\theendnotes
-
 \end{document}

### 2013-10-13 article.tex
Fixes according to Yoav

@@
   tomography. The process involves wide angle integral imaging of the
-  sky on a very large scale. The sensing can use an array of cameras in visible light.
+  sky on a very large scale. The imaging can use an array of cameras in visible light.
   We formulate an image formation model
@@
 \end{figure}
-To demonstrate the model, we simulated some scenarios, whose details are as follows.
+\Cref{fig:simulation-results1} shows examples of photographs rendered
+using the single-scattering model. To create these photographs we
+simulated several scenarios, whose details are as follows.
 \\
@@
 contrast enhancement (stretching), including gamma-correction.
-The recovery algorithms, of course, have used the raw (not brightness
+The recovery algorithms, of course, uses the raw (not brightness
 enhanced) images.
@@
 propagation (denoted {\tt ii} above) proceeds.
-
-The quality of MC increases with the number of photons launched.
-\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
-scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}(a).
-\Cref{fig:cross_sections} plots the intensity profile
-along a horizontal cross section of the viewed field,
-comparing photographs simulated using the single-scattering and the  MC forward models.
-\Cref{fig:cross_sections}(a) compares photographs of the {\em Haze Blobs} scene described in \cref{sec:simul}.
-This plot demonstrates consistency in this scene, for most pixels.
-\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
-where the aerosol density was increased ten folds (see \cref{sec:optimization-results}).
-In this plot the single-scattering and MC cross sections diverge
-due to the effect of the high order scattering.
 \begin{figure}[t]
@@
 \end{figure}
-
+\begin{figure}[b]
+  \centering
+  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
+  \caption{\small Images simulated by MC, from the same viewpoint, but different
+  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
+  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function.
+  (d) High aerosol density. Details of the scenarios used in creating (b) and
+  (c) are given in \cref{sec:optimization-results}.}
+  \label{fig:simulation_particles}
+\end{figure}
+
+The quality of MC increases with the number of photons launched.
+\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
+scene, derived by the MC process, using \num{10000} photons per pixel,
+from the same viewpoint as \cref{fig:simulation-results1}(a).
+\Cref{fig:cross_sections} plots the intensity profile
+along a horizontal cross section of the viewed field,
+comparing photographs simulated using the single-scattering and the  MC forward models.
+\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
+and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
+This plot demonstrates consistency in this scene, for most pixels.
+\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
+where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
+and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
+In this plot the single-scattering and MC cross sections diverge
+due to the effect of the high order scattering.
 \Cref{fig:scatter_order} shows the contribution by successive
@@
 (See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
-\begin{figure}[b]
-  \centering
-  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
-  \caption{\small Images simulated by MC, from the same viewpoint, but different
-  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
-  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
-  \label{fig:simulation_particles}
-\end{figure}
 Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
@@
 US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
-Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
-by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.
+Ollendorff Minerva Center. Minerva is funded through the BMBF. Part of this work
+was performed at the Jet Propulsion Laboratory, California Institute of Technology,
+under contract with NASA and with support by NASA's Earth Science Technology Office
+Advanced Information Systems Technology Program.
 

### 2013-10-13 article.tex
Added missing redline packages and commands
Modifications by Yoav

@@
 \renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
-\newcommand{\fix}[2]{\st{#1}\hl{#2}}
+
+%
+% Red-lined version settings
+%
+\newcommand{\del}[1]{\sout{#1}}
+\newcommand{\rl}[1]{\uwave{#1}}
+\newcommand{\fix}[2]{\del{#1}\rl{#2}}
+\newcommand{\rleq}[1]{%
+  \colorbox{red!50}{$\displaystyle#1$}}
 
@@
 \Cref{fig:simulation-results1} shows examples of photographs rendered
-using the single-scattering model. To create these photographs we
+using the single-scattering model. To create such photographs we
 simulated several scenarios, whose details are as follows.
@@
 contrast enhancement (stretching), including gamma-correction.
-The recovery algorithms, of course, uses the raw (not brightness
+The recovery algorithm, of course, uses the raw (not brightness
 enhanced) images.
@@
 propagation (denoted {\tt ii} above) proceeds.
+
+The quality of MC increases with the number of photons launched.
+\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
+scene, derived by the MC process, using \num{10000} photons per pixel,
+from the same viewpoint as \cref{fig:simulation-results1}(a).
+Similarly, \cref{fig:simulation_particles}(a) corresponds to the same
+viewpoint as \cref{fig:simulation-results1}(d).
 \begin{figure}[t]
-  \centering
-  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
-  \caption{\small Cross-sections along the $X$-axis of photographs rendered
-    by the single-scattering (dotted) and MC (solid line) forward models.
-    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
-    The difference between the models is much more pronounced (b) 
-    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
-  }
-  \label{fig:cross_sections}
-\end{figure}
-\begin{figure}[b]
   \centering
@@
 \end{figure}
-
-The quality of MC increases with the number of photons launched.
-\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
-scene, derived by the MC process, using \num{10000} photons per pixel,
-from the same viewpoint as \cref{fig:simulation-results1}(a).
-\Cref{fig:cross_sections} plots the intensity profile
-along a horizontal cross section of the viewed field,
-comparing photographs simulated using the single-scattering and the  MC forward models.
-\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
-and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
-This plot demonstrates consistency in this scene, for most pixels.
-\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
-where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
-and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
-In this plot the single-scattering and MC cross sections diverge
-due to the effect of the high order scattering.
 \Cref{fig:scatter_order} shows the contribution by successive
@@
   \label{fig:scatter_order}
+\end{figure}
+
+\Cref{fig:cross_sections} plots the intensity profile
+along a horizontal cross section of the viewed field,
+comparing photographs simulated using the single-scattering and the  MC forward models.
+\Cref{fig:cross_sections}(a) is extracted from \cref{fig:simulation-results1}(d)
+and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
+This plot demonstrates consistency in this scene, for most pixels.
+\Cref{fig:cross_sections}(b) plots the same profiles,
+where the aerosol density was increased tenfold (see \cref{sec:optimization-results}
+and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
+In \cref{fig:cross_sections}(b) the plots differ more than in \cref{fig:cross_sections}(a),
+due to high order scattering.
+\begin{figure}[t]
+  \centering
+  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
+  \caption{\small Cross-sections along the $X$-axis of photographs rendered
+    by the single-scattering (dotted) and MC (solid line) forward models.
+    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
+    The difference between the models is much more pronounced (b) 
+    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
+  }
+  \label{fig:cross_sections}
 \end{figure}

### 2013-10-14 article.tex
Yoav last changes

@@
 
-\Cref{fig:cross_sections} plots the intensity profile
-along a horizontal cross section of the viewed field,
-comparing photographs simulated using the single-scattering and the  MC forward models.
+\Cref{fig:cross_sections} plots the image intensity profile along a straight
+line from left to right, via the image center (zenith). The plot compares
+photographs simulated using the single-scattering and the  MC forward models.
 \Cref{fig:cross_sections}(a) is extracted from \cref{fig:simulation-results1}(d)

### 2013-10-14 article.tex
Final version

@@
 These results are listed in Table~\ref{tbl:mass}. \\
+\newcolumntype{g}{>{\columncolor{Gray}}r}
+\begin{table}[bt]
+  \centering
+  \begin{tabular}{cccccgg}
+    \toprule
+    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
+    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
+     \midrule                                                                                             
+    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
+    \cmidrule(r){1-5}                                                                                     
+     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
+           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
+    \bottomrule
+  \end{tabular}
+  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
+  \label{tbl:mass}
+\end{table}
 
@@
 original distributions of \cref{fig:distributions}.
-\begin{figure}[t]
+\begin{figure}[b]
   \centering
@@
 render the images, since high-order scattering is not accounted for in
-\newcolumntype{g}{>{\columncolor{Gray}}r}
-\begin{table}[t]
-  \centering
-  \begin{tabular}{cccccgg}
-    \toprule
-    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
-    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
-     \midrule                                                                                             
-    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
-    \cmidrule(r){1-5}                                                                                     
-     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
-           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
-    \bottomrule
-  \end{tabular}
-  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
-  \label{tbl:mass}
-\end{table}
 the algorithm of \cref{sec:inverse-problem}. \\

### 2013-10-14 opex2013_cover.tex
Final version

--- 2013-10-03 opex2013_reply.tex
@@
 To:\\
-Dr. James Churnside,\\
-Editor,\\
-Associate Editor, Optics Express\\[0.6cm]
+Production Editor, Optics Express\\[0.6cm]
 
@@
 
-Dear Dr. Churnside,
+Dear production editor,
 
-We are pleased to submit our revised manuscript {\em Multi sky-view 3D
-  aerosol distribution recovery}, (195261).  We have addressed all the
-requests made by the reviewers. The changes made to the manuscript are
-detailed in the following pages. We thank the reviewers for their
-helpful comments and hope that the paper in its current form satisfies
-your requirements.
+Thank you for accepting our manuscript for publication.
+We have applied the required formatting changes. In order to correct
+the citation order of Fig. 9, we moved the figure into section 6 of
+the article. This change required us to re-arange the order of figures
+in this section (section 6) and make minor changes to the body of 
+the text.
+We made minor textual corrections in several other locations, to smooth
+the flow. Specifically, in the abstract we moved the reference of
+"visibile light" from sentence 3 to sentence 6; we refer to Fig.3
+in the begining of Sec.5; we inserted our prior footnote into the main text
+of Sec.5; and we wrote a corrected ackowlegements.
 
-We look forward to hearing from you,\\
+Is it possible to receive the proof, before you publish, so we
+verify and approve that all is in order?\\
 
@@
 \vspace{0.6cm}
-Amit Aides and Yoav Schechner\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% if the letter runs to a second page, or longer, the following lines
-% must be inserted on the second page to prevent the heading and
-% footer from appearing
-\newpage
-
-{\Large Changes Following the Comments by the Reviewers}\\
-
-We would like to thank the reviewers for their general approval. In
-the following we describe the changes made to the manuscript following
-their remarks. Each reviewer's comment is summarized (colored in
-blue), followed by our reply.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REVIEWER I
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\noindent \underline {\bf Reviewer 1}
-
-We appreciate the reviewer's comment. We address it below.
-
-\begin{enumerate}
-
-\item \textcolor{blue}{ ``The paper can be devided in two parts, one
-    for computing single scattering, the other for multiple
-    scattering. While the first part can be treated by a simple
-    inverse transformation sampling as presented by the authors, the
-    second part should have a different more complex inversion. For
-    this reason I think that larger errors arise in multiple
-    scattering. I feel the authors should dedicate some time to review
-    this second part, that is more realistic."}
-
-  {}
-
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REVIEWER II
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\noindent \underline {\bf Reviewer 2}
-
-Reviewer 2 sees the paper as novel, highly relevant and well written.
-The reviewer suggests that the paper is well worth publishing and
-recommends accepting the paper after a minor revision.  We thank the
-reviewer for his general approval. Below we address his/her comments:
-
-\begin{enumerate}
-
-%%%%%%%%%%%%%%%%
-\item \textcolor{blue}{``I don’t understand Eq 9. If $F(u) =
-    1-\exp(-u)$ how is $\nicefrac{1}{F} = -\ln(1-u)$?''}
-
-  {There is no contradiction. The notation $F^{-1}$ refers to the
-    inverse function of function $F$ and not to $\nicefrac{1}{F}$}
-
-%%%%%%%%%%%%%%%%
-\item \textcolor{blue}{ ``Maybe define $\mu$ and voxel''}
-
-  {Following the reviewer's comment, we have defined $\mu$ after
-    Eq.~5, and revised the definition of the term ``voxel''. }
-
-%%%%%%%%%%%%%%%%
-
-\item \textcolor{blue}{ ``How do you predefine the voxels
-    vertically?''}
-
-  {}
-
-%%%%%%%%%%%%%%%%
-
-\item \textcolor{blue}{ ``The result of the example (sec. 8) could be
-    a little more precise in the sense that non-specialists get a
-    clear idea of how your method works and which aerosol properties
-    hinder or favor retrieval.''}
-
-  {}
-
-%%%%%%%%%%%%%%%%
-
-\item \textcolor{blue}{ ``How many cameras in which distance do you
-    need to obtain feasible results for the case of Sec. 5?''}
-
-  {}
-
-\end{enumerate}
+Amit Aides, corresponding author.\\
 
